### 2017-12-28 Desktop/461/Extended Abstract/ext_abs.tex
Added first draft

\documentclass[12pt]{article}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage{amsmath}
\graphicspath{ {} }
\setcounter{secnumdepth}{0}
\usepackage{cite}

\begin{document}

\title{Level 1 probabilistic risk analysis of a molten salt reactor}

\author{Anshuman Chaube}%
%   \thanks{Email:\texttt{anshumanchaube95@gmail.com}; }}
\affil{NPRE 461 Project: Extended Abstract}

\date{}

\maketitle

\begin{abstract}
While most molten salt reactor designs are inherently proof against many design based accidents that most light water and presurrized water reactors are susceptible to, systematic studies are required to characterize the safety and reliability of these designs. The focus of this project has the estimation of probability of overheating of the MSR core, resulting in the melting of core components and release of molten salt and gaseous fission products. The major MSR components contributing to such an eventuality are described, and the method of estimation of probability is outlined.
\end{abstract}

\section{Introduction}

Molten Salt Reactors are being studied by the Generation IV forum as one of the safest and most proliferation resistant designs of all the other candidate reactors. The molten salt fuel and moderator creates many passibe safety features and makes the reactor designs immune to many design based accidents that are likely in conventional pressurized water and light water reactors \cite{elsheikh_safety_2013}. Such accidents include:
\begin{itemize}

\item \textbf{Core Meltdown} : Since the reactor core comprises of molten salt, there is no risk of meltdown. As the salt heats up, reaction rate decreases due to the large negative reactivity coefficient of fuel-salt. If it overheats, the salt can be drained into secure tanks beneath the reactor where it may cool off as the reactions in it die down.

\item \textbf{Control Rod Ejection and Reactivity Initiated Accident}: The occurence of this accident due to mechanical or operator error creates excess reactivity in conventional reactors. However, as mentioned previously, the negative coefficient of reactivity precludes any major mishaps in MSRs due to such an accident.

\item \textbf{Criticality Accident} : Excess reactivity can be easily controlled due to the negative temperature coefficient of the salt. The reactivity can be controlled without control rods. Online fuel processing keeps a tight check on the amount of fuel in circulation. The core design and geometry is also optmized such that there is no external structure that can be compromized.

\end{itemize}

\section{Level 1 PRA: Core overheating scenario}

\subsection{Possible contributors}

However, due to the unique design and operating requirements of the MSR, certain components are vulnerable to failure and can result in overheating of the core. It is possible for the core components to melt in such circumstances, allowing molten salts and gaseous fission products to escape the reactor. This can cause radiation poisoning and boron poisoning in the immediate vicinity of the reactor and release of radioactive material to the public at large.

The major contributors to such a scenario are:

\begin{itemize}

\item \textbf{Pump failure} : The failure of pumps in either the primary or the secondary loop can result in loss of circulation of salts. This effectively stops heat transfer from the core and can very quickly result in core damage \cite{elsheikh_safety_2013} \cite{yoshioka_guidelines_2012} .

\item \textbf{Sparging system failure} : While most fission products remain dissolved in the fuel salts, the MSR design requires the injection of He into the salts to remove gaseuos fission products such as Xe and Kr to prevent neutron poisoning. The shutdown of the sparging system can cause the core to evolve an excess of neutron poisons. However, excessive insertion of He can cause positive reactivity to be inserted which further heats the core \cite{yoshioka_guidelines_2012} \cite{moir_recommendations_2008}.

\item \textbf{Salt freeze in secondary loop}: The molten salt is kept above its freezing point by electrically heating the pipes in the secondary loop, as it was done in the molten salt reactor experiment at Oak Ridge National Laboratory. The backup system that must maintain this temperature during transients can fail, causing the salt temperature to fall below its melting point in certain sections of the secondary loop. The solidified salt can accrue and eventually create a blockage, causing loss of heat transfer similar to pump failure \cite{haubenreich_experience_1970}.

\item \textbf{Excess fuel in core} : The fuel reprocessing system is responsible for maintaining the concentration of fuel dissolved in the molten salt and for removing dissolved fission products. Insertion of excess fuel in the salt can cause excess reactivity to be inserted, overheating the core \cite{haubenreich_experience_1970}.

\item \textbf{Drainage system failure}: For a given core that has overheated, the final fail safe is the freeze plug and drainage tank system. During normal operation, a section of the pipes above the drainage tanks is kept blocked by cooling it and solidifying a portion of the molten salt. As the core overheats, this freeze plug should melt and open the drainage pipes, allowing the overheated molten salt to safely pass into the drainage tanks where it can cool. This final line of defence can fail if (i) the pipes have manufacturing defects such as non-uniform cross section that is smaller than specified, preventing drainaige of the core in a reasonable amount of time (ii) the cooling system for the drainage tanks fails, allowing nuclear reactions to go on in the salt and failing to cool it before it leaks\cite{elsheikh_safety_2013}.

\end{itemize}

With these vulnerabilities in mind, it is possible for the reactor to reach a state of catastrophic failure in many ways. One possible consequence, overheating of the core followed by molten salt leak, is analyzed herein.

\subsection{Analysis method}

The major modes of overheating the core are excess reactivity insertion and loss of cooling, and the simultaneous failure of the drainage system failsafe. Their relationship can be modelled using a fault tree.

Excess reactivity can be inserted by either insertion of excess He from the sparging system or by addition of excess fuel in the molten salt through the reprocessing system. Both are possible due to pumps malfunctioning, the data of which can be obtained from IAEA PRA databases \cite{iaea_component_1988}, or due to human error, which can be estimated using THERP. Failure of primary loop's circulation pumps can similarly create excess reactivity, which can again be modelled using the PRA databases.

The loss of cooling can occur due to freezing of salts after failure of the heating generators, due to pipe breakage or due to secondary pump failure, each of which can be quantified using the aformentioned databases.

Finally, drainage system failure can be quantified as the probability of manufacturing defects in the pipe that cause clogging, or failure of the cooling system in the drainage tanks.

\bibliography{ext_ab_ref}
\bibliographystyle{abbrv}

\end{document}

### 2017-12-28 Desktop/247/CP3/CP3_247/results/achaube2/CP3_247/results/achaube2/CP3_247/output/cp3_pin_input_3_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 30])  = '/home/achaube2/cp3_pin_input_3' ;
+WORKING_DIRECTORY         (idx, [1: 14])  = '/home/achaube2' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 11:29:38 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 11:33:29 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512754178 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
+IMPLICIT_REACTION_RATES   (idx, 1)        = 1 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results/achaube2/CP3_247/results/achaube2/CP3_247/output/cp3_pin_input_9_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 38])  = '/home/achaube2/CP3_247/cp3_pin_input_9' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 14:45:24 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 14:49:13 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512765924 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results/achaube2/CP3_247/results/output/cp3_pin_input_12_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_12' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 14:58:52 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 15:02:44 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512766732 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results/output/cp3_pin_input_19_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_19' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 15:31:39 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 15:35:44 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512768699 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results2/achaube2/CP3_247/cp3_pin_input_23_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_23' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 17:29:30 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 17:33:31 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512775770 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results2/achaube2/CP3_247/results/output/cp3_pin_input_15_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_15' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 15:15:00 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 15:18:54 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512767700 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results2/achaube2/CP3_247/results/output/cp3_pin_input_2_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 30])  = '/home/achaube2/cp3_pin_input_2' ;
+WORKING_DIRECTORY         (idx, [1: 14])  = '/home/achaube2' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 11:22:03 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 11:25:53 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512753723 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
+IMPLICIT_REACTION_RATES   (idx, 1)        = 1 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results2/achaube2/CP3_247/results/output/cp3_pin_input_4_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 30])  = '/home/achaube2/cp3_pin_input_4' ;
+WORKING_DIRECTORY         (idx, [1: 14])  = '/home/achaube2' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 14:20:02 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 14:24:00 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512764402 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
+IMPLICIT_REACTION_RATES   (idx, 1)        = 1 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results2/achaube2/CP3_247/results/output/cp3_pin_input_6_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 38])  = '/home/achaube2/CP3_247/cp3_pin_input_6' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 14:33:22 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 14:37:11 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512765202 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results/achaube2/CP3_247/cp3_pin_input_31_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_31' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 17:16:11 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 17:20:19 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512774971 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results/achaube2/CP3_247/results/cp3_pin_input_28_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_28' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 17:02:08 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 17:06:16 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512774128 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results/output/cp3_pin_input_16_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_16' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 15:19:09 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 15:23:12 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512767949 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results2/achaube2/CP3_247/op2/cp3_pin_input_17_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_17' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 15:23:21 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 15:27:18 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512768201 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results2/achaube2/CP3_247/op2/cp3_pin_input_25_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_25' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 16:32:39 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 16:36:44 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512772359 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/CP3_247/results2/achaube2/CP3_247/results/achaube2/CP3_247/output/cp3_pin_input_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 28])  = '/home/achaube2/cp3_pin_input' ;
+WORKING_DIRECTORY         (idx, [1: 14])  = '/home/achaube2' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Dec  4 14:10:40 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Dec  4 14:14:37 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512418240 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
+IMPLICIT_REACTION_RATES   (idx, 1)        = 1 ;
+
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/cp3_pin_input_32_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_32' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 18:26:49 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 18:30:59 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512779209 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/cp3_pin_input_33_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_33' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 18:31:23 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 18:35:38 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512779483 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/CP3_247/results3/cp3_pin_input_34_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 39])  = '/home/achaube2/CP3_247/cp3_pin_input_34' ;
+WORKING_DIRECTORY         (idx, [1: 22])  = '/home/achaube2/CP3_247' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Dec  8 18:36:57 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Dec  8 18:41:19 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512779817 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results4/cp3_pin_input_12_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 44])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_12' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 15:39:37 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 15:43:59 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512941977 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results4/cp3_pin_input_4_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 43])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_4' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 15:11:59 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 15:15:28 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512940319 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results5/inputs/cp3_pin_input_2_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 43])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_2' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 15:54:48 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 15:58:14 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512942888 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results5/inputs/cp3_pin_input_4_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 43])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_4' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 16:01:24 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 16:04:51 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512943284 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results5/inputs/cp3_pin_input_7_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 43])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_7' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 15:26:51 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 15:30:23 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512941211 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/247/CP3/results5/inputs/cp3_pin_input_9_res.m

@@ -1,0 +1,492 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.26' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Apr 23 2016 19:45:46' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1: 27])  = 'Pin-cell burnup calculation' ;
+INPUT_FILE_NAME           (idx, [1: 43])  = '/home/achaube2/cp3_2/inputs/cp3_pin_input_9' ;
+WORKING_DIRECTORY         (idx, [1: 27])  = '/home/achaube2/cp3_2/inputs' ;
+HOSTNAME                  (idx, [1:  7])  = 'arts-01' ;
+CPU_TYPE                  (idx, [1: 39])  = 'Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz' ;
+CPU_MHZ                   (idx, 1)        = 23.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Dec 10 15:35:36 2017' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Dec 10 15:39:23 2017' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 10000 ;
+CYCLES                    (idx, 1)        = 200 ;
+SKIP                      (idx, 1)        = 20 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1512941736 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 1 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
+B1_BURNUP_CORRECTION      (idx, 1)        = 0 ;
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/qt4/tests/check_links.cpp

@@ -1,0 +1,98 @@
+#include <QtTest/QtTest>
+
+#include <poppler-qt4.h>
+
+#include <memory>
+
+class TestLinks : public QObject
+{
+    Q_OBJECT
+private slots:
+    void checkDocumentWithNoDests();
+    void checkDests_xr01();
+    void checkDests_xr02();
+};
+
+static bool isDestinationValid_pageNumber( const Poppler::LinkDestination *dest, const Poppler::Document *doc )
+{
+    return dest->pageNumber() > 0 && dest->pageNumber() <= doc->numPages();
+}
+
+static bool isDestinationValid_name( const Poppler::LinkDestination *dest )
+{
+    return !dest->destinationName().isEmpty();
+}
+
+
+void TestLinks::checkDocumentWithNoDests()
+{
+    Poppler::Document *doc;
+    doc = Poppler::Document::load(TESTDATADIR "/unittestcases/WithAttachments.pdf");
+    QVERIFY( doc );
+
+    std::unique_ptr< Poppler::LinkDestination > dest;
+    dest.reset( doc->linkDestination("no.dests.in.this.document") );
+    QVERIFY( !isDestinationValid_pageNumber( dest.get(), doc ) );
+    QVERIFY( isDestinationValid_name( dest.get() ) );
+
+    delete doc;
+}
+
+void TestLinks::checkDests_xr01()
+{
+    Poppler::Document *doc;
+    doc = Poppler::Document::load(TESTDATADIR "/unittestcases/xr01.pdf");
+    QVERIFY( doc );
+
+    Poppler::Page *page = doc->page(0);
+    QVERIFY( page );
+
+    QList< Poppler::Link* > links = page->links();
+    QCOMPARE( links.count(), 2 );
+
+    {
+    QCOMPARE( links.at(0)->linkType(), Poppler::Link::Goto );
+    Poppler::LinkGoto *link = static_cast< Poppler::LinkGoto * >( links.at(0) );
+    const Poppler::LinkDestination dest = link->destination();
+    QVERIFY( !isDestinationValid_pageNumber( &dest, doc ) );
+    QVERIFY( isDestinationValid_name( &dest ) );
+    QCOMPARE( dest.destinationName(), QString::fromLatin1("section.1") );
+    }
+
+    {
+    QCOMPARE( links.at(1)->linkType(), Poppler::Link::Goto );
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/qt5/tests/check_dateConversion.cpp

@@ -1,0 +1,142 @@
+#include <QtTest/QtTest>
+
+Q_DECLARE_METATYPE(QDate)
+Q_DECLARE_METATYPE(QTime)
+
+#include <poppler-qt5.h>
+
+class TestDateConv: public QObject
+{
+    Q_OBJECT
+private slots:
+    void initTestCase();
+    void checkDates_data();
+    void checkDates();
+    void checkInvalidDates_data();
+    void checkInvalidDates();
+};
+
+void TestDateConv::initTestCase()
+{
+    qRegisterMetaType<QDate>("QDate");
+    qRegisterMetaType<QTime>("QTime");
+}
+
+void TestDateConv::checkDates_data()
+{
+    QTest::addColumn<QByteArray>("input");
+    QTest::addColumn<QDate>("day");
+    QTest::addColumn<QTime>("time");
+
+    // This is a typical case - all data provided
+    QTest::newRow("D:20040101121110")
+      << QByteArray("D:20040101121110Z")
+      << QDate( 2004, 1, 1)
+      << QTime( 12, 11, 10);
+
+    // The D: is strongly recommended, but optional
+    QTest::newRow("20040101121110")
+      << QByteArray("20040101121110Z")
+      << QDate( 2004, 1, 1)
+      << QTime( 12, 11, 10);
+
+    // Only the year is actually required
+    QTest::newRow("D:2006")
+      << QByteArray("D:2006")
+      << QDate( 2006, 1, 1)
+      << QTime( 0, 0, 0);
+
+    QTest::newRow("D:200602")
+      << QByteArray("D:200602")
+      << QDate( 2006, 2, 1)
+      << QTime( 0, 0, 0);
+
+    QTest::newRow("D:20060304")
+      << QByteArray("D:20060304")
+      << QDate( 2006, 3, 4)
+      << QTime( 0, 0, 0);
+
+    QTest::newRow("D:2006030405")
+      << QByteArray("D:2006030405")
+      << QDate( 2006, 3, 4)
+      << QTime( 5, 0, 0);
+
+    QTest::newRow("D:200603040512")
+      << QByteArray("D:200603040512")
+      << QDate( 2006, 3, 4)
+      << QTime( 5, 12, 0);
+
+    // If the timezone isn't specified, I assume UTC
+    QTest::newRow("D:20060304051226")
+      << QByteArray("D:20060304051226")
+      << QDate( 2006, 3, 4)
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/qt5/tests/check_metadata.cpp

@@ -1,0 +1,274 @@
+#include <QtTest/QtTest>
+
+#include <poppler-qt5.h>
+
+class TestMetaData: public QObject
+{
+    Q_OBJECT
+private slots:
+    void checkStrings_data();
+    void checkStrings();
+    void checkStrings2_data();
+    void checkStrings2();
+    void checkStringKeys();
+    void checkLinearised();
+    void checkNumPages();
+    void checkDate();
+    void checkPageSize();
+    void checkPortraitOrientation();
+    void checkLandscapeOrientation();
+    void checkUpsideDownOrientation();
+    void checkSeascapeOrientation();
+    void checkVersion();
+    void checkPdfId();
+    void checkNoPdfId();
+};
+
+void TestMetaData::checkStrings_data()
+{
+    QTest::addColumn<QString>("key");
+    QTest::addColumn<QString>("value");
+
+    QTest::newRow( "Author" ) << "Author" << "Brad Hards";
+    QTest::newRow( "Title" ) << "Title" << "Two pages";
+    QTest::newRow( "Subject" ) << "Subject"
+			       << "A two page layout for poppler testing";
+    QTest::newRow( "Keywords" ) << "Keywords" << "Qt4 bindings";
+    QTest::newRow( "Creator" ) << "Creator" << "iText: cgpdftops CUPS filter";
+    QTest::newRow( "Producer" ) << "Producer" << "Acrobat Distiller 7.0 for Macintosh";
+}
+
+void TestMetaData::checkStrings()
+{
+    Poppler::Document *doc;
+    doc = Poppler::Document::load(TESTDATADIR "/unittestcases/doublepage.pdf");
+    QVERIFY( doc );
+
+    QFETCH( QString, key );
+    QFETCH( QString, value );
+    QCOMPARE( doc->info(key), value );
+
+    delete doc;
+}
+
+void TestMetaData::checkStrings2_data()
+{
+    QTest::addColumn<QString>("key");
+    QTest::addColumn<QString>("value");
+
+    QTest::newRow( "Title" ) << "Title" << "Malaga hotels";
+    QTest::newRow( "Author" ) << "Author" << "Brad Hards";
+    QTest::newRow( "Creator" ) << "Creator" << "Safari: cgpdftops CUPS filter";
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/splash/SplashFTFontFile.cc

@@ -1,0 +1,153 @@
+//========================================================================
+//
+// SplashFTFontFile.cc
+//
+//========================================================================
+
+//========================================================================
+//
+// Modified under the Poppler project - http://poppler.freedesktop.org
+//
+// All changes made under the Poppler project to this file are licensed
+// under GPL version 2 or later
+//
+// Copyright (C) 2006 Takashi Iwai <tiwai@suse.de>
+// Copyright (C) 2014 Adrian Johnson <ajohnson@redneon.com>
+// Copyright (C) 2017 Oliver Sander <oliver.sander@tu-dresden.de>
+//
+// To see a description of the changes please see the Changelog file that
+// came with your tarball or type make ChangeLog if you are building from git
+//
+//========================================================================
+
+#include <config.h>
+
+#if HAVE_FREETYPE_FREETYPE_H || HAVE_FREETYPE_H
+
+#ifdef USE_GCC_PRAGMAS
+#pragma implementation
+#endif
+
+#include "goo/gmem.h"
+#include "goo/GooString.h"
+#include "poppler/GfxFont.h"
+#include "SplashFTFontEngine.h"
+#include "SplashFTFont.h"
+#include "SplashFTFontFile.h"
+
+//------------------------------------------------------------------------
+// SplashFTFontFile
+//------------------------------------------------------------------------
+
+SplashFontFile *SplashFTFontFile::loadType1Font(SplashFTFontEngine *engineA,
+						SplashFontFileID *idA,
+						SplashFontSrc *src,
+						const char **encA) {
+  FT_Face faceA;
+  int *codeToGIDA;
+  const char *name;
+  int i;
+
+  if (src->isFile) {
+    if (FT_New_Face(engineA->lib, src->fileName->getCString(), 0, &faceA))
+      return NULL;
+  } else {
+    if (FT_New_Memory_Face(engineA->lib, (const FT_Byte *)src->buf, src->bufLen, 0, &faceA))
+      return NULL;
+  }
+  codeToGIDA = (int *)gmallocn(256, sizeof(int));
+  for (i = 0; i < 256; ++i) {
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/utils/pdfseparate.cc

@@ -1,0 +1,178 @@
+//========================================================================
+//
+// pdfseparate.cc
+//
+// This file is licensed under the GPLv2 or later
+//
+// Copyright (C) 2011, 2012, 2015 Thomas Freitag <Thomas.Freitag@alfa.de>
+// Copyright (C) 2012-2014, 2017 Albert Astals Cid <aacid@kde.org>
+// Copyright (C) 2013, 2016 Pino Toscano <pino@kde.org>
+// Copyright (C) 2013 Daniel Kahn Gillmor <dkg@fifthhorseman.net>
+// Copyright (C) 2013 Suzuki Toshiya <mpsuzuki@hiroshima-u.ac.jp>
+// Copyright (C) 2017 Léonard Michelet <leonard.michelet@smile.fr>
+//
+//========================================================================
+#include "config.h"
+#include <poppler-config.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <stddef.h>
+#include <string.h>
+#include "parseargs.h"
+#include "goo/GooString.h"
+#include "PDFDoc.h"
+#include "ErrorCodes.h"
+#include "GlobalParams.h"
+#include <ctype.h>
+
+static int firstPage = 0;
+static int lastPage = 0;
+static GBool printVersion = gFalse;
+static GBool printHelp = gFalse;
+
+static const ArgDesc argDesc[] = {
+  {"-f", argInt, &firstPage, 0,
+   "first page to extract"},
+  {"-l", argInt, &lastPage, 0,
+   "last page to extract"},
+  {"-v", argFlag, &printVersion, 0,
+   "print copyright and version info"},
+  {"-h", argFlag, &printHelp, 0,
+   "print usage information"},
+  {"-help", argFlag, &printHelp, 0,
+   "print usage information"},
+  {"--help", argFlag, &printHelp, 0,
+   "print usage information"},
+  {"-?", argFlag, &printHelp, 0,
+   "print usage information"},
+  {NULL}
+};
+
+static bool extractPages (const char *srcFileName, const char *destFileName) {
+  char pathName[4096];
+  GooString *gfileName = new GooString (srcFileName);
+  PDFDoc *doc = new PDFDoc (gfileName, NULL, NULL, NULL);
+
+  if (!doc->isOk()) {
+    error(errSyntaxError, -1, "Could not extract page(s) from damaged file ('{0:s}')", srcFileName);
+    delete doc;
+    return false;
+  }
+
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/utils/pdftocairo-win32.cc

@@ -1,0 +1,564 @@
+//========================================================================
+//
+// This file is licensed under the GPLv2 or later
+//
+// Copyright (C) 2014 Rodrigo Rivas Costa <rodrigorivascosta@gmail.com>
+// Copyright (C) 2014 Adrian Johnson <ajohnson@redneon.com>
+// Copyright (C) 2017 Albert Astals Cid <aacid@kde.org>
+//
+// To see a description of the changes please see the Changelog file that
+// came with your tarball or type make ChangeLog if you are building from git
+//
+//========================================================================
+
+#include <cairo.h>
+#ifdef CAIRO_HAS_WIN32_SURFACE
+
+#include <cairo-win32.h>
+
+#include "parseargs.h"
+#include "pdftocairo-win32.h"
+
+#include <dlgs.h>
+#include <commctrl.h>
+#include <commdlg.h>
+#include <windowsx.h>
+#include <winspool.h>
+
+static HDC hdc;
+static HGLOBAL hDevmode = 0;
+static HGLOBAL hDevnames = 0;
+static DEVMODEA *devmode;
+static char *printerName;
+
+struct Win32Option
+{
+  const char *name;
+  int value;
+};
+
+static const Win32Option win32PaperSource[] =
+{
+  {"upper", DMBIN_UPPER},
+  {"onlyone", DMBIN_ONLYONE},
+  {"lower", DMBIN_LOWER},
+  {"middle", DMBIN_MIDDLE},
+  {"manual", DMBIN_MANUAL},
+  {"envelope", DMBIN_ENVELOPE},
+  {"envmanual", DMBIN_ENVMANUAL},
+  {"auto", DMBIN_AUTO},
+  {"tractor", DMBIN_TRACTOR},
+  {"smallfmt", DMBIN_SMALLFMT},
+  {"largefmt", DMBIN_LARGEFMT},
+  {"largecapacity", DMBIN_LARGECAPACITY},
+  {"formsource", DMBIN_FORMSOURCE},
+  {NULL, 0}
+};
+
+static void parseSource(GooString *source)
+{
+  const Win32Option *option = win32PaperSource;
+  while (option->name) {
+    if (source->cmp(option->name) == 0) {
+      devmode->dmDefaultSource = option->value;
+      devmode->dmFields |= DM_DEFAULTSOURCE;
+      return;
+    }
[…]

### 2017-12-28 Desktop/texmaker packages/poppler-0.60.1/utils/pdftotext.cc

@@ -1,0 +1,563 @@
+//========================================================================
+//
+// pdftotext.cc
+//
+// Copyright 1997-2003 Glyph & Cog, LLC
+//
+// Modified for Debian by Hamish Moffatt, 22 May 2002.
+//
+//========================================================================
+
+//========================================================================
+//
+// Modified under the Poppler project - http://poppler.freedesktop.org
+//
+// All changes made under the Poppler project to this file are licensed
+// under GPL version 2 or later
+//
+// Copyright (C) 2006 Dominic Lachowicz <cinamod@hotmail.com>
+// Copyright (C) 2007-2008, 2010, 2011, 2017 Albert Astals Cid <aacid@kde.org>
+// Copyright (C) 2009 Jan Jockusch <jan@jockusch.de>
+// Copyright (C) 2010, 2013 Hib Eris <hib@hiberis.nl>
+// Copyright (C) 2010 Kenneth Berland <ken@hero.com>
+// Copyright (C) 2011 Tom Gleason <tom@buildadam.com>
+// Copyright (C) 2011 Steven Murdoch <Steven.Murdoch@cl.cam.ac.uk>
+// Copyright (C) 2013 Yury G. Kudryashov <urkud.urkud@gmail.com>
+// Copyright (C) 2013 Suzuki Toshiya <mpsuzuki@hiroshima-u.ac.jp>
+// Copyright (C) 2015 Jeremy Echols <jechols@uoregon.edu>
+//
+// To see a description of the changes please see the Changelog file that
+// came with your tarball or type make ChangeLog if you are building from git
+//
+//========================================================================
+
+#include "config.h"
+#include <poppler-config.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <stddef.h>
+#include <string.h>
+#include "parseargs.h"
+#include "printencodings.h"
+#include "goo/GooString.h"
+#include "goo/gmem.h"
+#include "GlobalParams.h"
+#include "Object.h"
+#include "Stream.h"
+#include "Array.h"
+#include "Dict.h"
+#include "XRef.h"
+#include "Catalog.h"
+#include "Page.h"
+#include "PDFDoc.h"
+#include "PDFDocFactory.h"
+#include "TextOutputDev.h"
+#include "CharTypes.h"
+#include "UnicodeMap.h"
+#include "PDFDocEncoding.h"
+#include "Error.h"
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_configdialog.h

@@ -1,0 +1,1405 @@
+/********************************************************************************
+** Form generated from reading UI file 'configdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_CONFIGDIALOG_H
+#define UI_CONFIGDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QCheckBox>
+#include <QtWidgets/QComboBox>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QFrame>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QGroupBox>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QListWidget>
+#include <QtWidgets/QPushButton>
+#include <QtWidgets/QRadioButton>
+#include <QtWidgets/QSpacerItem>
+#include <QtWidgets/QSpinBox>
+#include <QtWidgets/QStackedWidget>
+#include <QtWidgets/QTableWidget>
+#include <QtWidgets/QWidget>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_ConfigDialog
+{
+public:
+    QGridLayout *gridLayout_7;
+    QListWidget *contentsWidget;
+    QStackedWidget *pagesWidget;
+    QWidget *pt;
+    QGridLayout *gridLayout_17;
+    QGroupBox *groupBox;
+    QGridLayout *gridLayout_16;
+    QFrame *frame_2;
+    QGridLayout *gridLayout_5;
+    QGridLayout *gridLayout_12;
+    QLabel *labelPsview;
+    QLineEdit *lineEditPsviewer;
+    QPushButton *pushButtonPsviewer;
+    QFrame *frame_3;
+    QGridLayout *gridLayout_15;
+    QGridLayout *gridLayout_2;
+    QLabel *labelPdfview;
+    QRadioButton *radioButtonInternalPdfViewer;
+    QFrame *line_12;
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_encodingdialog.h

@@ -1,0 +1,89 @@
+/********************************************************************************
+** Form generated from reading UI file 'encodingdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_ENCODINGDIALOG_H
+#define UI_ENCODINGDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QComboBox>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_EncodingDialog
+{
+public:
+    QGridLayout *gridLayout;
+    QLabel *label;
+    QLabel *label_2;
+    QComboBox *comboBoxEncoding;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *EncodingDialog)
+    {
+        if (EncodingDialog->objectName().isEmpty())
+            EncodingDialog->setObjectName(QStringLiteral("EncodingDialog"));
+        EncodingDialog->resize(374, 125);
+        gridLayout = new QGridLayout(EncodingDialog);
+        gridLayout->setObjectName(QStringLiteral("gridLayout"));
+        label = new QLabel(EncodingDialog);
+        label->setObjectName(QStringLiteral("label"));
+        label->setAlignment(Qt::AlignLeading|Qt::AlignLeft|Qt::AlignTop);
+
+        gridLayout->addWidget(label, 0, 0, 1, 2);
+
+        label_2 = new QLabel(EncodingDialog);
+        label_2->setObjectName(QStringLiteral("label_2"));
+
+        gridLayout->addWidget(label_2, 1, 0, 1, 1);
+
+        comboBoxEncoding = new QComboBox(EncodingDialog);
+        comboBoxEncoding->setObjectName(QStringLiteral("comboBoxEncoding"));
+
+        gridLayout->addWidget(comboBoxEncoding, 1, 1, 1, 1);
+
+        buttonBox = new QDialogButtonBox(EncodingDialog);
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_exportdialog.h

@@ -1,0 +1,206 @@
+/********************************************************************************
+** Form generated from reading UI file 'exportdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_EXPORTDIALOG_H
+#define UI_EXPORTDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QGroupBox>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QPlainTextEdit>
+#include <QtWidgets/QPushButton>
+#include <QtWidgets/QRadioButton>
+#include <QtWidgets/QSpacerItem>
+#include <QtWidgets/QVBoxLayout>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_ExportDialog
+{
+public:
+    QGridLayout *gridLayout;
+    QHBoxLayout *horizontalLayout;
+    QLabel *labelPath;
+    QLineEdit *lineEditPath;
+    QPushButton *pushButtonPath;
+    QGroupBox *groupBox;
+    QVBoxLayout *verticalLayout;
+    QRadioButton *radioButton1;
+    QRadioButton *radioButton2;
+    QRadioButton *radioButton3;
+    QRadioButton *radioButton4;
+    QRadioButton *radioButton5;
+    QHBoxLayout *horizontalLayout_2;
+    QLabel *labelOPtions;
+    QLineEdit *lineEditOptions;
+    QHBoxLayout *horizontalLayout_3;
+    QSpacerItem *horizontalSpacer;
+    QPushButton *pushButtonRun;
+    QPlainTextEdit *plainTextEditResult;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *ExportDialog)
+    {
+        if (ExportDialog->objectName().isEmpty())
+            ExportDialog->setObjectName(QStringLiteral("ExportDialog"));
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_filechooser.h

@@ -1,0 +1,119 @@
+/********************************************************************************
+** Form generated from reading UI file 'filechooser.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_FILECHOOSER_H
+#define UI_FILECHOOSER_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QPushButton>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_FileChooser
+{
+public:
+    QGridLayout *gridLayout;
+    QHBoxLayout *hboxLayout;
+    QLabel *label;
+    QLineEdit *lineEdit;
+    QPushButton *pushButton;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *FileChooser)
+    {
+        if (FileChooser->objectName().isEmpty())
+            FileChooser->setObjectName(QStringLiteral("FileChooser"));
+        FileChooser->resize(402, 82);
+        gridLayout = new QGridLayout(FileChooser);
+        gridLayout->setObjectName(QStringLiteral("gridLayout"));
+        hboxLayout = new QHBoxLayout();
+#ifndef Q_OS_MAC
+        hboxLayout->setSpacing(6);
+#endif
+#ifndef Q_OS_MAC
+        hboxLayout->setContentsMargins(0, 0, 0, 0);
+#endif
+        hboxLayout->setObjectName(QStringLiteral("hboxLayout"));
+        label = new QLabel(FileChooser);
+        label->setObjectName(QStringLiteral("label"));
+        QSizePolicy sizePolicy(QSizePolicy::Minimum, QSizePolicy::MinimumExpanding);
+        sizePolicy.setHorizontalStretch(0);
+        sizePolicy.setVerticalStretch(0);
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_findwidget.h

@@ -1,0 +1,193 @@
+/********************************************************************************
+** Form generated from reading UI file 'findwidget.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_FINDWIDGET_H
+#define UI_FINDWIDGET_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QCheckBox>
+#include <QtWidgets/QComboBox>
+#include <QtWidgets/QFrame>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QPushButton>
+#include <QtWidgets/QRadioButton>
+#include <QtWidgets/QSpacerItem>
+#include <QtWidgets/QWidget>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_FindWidget
+{
+public:
+    QGridLayout *gridLayout;
+    QComboBox *comboFind;
+    QPushButton *findButton;
+    QRadioButton *radioForward;
+    QRadioButton *radioBackward;
+    QPushButton *closeButton;
+    QSpacerItem *spacerItem;
+    QCheckBox *checkWords;
+    QCheckBox *checkCase;
+    QCheckBox *checkBegin;
+    QPushButton *moreButton;
+    QFrame *extension;
+    QHBoxLayout *horizontalLayout;
+    QCheckBox *checkRegExp;
+    QCheckBox *checkSelection;
+
+    void setupUi(QWidget *FindWidget)
+    {
+        if (FindWidget->objectName().isEmpty())
+            FindWidget->setObjectName(QStringLiteral("FindWidget"));
+        FindWidget->resize(513, 94);
+        QSizePolicy sizePolicy(QSizePolicy::Preferred, QSizePolicy::Minimum);
+        sizePolicy.setHorizontalStretch(0);
+        sizePolicy.setVerticalStretch(0);
+        sizePolicy.setHeightForWidth(FindWidget->sizePolicy().hasHeightForWidth());
+        FindWidget->setSizePolicy(sizePolicy);
+        FindWidget->setFocusPolicy(Qt::NoFocus);
+        gridLayout = new QGridLayout(FindWidget);
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_refdialog.h

@@ -1,0 +1,123 @@
+/********************************************************************************
+** Form generated from reading UI file 'refdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_REFDIALOG_H
+#define UI_REFDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QComboBox>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QSpacerItem>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_RefDialog
+{
+public:
+    QGridLayout *gridLayout;
+    QHBoxLayout *hboxLayout;
+    QLabel *label;
+    QComboBox *comboBox;
+    QHBoxLayout *hboxLayout1;
+    QSpacerItem *spacerItem;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *RefDialog)
+    {
+        if (RefDialog->objectName().isEmpty())
+            RefDialog->setObjectName(QStringLiteral("RefDialog"));
+        RefDialog->resize(279, 97);
+        gridLayout = new QGridLayout(RefDialog);
+#ifndef Q_OS_MAC
+        gridLayout->setSpacing(6);
+#endif
+#ifndef Q_OS_MAC
+        gridLayout->setContentsMargins(9, 9, 9, 9);
+#endif
+        gridLayout->setObjectName(QStringLiteral("gridLayout"));
+        hboxLayout = new QHBoxLayout();
+#ifndef Q_OS_MAC
+        hboxLayout->setSpacing(6);
+#endif
+#ifndef Q_OS_MAC
+        hboxLayout->setContentsMargins(0, 0, 0, 0);
+#endif
+        hboxLayout->setObjectName(QStringLiteral("hboxLayout"));
+        label = new QLabel(RefDialog);
+        label->setObjectName(QStringLiteral("label"));
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_texdocdialog.h

@@ -1,0 +1,179 @@
+/********************************************************************************
+** Form generated from reading UI file 'texdocdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_TEXDOCDIALOG_H
+#define UI_TEXDOCDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QFrame>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QPushButton>
+#include <QtWidgets/QSpacerItem>
+#include <QtWidgets/QVBoxLayout>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_TexdocDialog
+{
+public:
+    QGridLayout *gridLayout_3;
+    QVBoxLayout *verticalLayout;
+    QHBoxLayout *horizontalLayout;
+    QLineEdit *lineEdit;
+    QHBoxLayout *horizontalLayout_2;
+    QPushButton *moreButton;
+    QSpacerItem *horizontalSpacer;
+    QDialogButtonBox *buttonBox;
+    QFrame *extension;
+    QGridLayout *gridLayout_2;
+    QGridLayout *gridLayout;
+    QLabel *labelCommand;
+    QLineEdit *lineEditCommand;
+    QPushButton *pushButton;
+
+    void setupUi(QDialog *TexdocDialog)
+    {
+        if (TexdocDialog->objectName().isEmpty())
+            TexdocDialog->setObjectName(QStringLiteral("TexdocDialog"));
+        TexdocDialog->resize(469, 119);
+        QSizePolicy sizePolicy(QSizePolicy::Preferred, QSizePolicy::Minimum);
+        sizePolicy.setHorizontalStretch(0);
+        sizePolicy.setVerticalStretch(0);
+        sizePolicy.setHeightForWidth(TexdocDialog->sizePolicy().hasHeightForWidth());
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_usermenudialog.h

@@ -1,0 +1,119 @@
+/********************************************************************************
+** Form generated from reading UI file 'usermenudialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_USERMENUDIALOG_H
+#define UI_USERMENUDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QFrame>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QListWidget>
+#include <QtWidgets/QPlainTextEdit>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_UserMenuDialog
+{
+public:
+    QGridLayout *gridLayout_2;
+    QListWidget *listWidget;
+    QFrame *line;
+    QGridLayout *gridLayout;
+    QLabel *label;
+    QLineEdit *itemEdit;
+    QLabel *label_2;
+    QPlainTextEdit *tagEdit;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *UserMenuDialog)
+    {
+        if (UserMenuDialog->objectName().isEmpty())
+            UserMenuDialog->setObjectName(QStringLiteral("UserMenuDialog"));
+        UserMenuDialog->resize(617, 313);
+        gridLayout_2 = new QGridLayout(UserMenuDialog);
+        gridLayout_2->setObjectName(QStringLiteral("gridLayout_2"));
+        listWidget = new QListWidget(UserMenuDialog);
+        listWidget->setObjectName(QStringLiteral("listWidget"));
+        QSizePolicy sizePolicy(QSizePolicy::Minimum, QSizePolicy::Expanding);
+        sizePolicy.setHorizontalStretch(0);
+        sizePolicy.setVerticalStretch(0);
+        sizePolicy.setHeightForWidth(listWidget->sizePolicy().hasHeightForWidth());
[…]

### 2017-12-28 Desktop/texmaker packages/texmaker-4.5/.ui/ui_x11fontdialog.h

@@ -1,0 +1,130 @@
+/********************************************************************************
+** Form generated from reading UI file 'x11fontdialog.ui'
+**
+** Created by: Qt User Interface Compiler version 5.6.2
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_X11FONTDIALOG_H
+#define UI_X11FONTDIALOG_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QComboBox>
+#include <QtWidgets/QDialog>
+#include <QtWidgets/QDialogButtonBox>
+#include <QtWidgets/QGridLayout>
+#include <QtWidgets/QHBoxLayout>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QSpacerItem>
+#include <QtWidgets/QSpinBox>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_X11FontDialog
+{
+public:
+    QGridLayout *gridLayout;
+    QGridLayout *gridLayout1;
+    QLabel *labelFamily;
+    QComboBox *comboBoxFont;
+    QLabel *labelSize;
+    QSpinBox *spinBoxSize;
+    QHBoxLayout *hboxLayout;
+    QSpacerItem *spacerItem;
+    QDialogButtonBox *buttonBox;
+
+    void setupUi(QDialog *X11FontDialog)
+    {
+        if (X11FontDialog->objectName().isEmpty())
+            X11FontDialog->setObjectName(QStringLiteral("X11FontDialog"));
+        X11FontDialog->resize(317, 116);
+        gridLayout = new QGridLayout(X11FontDialog);
+#ifndef Q_OS_MAC
+        gridLayout->setSpacing(6);
+#endif
+#ifndef Q_OS_MAC
+        gridLayout->setContentsMargins(9, 9, 9, 9);
+#endif
+        gridLayout->setObjectName(QStringLiteral("gridLayout"));
+        gridLayout1 = new QGridLayout();
+#ifndef Q_OS_MAC
+        gridLayout1->setSpacing(6);
+#endif
+#ifndef Q_OS_MAC
+        gridLayout1->setContentsMargins(0, 0, 0, 0);
+#endif
[…]

### 2017-12-28 poster_20170131/poster.tex
added poster draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.1 (14/06/14)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.0]{beamerposter} % Use the beamerposter package for laying out the poster
\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=dblue!80,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. 
% (1-(3+1)*0.025)/3 = 0.3
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{48in} % A0 height: 33.1in
\setlength{\textwidth}{34in} % A0 width: 46.8in
\setlength{\textheight}{46in} % A0 height: 33.1in
\setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
\setlength{\twocolwid}{0.625\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{tabularx}
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{z}{>{\hsize=.65\hsize}X}

\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{xspace}

\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes, calc }
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]

\tikzstyle{block} = [rectangle, draw, text centered, fill=blue!20]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=6em,
minimum height=2em]

\usetikzlibrary{shapes.multipart}
\usetikzlibrary{positioning}

\setbeamertemplate{bibliography item}[text]

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transtitions} % Poster title

\author{Kathryn D. Huff, James Stubbins}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

%=======================================================
% FIRST COLUMN BEGINS
%=========================================================

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Objectives}

Evaluate potential impact of novel energy technologies within Japan's energy system. Specifically:
\begin{itemize}
	\item Help guide practical near term (2010-2050) transition strategies to minimize carbon emissions within realistic constraints.
	\item Identify high impact technologies.
	\item Assess role of technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\item Identify ideal timelines for energy system deployment, infrastructure development, high impact R\&D investment.

\end{itemize}

\end{alertblock}

\begin{block}{Collaborators}

I\textsuperscript{2}CNER collaborators will include primarily the members of the Energy Analysis Division (EAD), including those members at other institutes, universities or industries with connections to the EAD.

\end{block}

%----------------------------------------------------------------------------------------
%	METHODOLOGY
%----------------------------------------------------------------------------------------

\begin{block}{Methodology}
Multiple studies have been conducted to compare the impact of innovative energy technologies in different regions of the world using \textit{static} scenario analyses \cite{chyong_chi_dynamics_2009} \cite{feng_system_2013} \cite{kikuchi_simulation-based_2017} \cite{li_energy_2010} \cite{pambudi_impact_2017} \cite{pambudi_future_2016}. We will simulate \textit{dynamic transition scenarios} \cite{jebaraj_review_2006} \cite{pfenninger_energy_2014} , with realistic constraints and technology readiness of energy generation technologies (in terms of generation, transmission \& storage), aimed at minimizing carbon emissions. We will further extend previous work by combining multiple technologies in a single heterogeneous system.\\

The TIMES (The Integrated MARKAL-EFOM System) model generator \cite{loulou_documentation_2005} \cite{seebregts_energy/environmental_2002} optimizes energy systems of a model using linear and mixed-linear algorithms while implementing user-defined objective functions (such as minimizing carbon emissions or costs) within user defined constraints such as energy generation demand. It will be used to simulate near-term energy transitions while focusing on reduction of carbon emissions.

\begin{figure}
	\centering
	\scalebox{0.8}{
		\begin{tikzpicture}[    >=stealth,
		node distance=8cm,
		on grid,
		align=center,
		auto]
		% Place nodes
		\node [block] (times) {\textbf{TIMES Model Generator}};
		\node [cloud, above left=13cm and 12cm of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ mutli-technology \\ model of JPN};
				\node [cloud, above=9cm of mod] (dat) { Data \\ collection};
		\node [cloud, above=9cm of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION} \\ e.g.: Minimize \\ carbon emissions \\ from all \\ deployed sources};
		\node [cloud, above right=13cm and 10cm of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\
		sources must\\ meet energy \\ demand};
		\node [cloud, below=of times] (res) {Simulation \\ Results};
		\node [cloud, below=of res] (eres) {Projections,\\ Conclusions, \\ Insights} ;

		\draw[->, ultra thick] let \p1=($(times)-(mod)$) in (mod) -- +(0,\y1)-- +(times);
		\draw[->, ultra thick] (of) -- (times);
		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
		\draw[->, ultra thick] (times) -- (res);
		\draw[->, ultra thick] (res) -- (eres);
		\draw[->, ultra thick] (dat) -- (mod);
 \end{tikzpicture}

	}
	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
\end{figure}

\end{block}

%----------------------------------------------------------------------------------------
%	Anticipated Results
%----------------------------------------------------------------------------------------

\begin{block}{Anticipated Results}

 \begin{itemize}
   \item Analysis results can be filtered by sector (commercial, industrial, residential, building etc) or by region.

   \item Many metrics are automatically postprocessed- such as energy intensity, thermal energy efficiency, transmission capacity.

   \item Technology deployment transitions driven by constrained optimization will have valuable strategic value.

 \end{itemize}

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

%===========================================================================================
% SECOND COLUMN BEGINS
%=============================================================================================

%----------------------------------------------------------------------------------------

\begin{column}{\onecolwid} % The second column

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

        \begin{alertblock}{Impact}
        \large Results will:
	\begin{itemize}
		\item {\large Assist in creation of realistic decarbonization roadmaps that maximize efficiency.}
        \item {\large Identify potential bottlenecks during transitions.}
		\item {\large Help Japan's policymakers create timelines for R\&D investment and for appropriate infrastructure development.}
		\item {\large Quantify system sensitivity to technology readiness.}
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% CHALLENGES
%---------------------------------------------------------
\begin{block}{Challenges}

 \begin{itemize}
   \item Reliable data for each technology's deployment and operation is required, such as:
    \begin{itemize}

     \item \normalsize Technology readiness

     \item Carbon intensity

     \item Capacity and availability factors

     \item Fuel costs and demands

     \item Thermal/electric generation capacity

     \item Storage capacity

     \item Thermal efficiency

     \item Construction time

     \item Construction costs

     \item Operation and maintenance costs\\

    \end{itemize}

   \item Mutiple constraints cause complications.

   \item Variation of goals or the objective function can significantly change each simulation. e.g.: cost could be objective function whereas carbon reduction up to a certain percentage (50-70\%) could be the constraint, flipping the script.

   \item Calculation of constituent parameters, such as carbon emissions per component and quantification of deployment, will be complex.

   \item Intermediate objective functions for a multi-objective formulation could additionally include intermediate-resolution-goals such as Efficiency Increase (EI) and Lower Carbon Intensity (LCI). These intermediate objectives will increase the complexity of the calculation.

 \end{itemize}

\end{block}

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Summary}
\begin{itemize}

\item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.

\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.

\item Simulations will quantify system sensitivity to technology readiness, and also account for secondary scenarios where decarbonization is not the main priority.

\end{itemize}

\end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color

\begin{block}{Acknowledgements}

This research is being performed using funding received
from the I\textsuperscript{2}CNER Programs under award number \textbf{<insert details here>}.

\vspace{10mm}
\begin{center}
\begin{tabular}{cccc}
\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
\end{tabular}
\end{center}

\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

\begin{alertblock}{Contact Information}
\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
\begin{itemize}

	\item Web: \href{arfc.github.io}{arfc.github.io}
	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
\end{itemize}

\end{alertblock}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column

\begin{block}{References}

        {\footnotesize\bibliographystyle{abbrv} 
        \bibliography{poster}}
\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}
\begin{column}{\sepwid}\end{column} % Empty spacer column

### 2018-01-03 docs/poster.tex
many adjustments to reduce text and increase figure prominence
Former-commit-id: 08695848edb673afee3facb7aa7b8182765beba4

--- 2017-12-28 poster_20170131/poster.tex
@@
 
+\tikzstyle{const} = [rectangle, draw, text centered, fill=purple!20]
+\tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]
+
 \tikzstyle{block} = [rectangle, draw, text centered, fill=blue!20]
@@
 
-\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transtitions} % Poster title
+\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
 
-\author{Kathryn D. Huff, James Stubbins}
+\author{Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
 \institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
@@
 \begin{itemize}
-	\item Help guide practical near term (2010-2050) transition strategies to minimize carbon emissions within realistic constraints.
+	\item Guide practical near term (2010-2050) transition strategies.
+        \item Minimize carbon emissions within realistic constraints.
 	\item Identify high impact technologies.
@@
 	\item Identify ideal timelines for energy system deployment, infrastructure development, high impact R\&D investment.
-
 \end{itemize}
@@
 \end{alertblock}
-
-\begin{block}{Collaborators}
-
-I\textsuperscript{2}CNER collaborators will include primarily the members of the Energy Analysis Division (EAD), including those members at other institutes, universities or industries with connections to the EAD.
-
-\end{block}
+%
+%\begin{block}{Collaborators}
+%
+%I\textsuperscript{2}CNER collaborators will include primarily the members of 
+%the Energy Analysis Division (EAD), including those members at other 
+%institutes, universities or industries with connections to the EAD.   
+%\end{block}
 
@@
 
-\begin{figure}
-	\centering
-	\scalebox{0.8}{
-		\begin{tikzpicture}[    >=stealth,
-		node distance=8cm,
-		on grid,
-		align=center,
-		auto]
-		% Place nodes
-		\node [block] (times) {\textbf{TIMES Model Generator}};
-		\node [cloud, above left=13cm and 12cm of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ mutli-technology \\ model of JPN};
-				\node [cloud, above=9cm of mod] (dat) { Data \\ collection};
-		\node [cloud, above=9cm of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION} \\ e.g.: Minimize \\ carbon emissions \\ from all \\ deployed sources};
-		\node [cloud, above right=13cm and 10cm of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\
-		sources must\\ meet energy \\ demand};
-		\node [cloud, below=of times] (res) {Simulation \\ Results};
-		\node [cloud, below=of res] (eres) {Projections,\\ Conclusions, \\ Insights} ;
+\end{block}
 
-		\draw[->, ultra thick] let \p1=($(times)-(mod)$) in (mod) -- +(0,\y1)-- +(times);
-		\draw[->, ultra thick] (of) -- (times);
-		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
-		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
-		\draw[->, ultra thick] (times) -- (res);
-		\draw[->, ultra thick] (res) -- (eres);
-		\draw[->, ultra thick] (dat) -- (mod);
- \end{tikzpicture}
+%----------------------------------------------------------------------------------------
 
-	}
-	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
-\end{figure}
+\end{column} % End of the first column
 
-\end{block}
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+%===========================================================================================
+% SECOND COLUMN BEGINS
+%=============================================================================================
+
+%----------------------------------------------------------------------------------------
+
+\begin{column}{\onecolwid} % The second column
 
@@
 %----------------------------------------------------------------------------------------
-
-\end{column} % End of the first column
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
-
-%===========================================================================================
-% SECOND COLUMN BEGINS
-%=============================================================================================
-
-%----------------------------------------------------------------------------------------
-
-\begin{column}{\onecolwid} % The second column
-
-%----------------------------------------------------------------------------------------
 %	RESULTS
@@
 	\begin{itemize}
-		\item {\large Assist in creation of realistic decarbonization roadmaps that maximize efficiency.}
-        \item {\large Identify potential bottlenecks during transitions.}
-		\item {\large Help Japan's policymakers create timelines for R\&D investment and for appropriate infrastructure development.}
-		\item {\large Quantify system sensitivity to technology readiness.}
+        \item {Optimize realistic decarbonization roadmaps.}
+        \item {Identify potential transition bottlenecks.}
+        \item {Help Japan's policymakers create timelines for R\&D investment and infrastructure development.}
+        \item {Quantify system sensitivity to technology readiness.}
 	\end{itemize}
@@
 \begin{block}{Challenges}
-
- \begin{itemize}
-   \item Reliable data for each technology's deployment and operation is required, such as:
-    \begin{itemize}
-
-     \item \normalsize Technology readiness
-
-     \item Carbon intensity
-
-     \item Capacity and availability factors
-
-     \item Fuel costs and demands
-
-     \item Thermal/electric generation capacity
-
-     \item Storage capacity
-
-     \item Thermal efficiency
-
-     \item Construction time
-
-     \item Construction costs
-
-     \item Operation and maintenance costs\\
-
-    \end{itemize}
-
-   \item Mutiple constraints cause complications.
-
-   \item Variation of goals or the objective function can significantly change each simulation.
-e.g.: cost could be objective function whereas carbon reduction up to a certain percentage (50-70\%) could be the constraint, flipping the script.
-
-   \item Calculation of constituent parameters, such as carbon emissions per component and quantification of deployment, will be complex.
-
-   \item Intermediate objective functions for a multi-objective formulation could additionally include intermediate-resolution-goals such as Efficiency Increase (EI) and Lower Carbon Intensity (LCI).
-These intermediate objectives will increase the complexity of the calculation.
-
- \end{itemize}
+   Reliable data for each technology's deployment and operation is required, such as:
 
 \end{block}
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of column 2
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The third column
 
@@
 
-\end{column} % End of column 2
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
-
-\begin{column}{\onecolwid} % The third column
-
-\begin{block}{References}
-
-        {\footnotesize\bibliographystyle{abbrv} 
-        \bibliography{poster}}
-\end{block}
-
-%----------------------------------------------------------------------------------------
-
 \end{column} % End of the third column
@@
 
+%=======================================================
+% Double Wide Figure Column 
+%=========================================================
+\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\twocolwid} % The double wide figure column
+
+%=======================================================
+% FIGURE BEGINS
+%=========================================================
+
+\newlength{\figwidth}
+\setlength{\figwidth}{8cm}
+
+\begin{figure}
+	\centering
+	\scalebox{1.0}{
+		\begin{tikzpicture}[>=stealth,
+		node distance=\figwidth,
+		on grid,
+		align=center,
+		auto]
+		% Place nodes
+		\node [block] (times) {\textbf{TIMES Model Generator}};
+		\node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
+                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] (dat) {\texttt{DATA}\\regarding\\both\\i$^2$cner\\ \&\\ conventional\\technologies};
+                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
+                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
+                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
+                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
+                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
+                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
+                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
+                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
+                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
+                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
+                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
+                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
+                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
+		\node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
+		\node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
+		\node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
+		\node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
+		\node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
+        \begin{scope}[on background layer]
+		\draw[->, ultra thick] let \p1=($(times)-(dat)$) in (dat) -- +(0,\y1)-- +(times);
+		\draw[->, ultra thick] (of) -- (times);
+		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
+		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
+		\draw[->, ultra thick] (times) -- (mod);
+		\draw[->, ultra thick] (min) -- (of);
+		\draw[->, ultra thick] (max) -- (of);
+		\draw[->, ultra thick] (dem) -- (const);
+		\draw[->, ultra thick] (dat1) -- (dat);
+		\draw[->, ultra thick] (dat2) -- (dat);
+		\draw[->, ultra thick] (dat3) -- (dat);
+		\draw[->, ultra thick] (dat4) -- (dat);
+		\draw[->, ultra thick] (dat5) -- (dat);
+		\draw[->, ultra thick] (dat6) -- (dat);
+		\draw[->, ultra thick] (dat7) -- (dat);
+		\draw[->, ultra thick] (dat8) -- (dat);
+		\draw[->, ultra thick] (dat9) -- (dat);
+		\draw[->, ultra thick] (dat10) -- (dat);
+		\draw[->, ultra thick] (dat11) -- (dat);
+		\draw[->, ultra thick] (dat12) -- (dat);
+		\draw[->, ultra thick] (dat13) -- (dat);
+               % \draw[out=330,in=300,looseness=8] (mod) -- (mod);
+        \end{scope}
+ \end{tikzpicture}
+	}
+	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
+\end{figure}
+
+\end{column} % End of the first column
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The second column
+
+\begin{block}{References}
+        {\footnotesize\bibliographystyle{abbrv} 
+        \bibliography{poster}}
+\end{block}
+\end{column} % End of the final column
+
+\end{columns}
 \end{frame} % End of the enclosing frame
@@
 \end{document}
-\begin{column}{\sepwid}\end{column} % Empty spacer column

### 2018-01-03 docs/poster.tex
fiddling with figure

@@
 \usepackage{tikz}
+\usetikzlibrary{arrows.meta}
+
 \usetikzlibrary{positioning, arrows, decorations, shapes, calc }
@@
 
-\tikzstyle{const} = [rectangle, draw, text centered, fill=purple!20]
+\tikzstyle{const} = [rectangle, draw, text centered, fill=orange!20]
 \tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]
@@
 \begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
 
@@
 
+\begin{block}{Introduction}
+Previous work has compared the impact of innovative energy technologies in 
+various world regions using \textbf{static} scenario analyses 
+\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
+We will simulate \textbf{dynamic} transition scenarios 
+\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
+emissions in Japan by 2050. These scenarios will include realistic constraints 
+regarding technology readiness (in terms of generation, transmission \& 
+storage) and will combine multiple technologies in a single heterogeneous 
+system model.
+\end{block}
+
 \begin{block}{Methodology}
-Multiple studies have been conducted to compare the impact of innovative energy technologies in different regions of the world using \textit{static} scenario analyses \cite{chyong_chi_dynamics_2009} \cite{feng_system_2013} \cite{kikuchi_simulation-based_2017} \cite{li_energy_2010} \cite{pambudi_impact_2017} \cite{pambudi_future_2016}.
-We will simulate \textit{dynamic transition scenarios} \cite{jebaraj_review_2006} \cite{pfenninger_energy_2014} , with realistic constraints and technology readiness of energy generation technologies (in terms of generation, transmission \& storage), aimed at minimizing carbon emissions.
-We will further extend previous work by combining multiple technologies in a single heterogeneous system.\\
-
-The TIMES (The Integrated MARKAL-EFOM System) model generator \cite{loulou_documentation_2005} \cite{seebregts_energy/environmental_2002} optimizes energy systems of a model using linear and mixed-linear algorithms while implementing user-defined objective functions (such as minimizing carbon emissions or costs) within user defined constraints such as energy generation demand.
-It will be used to simulate near-term energy transitions while focusing on reduction of carbon emissions.
-
+        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
+        \cite{loulou_documentation_2005} 
+        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
+        using linear and mixed-linear algorithms. A user-defined objective 
+        function (such as minimizing carbon emissions or costs) is solve within user defined constraints such as energy generation demand.  
 \end{block}
@@
 %----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
-
-\begin{block}{Acknowledgements}
-
-This research is being performed using funding received
-from the I\textsuperscript{2}CNER Programs under award number \textbf{<insert details here>}.
-
-\vspace{10mm}
-\begin{center}
-\begin{tabular}{cccc}
-\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
-%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
-\end{tabular}
-\end{center}
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	CONTACT INFORMATION
-%----------------------------------------------------------------------------------------
-
-\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
-\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
-
-\begin{alertblock}{Contact Information}
-\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
-\begin{itemize}
-
-	\item Web: \href{arfc.github.io}{arfc.github.io}
-	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
-\end{itemize}
-
-\end{alertblock}
-
-%----------------------------------------------------------------------------------------
 
@@
 	\scalebox{1.0}{
-		\begin{tikzpicture}[>=stealth,
+                \begin{tikzpicture}[>={Latex[width=6mm,length=6mm]}, 
                                 node distance=\figwidth, 
@@
 		\node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
-                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] (dat) {\texttt{DATA}\\regarding\\both\\i$^2$cner\\ \&\\ conventional\\technologies};
+                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] 
+                (dat) {\texttt{DATA}\\regarding both\\i$^2$cner and\\ conventional\\technologies};
                 \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
@@
 		\node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
+		\node [const, left=\figwidth of dem ] (init) {initial\\condition (2010)};
+		\node [const, above=0.5*\figwidth of dem] (infra) {infrastructure\\availability};
+		\node [const, left=\figwidth of infra] (sec) {consumption\\by sector};
+		\node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
         \begin{scope}[on background layer]
@@
 		\draw[->, ultra thick] (dat13) -- (dat);
-               % \draw[out=330,in=300,looseness=8] (mod) -- (mod);
+		\draw[->, ultra thick] (reg) -- (const);
+		\draw[->, ultra thick] (infra) -- (const);
+		\draw[->, ultra thick] (sec) -- (const);
+		\draw[->, ultra thick] (init) -- (const);
+                \path[->] (mod) edge [ultra thick,out=330,in=0,looseness=10] (mod) node[above right=0.1\figwidth and 0.8\figwidth] {simulate\\2010-2050};
+                %\draw (mod.east) to [->, ultra thick,looseness=10] (mod.south) node[above right=0.1\figwidth and 0.1\figwidth] {simulate\\2010-2050};
         \end{scope}
@@
 \end{block}
+
+%----------------------------------------------------------------------------------------
+%	CONTACT INFORMATION
+%----------------------------------------------------------------------------------------
+
+\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
+\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
+
+\begin{alertblock}{Contact Information}
+\begin{itemize}
+	\item Web: \href{arfc.github.io}{arfc.github.io}
+	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
+\end{itemize}
+
+\end{alertblock}
+
+%----------------------------------------------------------------------------------------
+%	ACKNOWLEDGEMENTS
+%----------------------------------------------------------------------------------------
+
+\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
+
+\begin{block}{Acknowledgements}
+
+This research is being performed using funding received
+from the International Institute for Carbon Neutral Energy Research (I$^2$CNER) 
+Initiative on Challenges in Energy Assessment and Energy Transitions at  the  
+University of Illinois under Director Petros Sofronis.
+
+\vspace{10mm}
+\begin{center}
+\begin{tabular}{cccc}
+\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
+%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
+\end{tabular}
+\end{center}
+
+\end{block}
+
 \end{column} % End of the final column

### 2018-01-03 docs/poster.tex
keep figure in its own doc

@@
 
-%=======================================================
-% FIGURE BEGINS
-%=========================================================
-
-\newlength{\figwidth}
-\setlength{\figwidth}{8cm}
-
-\begin{figure}
-	\centering
-	\scalebox{1.0}{
-                \begin{tikzpicture}[>={Latex[width=6mm,length=6mm]}, 
-                                node distance=\figwidth, 
-                                on grid, 
-                                align=center, 
-                                auto]
-		% Place nodes
-		\node [block] (times) {\textbf{TIMES Model Generator}};
-		\node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
-                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] 
-                (dat) {\texttt{DATA}\\regarding both\\i$^2$cner and\\ conventional\\technologies};
-                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
-                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
-                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
-                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
-                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
-                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
-                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
-                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
-                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
-                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
-                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
-                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
-                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
-		\node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
-		\node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
-		\node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
-		\node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
-		\node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
-		\node [const, left=\figwidth of dem ] (init) {initial\\condition (2010)};
-		\node [const, above=0.5*\figwidth of dem] (infra) {infrastructure\\availability};
-		\node [const, left=\figwidth of infra] (sec) {consumption\\by sector};
-		\node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
-        \begin{scope}[on background layer]
-		\draw[->, ultra thick] let \p1=($(times)-(dat)$) in (dat) -- +(0,\y1)-- +(times);
-		\draw[->, ultra thick] (of) -- (times);
-		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
-		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
-                \draw[->, ultra thick] (times) -- (mod);
-		\draw[->, ultra thick] (min) -- (of);
-		\draw[->, ultra thick] (max) -- (of);
-		\draw[->, ultra thick] (dem) -- (const);
-		\draw[->, ultra thick] (dat1) -- (dat);
-		\draw[->, ultra thick] (dat2) -- (dat);
-		\draw[->, ultra thick] (dat3) -- (dat);
-		\draw[->, ultra thick] (dat4) -- (dat);
-		\draw[->, ultra thick] (dat5) -- (dat);
-		\draw[->, ultra thick] (dat6) -- (dat);
-		\draw[->, ultra thick] (dat7) -- (dat);
-		\draw[->, ultra thick] (dat8) -- (dat);
-		\draw[->, ultra thick] (dat9) -- (dat);
-		\draw[->, ultra thick] (dat10) -- (dat);
-		\draw[->, ultra thick] (dat11) -- (dat);
-		\draw[->, ultra thick] (dat12) -- (dat);
-		\draw[->, ultra thick] (dat13) -- (dat);
-		\draw[->, ultra thick] (reg) -- (const);
-		\draw[->, ultra thick] (infra) -- (const);
-		\draw[->, ultra thick] (sec) -- (const);
-		\draw[->, ultra thick] (init) -- (const);
-                \path[->] (mod) edge [ultra thick,out=330,in=0,looseness=10] (mod) node[above right=0.1\figwidth and 0.8\figwidth] {simulate\\2010-2050};
-                %\draw (mod.east) to [->, ultra thick,looseness=10] (mod.south) node[above right=0.1\figwidth and 0.1\figwidth] {simulate\\2010-2050};
-        \end{scope}
- \end{tikzpicture}
-	}
-	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
-\end{figure}
-
+        \input{model-fig}
 \end{column} % End of the first column

### 2018-01-03 docs/model-fig.tex

%=======================================================
% FIGURE BEGINS
%=========================================================

\newlength{\figwidth}
\setlength{\figwidth}{8cm}

\begin{figure}
    \centering
    \scalebox{1.0}{
                \begin{tikzpicture}[>={Latex[width=6mm,length=6mm]},
                                node distance=\figwidth,
                                on grid,
                                align=center,
                                auto]
        % Place nodes
        \node [block] (times) {\textbf{TIMES Model Generator}};
        \node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times]
                (dat) {\texttt{DATA}\\regarding both\\i$^2$cner and\\ conventional\\technologies};
                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
        \node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
        \node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
        \node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
        \node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
        \node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
        \node [const, left=\figwidth of dem ] (init) {initial\\condition (2010)};
        \node [const, above=0.5*\figwidth of dem] (infra) {infrastructure\\availability};
        \node [const, left=\figwidth of infra] (sec) {consumption\\by sector};
        \node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
        \begin{scope}[on background layer]
        \draw[->, ultra thick] let \p1=($(times)-(dat)$) in (dat) -- +(0,\y1)-- +(times);
        \draw[->, ultra thick] (of) -- (times);
        %\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
        \draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
                \draw[->, ultra thick] (times) -- (mod);
        \draw[->, ultra thick] (min) -- (of);
        \draw[->, ultra thick] (max) -- (of);
        \draw[->, ultra thick] (dem) -- (const);
        \draw[->, ultra thick] (dat1) -- (dat);
        \draw[->, ultra thick] (dat2) -- (dat);
        \draw[->, ultra thick] (dat3) -- (dat);
        \draw[->, ultra thick] (dat4) -- (dat);
        \draw[->, ultra thick] (dat5) -- (dat);
        \draw[->, ultra thick] (dat6) -- (dat);
        \draw[->, ultra thick] (dat7) -- (dat);
        \draw[->, ultra thick] (dat8) -- (dat);
        \draw[->, ultra thick] (dat9) -- (dat);
        \draw[->, ultra thick] (dat10) -- (dat);
        \draw[->, ultra thick] (dat11) -- (dat);
        \draw[->, ultra thick] (dat12) -- (dat);
        \draw[->, ultra thick] (dat13) -- (dat);
        \draw[->, ultra thick] (reg) -- (const);
        \draw[->, ultra thick] (infra) -- (const);
        \draw[->, ultra thick] (sec) -- (const);
        \draw[->, ultra thick] (init) -- (const);
                \path[->] (mod) edge [ultra thick,out=330,in=0,looseness=10] (mod) node[above right=0.1\figwidth and 0.8\figwidth] {simulate\\2010-2050};
                %\draw (mod.east) to [->, ultra thick,looseness=10] (mod.south) node[above right=0.1\figwidth and 0.1\figwidth] {simulate\\2010-2050};
        \end{scope}
 \end{tikzpicture}
    }
    \caption{Basic methodology for dynamic simulation of Japan's energy system.}
\end{figure}

### 2018-01-04 doc/poster.tex
closes #6
Former-commit-id: a1f7bc708ef2cd06dcbec85e63ba10690ed615b7

--- 2018-01-03 docs/poster.tex
@@
 \usepackage{tikz}
+\usepackage{chronology}
 \usetikzlibrary{arrows.meta}
@@
 
-\begin{column}{\onecolwid} % The first column
+\begin{column}{\twocolwid} % The first two columns, two cols wide
+\begin{columns}[t,totalwidth=\twocolwid] % Split up the first column into two, 
+\begin{column}{\onecolwid} % The first column, one col wide
 
@@
         using linear and mixed-linear algorithms. A user-defined objective 
-        function (such as minimizing carbon emissions or costs) is solve within user defined constraints such as energy generation demand.  
+        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.  
 \end{block}
@@
 \end{column} % End of the first column
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
 
@@
 
-%--------------------------------------------------------
-% CHALLENGES
-%---------------------------------------------------------
-\begin{block}{Challenges}
-   Reliable data for each technology's deployment and operation is required, such as:
-
-\end{block}
-
 %----------------------------------------------------------------------------------------
 
-\end{column} % End of column 2
+\end{column} % End of column 2, top half
+\end{columns}
+%=======================================================
+% Double Wide Figure Column 
+%=========================================================
+\input{model-fig}
 
-\begin{column}{\sepwid}\end{column} % Empty spacer column
+\end{column} % End of wide column, total length
 
 \begin{column}{\onecolwid} % The third column
+
+%--------------------------------------------------------
+% PROJECT TIMELINE
+%---------------------------------------------------------
+\begin{block}{Timeline}
+        \input{timeline}
+\end{block}
 
@@
 
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of the third column
-
-\end{columns} % End of all the columns in the poster
-
-%=======================================================
-% Double Wide Figure Column 
-%=========================================================
-\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
-
-\begin{column}{\twocolwid} % The double wide figure column
-
-        \input{model-fig}
-\end{column} % End of the first column
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
-
-\begin{column}{\onecolwid} % The second column
-
 \begin{block}{References}
@@
 \end{block}
+
+%----------------------------------------------------------------------------------------
 

### 2018-01-12 doc/poster.tex
we are required to include the division name.

@@
 
-\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
+\title{Dynamic Transition Analysis with TIMES:\\ 
+I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
 
-\author{Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
+\author{Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}\\Energy Analysis Division}
 \institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}

### 2018-01-12 doc/poster.tex
I'm not sure we do want to investigate scenarios where decarbonization isn't the main priority

--- 2018-01-04 doc/poster.tex
@@
 
-\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
+\title{Dynamic Transition Analysis with TIMES\\ 
+I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
 
-\author{Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
+\author{\textbf{\textsc{Energy Analysis Division}}\\
+        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
 \institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
@@
 \item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.
-
 \item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
-
-\item Simulations will quantify system sensitivity to technology readiness, and also account for secondary scenarios where decarbonization is not the main priority.
+\item Simulations will quantify system sensitivity to technology readiness.
 

### 2018-01-12 doc/poster.tex
title shouldn't include the initiative name
Former-commit-id: 035b4e0ce9e5e4dee0c04e5a5c9c6abccbd99ef1

@@
 
-\title{Dynamic Transition Analysis with TIMES\\ 
-I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title
+\title{Dynamic Transition Analysis with TIMES}
 
-\author{\textbf{\textsc{Energy Analysis Division}}\\
+\author{\textbf{Energy Analysis Division}\\
+        \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy 
+        Assessment and Energy Transitions}\\
         Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
@@
 
-\item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.
+\item Dynamic simulation of Japan's energy system transition in the TIMES model 
+        generator will help develop near-term decarbonization strategies.
 \item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.

### 2018-01-12 doc/poster.tex
the poster size was wrong.
Former-commit-id: 1d2d535ae3206e8f27a81032157657208435e7f1

@@
 
-\usepackage[scale=1.0]{beamerposter} % Use the beamerposter package for laying out the poster
+\usepackage[scale=0.9]{beamerposter} % Use the beamerposter package for laying out the poster
 \usetheme{confposter} % Use the confposter theme supplied with this template
@@
 \newlength{\threecolwid}
-\setlength{\paperwidth}{36in} % A0 width: 46.8in
-\setlength{\paperheight}{48in} % A0 height: 33.1in
-\setlength{\textwidth}{34in} % A0 width: 46.8in
-\setlength{\textheight}{46in} % A0 height: 33.1in
+\setlength{\paperwidth}{33.1in} % A0 width: 46.8in
+\setlength{\paperheight}{46.8in} % A0 height: 33.1in
+\setlength{\textwidth}{33.1in} % A0 width: 46.8in
+\setlength{\textheight}{46.8in} % A0 height: 33.1in
 \setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
@@
 \setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
-\setlength{\topmargin}{-0.5in} % Reduce the top margin size
+\setlength{\topmargin}{-1in} % Reduce the top margin size
 %-----------------------------------------------------------
@@
 
-\author{\textbf{Energy Analysis Division}\\
-        \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy 
-        Assessment and Energy Transitions}\\
+\author{
+       % \textbf{ENERGY ANALYSIS DIVISION}\\
+       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
         Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
@@
 
-Evaluate potential impact of novel energy technologies within Japan's energy system. Specifically:
+\begin{description}
+{\large 
+        \item[\textbf{Division:}] Energy Analysis Division
+        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
+        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
+\item[\textbf{Milestones:}] ~\\}
         \begin{itemize}
-	\item Guide practical near term (2010-2050) transition strategies.
         \item Minimize carbon emissions within realistic constraints.
+        \item Optimize realistic 2010-2050 decarbonization roadmaps.
 	\item Identify high impact technologies.
-	\item Assess role of technology readiness.
+        \item Identify potential transition bottlenecks.
+        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
+        \item Quantify system sensitivity to technology readiness.
 	\item Predict impediments to strategically optimal technology deployment.
-	\item Identify ideal timelines for energy system deployment, infrastructure development, high impact R\&D investment.
 	\end{itemize}
+\end{description}
 
@@
 
-\begin{block}{Methodology}
-        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
-        \cite{loulou_documentation_2005} 
-        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
-        using linear and mixed-linear algorithms. A user-defined objective 
-        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.  
-\end{block}
-
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-%	Anticipated Results
-%----------------------------------------------------------------------------------------
+\begin{block}{Methodology}
+        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
+        \cite{loulou_documentation_2005} 
+        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
+        using linear and mixed-linear algorithms. A user-defined objective 
+        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.
 
-\begin{block}{Anticipated Results}
-
- \begin{itemize}
-   \item Analysis results can be filtered by sector (commercial, industrial, residential, building etc) or by region.
-
-   \item Many metrics are automatically postprocessed- such as energy intensity, thermal energy efficiency, transmission capacity.
-
-   \item Technology deployment transitions driven by constrained optimization will have valuable strategic value.
-
- \end{itemize}
+\begin{description}
+        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
+                 consumption by sector (commercial, industrial, residential, 
+                 building etc). 
+         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
+         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
+                 (i.e. energy intensity, thermal energy efficiency, 
+                 transmission capacity).. 
+         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
+                 transition as a constrained optimization problem will
+                 drive insights.
+ \end{description}
 
 \end{block}
-
-%----------------------------------------------------------------------------------------
-%	RESULTS
-%----------------------------------------------------------------------------------------
-
-        \begin{alertblock}{Impact}
-        \large Results will:
-	\begin{itemize}
-        \item {Optimize realistic decarbonization roadmaps.}
-        \item {Identify potential transition bottlenecks.}
-        \item {Help Japan's policymakers create timelines for R\&D investment and infrastructure development.}
-        \item {Quantify system sensitivity to technology readiness.}
-	\end{itemize}
-        \end{alertblock}
-
-%----------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------
+%	TAKE AWAY
+%----------------------------------------------------------------------------------------
+
+        \begin{alertblock}{Take Aways}
+	\begin{itemize}
+                \item Dynamic simulation of Japan's energy system transition in 
+                        the TIMES model generator will help develop near-term 
+                        decarbonization strategies.
+                \item Policymakers will benefit from identification of high 
+                        impact technologies, and creation of R\&D investment 
+                        and infrastructure development timelines.  
+                \item Simulations will quantify system sensitivity to 
+                        technology readiness. 
+                \item Dynamic analysis will identify potential transition 
+                        bottlenecks.
+	\end{itemize}
+        \end{alertblock}
+
 %--------------------------------------------------------
@@
         \input{timeline}
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	CONCLUSION
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Summary}
-\begin{itemize}
-
-\item Dynamic simulation of Japan's energy system transition in the TIMES model 
-        generator will help develop near-term decarbonization strategies.
-\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
-\item Simulations will quantify system sensitivity to technology readiness.
-
-\end{itemize}
-
 \end{block}

### 2018-01-12 doc/poster.tex

@@
 \usetikzlibrary{positioning}
+
+%-----------------------------------------------------------
+% KNOWN ISSUE IN TIKZ MATH: tiny big symbols, like sum.
+%-----------------------------------------------------------
+
+% declare `cmex` to be arbitrary scalable
+\DeclareFontShape{OMX}{cmex}{m}{n}{
+  <-7.5> cmex7
+  <7.5-8.5> cmex8
+  <8.5-9.5> cmex9
+  <9.5-> cmex10
+}{}
+
+\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
+\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}
 
@@
                  (i.e. energy intensity, thermal energy efficiency, 
-                 transmission capacity).. 
+                 transmission capacity). 
          \item[\textbf{Constrained Optimization}] Modeling technology deployment 
@@
 
+         The key objective function is minimization of carbon emissions in 2050 
+         and a key
+         constraint will be that deployed generation capacity must meet energy 
+         demand. This can na\"ively be written:
+
+\begin{align}
+        \intertext{minimize:}
+        &\sum_g^G C_g x_g 
+        \intertext{subject to:}
+        &\sum_g^Gx_g = d
+        \intertext{where}
+        C_g =& \mbox{ carbon emissions from generation component g}\\
+        x_g =& \mbox{ deployment of generation component g}\\
+        d =& \mbox{ generation demand}
+\end{align}
+
+A simple \textbf{static} formulation is straightforward to write, as above.  
+However this  formulation is quickly complicated by including \textbf{dynamic 
+time} as well as additional constraints (energy storage, variable demand, 
+$CO_2$ sequestration, efficiency, costs, etc.)
 \end{block}

### 2018-08-02 doc/2019-01-poster/poster.tex

--- 2018-01-12 doc/poster.tex
@@
 \setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
+\setbeamertemplate{caption}[numbered]
+
 % Many more colors are available for use in beamerthemeconfposter.sty
@@
 \usepackage{graphicx}  % Required for including images
+\usepackage{hyperref}
+\usepackage{cite}
 
@@
 
+%-----------------------------------------------------------
+% KNOWN ISSUE IN TIKZ MATH: tiny big symbols, like sum.
+%-----------------------------------------------------------
+
+% declare `cmex` to be arbitrary scalable
+\DeclareFontShape{OMX}{cmex}{m}{n}{
+  <-7.5> cmex7
+  <7.5-8.5> cmex8
+  <8.5-9.5> cmex9
+  <9.5-> cmex10
+}{}
+
+\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
+\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}
+
+\usepackage{amssymb}
+\usepackage{pifont}
+\usepackage{xcolor}
+\newcommand{\greencheck}{{\color{green}\checkmark}}
+\newcommand{\xmark}{{\color{red}\ding{55}}}
+
 \setbeamertemplate{bibliography item}[text]
+
+\makeatletter
+\def\beamer@andinst{\\[0em]}
+\makeatother
 
@@
        % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
-        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
-\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
+        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
+\institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
 %----------------------------------------------------------------------------------------
@@
 various world regions using \textbf{static} scenario analyses 
-\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
-We will simulate \textbf{dynamic} transition scenarios 
-\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
-emissions in Japan by 2050. These scenarios will include realistic constraints 
-regarding technology readiness (in terms of generation, transmission \& 
-storage) and will combine multiple technologies in a single heterogeneous 
-system model.
+\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
+We are simulating \textbf{dynamic} transition scenarios 
+\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
+emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
+
+Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
+\hfill \break
+
 \end{block}
+
+%\vspace{77mm}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nuc_elc}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
+\label{s1e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nuc_co2}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
+\label{s1c}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nonuc_elc}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
+\label{s2e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nonuc_co2}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
+\label{s2c}
+\end{figure}
 
@@
         using linear and mixed-linear algorithms. A user-defined objective 
-        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.
+        function is solved within user defined constraints.\\
+\textbf{Key assumptions:}
 
-\begin{description}
-        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
-                 consumption by sector (commercial, industrial, residential, 
-                 building etc). 
-         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
-         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
-                 (i.e. energy intensity, thermal energy efficiency, 
-                 transmission capacity).. 
-         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
-                 transition as a constrained optimization problem will
-                 drive insights.
- \end{description}
+\begin{itemize}
+        \item\textbf{Objective function:} System cost.
+
+         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.
+
+         \item Hydropower and geothermal capacity held constant \cite{noauthor_energy_2018}.
+
+         \item Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.
+
+         \item All new nuclear reactors are ABWRs \cite{rothwell_real_2006}.
+
+         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan.
+\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}
+
+         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}
+
+         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030.
+Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies.
+\cite{kato_energy_2016} \cite{acar_comparative_2014} \\
+
+ \end{itemize}
+
+We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break
+
+\begin{tabular}{c c c c c}
+
+\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
+                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
+1                 & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
+2                 & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
+3                 & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
+4                 & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
+\end{tabular}
 
 \end{block}
+
+%\vspace{65 mm}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{legend}
+%\caption{Legend}
+\label{legend}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nuc_elc}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
+\label{s3e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nuc_co2}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
+\label{s3c}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nonuc_elc}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
+\label{s4e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nonuc_co2}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
+\label{s4c}
+\end{figure}
 
@@
 %=========================================================
-\input{model-fig}
+%\input{model-fig}
 
@@
 %----------------------------------------------------------------------------------------
-
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{cost}
+\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
+\label{cost}
+\end{figure}
          \begin{alertblock}{Take Aways}
 	\begin{itemize}
-                \item Dynamic simulation of Japan's energy system transition in 
-                        the TIMES model generator will help develop near-term 
-                        decarbonization strategies.
-                \item Policymakers will benefit from identification of high 
-                        impact technologies, and creation of R\&D investment 
-                        and infrastructure development timelines.  
-                \item Simulations will quantify system sensitivity to 
-                        technology readiness. 
-                \item Dynamic analysis will identify potential transition 
-                        bottlenecks.
+                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.
+
+                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.
+
+                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.
+
+                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
 	\end{itemize}
@@
 %---------------------------------------------------------
-\begin{block}{Timeline}
-        \input{timeline}
+\begin{block}{Limitations and Future work}
+    \begin{itemize}
+
+    \item Model focuses entirely on \textbf{electricity supply sector}.
+
+    \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.
+
+    \item No limit on penetration of solar or wind except maximum potential.
+
+    \item Annual timesteps and annually averaged capacity factors limit ability to capture seasonal and daily variation in wind and solar.
+
+    \item Capture realistic, gradual transition behaviour and fluctuations in demand due to population decline in Japan.
+
+    \item Incorporation of more I$^2$CNER technologies.
+
+    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.
+
+    \item Detailed cost analysis
+
+    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.
+
+    \end{itemize}
 \end{block}
@@
 \begin{block}{References}
-        {\footnotesize\bibliographystyle{abbrv} 
-        \bibliography{poster}}
+        {\footnotesize\bibliographystyle{ieeetr} 
+        \bibliography{2019-chaube-i2cner-poster}}
 \end{block}

### 2018-09-24 doc/2018-09-report/2018-09-i2cner-report.tex
Added September report. Reorganized "doc" folder

\documentclass[14pt,a4paper]{article} %openany
\usepackage[affil-it]{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{courier}
\usepackage{verbatim}
\usepackage{url}
\usepackage{float}
\usepackage{array}
\usepackage{breakcites}
\usepackage{gensymb}
\usepackage{booktabs,tabularx}
\usepackage{listings}
\usepackage{appendix}
\usepackage{blindtext}
\title{I\textsuperscript{2}CNER Project Report \\ Dynamic Transition Analysis With TIMES}
\date{September 2018}
\author{Anshuman Chaube\\UIUC}
\begin{document}
\maketitle

\section{Introduction}
We initiated a project in January 2018 to simulate dynamic transition scenarios for the energy industry in Japan to suggest pathways for minimizing carbon emissions. This report is a summary of the progress we have made so far, the challenges we currently face, and the future direction of this research.

\section{Progress Summary}

\subsection{Accomplishments}

The tasks that we performed can be divided into two categories: technical tasks associated with implementation of details and features in our model, and data collection and organization. Our accomplishments have been:

\begin{enumerate}
\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan’s energy industry, we chose VEDA, a TIMES (The Integrated MARKAL-EFOM System) <cite something> model generator. We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes. Therefore, we took the time to develop our own model files, which we have progressively refined since then. Major impediments to this process were the quality of documentation and customer-support provided by VEDA developers, which delayed the process.
At the same time, we collected data pertaining to electricity generation and carbon emissions.

\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the EDMC databank, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan. \\

While collecting this data, we noticed that the EDMC databank that we have been relying on has no data for the amount of electricity generated from individual fossil fuels for the years 2011-12. Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category titled “thermal”. Further, the 2016 data seems slightly inconsistent across different data tables in the EDMC databank. The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.

\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources (EIA, IEA). We have also included processes for the projected growth of nuclear, solar and wind based on data from the Federation of <bleh>, JWPA, and <some solar body.>

\item \textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan. The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel’s energy cycle having different emission coefficients. We estimated the missing figures based on previous years’ trends (cite EDMC 2012 handbook) and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.

\end{enumerate}

\subsection{Results}

	Our model focuses on the electricity generation sector. The following assumptions and limitations are present in our model:

\begin{enumerate}

\item All the energy generated by a given process is transferred to the grid without losses to satisfy the demand process. Since the EDMC data has values in terms of units of electrical energy produced (GWh), we have had no need for incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors.

\item The coal and natural gas capacities are held constant throughout the simulation.

\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the EDMC data indicating declining use of oil.

\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi’s ABWRs, which are under consideration for construction <cite elec review>, with efficiency values based on existing ABWRs in operation. It has been assumed that there can be as many as 22 ABWRs constructed in between 2020-2100, with the number of reactors constructed during the earlier years based on the number of projects currently under consideration for construction, and the pace of construction based on similar reactors constructed in Japan. All nuclear technology, current or future, has a finite lifetime based realistic values <cite hitachi>.

\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking. The maximum capacity implemented is based on <>

\item Wind –The offshore and onshore wind capacity potential for Japan is based on the report by <>.

\item Hydropower – held constant at current levels.

\item Geothermal – expanded to maximum potential <cite>.

\item The values of electricity generated from coal, oil and natural gas in 2011 and 2012 have been estimated using previous years’ values and CO\textsubscript{2} emissions.

\item The CO\textsubscript{2} emission constraints implemented are very lax and not representative of any constraints that the Japanese government or I\textsuperscript{2}CNER wish to implement. This feature of the model is still under-development, since we do not have accurate data for electricity generated from fossil fuels for the years 2011, 2012, and 2016.

\end{enumerate}

Based on these assumptions, the preliminary transition scenario gives the following distribution of electric utilities to meet the supplied demand process:

%\begin{figure}[H]
%\centering
%\includegraphics[scale=0.4]{q1_1_1}
%\caption{The partial sum $g ^N (x)$ for %$f_1 (x)$ for $N=1,2,...10$.}
%\end{figure}

The emitted CO\textsubscript{2} values for the period 2011-16 are as follows. The error is at most 5.7\% (see fig), which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.

\subsection{Post Hoc Analysis and Challenges}

The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers. The primitive, black-box like nature of the software often produces inexplicable, illogical results and inhibits efficient debugging. Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule, by about three months. \\

In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, EDMC has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called “thermal” in its databank. This complicates the process of estimating CO\textsubscript{2} emissions from these energy sources, since each fossil fuel has a different emission coefficient. Losing the primary data that we have been relying on has affected our pace and the reproducibility of our research significantly. The EDMC databank figures in GWh, instead of in tons of coal or oil, have influenced our model’s simplistic design, as discussed previously. Our efforts to find similar data have been unsuccessful. Switching to data in terms of the quantity of raw fossil fuels consumed instead of GWh of electricity produced may require a substantial revision of our model.

\section{Future Work} 
Considering these challenges, any future efforts on this project will be concentrated in the following areas, in this order of precedence:

\begin{itemize}

\item Acquisition of accurate data for electricity generation from fossil fuels. The most promising source now seems to be the EDMC 2017 handbook.

\item Refining fossil fuel-based electricity generation values and hence CO\textsubscript{2} emission values.

\item Implementation of realistic CO\textsubscript{2} constraints based on Kyoto protocols and I\textsuperscript{2}CNER targets.

\item Refining the demand process and aligning it more closely with realistic projections.

\item Incorporation of I\textsuperscript{2}CNER technologies in the model.

\item Incorporating capacity constraints on technologies such as nuclear power, geothermal power, carbon sequestration etc to model different scenarios.

\item Sensitivity analysis of model parameters to analyze the relative impact of incorporated technologies on the decarbonization goal.

\end{itemize}

In case we must switch to more accurate data that is different from the EDMC figures, we may have to modify the model accordingly. For instance, if the data is in terms of units of fossil fuels consumed, we must model the appropriate fossil fuel conversion processes with the relevant conversion factors and efficiencies. This will further delay the project by another one to two months.

%\begin{thebibliography}{1}

%\bibitem{dude} Duderstadt and Hamilton, %"Nuclear Reactor Analysis", 1976, John %Wiley and Sons.

%\end{thebibliography}

\end{document}

### 2018-09-28 doc/2018-09-report/2018-09-i2cner-report.tex
Corrected -, ", '. Added bib file
Former-commit-id: 51c2409ff0c3a1438730b54e6583e9fdd42a008d [formerly 598cf862a9d551409e6d702b3ae5b53dfae4c034]
Former-commit-id: 0cc918b0cdd6079c061f818680ca1367ab792c1d

@@
 \usepackage{rotating}
-\usepackage{amsmath}
+%\usepackage{bibtex}
+%\usepackage[utf8]{inputenc}
+%\usepackage[english]{babel}
 \usepackage{adjustbox}
@@
 \usepackage{gensymb}
+\usepackage{bib}
 \usepackage{booktabs,tabularx}
@@
 \usepackage{blindtext}
+
+\bibliographystyle{unsrt}
+
+\bibliography{2018-chaube-i2cner-report-sept}
+
 \title{I\textsuperscript{2}CNER Project Report \\ Dynamic Transition Analysis With TIMES}
@@
 \begin{enumerate}
-\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan’s energy industry, we chose VEDA, a TIMES (The Integrated MARKAL-EFOM System) <cite something> model generator.
+\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a TIMES (The Integrated MARKAL-EFOM System) \cite{loulou_documentation_2005} \cite{gargiulo_et_al._documentation_nodate}model generator.
 We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes.
@@
 
-\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the EDMC databank, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
+\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the EDMC databank\cite{edmc_ieej_edmc_nodate}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
 \\
@@
 While collecting this data, we noticed that the EDMC databank that we have been relying on has no data for the amount of electricity generated from individual fossil fuels for the years 2011-12.
-Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category titled “thermal”.
+Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category titled "thermal".
 Further, the 2016 data seems slightly inconsistent across different data tables in the EDMC databank.
@@
 
-\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources (EIA, IEA).
-We have also included processes for the projected growth of nuclear, solar and wind based on data from the Federation of <bleh>, JWPA, and <some solar body.>
+\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources \cite{edmc_ieej_edmc_nodate} \cite{iea_iea_2017} \cite{japan_electric_power_information_centerjepic_japan_2017}.
+We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
+\cite{publicover_japan_2017} \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{the_geothermal_research_society_of_japan_geothermal_nodate} \cite{heger_wind_2016} \cite{japan_nuclear_energy_safety_organization_operational_2013} \cite{the_federation_of_electric_power_companies_of_japan_electricity_2017}
 
 \item \textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan.
-The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel’s energy cycle having different emission coefficients.
-We estimated the missing figures based on previous years’ trends (cite EDMC 2012 handbook) and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.
+The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
+We estimated the missing figures based on previous years' trends \cite{edmc_ieej_edmc_nodate} \cite{ministry_of_the_environment_japan_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.
 
@@
 
-\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the EDMC data indicating declining use of oil.
+\item The levelized cost of electricity (LCOE) for fossil fuels has been held constant throughout the simulation \cite{chapman_energy_2018} \cite{lazard_lazards_2017} \cite{iea_iea_2017}.
+LCoE projections for wind and solar have been incorporated \cite{lazard_lazards_2017}.
+However, the implementation of costs associated with electricity generation is still under-development.
 
-\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi’s ABWRs, which are under consideration for construction <cite elec review>, with efficiency values based on existing ABWRs in operation.
+\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the EDMC data \cite{edmc_ieej_edmc_nodate} indicating declining use of oil.
+
+\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's ABWRs \cite{ge_hitachi_nuclear_energy_advanced_2007}, which are under consideration for construction \cite{the_federation_of_electric_power_companies_of_japan_electricity_2017}, with efficiency values based on existing ABWRs in operation.
 It has been assumed that there can be as many as 22 ABWRs constructed in between 2020-2100, with the number of reactors constructed during the earlier years based on the number of projects currently under consideration for construction, and the pace of construction based on similar reactors constructed in Japan.
-All nuclear technology, current or future, has a finite lifetime based realistic values <cite hitachi>.
+All nuclear technology, current or future, has a finite lifetime based realistic values.
 
-\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking. The maximum capacity implemented is based on <>
-
-\item Wind –The offshore and onshore wind capacity potential for Japan is based on the report by <>.
+\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking.
 
@@
 
-\item Geothermal – expanded to maximum potential <cite>.
+\item Geothermal is expanded to its maximum potential \cite{the_geothermal_research_society_of_japan_geothermal_nodate}.
 
-\item The values of electricity generated from coal, oil and natural gas in 2011 and 2012 have been estimated using previous years’ values and CO\textsubscript{2} emissions.
+\item The values of electricity generated from coal, oil and natural gas in 2011 and 2012 have been estimated using previous years' values and CO\textsubscript{2} emissions.
 
 \item The CO\textsubscript{2} emission constraints implemented are very lax and not representative of any constraints that the Japanese government or I\textsuperscript{2}CNER wish to implement.
-This feature of the model is still under-development, since we do not have accurate data for electricity generated from fossil fuels for the years 2011, 2012, and 2016.
+Since we do not have accurate data for electricity generated from fossil fuels for the years 2011, 2012, and 2016, we have been focusing our efforts on modelling CO\textsubscript{2} emissions from previous years accurately.
 
@@
 
-In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, EDMC has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called “thermal” in its databank.
+In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, EDMC has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called "thermal" in its databank.
 This complicates the process of estimating CO\textsubscript{2} emissions from these energy sources, since each fossil fuel has a different emission coefficient.
 Losing the primary data that we have been relying on has affected our pace and the reproducibility of our research significantly.
-The EDMC databank figures in GWh, instead of in tons of coal or oil, have influenced our model’s simplistic design, as discussed previously.
+The EDMC databank figures in GWh, instead of in tons of coal or oil, have influenced our model's simplistic design, as discussed previously.
 Our efforts to find similar data have been unsuccessful.
@@
 
-%\begin{thebibliography}{1}
+%\bibliographystyle{plain}
 
-%\bibitem{dude} Duderstadt and Hamilton, %"Nuclear Reactor Analysis", 1976, John %Wiley and Sons.
-
-%\end{thebibliography}
+%\printbibliography
 

### 2018-09-28 doc/2018-09-report/2018-09-i2cner-report.tex
added references, title page
Former-commit-id: ccb48af4577408a8fbe2cb3629694fbebbade309 [formerly 535dd5f0ef9b13796d92840c5fc5af558c9bba0a]
Former-commit-id: eacd016db02522a934e54ac0da0a3d78a37378ae

@@
 \usepackage{gensymb}
-\usepackage{bib}
+%\usepackage[backend=biber]{biblatex}
 \usepackage{booktabs,tabularx}
@@
 \usepackage{appendix}
+\usepackage{cite}
 \usepackage{blindtext}
+\usepackage[utf8]{inputenc} % Required for inputting international characters
+\usepackage[T1]{fontenc} % Output font encoding for international characters
+\usepackage{mathpazo} % Palatino font
+\usepackage{graphicx} % For the logo
 
-\bibliographystyle{unsrt}
+%\bibliographystyle{numeric}
 
-\bibliography{2018-chaube-i2cner-report-sept}
+\begin{document}
 
-\title{I\textsuperscript{2}CNER Project Report \\ Dynamic Transition Analysis With TIMES}
-\date{September 2018}
-\author{Anshuman Chaube\\UIUC}
-\begin{document}
-\maketitle
+\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
+    \newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
+
+    \center % Centre everything on the page
+
+    %------------------------------------------------
+    %    Title
+    %------------------------------------------------
+
+    \HRule\\[0.2cm]
+
+     \begin{minipage}{0.4\textwidth}
+        \includegraphics[width=\textwidth]{arfc-logo}
+        \end{minipage}%
+        \begin{minipage}{0.6\textwidth}
+        {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With TIMES\end{flushright}}
+        {\begin{flushright}\large\textit{ I\textsuperscript{2}CNER Project Report}\end{flushright}}
+
+        \end{minipage}
+
+    \vspace{0.2cm}
+    \HRule
+    \vspace{0.5cm}
+
+    % If you don't want a supervisor, uncomment the two lines below and comment the code above
+    %{\large\textit{Author}}\\
+    %John \textsc{Smith} % Your name
+
+    %------------------------------------------------
+    %    Report Number
+    %------------------------------------------------
+    \vspace{1cm}
+    \textsc{\LARGE\bfseries UIUC-ARFC-2018-01} % Replace YYYY with the year, NN with report index
+    \vspace{0.5cm}
+
+    %------------------------------------------------
+    %    Date
+    %------------------------------------------------
+
+    \vspace{0.5cm} % Position the date further down the remaining page
+    {\large\today} % Date, change the \today to a set date if you want to be precise
+    \vspace{0.5cm}
+
+%------------------------------------------------
+    %    Headings
+    %------------------------------------------------
+
+    \textsc{\LARGE Advanced Reactors and Fuel Cycles}\\[0.25cm] % Research Group
+
+    \textsc{\large Dept. of Nuclear, Plasma, \& Radiological Engineering}\\% Department
+
+    \textsc{\large University of Illiois at Urbana-Champaign}\\ % University
+
+    %------------------------------------------------
+    %    Logo
+    %------------------------------------------------
+
+    \vspace{0.5cm}
+    \includegraphics[scale=0.2]{arfc_logo}
+    \includegraphics[scale=0.3]{i2cner_logo}
+    \includegraphics[scale=0.2]{wpi_logo}
+    \includegraphics[scale=0.04]{ku_logo}\\[1cm] % Include a department/university logo - this will require the graphicx package
+
+    %----------------------------------------------------------------------------------------
+
+    %------------------------------------------------
+    %   Funding 
+    %------------------------------------------------
+    % For this section, either use \vfill to fill the space 
+    % or insert funding acknowledgement
+    \textit{The authors gratefully acknowledge the support of the International Institute for Carbon
+Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.}
+
+\end{titlepage}
 
@@
 \begin{enumerate}
-\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a TIMES (The Integrated MARKAL-EFOM System) \cite{loulou_documentation_2005} \cite{gargiulo_et_al._documentation_nodate}model generator.
+\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a TIMES (The Integrated MARKAL-EFOM System) \cite{loulou_documentation_2005} \cite{gargiulo_documentation_2005} generator.
 We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes.
@@
 
-\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the EDMC databank\cite{edmc_ieej_edmc_nodate}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
+\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the EDMC databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
 \\
@@
 
-\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources \cite{edmc_ieej_edmc_nodate} \cite{iea_iea_2017} \cite{japan_electric_power_information_centerjepic_japan_2017}.
+\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources \cite{noauthor_energy_2018} \cite{noauthor_iea_2017} \cite{noauthor_japan_2017}.
 We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
-\cite{publicover_japan_2017} \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{the_geothermal_research_society_of_japan_geothermal_nodate} \cite{heger_wind_2016} \cite{japan_nuclear_energy_safety_organization_operational_2013} \cite{the_federation_of_electric_power_companies_of_japan_electricity_2017}
+\cite{publicover_japan_2017} \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}
 
@@
 The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
-We estimated the missing figures based on previous years' trends \cite{edmc_ieej_edmc_nodate} \cite{ministry_of_the_environment_japan_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.
+We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018} \cite{noauthor_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.
 
@@
 
-\item The levelized cost of electricity (LCOE) for fossil fuels has been held constant throughout the simulation \cite{chapman_energy_2018} \cite{lazard_lazards_2017} \cite{iea_iea_2017}.
-LCoE projections for wind and solar have been incorporated \cite{lazard_lazards_2017}.
+\item The levelized cost of electricity (LCOE) for fossil fuels has been held constant throughout the simulation \cite{chapman_energy_2018} \cite{noauthor_lazards_2017} \cite{noauthor_iea_2017}.
+LCoE projections for wind and solar have been incorporated \cite{noauthor_lazards_2017}.
 However, the implementation of costs associated with electricity generation is still under-development.
 
-\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the EDMC data \cite{edmc_ieej_edmc_nodate} indicating declining use of oil.
+\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the EDMC data \cite{noauthor_energy_2018} indicating declining use of oil.
 
-\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's ABWRs \cite{ge_hitachi_nuclear_energy_advanced_2007}, which are under consideration for construction \cite{the_federation_of_electric_power_companies_of_japan_electricity_2017}, with efficiency values based on existing ABWRs in operation.
+\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's ABWRs \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}, with efficiency values based on existing ABWRs in operation.
 It has been assumed that there can be as many as 22 ABWRs constructed in between 2020-2100, with the number of reactors constructed during the earlier years based on the number of projects currently under consideration for construction, and the pace of construction based on similar reactors constructed in Japan.
@@
 
-\item Geothermal is expanded to its maximum potential \cite{the_geothermal_research_society_of_japan_geothermal_nodate}.
+\item Geothermal is expanded to its maximum potential \cite{noauthor_geothermal_2018}.
 
@@
 
+\bibliographystyle{ieeetr}
+%\addbibresource{2018-chaube-i2cner-report-sept}
+\bibliography{2018-chaube-i2cner-report-sept}
+
 %\bibliographystyle{plain}

### 2018-09-28 doc/2018-09-report/plot/plotter-co2.py
Added plotting scripts, plots, makefile

@@ -1,0 +1,45 @@
+import xlrd
+import numpy as np
+import matplotlib.pyplot as plt
+
+title='CO2 emissions from electricity generation'
+yax='CO2 produced (Mt)'
+format='.png'
+fname='co2-2016'+format
+
+f1='CO2-2016.xlsx'
+
+wb=xlrd.open_workbook(f1)
+sheet = wb.sheet_by_index(0)
+
+r=int(sheet.nrows)
+c=int(sheet.ncols)
+
+labels=[]
+x=np.zeros(c-1)
+y=np.zeros((r-1,c-1))
+
+for i in range(1,r):
+    labels.append(sheet.cell_value(i,0))
+
+for i in range(1,c):
+    x[i-1]=sheet.cell_value(0,i)
+    for j in range(1,r):
+        y[j-1,i-1]=sheet.cell_value(j,i)
+                              
+fig = plt.figure()
+ax1=fig.add_subplot(111)
+
+ax1.scatter(x,y[0,:],marker='x',color='blue')
+plt.plot(x,y[0,:],linestyle='dashed',color='blue')
+ax1.scatter(x,y[1,:],marker='o',color='red')
+plt.plot(x,y[1,:],linestyle='dashed',color='red')
+plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 14})
+plt.xlabel('Years',fontsize='14')
+plt.ylabel(yax,fontsize='14')
+plt.title(title,fontsize='16')
+plt.grid(True)
+#plt.show()
+plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
+
+

### 2018-09-28 doc/2018-09-report/2018-09-i2cner-report.tex
Added plotting scripts, plots, makefile
Former-commit-id: 7dd97762133d1707a20324906e8576e2644373d9 [formerly 479c81084261d43e24ef86d9b217e8e2e2b39dd3]
Former-commit-id: f00ddcd34d8de4fcf316faae835496663e102f8c

@@
 
+%----------------------------------------------------------------------------------------
+%    TITLE PAGE
+%----------------------------------------------------------------------------------------
+
 \begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
@@
         {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With TIMES\end{flushright}}
-        {\begin{flushright}\large\textit{ I\textsuperscript{2}CNER Project Report}\end{flushright}}
+        {\begin{flushright}\large\textit{I\textsuperscript{2}CNER Project Report}\end{flushright}}
 
@@
     \vspace{0.5cm}
+
+    %------------------------------------------------
+    %    Author(s)
+    %------------------------------------------------
+
+    \begin{minipage}{0.4\textwidth}
+        \begin{flushleft}
+            \large
+            \textit{Author}\\
+            Anshuman \textsc{Chaube}\\
+        \end{flushleft}
+    \end{minipage}
+    ~
+    \begin{minipage}{0.4\textwidth}
+        \begin{flushright}
+            \large
+            \textit{Principal Investigator}\\
+            Kathryn D. \textsc{Huff} % Supervisor's name
+        \end{flushright}
+    \end{minipage}
 
@@
 
-Based on these assumptions, the preliminary transition scenario gives the following distribution of electric utilities to meet the supplied demand process:
+Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by EDMC:
 
-%\begin{figure}[H]
-%\centering
-%\includegraphics[scale=0.4]{q1_1_1}
-%\caption{The partial sum $g ^N (x)$ for %$f_1 (x)$ for $N=1,2,...10$.}
-%\end{figure}
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{elc-2016}
+\caption{Electricity generated from different sources}
+\end{figure}
 
-The emitted CO\textsubscript{2} values for the period 2011-16 are as follows. The error is at most 5.7\% (see fig), which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.
+The emitted CO\textsubscript{2} values for the period 2011-16 are as follows.
+The error is at most 5.7\% \ref{co2err}, which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{co2-2016}
+\caption{CO2 emissions from electricity generation compared with actual emissions reported by Ministry of Environment(MoE), Japan}
+\end{figure}
+
+\begin{figure}[H] \label{co2err}
+\centering
+\includegraphics[scale=0.6]{co2-err}
+\caption{Relative error in CO2 emissions.}
+\end{figure}
 

### 2018-11-05 doc/2018-09-report/2018-09-i2cner-report.tex
report-minor corrections
Former-commit-id: e29eb807696e9071cbfd10da298df421261d7ae2 [formerly fb9e0afab2b52caeef72bf4ec58783f467bbad54]
Former-commit-id: a9c07d8dfcd4ea5b524b13361e1fa2dc0659f9ba

@@
     \vspace{1cm}
-    \textsc{\LARGE\bfseries UIUC-ARFC-2018-01} % Replace YYYY with the year, NN with report index
+    \textsc{\LARGE\bfseries UIUC-ARFC-2018-00} \textit{work in progress} % Replace YYYY with the year, NN with report index
     \vspace{0.5cm}
@@
 We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
-\cite{publicover_japan_2017} \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}
+\cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}
 

### 2019-01-04 doc/2019-01-poster/poster.tex
Updated plots, added poster tex
Former-commit-id: c311aeaf9285b06e2c774b9c3efc9d3be5f5f1b8 [formerly ac2aa4f57b7d4fe8bc67b991fd2642e96e46603e]
Former-commit-id: f39c455b1448ad396a78d3086f3f07df25093988

--- 2018-01-12 doc/poster.tex
@@
 \cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
-We will simulate \textbf{dynamic} transition scenarios 
-\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
-emissions in Japan by 2050. These scenarios will include realistic constraints 
-regarding technology readiness (in terms of generation, transmission \& 
-storage) and will combine multiple technologies in a single heterogeneous 
-system model.
+We are simulating \textbf{dynamic} transition scenarios 
+\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
+emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
+Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear energy, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
 \end{block}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nuc_elc}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
+\label{s1e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nuc_co2}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
+\label{s1c}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nonuc_elc}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
+\label{s2e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{conv_nonuc_co2}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
+\label{s2c}
+\end{figure}
 
@@
         using linear and mixed-linear algorithms. A user-defined objective 
-        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.
+        function is solved within user defined constraints.\hfill \break
+
+\textbf{Key assumptions:}
+
+\begin{itemize}
+        \item\textbf{Objective function:} System cost.
+
+         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year).
+
+         \item Hydropower capacity held constant
+
+         \item All new nuclear power is based on ABWR designs.
+
+         \item Growth rate and discrete investment size of nuclear, wind and solar is based on data and trends seen in the US, Chinese, and Japanese energy sectors.
+
+         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with their costs reducing by 2050 as per projected trends.
+
+         \item \textbf{Photocatalytic conversion:} Deployed in 2050, assumed to be cost-competitive with other H$_2$ producing technologies. \hfill \break
+
+ \end{itemize}
+
+We have modeled \textbf{four scenarios:}
 
 \begin{description}
-        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
-                 consumption by sector (commercial, industrial, residential, 
-                 building etc). 
-         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
-         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
-                 (i.e. energy intensity, thermal energy efficiency, 
-                 transmission capacity).. 
-         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
-                 transition as a constrained optimization problem will
-                 drive insights.
+        \item[\textbf{Scenario 1:}]
+        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled (Fig. \ref{s1e} and \ref{s1c}.
+
+        \item[\textbf{Scenario 2:}]
+        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{except new ABWR reactors}, enabled (Fig. \ref{s2e} and \ref{s2c}).
+
+        \item[\textbf{Scenario 3:}]
+        I$^2$CNER technologies \textbf{enabled}.  Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled. (Fig.\ref{s3e} and \ref{s3c}).
+
+        \item[\textbf{Scenario 4:}] 
+ I$^2$CNER technologies \textbf{enabled}. Deployment of all conventional technologies, \textbf{excluding new ABWR reactors}, enabled (Fig.\ref{s4e} and \ref{s4c})
+
 \end{description}
@@
 \end{block}
+
+\vspace{11mm}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nuc_elc}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
+\label{s3e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nuc_co2}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
+\label{s3c}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nonuc_elc}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
+\label{s4e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{i2cner_nonuc_co2}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
+\label{s4c}
+\end{figure}
 
@@
 	\begin{itemize}
-                \item Dynamic simulation of Japan's energy system transition in 
-                        the TIMES model generator will help develop near-term 
-                        decarbonization strategies.
-                \item Policymakers will benefit from identification of high 
-                        impact technologies, and creation of R\&D investment 
-                        and infrastructure development timelines.  
-                \item Simulations will quantify system sensitivity to 
-                        technology readiness. 
-                \item Dynamic analysis will identify potential transition 
-                        bottlenecks.
+                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy mix, despite high investment costs.
+
+                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience
+
+                \item Cost competitive photocatalytic H$_2$ and offshore wind can replace nuclear, resulting in significantly higher system costs.
+
+                \item Technologies with the highest impact: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
 	\end{itemize}
@@
 %---------------------------------------------------------
-\begin{block}{Timeline}
-        \input{timeline}
+\begin{block}{Future work}
+    no
 \end{block}
@@
 \begin{block}{References}
-        {\footnotesize\bibliographystyle{abbrv} 
+        {\small\bibliographystyle{abbrv} 
         \bibliography{poster}}

### 2019-01-07 doc/2019-01-poster/poster.tex
cleanup
Former-commit-id: fec7a0d747ca9917b3e80fa055c5ef63000bec32 [formerly 6b1dc9f99b8f746b0eda8927ea41432168ad4696]
Former-commit-id: 2e3f136a089a1f9282ee0dc17a5eab5c60deae4b

@@
         Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
-\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
+\institute{University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
 %----------------------------------------------------------------------------------------
@@
 various world regions using \textbf{static} scenario analyses 
-\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
+\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
 We are simulating \textbf{dynamic} transition scenarios 
-\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
+\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
 emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
-Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear energy, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
+Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
 \end{block}
@@
 
-         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year).
+         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.
 
-         \item Hydropower capacity held constant
+         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.
 
-         \item All new nuclear power is based on ABWR designs.
+         \item All new nuclear reactors are ABWRs \cite{rothwell_real_2006}.
 
-         \item Growth rate and discrete investment size of nuclear, wind and solar is based on data and trends seen in the US, Chinese, and Japanese energy sectors.
+         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan.
+\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}
 
-         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with their costs reducing by 2050 as per projected trends.
+         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}
 
-         \item \textbf{Photocatalytic conversion:} Deployed in 2050, assumed to be cost-competitive with other H$_2$ producing technologies. \hfill \break
+         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030.
+Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies.
+\cite{kato_energy_2016} \cite{acar_comparative_2014} \hfill \break
 
@@
 
-\vspace{11mm}
+%\vspace{11mm}
 
@@
 	\begin{itemize}
-                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy mix, despite high investment costs.
+                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.
 
-                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience
+                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.
 
-                \item Cost competitive photocatalytic H$_2$ and offshore wind can replace nuclear, resulting in significantly higher system costs.
+                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.
 
@@
 \begin{block}{Future work}
-    no
+    \begin{itemize}
+
+    \item Incorporation of more I$^2$CNER technologies.
+
+    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.
+
+    \item Detailed cost analysis
+
+    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.
+
+    \end{itemize}
 \end{block}
@@
 \begin{block}{References}
-        {\small\bibliographystyle{abbrv} 
-        \bibliography{poster}}
+
+        {\small\bibliographystyle{unsrt} 
+        \bibliography{2019-chaube-i2cner-poster}}
 \end{block}

### 2019-01-07 doc/2019-01-poster/poster.tex
adjusted title spacing

@@
 
+\makeatletter
+\def\beamer@andinst{\\[0em]}
+\makeatother
+
 %----------------------------------------------------------------------------------------
@@
        % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
-        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
-\institute{University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
+        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
+\institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
 %----------------------------------------------------------------------------------------

### 2019-01-08 doc/2019-01-poster/poster.tex
Update poster.tex

@@
 emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
-Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
+
+Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
+\hfill \break
+
 \end{block}
+
+%\vspace{77mm}
 
@@
         using linear and mixed-linear algorithms. A user-defined objective 
-        function is solved within user defined constraints.\hfill \break
+        function is solved within user defined constraints. \hfill \break
 
@@
 
-We have modeled \textbf{four scenarios:}
+We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break
 
-\begin{description}
-        \item[\textbf{Scenario 1:}]
-        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled (Fig. \ref{s1e} and \ref{s1c}.
+\begin{tabular}{c c c c c}
 
-        \item[\textbf{Scenario 2:}]
-        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{except new ABWR reactors}, enabled (Fig. \ref{s2e} and \ref{s2c}).
-
-        \item[\textbf{Scenario 3:}]
-        I$^2$CNER technologies \textbf{enabled}.  Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled. (Fig.\ref{s3e} and \ref{s3c}).
-
-        \item[\textbf{Scenario 4:}] 
- I$^2$CNER technologies \textbf{enabled}. Deployment of all conventional technologies, \textbf{excluding new ABWR reactors}, enabled (Fig.\ref{s4e} and \ref{s4c})
-
-\end{description}
+\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
+                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
+1                 & Fig. \ref{s1e}\&\ref{s1c}&        Yes                 &           No         &       Yes            \\ 
+2                 & Fig. \ref{s2e}\&\ref{s2c}&        Yes                 &           No         &       No             \\ 
+3                 & Fig. \ref{s3e}\&\ref{s3c}&        Yes                 &           Yes        &       Yes            \\ 
+4                 & Fig. \ref{s4e}\&\ref{s4c}&        Yes                 &           Yes        &       No             \\
+\end{tabular}
 
@@
 
-%\vspace{11mm}
+\vspace{65 mm}
 
@@
     \begin{itemize}
+
+    \item Making transitions more gradual.
 

### 2019-01-10 doc/2019-01-poster/poster.tex
added check marks to table, fixed legend size and references, modified "future work" section
changed take aways
Former-commit-id: a022240e0b5adb30ff79d69cd045c581800357f3 [formerly cb6a761acbf7b95577de4d47115ec0ee6ee86c03]
Former-commit-id: 15e28a4e2c41e5ea2ccff711a62f03041376f32e
added costs plot
Former-commit-id: 0237ea97ae76e97243bca32f2b9ecac32f471b54 [formerly 6b30ab847fc24064a74d4fc9fc1fd31d1c53a2c9]
Former-commit-id: cb897036ac48024a4d5fe52214f7c9949dac626e

@@
 \SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}
+
+\usepackage{amssymb}
+\usepackage{pifont}
+\usepackage{xcolor}
+\newcommand{\greencheck}{{\color{green}\checkmark}}
+\newcommand{\xmark}{{\color{red}\ding{55}}}
 
@@
         using linear and mixed-linear algorithms. A user-defined objective 
-        function is solved within user defined constraints. \hfill \break
-
+        function is solved within user defined constraints.\\
 \textbf{Key assumptions:}
@@
          \item Hydropower capacity held constant \cite{noauthor_energy_2018}.
+
+         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.
+Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig.
+\ref{cost}.
 
@@
 Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies.
-\cite{kato_energy_2016} \cite{acar_comparative_2014} \hfill \break
+\cite{kato_energy_2016} \cite{acar_comparative_2014} \\
 
@@
                   &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
-1                 & Fig. \ref{s1e}\&\ref{s1c}&        Yes                 &           No         &       Yes            \\ 
-2                 & Fig. \ref{s2e}\&\ref{s2c}&        Yes                 &           No         &       No             \\ 
-3                 & Fig. \ref{s3e}\&\ref{s3c}&        Yes                 &           Yes        &       Yes            \\ 
-4                 & Fig. \ref{s4e}\&\ref{s4c}&        Yes                 &           Yes        &       No             \\
+1                 & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
+2                 & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
+3                 & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
+4                 & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
 \end{tabular}
@@
 
-\vspace{65 mm}
+%\vspace{65 mm}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{legend}
+%\caption{Legend}
+\label{legend}
+\end{figure}
 
@@
 %----------------------------------------------------------------------------------------
-
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.2]{cost}
+\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
+\label{cost}
+\end{figure}
          \begin{alertblock}{Take Aways}
@@
 
-                \item Technologies with the highest impact: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
+                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
 	\end{itemize}
@@
 
-    \item Making transitions more gradual.
+    \item Capture realistic, gradual transition behaviour.
 
@@
 \begin{block}{References}
-
-        {\small\bibliographystyle{unsrt} 
+        {\footnotesize\bibliographystyle{ieeetr} 
         \bibliography{2019-chaube-i2cner-poster}}

### 2019-01-12 doc/2019-01-poster/poster.tex
updated poster, added new data
Former-commit-id: 58ff1cab0f45228c427b60b60ca011f0636f7a36 [formerly 4f2bf9a0b4c76fe6832c739e19ce11de67b30fa9]
Former-commit-id: 9671cbfeff916ede3f4ea25d12f298abbbffbd81

@@
         \item Minimize carbon emissions within realistic constraints.
-        \item Optimize realistic 2010-2050 decarbonization roadmaps.
+        \item Optimize realistic 2010-2100 decarbonization roadmaps.
 	\item Identify high impact technologies.
@@
 
-         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.
+         \item Hydropower and geothermal capacity held constant \cite{noauthor_energy_2018}.
 
-         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.
-Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig.
-\ref{cost}.
+         \item Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.
 
@@
 %---------------------------------------------------------
-\begin{block}{Future work}
+\begin{block}{Limitations and Future work}
     \begin{itemize}
 
-    \item Capture realistic, gradual transition behaviour.
+    \item Model focuses entirely on \textbf{electricity supply sector}.
+
+    \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.
+
+    \item No limit on penetration of solar or wind except maximum potential.
+
+    \item Annual timestep does not capture seasonal and daily variation in wind and solar.
+
+    \item Capture realistic, gradual transition behaviour and fluctuations in demand.
 
@@
 
-\vspace{10mm}
+%\vspace{10mm}
 \begin{center}

### 2019-01-13 doc/2019-01-poster/poster.tex
changed cost plot's size
Former-commit-id: 5820c1553bfd56210cdea02007787819f60cb187 [formerly d56758327126644dc6679439d39c83f24b13233d]
Former-commit-id: d77443d12d2af53eb7c755a745163a88b2e79b1b
changed limitations
Former-commit-id: 956028773ff0e17257623b287fba622807fe26f1 [formerly c894042215b115d74fe4d924b3065ca9c7d1a613]
Former-commit-id: eea32f176fe0496ef623bd534df81467ea4a9558
reduced text, made plots larger

--- 2019-01-10 doc/2019-01-poster/poster.tex
@@
 \begin{description}
-{\large 
+{%\large 
         \item[\textbf{Division:}] Energy Analysis Division
@@
         \item Minimize carbon emissions within realistic constraints.
-        \item Optimize realistic 2010-2050 decarbonization roadmaps.
+        \item Create realistic decarbonization roadmaps.
 	    \item Identify high impact technologies.
         \item Identify potential transition bottlenecks.
-        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
-        \item Quantify system sensitivity to technology readiness.
-	\item Predict impediments to strategically optimal technology deployment.
+        %\item Help create timelines for R\&D investment and infrastructure development.
      	\end{itemize}
@@
 We are simulating \textbf{dynamic} transition scenarios 
-\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
-emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
-
-Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
-\hfill \break
-
+\cite{pfenninger_energy_2014} aimed at \textbf{optimizing energy supply} to minimize carbon 
+emissions in Japan to 80\% of 1990 levels by 2050.
+Our model has conventional and I$^2$CNER technologies (\textbf{carbon capture(CCS)} \& \textbf{H$_2$} production).
 \end{block}
@@
 \centering
-\includegraphics[scale=1.2]{conv_nuc_elc}
+\includegraphics[scale=1.1]{legend}
+%\caption{Legend}
+\label{legend}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.51]{conv_nuc_elc}
 \caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
@@
 \centering
-\includegraphics[scale=1.2]{conv_nuc_co2}
+\includegraphics[scale=1.51]{conv_nuc_co2}
 \caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
@@
 \centering
-\includegraphics[scale=1.2]{conv_nonuc_elc}
+\includegraphics[scale=1.51]{conv_nonuc_elc}
 \caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
@@
 \centering
-\includegraphics[scale=1.2]{conv_nonuc_co2}
+\includegraphics[scale=1.51]{conv_nonuc_co2}
 \caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
@@
 %----------------------------------------------------------------------------------------
-
 \begin{column}{\onecolwid} % The second column
-
 %----------------------------------------------------------------------------------------
 \begin{block}{Methodology}
-        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
+        \textbf{The Integrated MARKAL-EFOM System (TIMES)} 
         \cite{loulou_documentation_2005} 
         \cite{seebregts_energy/environmental_2002} optimizes energy systems 
-        using linear and mixed-linear algorithms. A user-defined objective 
-        function is solved within user defined constraints.\\
+        using linear \& mixed-linear algorithms. An objective 
+        function is solved within given constraints.\\
 \textbf{Key assumptions:}
+\begin{itemize}
+        \item\textbf{Objective function:} System cost \ref{cost}.
 
-\begin{itemize}
-        \item\textbf{Objective function:} System cost.
+         \item\textbf{Constraints:} CO$_2$ emissions, demand(+1.7\% per year) \cite{noauthor_electricity_2017}.
 
-         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.
-
-         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.
-
-         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.
-Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig.
-\ref{cost}.
+         \item Hydropower and geothermal capacity are constant \cite{noauthor_energy_2018}.
 
@@
 
-         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan.
-\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}
+         \item Nuclear, wind, solar growth rate based on trends in USA, China, and Japan.\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}
 
-         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}
+         \item \textbf{CCS:} Deploys in 2030,costs reduce by 2050. \cite{kato_energy_2016}
 
-         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030.
-Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies.
-\cite{kato_energy_2016} \cite{acar_comparative_2014} \\
-
+         \item \textbf{H$_2$:} Steam reforming deploys in 2030. Photocatalytic H$_2$ deploys in 2050, assumed cost-competitive. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\         
  \end{itemize}
 
-We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break
+We have modeled \textbf{four scenarios}:\hfill \break
 
-\begin{tabular}{c c c c c}
-
-\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
-                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
+\begin{tabular}{| c | c | c | c | c |}
+\hline
+\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{I$^2$CNER}&\textbf{New nuclear}\\
+                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+                  \hline
 1               & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
@@
 4               & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
+\hline
 \end{tabular}
-
 \end{block}
@@
 \centering
-\includegraphics[scale=1.2]{legend}
-%\caption{Legend}
-\label{legend}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.2]{i2cner_nuc_elc}
+\includegraphics[scale=1.62]{i2cner_nuc_elc}
 \caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
@@
 \centering
-\includegraphics[scale=1.2]{i2cner_nuc_co2}
+\includegraphics[scale=1.62]{i2cner_nuc_co2}
 \caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
@@
 \centering
-\includegraphics[scale=1.2]{i2cner_nonuc_elc}
+\includegraphics[scale=1.62]{i2cner_nonuc_elc}
 \caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
@@
 \centering
-\includegraphics[scale=1.2]{i2cner_nonuc_co2}
+\includegraphics[scale=1.62]{i2cner_nonuc_co2}
 \caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
@@
 \centering
-\includegraphics[scale=1.2]{cost}
+\includegraphics[scale=1.4]{cost}
 \caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
@@
 	\begin{itemize}
-                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.
+                \item Nuclear power is the cleanest and cheapest.
 
-                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.
+                \item Without nuclear and I$^2$CNER, solar and wind are deployed in a 1:2 ratio.
 
-                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.
+                \item H$_2$ and wind can meet I$^2$CNER targets without nuclear, at high cost.
 
-                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
+                \item Highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$, solar
 	\end{itemize}
@@
 %---------------------------------------------------------
-\begin{block}{Future work}
+\begin{block}{Limitations and Future work}
     \begin{itemize}
 
-    \item Capture realistic, gradual transition behaviour.
+    \item Model focuses on \textbf{electricity supply sector}.
+
+    \item Cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is constant.
+
+    \item Emissions tied to energy production, not capacity installation.
+
+    \item Annual timestep can't capture variation in wind, solar.
+
+    \item Capture realistic transitions and fluctuations in demand.
 
@@
 
-    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.
+    \item Sensitivity and cost analysis to maximize I$^2$CNER's impact.
 
-    \item Detailed cost analysis
+    %\item Detailed cost analysis
 
-    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.
+    \item Add energy storage to supplement renewables and H$_2$.
 

### 2019-01-15 doc/2019-01-poster/poster.tex
changed plot sizes
Former-commit-id: 2c4e4bed8cf810e96bb2e7f6e03419136e2b2c03 [formerly fc227173353422fcc65b0dfb240ca0c8856e7964]
Former-commit-id: 7b2a73d86c7662951e700189a55c75f167ddc0c5
updated UIUC logo
Former-commit-id: 62c116882761f2fbf64d33495f1fc9c6f3dc17f9 [formerly 3416457406c39478f85bf2d64e5fb07f260ab827]
Former-commit-id: b8ee3fa6347c948186bbae81961f728fd0a106d4

@@
 \centering
-\includegraphics[scale=1.4]{cost}
+\includegraphics[scale=1.6]{cost}
 \caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
@@
 \begin{tabular}{cccc}
-\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
+\includegraphics[scale=0.7]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
 %\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}

### 2019-01-16 doc/2019-01-poster/presentation/cat_appearance.tex
added presentation template

\begin{frame}
  \frametitle{Columns}
  % a comment
        \begin{columns}
                \column[t]{5cm}
                Sometimes things need to be put side by side, in two nice 
                looking columns.

                Maybe one column involves a quotation.

                \begin{quote}
                        Explicit is better than implicit. -- The Zen of Python
                \end{quote}

                And, also, perhaps, a logo.
                \begin{center}
                        \includegraphics[height=0.2\textheight]{./images/arfc-logo}
                \end{center}
                \column[t]{5cm}
        \begin{figure}[htbp!]
        \begin{center}
      \includegraphics[height=4cm]{./images/kitten}
    \end{center}
          \caption{A caption describing the image. \cite{lastname_firstword_1900}.}
    \label{fig:kittenfigure}
  \end{figure}
        \end{columns}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Some Code}
        I have to use the fragile syntax for code slides.
\end{frame}

### 2019-01-17 doc/2019-01-poster/presentation/motivation.tex
updated presentation
Former-commit-id: 08316fc1d9fac56701f721baa9f6361ff3f8ea22 [formerly 74c1a4017515d4440307a812b7e01b0aea8b2169]
Former-commit-id: 2a70f17cd8df626da8278cd57d6854093a860d66

%\begin{frame}
  %\frametitle{Motivation}
  % a comment
%  \begin{figure}[htbp!]
%    \begin{center}
%      \includegraphics[height=4cm]{./images/kitten}
%    \end{center}
%          \caption{A caption describing the image. \cite{lastname_firstword_1900}.}
%    \label{fig:kittenfigure}
%  \end{figure}
%\end{frame}

\begin{frame}
  \frametitle{Motivation}
   \begin{itemize}

   \item Dynamic transition analysis to minimize CO$_2$ emissions.

   \item Focus on optimizing \textbf{electricity supply}.

   \item Emissions reduced by 80\% from 1990 levels by 2050, held constant until 2100 if possible.

   \item Energy supply includes conventional and some I$^2$CNER technology.

   \item Using The Integrated MARKAL-EFOM System (TIMES).
   \end{itemize}
%        Frames (slides) can have ``blocks.'' 
%        \begin{block}{This one is about a cat}
%                A cat in a hat.
%        \end{block}
%        \begin{block}{A cat}
%                In a hat.
%
%                \includegraphics[height=0.2\textheight]{./images/catinhat}
%        \end{block}

\end{frame}

### 2019-01-17 doc/2019-01-poster/presentation/s4.tex
updated presentation
Former-commit-id: 08316fc1d9fac56701f721baa9f6361ff3f8ea22 [formerly 74c1a4017515d4440307a812b7e01b0aea8b2169]
Former-commit-id: 2a70f17cd8df626da8278cd57d6854093a860d66

\begin{frame}
  \frametitle{Limitations}
  % a comment
        \begin{itemize}

         \item Focus entirely on \textbf{electricity supply sector}

         \item Cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is constant.

         \item Emissions tied to energy production, not capacity installation

         \item Annual time-step cannot capture seasonal/daily variation in wind, solar.

        \end{itemize}

\end{frame}

### 2019-01-22 doc/2019-02-presentation/assums.tex
reorganized docs, corrected assumptions slide
Former-commit-id: f44c5c32bcf6c2f8dbb3642d31b2df8f8ad6ea89 [formerly 92ce9c2ab44f4d38b98b22cbd6208c607a6980d3]
Former-commit-id: edcc5a8790eae756807361a8b7d9692cf07d9259

\begin{frame}
  \frametitle{Assumptions}

  \begin{itemize}

  \item New Nuclear = ABWRs

  \item Nuclear, wind, solar growth rates based on trends in USA, China, Japan.

  \item CCS: Available for deployment in 2030, costs reduce by 2050.

  \item H$_2$: Steam reforming available in 2030, photocatalytic conversion in 2050.

  \item Hydropower, geothermal capacity held constant.

  \end{itemize}

\end{frame}

### 2019-01-23 doc/2019-02-presentation/basics.tex
minor punctuation corrections, added scenario frame title
Former-commit-id: 9e89b78dcdf4c533730cf1c055de182db6beb53b [formerly 20d17d0febcd06be3f506b362ab97d808910e4cf]
Former-commit-id: 02093b75aa75bd3201815b77b46f7e57b644889c

\begin{frame}
  \frametitle{Basics}
  % a comment
        \begin{itemize}

        \item Constrained linear/mixed-linear optimization problem.

        \item Objective function - System Cost.

        \item Constraints - CO$_2$ emissions, demand.

        \item Novel tech - H$_2$ (steam reforming, photocatalytic conversion), carbon capture and sequestration (absorption type).

        \end{itemize}
\end{frame}

### 2019-01-23 doc/2019-02-presentation/limits.tex
minor punctuation corrections, added scenario frame title
Former-commit-id: 9e89b78dcdf4c533730cf1c055de182db6beb53b [formerly 20d17d0febcd06be3f506b362ab97d808910e4cf]
Former-commit-id: 02093b75aa75bd3201815b77b46f7e57b644889c

--- 2019-01-15 doc/2019-01-poster/poster.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Jacobs Landscape Poster
-% LaTeX Template
-% Version 1.1 (14/06/14)
-%
-% Created by:
-% Computational Physics and Biophysics Group, Jacobs University
-% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
-% 
-% Further modified by:
-% Nathaniel Johnston (nathaniel@njohnston.ca)
-%
-% This template has been downloaded from:
-% http://www.LaTeXTemplates.com
-%
-% License:
-% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
-
-\documentclass[final]{beamer}
-
-\usepackage[scale=0.9]{beamerposter} % Use the beamerposter package for laying out the poster
-\usetheme{confposter} % Use the confposter theme supplied with this template
-
-\setbeamercolor{block title}{fg=dblue!80,bg=white} % Colors of the block titles
-\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
-\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
-\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
-\setbeamertemplate{caption}[numbered]
-
-% Many more colors are available for use in beamerthemeconfposter.sty
-
-%-----------------------------------------------------------
-% Define the column widths and overall poster size
-% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
-% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
-% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
-% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. 
-% (1-(3+1)*0.025)/3 = 0.3
-% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
-% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708
-\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
-
-\newlength{\sepwid}
-\newlength{\onecolwid}
-\newlength{\twocolwid}
-\newlength{\threecolwid}
-\setlength{\paperwidth}{33.1in} % A0 width: 46.8in
-\setlength{\paperheight}{46.8in} % A0 height: 33.1in
-\setlength{\textwidth}{33.1in} % A0 width: 46.8in
-\setlength{\textheight}{46.8in} % A0 height: 33.1in
-\setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
-\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
-\setlength{\twocolwid}{0.625\paperwidth} % Width of two columns
-\setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
-\setlength{\topmargin}{-1in} % Reduce the top margin size
-%-----------------------------------------------------------
-
-\usepackage{graphicx}  % Required for including images
-\usepackage{hyperref}
-\usepackage{cite}
-
-\usepackage{tabularx}
-\newcolumntype{b}{X}
-\newcolumntype{s}{>{\hsize=.5\hsize}X}
-\newcolumntype{m}{>{\hsize=.75\hsize}X}
-\newcolumntype{z}{>{\hsize=.65\hsize}X}
-
-\usepackage{booktabs} % Top and bottom rules for tables
-\usepackage{xspace}
-
-\usepackage{tikz}
-\usepackage{chronology}
-\usetikzlibrary{arrows.meta}
-
-\usetikzlibrary{positioning, arrows, decorations, shapes, calc }
-% Define block styles
-\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
-text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
-
-\tikzstyle{const} = [rectangle, draw, text centered, fill=orange!20]
-\tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]
-
-\tikzstyle{block} = [rectangle, draw, text centered, fill=blue!20]
-\tikzstyle{line} = [draw, -latex']
-\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=6em,
-minimum height=2em]
-
-\usetikzlibrary{shapes.multipart}
-\usetikzlibrary{positioning}
-
-%-----------------------------------------------------------
-% KNOWN ISSUE IN TIKZ MATH: tiny big symbols, like sum.
-%-----------------------------------------------------------
-
-% declare `cmex` to be arbitrary scalable
-\DeclareFontShape{OMX}{cmex}{m}{n}{
-  <-7.5> cmex7
-  <7.5-8.5> cmex8
-  <8.5-9.5> cmex9
-  <9.5-> cmex10
-}{}
-
-\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
-\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}
-
-\usepackage{amssymb}
-\usepackage{pifont}
-\usepackage{xcolor}
-\newcommand{\greencheck}{{\color{green}\checkmark}}
-\newcommand{\xmark}{{\color{red}\ding{55}}}
-
-\setbeamertemplate{bibliography item}[text]
-
-\makeatletter
-\def\beamer@andinst{\\[0em]}
-\makeatother
-
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION 
-%----------------------------------------------------------------------------------------
-
-\title{Dynamic Transition Analysis with TIMES}
-
-\author{
-       % \textbf{ENERGY ANALYSIS DIVISION}\\
-       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
-        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
-\institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
-%----------------------------------------------------------------------------------------
-
-\begin{document}
-
-\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
-\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks
-
-\setlength{\belowcaptionskip}{2ex} % White space under figures
-\setlength\belowdisplayshortskip{2ex} % White space under equations
-
-\begin{frame}[t] % The whole poster is enclosed in one beamer frame
-
-\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
-
-%=======================================================
-% FIRST COLUMN BEGINS
-%=========================================================
-
-\begin{column}{\twocolwid} % The first two columns, two cols wide
-\begin{columns}[t,totalwidth=\twocolwid] % Split up the first column into two, 
-\begin{column}{\onecolwid} % The first column, one col wide
-
-%----------------------------------------------------------------------------------------
-%	OBJECTIVES
-%----------------------------------------------------------------------------------------
-
-\begin{alertblock}{Objectives}
-
-\begin{description}
-{%\large 
-        \item[\textbf{Division:}] Energy Analysis Division
-        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
-        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
-\item[\textbf{Milestones:}] ~\\}
-        \begin{itemize}
-        \item Minimize carbon emissions within realistic constraints.
-        \item Create realistic decarbonization roadmaps.
-	    \item Identify high impact technologies.
-        \item Identify potential transition bottlenecks.
-        %\item Help create timelines for R\&D investment and infrastructure development.
-     	\end{itemize}
-\end{description}
-
-\end{alertblock}
-%
-%\begin{block}{Collaborators}
-%
-%I\textsuperscript{2}CNER collaborators will include primarily the members of 
-%the Energy Analysis Division (EAD), including those members at other 
-%institutes, universities or industries with connections to the EAD.   
-%\end{block}
-
-%----------------------------------------------------------------------------------------
-%	METHODOLOGY
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Introduction}
-Previous work has compared the impact of innovative energy technologies in 
-various world regions using \textbf{static} scenario analyses 
-\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
-We are simulating \textbf{dynamic} transition scenarios 
-\cite{pfenninger_energy_2014} aimed at \textbf{optimizing energy supply} to minimize carbon 
-emissions in Japan to 80\% of 1990 levels by 2050.
-Our model has conventional and I$^2$CNER technologies (\textbf{carbon capture(CCS)} \& \textbf{H$_2$} production).
-\end{block}
-
-%\vspace{77mm}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.1]{legend}
-%\caption{Legend}
-\label{legend}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.51]{conv_nuc_elc}
-\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
-\label{s1e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.51]{conv_nuc_co2}
-\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
-\label{s1c}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.51]{conv_nonuc_elc}
-\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
-\label{s2e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.51]{conv_nonuc_co2}
-\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
-\label{s2c}
-\end{figure}
-
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of the first column
-
-%===========================================================================================
-% SECOND COLUMN BEGINS
-%=============================================================================================
-
-%----------------------------------------------------------------------------------------
-\begin{column}{\onecolwid} % The second column
-%----------------------------------------------------------------------------------------
-\begin{block}{Methodology}
-        \textbf{The Integrated MARKAL-EFOM System (TIMES)} 
-        \cite{loulou_documentation_2005} 
-        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
-        using linear \& mixed-linear algorithms. An objective 
-        function is solved within given constraints.\\
-\textbf{Key assumptions:}
-\begin{itemize}
-        \item\textbf{Objective function:} System cost \ref{cost}.
-
-         \item\textbf{Constraints:} CO$_2$ emissions, demand(+1.7\% per year) \cite{noauthor_electricity_2017}.
-
-         \item Hydropower and geothermal capacity are constant \cite{noauthor_energy_2018}.
-
-         \item All new nuclear reactors are ABWRs \cite{rothwell_real_2006}.
-
-         \item Nuclear, wind, solar growth rate based on trends in USA, China, and Japan.\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}
-
-         \item \textbf{CCS:} Deploys in 2030,costs reduce by 2050. \cite{kato_energy_2016}
-
-         \item \textbf{H$_2$:} Steam reforming deploys in 2030. Photocatalytic H$_2$ deploys in 2050, assumed cost-competitive. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\         
- \end{itemize}
-
-We have modeled \textbf{four scenarios}:\hfill \break
-
-\begin{tabular}{| c | c | c | c | c |}
-\hline
-\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{I$^2$CNER}&\textbf{New nuclear}\\
-                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
-                  \hline
-1               & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
-2               & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
-3               & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
-4               & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
-\hline
-\end{tabular}
-\end{block}
-
-%\vspace{65 mm}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nuc_elc}
-\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
-\label{s3e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nuc_co2}
-\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
-\label{s3c}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nonuc_elc}
-\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
-\label{s4e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nonuc_co2}
-\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
-\label{s4c}
-\end{figure}
-
-\end{column} % End of column 2, top half
-\end{columns}
-%=======================================================
-% Double Wide Figure Column 
-%=========================================================
-%\input{model-fig}
-
-\end{column} % End of wide column, total length
-
-\begin{column}{\onecolwid} % The third column
-
-%----------------------------------------------------------------------------------------
-%	TAKE AWAY
-%----------------------------------------------------------------------------------------
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.6]{cost}
-\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
-\label{cost}
-\end{figure}
-         \begin{alertblock}{Take Aways}
-	\begin{itemize}
-                \item Nuclear power is the cleanest and cheapest.
-
-                \item Without nuclear and I$^2$CNER, solar and wind are deployed in a 1:2 ratio.
-
-                \item H$_2$ and wind can meet I$^2$CNER targets without nuclear, at high cost.
-
-                \item Highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$, solar
-	\end{itemize}
-        \end{alertblock}
-
-%--------------------------------------------------------
-% PROJECT TIMELINE
-%---------------------------------------------------------
-\begin{block}{Limitations and Future work}
+\begin{frame}
+  \frametitle{Limitations}
+  % a comment
         \begin{itemize}
 
-    \item Model focuses on \textbf{electricity supply sector}.
+         \item Focus entirely on \textbf{electricity supply sector}.
 
@@
 
-    \item Annual timestep can't capture variation in wind, solar.
-
-    \item Capture realistic transitions and fluctuations in demand.
-
-    \item Incorporation of more I$^2$CNER technologies.
-
-    \item Sensitivity and cost analysis to maximize I$^2$CNER's impact.
-
-    %\item Detailed cost analysis
-
-    \item Add energy storage to supplement renewables and H$_2$.
+         \item Annual time-step cannot capture seasonal/daily variation in wind, solar (however annually averaged availability factors are incorporated).
 
         \end{itemize}
-\end{block}
 
-\begin{block}{References}
-        {\footnotesize\bibliographystyle{ieeetr} 
-        \bibliography{2019-chaube-i2cner-poster}}
-\end{block}
-
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-%	CONTACT INFORMATION
-%----------------------------------------------------------------------------------------
-
-\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
-\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
-
-\begin{alertblock}{Contact Information}
-\begin{itemize}
-	\item Web: \href{arfc.github.io}{arfc.github.io}
-	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
-\end{itemize}
-
-\end{alertblock}
-
-%----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
-
-\begin{block}{Acknowledgements}
-
-This research is being performed using funding received
-from the International Institute for Carbon Neutral Energy Research (I$^2$CNER) 
-Initiative on Challenges in Energy Assessment and Energy Transitions at  the  
-University of Illinois under Director Petros Sofronis.
-
-%\vspace{10mm}
-\begin{center}
-\begin{tabular}{cccc}
-\includegraphics[scale=0.7]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
-%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
-\end{tabular}
-\end{center}
-
-\end{block}
-
-\end{column} % End of the final column
-
-\end{columns}
-\end{frame} % End of the enclosing frame
-
-\end{document}
+\end{frame}

### 2019-01-24 doc/2019-02-presentation/assums.tex
moved cost plot to assumptions
minor punctuation corrections, added scenario frame title
Former-commit-id: 9e89b78dcdf4c533730cf1c055de182db6beb53b [formerly 20d17d0febcd06be3f506b362ab97d808910e4cf]
Former-commit-id: 02093b75aa75bd3201815b77b46f7e57b644889c
added authors

@@
 
-  \item New Nuclear = ABWRs
+  \item New Nuclear = Advanced Boiling Water Reactors.
 
-  \item Nuclear, wind, solar growth rates based on trends in USA, China, Japan.
+  \item Simplistic, conservative assumption about demand growth = +1.7\% per year.
+
+  \item Nuclear, wind, solar annual growth rate \textbf{limits} based on trends in USA, China, Japan.
 
   \item CCS: Available for deployment in 2030, costs reduce by 2050.
+
+  \item Offshore and onshore wind capacity limited to theoretical potential (about 450 GW and 200 GW respectively).
 
@@
 \end{frame}
+
+\begin{frame}
+  \frametitle{Levelized cost projections for solar and wind}
+  \begin{figure}[htbp!]
+    \begin{center}
+      \includegraphics[scale=0.6]{./images/cost}
+    \end{center}
+          \caption{Cost variation of solar, wind, and H$_2$ production.}
+    \label{cost}
+  \end{figure}
+\end{frame}

### 2019-01-24 doc/2019-02-presentation/conclusion.tex
added authors

\begin{frame}
  \frametitle{Conclusions}
        \begin{itemize}

        \item Highest impact (so far): nuclear, offshore wind, photocatalytic H$_2$, solar.

        \item Transition scenario cost (from least to most expensive):

        \begin{enumerate}

        \item Scenario 1 (conventional with nuclear) = Scenario 3 (I$^2$CNER with nuclear)

        \item Scenario 2 (conventional without nuclear)

        \item Scenario 4 (I$^2$CNER without nuclear)

        \end{enumerate}

        \item H$_2$ and wind can meet I$^2$CNER goals at high cost without nuclear.

        \item Nuclear is the cleanest, cheapest source of energy.

        \item Without novel technology, solar and wind are deployed in a 1:2 ratio.

        \end{itemize}
\end{frame}

### 2019-01-24 doc/2019-02-presentation/future.tex
added authors

\begin{frame}
  \frametitle{Future work}
   \begin{itemize}

   \item Fix premature retirement bug.

   \item Develop a scenario with more restricted nuclear (similar to METI projections).

   \item Transition from model creation to model refinement.

   \item Capture realistic, gradual transitions.

   \item Incorporate fluctuations in demand.

   \item Add energy storage to supplement renewables and H$_2$.

   \item Incorporate more I$^2$CNER technologies.

   \item Conduct sensitivity and cost analysis.

   \end{itemize}

\end{frame}

### 2019-01-24 doc/2019-02-presentation/motivation.tex
added Japan, institute name
Former-commit-id: e4906c7fec5c01ddbc3e6d1ee62d31cd55d4eb8d [formerly c43586cb782ac88d17c8683be43789b1d61fef85]
Former-commit-id: 53f869447949beeabf2da0cc26d732ed8d2ff031
added authors

--- 2019-01-17 doc/2019-01-poster/presentation/motivation.tex
@@
 
-   \item Dynamic transition analysis to minimize CO$_2$ emissions.
+   \item Dynamic transition analysis to minimize CO$_2$ emissions in Japan.
 
@@
 
-   \item Emissions reduced by 80\% from 1990 levels by 2050, held constant until 2100 if possible.
+   \item \textbf{I$^2$CNER goal:} Reduce emissions by 80\% from 1990 levels by 2050,
+
+   \item After 2050: emissions held constant until 2100 if possible.
 

### 2019-01-24 doc/2019-02-presentation/assums.tex
Update assums.tex

@@
 \end{frame}
+
+\begin{frame}
+\frametitle{Contribution to peak factor (C2P factor}
+This is a TIMES parameter that defines what fraction of a energy source's capacity is guaranteed to be available during peak demand.
+\begin{tabular}{|c|c|}
+\textbf{Energy source} &
+\textbf{C2P factor} \\
+\hline 
+Fossil fuels & 1 \\
+Nuclear power & 1 \\
+Solar power & 0.42 \\
+Wind & 0.20 \\
+\end{tabular}
+
+This factor is reduced for solar and wind with increasing penetration.
+\end{frame}

### 2019-01-25 doc/2019-02-presentation/basics.tex
added authors
added references, readjusted plot size to include caption, added c2peak factor table

@@
 
-        \item Constrained linear/mixed-linear optimization problem.
+        \item Constrained linear/mixed-linear optimization problem \cite{loulou_etsap-tiam:_2008}.
 
@@
 
-        \item Novel tech - H$_2$ (steam reforming, photocatalytic conversion), carbon capture and sequestration (absorption type).
+        \item Novel tech - H$_2$ (steam reforming, photocatalytic conversion), absorption type carbon capture and sequestration (CCS)\cite{kato_energy_2016}.
 
@@
 \end{frame}
+
+%\begin{frame}
+%\include{model-fig}
+%\end{frame}

### 2019-01-25 doc/2019-02-presentation/model-fig.tex
added references, readjusted plot size to include caption, added c2peak factor table

--- 2018-01-03 docs/model-fig.tex
@@
 
+% tell TikZ how to stack them (back to front)
 \newlength{\figwidth}
@@
         \node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
+
         \begin{scope}[on background layer]

### 2019-01-26 doc/2019-02-presentation/times-fig.tex
added TIMES figure

--- 2019-01-25 doc/2019-02-presentation/model-fig.tex
@@
 % tell TikZ how to stack them (back to front)
+\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
+text width=2.5em, text badly centered, node distance=1cm, inner sep=0pt]
+
+\tikzstyle{const} = [rectangle, draw, text centered, fill=orange!20]
+\tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]
+
+\tikzstyle{block} = [rectangle, draw, text centered, fill=blue!20]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=1em,
+minimum height=1em]
+
 \newlength{\figwidth}
-\setlength{\figwidth}{8cm}
+\setlength{\figwidth}{4cm}
 
@@
     \centering
-    \scalebox{1.0}{
-                \begin{tikzpicture}[>={Latex[width=6mm,length=6mm]},
-                                node distance=\figwidth,
+    \scalebox{0.4}{\scalefont{2.25}
+                \begin{tikzpicture}[>={Latex[width=8mm,length=8mm]},
+                                node distance=0.5\figwidth,
                                 on grid,
@@
                                 auto]
+% \tikzstyle{every node}=[font=\Large]       
         % Place nodes
-        \node [block] (times) {\textbf{TIMES Model Generator}};
+        \node [block=1.5\figwidth and 2*\figwidth] (times) {\textbf{TIMES Model Generator}};
         \node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
                 \node [cloud, above left=1.5\figwidth and 2*\figwidth of times]
-                (dat) {\texttt{DATA}\\regarding both\\i$^2$cner and\\ conventional\\technologies};
-                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
-                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
-                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
-                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
-                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
-                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
-                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
-                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
-                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
-                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
-                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
-                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
-                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
+                (dat) {\texttt{DATA}\\METI,EDMC,\\ IEA,EIA\\I$^2$CNER};
         \node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
-        \node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
-        \node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
-        \node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
-        \node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
-        \node [const, left=\figwidth of dem ] (init) {initial\\condition (2010)};
-        \node [const, above=0.5*\figwidth of dem] (infra) {infrastructure\\availability};
-        \node [const, left=\figwidth of infra] (sec) {consumption\\by sector};
-        \node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
-
+        \node [block, above=\figwidth of of] (min) {Minimize\\cost};
+        \node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ CO$_2$ target \\ Demand \\ Initial condition (2013)};
         \begin{scope}[on background layer]
@@
         \draw[->, ultra thick] (of) -- (times);
-        %\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
         \draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
@@
         \draw[->, ultra thick] (min) -- (of);
-        \draw[->, ultra thick] (max) -- (of);
-        \draw[->, ultra thick] (dem) -- (const);
-        \draw[->, ultra thick] (dat1) -- (dat);
-        \draw[->, ultra thick] (dat2) -- (dat);
-        \draw[->, ultra thick] (dat3) -- (dat);
-        \draw[->, ultra thick] (dat4) -- (dat);
-        \draw[->, ultra thick] (dat5) -- (dat);
-        \draw[->, ultra thick] (dat6) -- (dat);
-        \draw[->, ultra thick] (dat7) -- (dat);
-        \draw[->, ultra thick] (dat8) -- (dat);
-        \draw[->, ultra thick] (dat9) -- (dat);
-        \draw[->, ultra thick] (dat10) -- (dat);
-        \draw[->, ultra thick] (dat11) -- (dat);
-        \draw[->, ultra thick] (dat12) -- (dat);
-        \draw[->, ultra thick] (dat13) -- (dat);
-        \draw[->, ultra thick] (reg) -- (const);
-        \draw[->, ultra thick] (infra) -- (const);
-        \draw[->, ultra thick] (sec) -- (const);
-        \draw[->, ultra thick] (init) -- (const);
                 \path[->] (mod) edge [ultra thick,out=330,in=0,looseness=10] (mod) node[above right=0.1\figwidth and 0.8\figwidth] {simulate\\2010-2050};                
-                %\draw (mod.east) to [->, ultra thick,looseness=10] (mod.south) node[above right=0.1\figwidth and 0.1\figwidth] {simulate\\2010-2050};
         \end{scope}

### 2019-04-22 doc/2019-04-report/2019-04-i2cner-report.tex
added 2019-04 report
Former-commit-id: 38419788f379127fa4f0ec987c210bafd9b4d541
Former-commit-id: e88cb25f96b22f5f19f7af646ef477e3bf0bb83c

\documentclass[14pt,a4paper]{article} %openany
\usepackage[affil-it]{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{rotating}
%\usepackage{bibtex}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{courier}
\usepackage{verbatim}
\usepackage{url}
\usepackage{float}
\usepackage{array}
\usepackage{breakcites}
\usepackage{gensymb}
%\usepackage[backend=biber]{biblatex}
\usepackage{booktabs,tabularx}
\usepackage{listings}
\usepackage{appendix}
\usepackage{cite}
\usepackage{blindtext}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Palatino font
\usepackage{graphicx} % For the logo
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

%\bibliographystyle{numeric}

\begin{document}

%----------------------------------------------------------------------------------------
%    TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
    \newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here

    \center % Centre everything on the page

    %------------------------------------------------
    %    Title
    %------------------------------------------------

    \HRule\\[0.2cm]

     \begin{minipage}{0.4\textwidth}
        \includegraphics[width=\textwidth]{arfc-logo}
        \end{minipage}%
        \begin{minipage}{0.6\textwidth}
        {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With TIMES\end{flushright}}
        {\begin{flushright}\large\textit{I\textsuperscript{2}CNER Project Report}\end{flushright}}

        \end{minipage}

    \vspace{0.2cm}
    \HRule
    \vspace{0.5cm}

    %------------------------------------------------
    %    Author(s)
    %------------------------------------------------

    \begin{minipage}{0.4\textwidth}
        \begin{flushleft}
            \large
            \textit{Author}\\
            Anshuman \textsc{Chaube}\\
        \end{flushleft}
    \end{minipage}
    ~
    \begin{minipage}{0.4\textwidth}
        \begin{flushright}
            \large
            \textit{Principal Investigator}\\
            Kathryn D. \textsc{Huff} % Supervisor's name
        \end{flushright}
    \end{minipage}

    % If you don't want a supervisor, uncomment the two lines below and comment the code above
    %{\large\textit{Author}}\\
    %John \textsc{Smith} % Your name

    %------------------------------------------------
    %    Report Number
    %------------------------------------------------
    \vspace{1cm}
    \textsc{\LARGE\bfseries UIUC-ARFC-2019-00} \textit{work in progress} % Replace YYYY with the year, NN with report index
    \vspace{0.5cm}

    %------------------------------------------------
    %    Date
    %------------------------------------------------

    \vspace{0.5cm} % Position the date further down the remaining page
    {\large\today} % Date, change the \today to a set date if you want to be precise
    \vspace{0.5cm}

%------------------------------------------------
    %    Headings
    %------------------------------------------------

    \textsc{\LARGE Advanced Reactors and Fuel Cycles}\\[0.25cm] % Research Group

    \textsc{\large Dept. of Nuclear, Plasma, \& Radiological Engineering}\\% Department

    \textsc{\large University of Illiois at Urbana-Champaign}\\ % University

    %------------------------------------------------
    %    Logo
    %------------------------------------------------

    \vspace{0.5cm}
    \includegraphics[scale=0.2]{arfc-logo}
    \includegraphics[scale=0.3]{i2cner_logo}
    \includegraphics[scale=0.2]{wpi_logo}
    \includegraphics[scale=0.04]{ku_logo}\\[1cm] % Include a department/university logo - this will require the graphicx package

    %----------------------------------------------------------------------------------------

    %------------------------------------------------
    %   Funding 
    %------------------------------------------------
    % For this section, either use \vfill to fill the space 
    % or insert funding acknowledgement
    \textit{The authors gratefully acknowledge the support of the International Institute for Carbon
Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.}

\end{titlepage}

\section{Introduction}
We initiated a project in January 2018 to simulate dynamic transition scenarios for the energy industry in Japan to suggest pathways for minimizing carbon emissions. This report is a summary of the progress we have made since the publication of the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{last report}, the challenges we currently face, and the future direction of this research. \\

\subsection{Model details}
The model's assumptions, workings, and the most current list of incorporated technologies is adequately described in the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{previous report}, and the I$^2$CNER Energy Analysis Division workshop \href{https://github.com/arfc/i2cner/tree/master/doc/2019-01-poster}{poster} and \href{https://github.com/arfc/i2cner/tree/master/doc/2019-02-presentation}{presentation}.

\section{Progress Summary}

\subsection{Accomplishments}

The major tasks that were completed leading up to the I$^2$CNER 2019 Annual Symposium are:

\begin{enumerate}
\item \textbf{Changing simulation timeframe to 2013-2100} : As discussed in the previous report, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012, and hence the total CO$_2$ emissions for those years were very slightly off the mark. We sidestepped this problem by changing the initial year to 2013, for which we have exact data from EDMC \cite{noauthor_energy_2018}.

\item \textbf{Incorporation of semi-discrete investment sizes}: Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}. It is desirable that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation/investment structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}. \\

\item \textbf{Incorporation of the contribution-to-peak (C2Peak) \citep{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby introducing a notion of the unreliability of wind and solar. The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\

\item \textbf{Basic Carbon Capture and Sequestration (CCS) Implementation} : Some CCS data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}. However, no CCS gets deployed in our models. We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only CCS can provide reliable, clean energy. We have identified a few shortcomings in the CCS implementation, some of which contribute to this problem:
\begin{itemize}

\item Large amounts of wind can be deployed. While we were initially reluctant to hard-code things into our model, we have since realized that Japan will not reach its wind potential for a very long time, due to the unusually steep fall of the seabed away from the coast. JWPA projections \cite{heger_wind_2016} are already rather ambitious, and our models should be more closely aligned with them, allowing for at-most a 10-20 \% increase in deployment capacities.

\item Wind is treated as any other energy source, with its variance not truly taken into account (discussed below). Its installed capacity should be matched by storage or natural gas. Possible ways to implement this are discussed later.

\item The costs associated with CCS for Japan have been hard to find as Japan, instead of building CCS pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$. Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.

\end{itemize}

\end{enumerate}

\section{Future Work}

\subsection{Critical Goals}

\begin{itemize}

\item \textbf{Restrict maximum wind capacity:} To align the model more closely with JWPA predictions \cite{heger_wind_2016}, the maximum allowed capacities for wind should be reduced in the respective MaxCAP files.

\item \textbf{Associate wind (and solar) with natural gas/storage:} There may be two ways to accomplish this:

\begin{itemize}

\item Replace annually averaged capacity factors and/or C2Peak factors with seasonal(summer/winter) and diurnal (day/night) (i.e. SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors/C2Peak factors. The model may then automatically deploy natural gas to supplement wind and solar. \textbf{This seems to be a more straightforward solution.}

\item Define a relationship between the capacities of wind and natural gas. Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the TIMES documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and quite possibly the assistance of the VEDA forum. \textbf{This is the more challenging fix to this problem.}

\end{itemize}

\item \textbf{Incorporation of Japan-specific costs for wind:} When incorporating JWPA predictions, it will be necessary to split off-shore wind into fixed and floating types. The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.

\item \textbf{Revise CCS structure:}

\item \textbf{Revise nuclear structure:}

\end{itemize}

\bibliographystyle{ieeetr}
%\addbibresource{2018-chaube-i2cner-report-sept}
\bibliography{2018-chaube-i2cner-report-sept}

%\bibliographystyle{plain}

%\printbibliography

\end{document}

### 2019-04-22 doc/2019-04-report/plot/plotter-err.py

@@ -1,0 +1,45 @@
+import xlrd
+import numpy as np
+import matplotlib.pyplot as plt
+
+title='CO2 emission values relative error'
+yax='Error (%)'
+format='.png'
+fname='co2-err'+format
+
+f1='co2-error.xlsx'
+
+wb=xlrd.open_workbook(f1)
+sheet = wb.sheet_by_index(0)
+
+r=int(sheet.nrows)
+c=int(sheet.ncols)
+
+#labels=[]
+x=np.zeros(c-1)
+y=np.zeros((r-1,c-1))
+
+#for i in range(1,r):
+#    labels.append(sheet.cell_value(i,0))
+
+for i in range(1,c):
+    x[i-1]=sheet.cell_value(0,i)
+    for j in range(1,r):
+        y[j-1,i-1]=sheet.cell_value(j,i)
+                              
+fig = plt.figure()
+ax1=fig.add_subplot(111)
+
+ax1.scatter(x,y[0,:],marker='o',color='red')
+plt.plot(x,y[0,:],linestyle='dashed',color='blue')
+#ax1.scatter(x,y[1,:],marker='o',color='red')
+#plt.plot(x,y[1,:],linestyle='dashed',color='red')
+#plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 14})
+plt.xlabel('Years',fontsize='14')
+plt.ylabel(yax,fontsize='14')
+plt.title(title,fontsize='16')
+#plt.grid(True)
+#plt.show()
+plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
+
+

### 2019-04-24 doc/2019-04-report/2019-04-i2cner-report.tex
closes #80
Former-commit-id: 38c7da17387c3ee86eb91a8e4610ea0ac63cb56d
Former-commit-id: 5283e5c2374c0f307c06ad010f7976f112934692

@@
 \begin{document}
+\sloppy
 
@@
 \begin{enumerate}
-\item \textbf{Changing simulation timeframe to 2013-2100} : As discussed in the previous report, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012, and hence the total CO$_2$ emissions for those years were very slightly off the mark.
+\item \textbf{Changing simulation timeframe to 2013-2100:} As discussed in the previous report, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012, and hence the total CO$_2$ emissions for those years were very slightly off the mark.
 We sidestepped this problem by changing the initial year to 2013, for which we have exact data from EDMC \cite{noauthor_energy_2018}.
 
-\item \textbf{Incorporation of semi-discrete investment sizes}: Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
-It is desirable that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation/investment structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.
-\\
+\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
+It is desirable that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
 
-\item \textbf{Incorporation of the contribution-to-peak (C2Peak) \citep{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
+\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
 This introduces a notion of an energy resource's reliability, thereby introducing a notion of the unreliability of wind and solar.
@@
 We have identified a few shortcomings in the CCS implementation, some of which contribute to this problem:
+
 \begin{itemize}
@@
 \subsection{Critical Goals}
+These targets are urgent and necessary.
 
 \begin{itemize}
+
+\item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
+Current trends indicate the opposite.
+While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.
 
@@
 
-\item Replace annually averaged capacity factors and/or C2Peak factors with seasonal(summer/winter) and diurnal (day/night) (i.e.
+\item Replace annually averaged capacity factors and/or C2Peak factors with seasonal(sumer/winter) and diurnal (day/night) (i.e.
 SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors/C2Peak factors.
@@
 
-\item \textbf{Revise CCS structure:}
+\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the corresponding fossil fuel.
+In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions.
+Such an implementation should \textbf{not} include retrofitting of CCS (i.e.
+adding carbon capture to previously deployed fossil fuel capacity - discussed below).
+While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and:
+\begin{itemize}
 
-\item \textbf{Revise nuclear structure:}
+\item Neglect the difference between Japan and the US, assuming that the government will foot the bill of setting up the CCS shipping network and offshore storage sites.
+Japan's shipping network is already well-developed, and further imprmay also tie into Japan's plans to import hydrogen from Australia, steel and fossil fuel from
+
+\item Roughly increase the cost by a small percentage, since the Japanese CCS shipping network and offshore storage sites will be more expensive.
+
+\item Attempt to conduct a rough ab-initio analysis, by find the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites.
+
+\end{itemize}
+
+\item \textbf{Revise nuclear costs:} Current models include the ideal cost of nuclear, but actual costs are often higher due to delays in construction.
+This is accurately reflected in data from EIA, which already exists in our \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs/fossil-ccs-nuc.xlsx}{repository}.
+This needs to be incorporated into our models to reduce over-deployment of nuclear.
+
+\end{itemize}
+
+\subsection{Desired Goals}
+These targets are not urgent but are strongly recommended for improving our results.
+
+\begin{itemize}
+
+\item Make electricity demand process more realistic:
+
+\begin{itemize}
+\item At the very least demand should increase at +1.7 \% per year until 2030 as per METI projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.
+
+\item More accurate data for 2030-2050 should be sought to further improve upon this, if possible.
+
+\end{itemize}
+
+\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated.
+For example, the levelized cost of electricity (LCoE) for each scenario for different years (say 2030,2050,2100) could be calculated, or quite simply the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
+
+\item Incorporate more I$^2$CNER technology, such as perovskite solar cells, fuel cells for storage etc.
+
+\end{itemize}
+
+\subsection{Stretch Goals}
+These targets are neither urgent nor necessary.
+
+\begin{itemize}
+
+\item \textbf{Implement CCS retrofitting:} The modelling process for this is somewhat complicated.
+One would have to track CO$_2$ emitted from different fossil fuels separately by creating TIMES CO$_2$ commodities for coal, oil and petroleum.
+Next, the process that converts this CO$_2$ to captured CO$_2$ and atmospheric CO$_2$ would need to be defined.
+The total amount of CO$_2$ captured may not be greater than the total capacity of the reservoirs around Japan \cite{kato_energy_2016}.\\
+The data for retrofitting in Japan is not easily available. Generic CCS data from other countries may be used if necessary.\\
+
+\item \textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially I$^2$CNER technology, to maximize their efficacy and penetration.
 

### 2019-04-24 doc/2019-04-report/2019-04-i2cner-report.tex
updated 2019-04 report
Former-commit-id: 1ae7716de02046a42a2cde65b0f27340c65ed792
Former-commit-id: 61b0be1c8de10aa75e6916b5de3224f77b0c78cc

@@
 \subsection{Model details}
-The model's assumptions, workings, and the most current list of incorporated technologies is adequately described in the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{previous report}, and the I$^2$CNER Energy Analysis Division workshop \href{https://github.com/arfc/i2cner/tree/master/doc/2019-01-poster}{poster} and \href{https://github.com/arfc/i2cner/tree/master/doc/2019-02-presentation}{presentation}.
+The model's assumptions, workings, and the most current list of incorporated technologies is adequately described in the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{previous report}, and the 2019 I$^2$CNER Energy Analysis Division workshop \href{https://github.com/arfc/i2cner/tree/master/doc/2019-01-poster}{poster} and \href{https://github.com/arfc/i2cner/tree/master/doc/2019-02-presentation}{presentation}.
 
@@
 \item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
-It is desirable that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
+It is desired that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
 
 \item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
-This introduces a notion of an energy resource's reliability, thereby introducing a notion of the unreliability of wind and solar.
+This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability.
 The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\
@@
 
-\item The costs associated with CCS for Japan have been hard to find as Japan, instead of building CCS pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
+\item We may be overesetimating CCS costs.
+The costs associated with CCS for Japan have been hard to find as Japan, instead of building CCS pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
 Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.
@@
 
-\begin{itemize}
+\begin{enumerate}
 
 \item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
-Current trends indicate the opposite.
+Current trends support this assumption.
 While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.
+
+\item \textbf{Incorporate semi-discrete investment sizes:} As stated previously, all DSCINV files must include semi-discrete capacity installation sizes for consistency.
 
@@
 
-\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the corresponding fossil fuel.
+\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits.
 In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions.
@@
 adding carbon capture to previously deployed fossil fuel capacity - discussed below).
-While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and:
+While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and do one of the following:
 \begin{itemize}
@@
 \item Neglect the difference between Japan and the US, assuming that the government will foot the bill of setting up the CCS shipping network and offshore storage sites.
-Japan's shipping network is already well-developed, and further imprmay also tie into Japan's plans to import hydrogen from Australia, steel and fossil fuel from
 
@@
 
-\item Attempt to conduct a rough ab-initio analysis, by find the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites.
+\item Attempt to conduct a rough ab-initio analysis by finding the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites by ship.
 
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 \begin{itemize}
-\item At the very least demand should increase at +1.7 \% per year until 2030 as per METI projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.
+\item At the very least, demand should increase at +1.7 \% per year until 2030 as per METI projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.
 
@@
 \item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated.
-For example, the levelized cost of electricity (LCoE) for each scenario for different years (say 2030,2050,2100) could be calculated, or quite simply the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
+For example, the levelized cost of electricity (LCoE) for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
 
@@
 \subsection{Stretch Goals}
-These targets are neither urgent nor necessary.
+At this time, these targets are neither urgent nor necessary.
 

### 2019-04-25 doc/2018-09-report/2019-04-i2cner-report.tex
updated reports
Former-commit-id: c59bae1eb3e129670245586fe9aa8d179648867e
Former-commit-id: fded899746f4578d27cd950d810e347eebac6e56

--- 2019-04-24 doc/2019-04-report/2019-04-i2cner-report.tex
@@
 This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability.
-The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\
+The values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as they are annually averaged.\\
 
@@
 However, no CCS gets deployed in our models.
-We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only CCS can provide reliable, clean energy.
-We have identified a few shortcomings in the CCS implementation, some of which contribute to this problem:
+We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only CCS can provide reliable, clean energy in conjunction with renewables.
+We have identified a few shortcomings in our model, some of which contribute to this problem:
 
@@
 
-\item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
+\item \textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
 Current trends support this assumption.
-While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.
+While a few models already exclude oil-based energy, other models should also replace it with combined-cycle electricity generation for the sake of consistency.
 
@@
 
-\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits.
+\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits \cite{kato_energy_2016}.
 In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions.

### 2019-04-25 doc/2018-09-report/plot/plotter-el.py

@@ -5,7 +5,7 @@ import matplotlib.pyplot as plt
 title='Electricity generation from different sources'
 yax='Electricity generated (GWh)'
 format='.png'
-fname='elc-2016'+fname
+fname='elc-2016'+format
 
 f1='energy2016.xlsx'
 
@@ -30,6 +30,7 @@ for i in range(1,c):
 fig, ax = plt.subplots()
 ax.stackplot(x,y)
 plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 10})
+ax.set_xlim(2011,2016)
 plt.xlabel('Years',fontsize='12')
 plt.ylabel(yax,fontsize='12')
 plt.title(title,fontsize='16')

### 2019-04-25 doc/2018-09-report/plot/plotter-err.py

@@ -1,6 +1,8 @@
 import xlrd
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.ticker import FormatStrFormatter
+
 
 title='CO2 emission values relative error'
 yax='Error (%)'
@@ -30,8 +32,9 @@ for i in range(1,c):
 fig = plt.figure()
 ax1=fig.add_subplot(111)
 
-ax1.scatter(x,y[0,:],marker='o',color='red')
-plt.plot(x,y[0,:],linestyle='dashed',color='blue')
+ax1.scatter(x.astype(int),y[0,:],marker='o',color='red')
+plt.plot(x.astype(int),y[0,:],linestyle='dashed',color='blue')
+ax1.xaxis.set_major_formatter(FormatStrFormatter('%.0f'))
 #ax1.scatter(x,y[1,:],marker='o',color='red')
 #plt.plot(x,y[1,:],linestyle='dashed',color='red')
 #plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 14})

### 2019-05-08 doc/2019-05-report/2019-05-i2cner-report.tex
added may report draft, moved old reports to may report folder
Former-commit-id: 69534b340da38c24f818d7771b0a9c26357987e9
Former-commit-id: b30f246ade50463be3ff7ebbed8367ed10593076

\documentclass[14pt,a4paper]{article} %openany
\usepackage[affil-it]{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{rotating}
%\usepackage{bibtex}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{courier}
\usepackage{verbatim}
\usepackage{url}
\usepackage{hyperref}
\usepackage{float}
\usepackage{array}
\usepackage{breakcites}
\usepackage{gensymb}
%\usepackage[backend=biber]{biblatex}
\usepackage{booktabs,tabularx}
\usepackage{listings}
\usepackage{appendix}
\usepackage{cite}
\usepackage{blindtext}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Palatino font
\usepackage{graphicx} % For the logo
\usepackage[acronym,toc]{glossaries}
\include{acros}

%\bibliographystyle{numeric}

\begin{document}

%----------------------------------------------------------------------------------------
%    TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
    \newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here

    \center % Centre everything on the page

    %------------------------------------------------
    %    Title
    %------------------------------------------------

    \HRule\\[0.2cm]

     \begin{minipage}{0.4\textwidth}
        \includegraphics[width=\textwidth]{arfc-logo}
        \end{minipage}%
        \begin{minipage}{0.6\textwidth}
        {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With \gls{TIMES} \end{flushright}}
        {\begin{flushright}\large\textit{\gls{I$^2$CNER}  Project Report}\end{flushright}}

        \end{minipage}

    \vspace{0.2cm}
    \HRule
    \vspace{0.5cm}

    %------------------------------------------------
    %    Author(s)
    %------------------------------------------------

    \begin{minipage}{0.4\textwidth}
        \begin{flushleft}
            \large
            \textit{Author}\\
            Anshuman \textsc{Chaube}\\
        \end{flushleft}
    \end{minipage}
    ~
    \begin{minipage}{0.4\textwidth}
        \begin{flushright}
            \large
            \textit{Principal Investigator}\\
            Kathryn D. \textsc{Huff} % Supervisor's name
        \end{flushright}
    \end{minipage}

    % If you don't want a supervisor, uncomment the two lines below and comment the code above
    %{\large\textit{Author}}\\
    %John \textsc{Smith} % Your name

    %------------------------------------------------
    %    Report Number
    %------------------------------------------------
    \vspace{1cm}
    \textsc{\LARGE\bfseries UIUC-ARFC-2018-00} \textit{work in progress} % Replace YYYY with the year, NN with report index
    \vspace{0.5cm}

    %------------------------------------------------
    %    Date
    %------------------------------------------------

    \vspace{0.5cm} % Position the date further down the remaining page
    {\large\today} % Date, change the \today to a set date if you want to be precise
    \vspace{0.5cm}

%------------------------------------------------
    %    Headings
    %------------------------------------------------

    \textsc{\LARGE Advanced Reactors and Fuel Cycles}\\[0.25cm] % Research Group

    \textsc{\large Dept. of Nuclear, Plasma, \& Radiological Engineering}\\% Department

    \textsc{\large University of Illiois at Urbana-Champaign}\\ % University

    %------------------------------------------------
    %    Logo
    %------------------------------------------------

    \vspace{0.5cm}
    \includegraphics[scale=0.2]{arfc-smol}
    \includegraphics[scale=0.3]{i2cner-logo}
    \includegraphics[scale=0.2]{wpi-logo}
    \includegraphics[scale=0.04]{ku-logo}\\[1cm] % Include a department/university logo - this will require the graphicx package

    %----------------------------------------------------------------------------------------

    %------------------------------------------------
    %   Funding 
    %------------------------------------------------
    % For this section, either use \vfill to fill the space 
    % or insert funding acknowledgement
    \textit{The authors gratefully acknowledge the support of the International Institute for Carbon
Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.}

\end{titlepage}

\section{Introduction}
We initiated a project in January 2018 to simulate dynamic transition scenarios for the energy industry in Japan to suggest pathways for minimizing carbon emissions. This report is a summary of the progress we have made so far, the challenges we currently face, and the future direction of this research.

\section{Progress Summary}

\subsection{Accomplishments}

The tasks that we performed can be divided into two categories: technical tasks associated with implementation of details and features in our model, and data collection and organization. Our accomplishments have been:

\begin{itemize}

\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005} \cite{gargiulo_documentation_2005} generator. We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes. Therefore, we took the time to develop our own model files, which we have progressively refined since then.\\

At the same time, we collected data pertaining to electricity generation and carbon emissions.

\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan. \\

While collecting this data, we noticed that the \gls{EDMC} databank that we have been relying on has no data for the amount of electricity generated from individual fossil fuels for the years 2011-12. Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category titled "thermal". Further, the 2016 data seems slightly inconsistent across different data tables in the \gls{EDMC} databank. The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.

\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from \gls{EDMC} was consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018} \cite{noauthor_iea_2017} \cite{noauthor_japan_2017}. We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles. \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}

\item \textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan. The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients. We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018} \cite{noauthor_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.

\item \textbf{October 2018 – April 2019:}

\begin{enumerate}

\item \textbf{Changing simulation timeframe to 2013-2100:} As discussed in the previous report, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012, and hence the total CO$_2$ emissions for those years were very slightly off the mark. We sidestepped this problem by changing the initial year to 2013, for which we have exact data from \gls{EDMC} \cite{noauthor_energy_2018}.\\

\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}. It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\

\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability. The values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as they are annually averaged.\\

\item \textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}. However, no \gls{CCS} gets deployed in our models. We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only \gls{CCS} can provide reliable, clean energy in conjunction with renewables. We have identified a few shortcomings in our model, some of which contribute to this problem:

\begin{itemize}

\item Large amounts of wind can be deployed. While we were initially reluctant to hard-code things into our model, we have since realized that Japan will not reach its wind potential for a very long time, due to the unusually steep fall of the seabed away from the coast. \gls{JWPA} projections \cite{heger_wind_2016} are already rather ambitious, and our models should be more closely aligned with them, allowing for at-most a 10-20 \% increase in deployment capacities.

\item Wind is treated as any other energy source, with its variance not truly taken into account (discussed below). Its installed capacity should be matched by storage or natural gas. Possible ways to implement this are discussed later.

\item We may be overestimating \gls{CCS} costs. The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$. Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.

\end{itemize}

\end{enumerate}

\end{itemize}

\section{Assumptions and Model Data}

	Our model focuses on the electricity generation sector. The following assumptions and limitations are present in our model:

\begin{enumerate}

\item All the energy generated by a given process is transferred to the grid without losses to satisfy the demand process. Since the \gls{EDMC} data has values in terms of units of electrical energy produced (GWh), we have had no need for incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors.

\item The coal and natural gas capacities are held constant throughout the simulation.

\item \gls{LCoE} for fossil fuels has been held constant throughout the simulation \cite{chapman_energy_2018} \cite{noauthor_lazards_2017} \cite{noauthor_iea_2017}. \gls{LCoE} projections for wind and solar have been incorporated \cite{noauthor_lazards_2017}. However, the implementation of costs associated with electricity generation is still under-development.

\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the \gls{EDMC} data \cite{noauthor_energy_2018} indicating declining use of oil.

\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's \gls{ABWR} \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}, with efficiency values based on existing \gls{ABWR}s in operation. It has been assumed that there can be as many as 22 \gls{ABWR}s constructed in between 2020-2100, with the number of reactors constructed during the earlier years based on the number of projects currently under consideration for construction, and the pace of construction based on similar reactors constructed in Japan. All nuclear technology, current or future, has a finite lifetime based realistic values.

\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking.

\item Hydropower – held constant at current levels.

\item Geothermal is expanded to its maximum potential \cite{noauthor_geothermal_2018}.

\item The values of electricity generated from coal, oil and natural gas in 2011 and 2012 have been estimated using previous years' values and CO\textsubscript{2} emissions.

\item The CO\textsubscript{2} emission constraints implemented are very lax and not representative of any constraints that the Japanese government or \gls{I$^2$CNER}  wish to implement. Since we do not have accurate data for electricity generated from fossil fuels for the years 2011, 2012, and 2016, we have been focusing our efforts on modelling CO\textsubscript{2} emissions from previous years accurately.
\end{enumerate}

\section{Results}

Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by \gls{EDMC}:

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{elc-2016}
\caption{Electricity generated from different sources}
\end{figure}

The emitted CO\textsubscript{2} values for the period 2011-16 are as follows. The error is at most 5.7\% \ref{co2err}, which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{co2-2016}
\caption{CO2 emissions from electricity generation compared with actual emissions reported by \gls{MoE}, Japan}
\end{figure}

\begin{figure}[H] \label{co2err}
\centering
\includegraphics[scale=0.6]{co2-err}
\caption{Relative error in CO2 emissions.}
\end{figure}

\subsection{Post Hoc Analysis and Challenges}

The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers. The primitive, black-box like nature of the software often produces inexplicable, illogical results and inhibits efficient debugging. Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule, by about three months. \\

In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, \gls{EDMC} has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called "thermal" in its databank. This complicates the process of estimating CO\textsubscript{2} emissions from these energy sources, since each fossil fuel has a different emission coefficient. Losing the primary data that we have been relying on has affected our pace and the reproducibility of our research significantly. The \gls{EDMC} databank figures in GWh, instead of in tons of coal or oil, have influenced our model's simplistic design, as discussed previously. Our efforts to find similar data have been unsuccessful. Switching to data in terms of the quantity of raw fossil fuels consumed instead of GWh of electricity produced may require a substantial revision of our model.

\section{Future Work}

\subsection{Critical Goals}
These targets are urgent and necessary.

\begin{enumerate}

\item \textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence. Current trends support this assumption. While a few models already exclude oil-based energy, other models should also replace it with combined-cycle electricity generation for the sake of consistency.

\item \textbf{Incorporate semi-discrete investment sizes:} As stated previously, all \gls{DSCINV} files must include semi-discrete capacity installation sizes for consistency.

\item \textbf{Restrict maximum wind capacity:} To align the model more closely with JWPA predictions \cite{heger_wind_2016}, the maximum allowed capacities for wind should be reduced in the respective \gls{MaxCAP} files.

\item \textbf{Associate wind (and solar) with natural gas/storage:} There may be two ways to accomplish this:

\begin{itemize}

\item Replace annually averaged capacity factors and/or \gls{C2Peak} factors with seasonal(sumer/winter) and diurnal (day/night) (i.e. SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors/\gls{C2Peak} factors. The model may then automatically deploy natural gas to supplement wind and solar. \textbf{This seems to be a more straightforward solution.}

\item Define a relationship between the capacities of wind and natural gas. Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the \gls{TIMES} documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and quite possibly the assistance of the VEDA forum. \textbf{This is the more challenging fix to this problem.}

\end{itemize}

\item \textbf{Incorporation of Japan-specific costs for wind:} When incorporating \gls{JWPA} predictions, it will be necessary to split off-shore wind into fixed and floating types. The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.

\item \textbf{Revise \gls{CCS} structure:} Simplified \gls{CCS} needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits \cite{kato_energy_2016}. In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions. Such an implementation should \textbf{not} include retrofitting of \gls{CCS} (i.e. adding carbon capture to previously deployed fossil fuel capacity - discussed below). While we do not have Japan-specific data for \gls{CCS}, we can simplify our model by using data from the US and do one of the following:
\begin{itemize}

\item Neglect the difference between Japan and the US, assuming that the government will foot the bill of setting up the \gls{CCS} shipping network and offshore storage sites.

\item Roughly increase the cost by a small percentage, since the Japanese \gls{CCS} shipping network and offshore storage sites will be more expensive.

\item Attempt to conduct a rough ab-initio analysis by finding the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites by ship.

\end{itemize}

\item \textbf{Revise nuclear costs:} Current models include the ideal cost of nuclear, but actual costs are often higher due to delays in construction. This is accurately reflected in data from \gls{EIA}, which already exists in our \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs/fossil-ccs-nuc.xlsx}{repository}. This needs to be incorporated into our models to reduce over-deployment of nuclear.

\end{enumerate}

\subsection{Desired Goals}
These targets are not urgent but are strongly recommended for improving our results.

\begin{itemize}

\item Make electricity demand process more realistic:

\begin{itemize}
\item At the very least, demand should increase at +1.7 \% per year until 2030 as per \gls{METI} projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.

\item More accurate data for 2030-2050 should be sought to further improve upon this, if possible.

\end{itemize}

\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated. For example, the \gls{LCoE}for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.

\item Incorporate more \gls{I$^2$CNER} technology, such as perovskite solar cells, fuel cells for storage etc.

\end{itemize}

\subsection{Stretch Goals}
At this time, these targets are neither urgent nor necessary.

\begin{itemize}

\item \textbf{Implement \gls{CCS} retrofitting:} The modelling process for this is somewhat complicated. One would have to track CO$_2$ emitted from different fossil fuels separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum. Next, the process that converts this CO$_2$ to captured CO$_2$ and atmospheric CO$_2$ would need to be defined. The total amount of CO$_2$ captured may not be greater than the total capacity of the reservoirs around Japan \cite{kato_energy_2016}.\\
The data for retrofitting in Japan is not easily available. Generic \gls{CCS} data from other countries may be used if necessary.\\

\item \textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially \gls{I$^2$CNER} technology, to maximize their efficacy and penetration.

\end{itemize}

\bibliographystyle{ieeetr}
%\addbibresource{2018-chaube-i2cner-report-sept}
\bibliography{2018-chaube-i2cner-report-sept}

%\bibliographystyle{plain}

%\printbibliography

\end{document}

### 2019-05-08 doc/2019-05-report/acros.tex
added may report draft, moved old reports to may report folder
Former-commit-id: 69534b340da38c24f818d7771b0a9c26357987e9
Former-commit-id: b30f246ade50463be3ff7ebbed8367ed10593076

%\newacronym{<++>}{<++>}{<++>}
%\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{EDMC}{EDMC}{Energy and Data Modelling Center}
\newacronym{FEPC}{FEPC}{Federation of Electric Power Companies of Japan}
\newacronym{EIA}{EIA}{Energy Information Administration}
\newacronym{TIMES}{TIMES}{The Integrated Markal-EFOM System}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon-Neutral Energy Research}
\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
\newacronym{JWPA}{JWPA}{Japan Wind Power Association}
\newacronym{LCoE}{LCoE}{Levelized Cost of Electricity}
\newacronym{ABWR}{ABWR}{Advanced Boiling Water Reactors}
\newacronym{MoE}{MoE}{Ministry of Environment}
\newacronym{METI}{METI}{Ministry of Environment}{Ministry of Economy, Trade and Industry}
\newacronym{DSCINV}{DSCINV}{Discrete Investment}
\newacronym{C2Peak}{C2Peak}{Contribution to Peak}
\newacronym{MaxCAP}{MaxCAP}{Maximum Capacity}
%\acro{H2O}[$\mathrm{H_2O}$]{water}

### 2019-05-08 doc/2019-05-report/old drafts/plot/plotter-el.py

@@ -1,0 +1,41 @@
+import xlrd
+import numpy as np
+import matplotlib.pyplot as plt
+
+title='Electricity generation from different sources'
+yax='Electricity generated (GWh)'
+format='.png'
+fname='elc-2016'+format
+
+f1='energy2016.xlsx'
+
+wb=xlrd.open_workbook(f1)
+sheet = wb.sheet_by_index(0)
+
+r=int(sheet.nrows)
+c=int(sheet.ncols)
+
+labels=[]
+x=np.zeros(c-1)
+y=np.zeros((r-1,c-1))
+
+for i in range(1,r):
+    labels.append(sheet.cell_value(i,0))
+
+for i in range(1,c):
+    x[i-1]=sheet.cell_value(0,i)
+    for j in range(1,r):
+        y[j-1,i-1]=sheet.cell_value(j,i)
+                              
+fig, ax = plt.subplots()
+ax.stackplot(x,y)
+plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 10})
+ax.set_xlim(2011,2016)
+plt.xlabel('Years',fontsize='12')
+plt.ylabel(yax,fontsize='12')
+plt.title(title,fontsize='16')
+plt.grid(True)
+#plt.show()
+plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
+
+

### 2019-05-08 doc/2019-05-report/old drafts/plot/plotter-err.py

@@ -1,0 +1,48 @@
+import xlrd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import FormatStrFormatter
+
+
+title='CO2 emission values relative error'
+yax='Error (%)'
+format='.png'
+fname='co2-err'+format
+
+f1='co2-error.xlsx'
+
+wb=xlrd.open_workbook(f1)
+sheet = wb.sheet_by_index(0)
+
+r=int(sheet.nrows)
+c=int(sheet.ncols)
+
+#labels=[]
+x=np.zeros(c-1)
+y=np.zeros((r-1,c-1))
+
+#for i in range(1,r):
+#    labels.append(sheet.cell_value(i,0))
+
+for i in range(1,c):
+    x[i-1]=sheet.cell_value(0,i)
+    for j in range(1,r):
+        y[j-1,i-1]=sheet.cell_value(j,i)
+                              
+fig = plt.figure()
+ax1=fig.add_subplot(111)
+
+ax1.scatter(x.astype(int),y[0,:],marker='o',color='red')
+plt.plot(x.astype(int),y[0,:],linestyle='dashed',color='blue')
+ax1.xaxis.set_major_formatter(FormatStrFormatter('%.0f'))
+#ax1.scatter(x,y[1,:],marker='o',color='red')
+#plt.plot(x,y[1,:],linestyle='dashed',color='red')
+#plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 14})
+plt.xlabel('Years',fontsize='14')
+plt.ylabel(yax,fontsize='14')
+plt.title(title,fontsize='16')
+#plt.grid(True)
+#plt.show()
+plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
+
+

### 2019-05-09 doc/2019-05-report/2019-05-i2cner-report.tex
edited challenges, progress report
Former-commit-id: 3baa53917e6174d9d3674b37ef31e6861e5be301
Former-commit-id: 13afd68ce7589a0577d245316b37b72315cf5874

@@
 
-\item \textbf{October 2018 – April 2019:}
+\item \textbf{October 2018 – January 2019:}
 
@@
 We sidestepped this problem by changing the initial year to 2013, for which we have exact data from \gls{EDMC} \cite{noauthor_energy_2018}.\\
-
-\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
-It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
 
@@
 \end{itemize}
+
+\item \textbf{February 2019 – April 2019:}
+
+\begin{enumerate}
+
+\item \textbf{Gradual collection and replacement of \gls{LCoE} data with accurate cost structure:} The results presented at the \gls{I$^2$CNER} Annual \gls{EAD} workshop (see fig.
+\ref{some fig} ) were based entirely on \gls{LCoE} analysis, as \gls{LCoE} data and projections were readily available.
+However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, fixed and variable operation and maintenance costs.
+This is due to the fact that when there is no investment cost associated with an energy source, the deplyment of a resource costs nothing, and hence the model may be retiring such capacity deployments before the end of their lifetime, which has been observed in a few bugs <ADD LINK/FIGURE>
+
+\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
+It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
+
+\end{enumerate}
 
@@
 The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers.
-The primitive, black-box like nature of the software often produces inexplicable, illogical results and inhibits efficient debugging.
-Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule, by about three months.
+The primitive, black-box like nature of the software inhibits efficient debugging.
+Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule.
 \\
 
-In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, \gls{EDMC} has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called "thermal" in its databank.
-This complicates the process of estimating CO\textsubscript{2} emissions from these energy sources, since each fossil fuel has a different emission coefficient.
-Losing the primary data that we have been relying on has affected our pace and the reproducibility of our research significantly.
-The \gls{EDMC} databank figures in GWh, instead of in tons of coal or oil, have influenced our model's simplistic design, as discussed previously.
-Our efforts to find similar data have been unsuccessful.
-Switching to data in terms of the quantity of raw fossil fuels consumed instead of GWh of electricity produced may require a substantial revision of our model.
-
+The \gls{EDMC} is constantly being revised and updated, for both earlier (2010-2013) and later years(2016-).
+Hence, this data is not always consistent or complete, and often secondary sources must be used for verification.
 \section{Future Work}

### 2019-05-14 doc/2019-05-report/2019-05-i2cner-report.tex
added final report
Former-commit-id: 1dba6026135c510c3d164165c9d45c68bf574b47
Former-commit-id: c6913c4087043151330c93b5f7f5f7da86e3005a

@@
         {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With \gls{TIMES} \end{flushright}}
-        {\begin{flushright}\large\textit{\gls{I$^2$CNER}  Project Report}\end{flushright}}
+        {\begin{flushright}\large\textit{\gls{I2CNER}  Project Report}\end{flushright}}
 
@@
 
-\subsection{Accomplishments}
-
 The tasks that we performed can be divided into two categories: technical tasks associated with implementation of details and features in our model, and data collection and organization.
@@
 
-\item \textbf{Changing simulation timeframe to 2013-2100:} As discussed in the previous report, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012, and hence the total CO$_2$ emissions for those years were very slightly off the mark.
+\item \textbf{Changing simulation timeframe to 2013-2100:} As discussed previously, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012.
+Hence the total CO$_2$ emissions for those years were very slightly off the mark.
 We sidestepped this problem by changing the initial year to 2013, for which we have exact data from \gls{EDMC} \cite{noauthor_energy_2018}.\\
 
-\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
-This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability.
-The values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as they are annually averaged.\\
+\item \textbf{Incorporation of the \gls{PEAK} factor \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
+This introduces a notion of an energy resource's reliability.
+Its incorporation reduced excessive deployment of wind and solar.
+The \gls{PEAK} factor values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as the factor is annually averaged.\\
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 
-\item Large amounts of wind can be deployed.
-While we were initially reluctant to hard-code things into our model, we have since realized that Japan will not reach its wind potential for a very long time, due to the unusually steep fall of the seabed away from the coast.
+\item Large amounts of offshore wind can be deployed.
+While we were initially reluctant to hard-code strict capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy due to the unusually deep seabed that is very close to the Japanese coast.
 \gls{JWPA} projections \cite{heger_wind_2016} are already rather ambitious, and our models should be more closely aligned with them, allowing for at-most a 10-20 \% increase in deployment capacities.
 
-\item Wind is treated as any other energy source, with its variance not truly taken into account (discussed below).
-Its installed capacity should be matched by storage or natural gas.
+\item Wind and solar are treated as any other energy source, with their daily or seasonal variance not truly taken into account (discussed below).
+Their installed capacity should be matched by storage or natural gas.
 Possible ways to implement this are discussed later.
@@
 The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
+While this would make \gls{CCS} plants more expensive in Japan, we cannot arrive at an exact figure.
 Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.
 
-\end{itemize}
+\end{enumerate}
 
@@
 
-\item \textbf{Gradual collection and replacement of \gls{LCoE} data with accurate cost structure:} The results presented at the \gls{I$^2$CNER} Annual \gls{EAD} workshop (see fig.
-\ref{some fig} ) were based entirely on \gls{LCoE} analysis, as \gls{LCoE} data and projections were readily available.
-However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, fixed and variable operation and maintenance costs.
-This is due to the fact that when there is no investment cost associated with an energy source, the deplyment of a resource costs nothing, and hence the model may be retiring such capacity deployments before the end of their lifetime, which has been observed in a few bugs <ADD LINK/FIGURE>
+\item \textbf{Gradual collection and replacement of \gls{LCoE} data with accurate cost structure:} The results presented at the \gls{I2CNER} Annual \gls{EAD} workshop \cite{chaube_dynamic_2019} were based entirely on \gls{LCoE} analysis, as \gls{LCoE} data and projections were readily available.
+However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, and fixed and variable \gls{OM} costs.
+This is due to the fact that when there is no investment cost associated with an energy source, the deployment or premature retirement has no cost-penalty.
+This causes resource deployments for unreasonably brief periods (see fig.
+\ref{flatgood} ).
 
-\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
-It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\
+\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
+It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
+\ref{flatbug} and fig.
+\ref{flatgood} ).\\
 
@@
 
-\section{Assumptions and Model Data}
+\section{Model description}
+
+\subsection{Assumptions}
 
@@
 
-\item All the energy generated by a given process is transferred to the grid without losses to satisfy the demand process.
-Since the \gls{EDMC} data has values in terms of units of electrical energy produced (GWh), we have had no need for incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors.
-
-\item The coal and natural gas capacities are held constant throughout the simulation.
+\item All the energy generated by a given process is transferred to the grid without losses.
+Since the \gls{EDMC} data has values in terms of units of electrical energy produced (GWh), we have had no need for incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors for the initially deployed electricity generation sources.
 
@@
 \gls{LCoE} projections for wind and solar have been incorporated \cite{noauthor_lazards_2017}.
-However, the implementation of costs associated with electricity generation is still under-development.
 
-\item Oil-based electricity has been gradually retired due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the \gls{EDMC} data \cite{noauthor_energy_2018} indicating declining use of oil.
+\item Oil-based electricity is retired relatively quickly, and new oil-based electricity deployment is disabled, due to the emphasis of the Japanese government on energy self-sufficiency and minimizing costs, and due to a general trend in the \gls{EDMC} data \cite{noauthor_energy_2018} indicating declining use of oil.
 
-\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's \gls{ABWR} \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}, with efficiency values based on existing \gls{ABWR}s in operation.
-It has been assumed that there can be as many as 22 \gls{ABWR}s constructed in between 2020-2100, with the number of reactors constructed during the earlier years based on the number of projects currently under consideration for construction, and the pace of construction based on similar reactors constructed in Japan.
-All nuclear technology, current or future, has a finite lifetime based realistic values.
+\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's \gls{ABWR} \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}.
 
-\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking.
+\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking type.
 
@@
 
-\item The values of electricity generated from coal, oil and natural gas in 2011 and 2012 have been estimated using previous years' values and CO\textsubscript{2} emissions.
+\item The CO\textsubscript{2} emission constraints implemented are representative of \gls{I2CNER} goals of an 80\% reduction in emissions from 1990 levels.
+\end{enumerate}
 
-\item The CO\textsubscript{2} emission constraints implemented are very lax and not representative of any constraints that the Japanese government or \gls{I$^2$CNER}  wish to implement.
-Since we do not have accurate data for electricity generated from fossil fuels for the years 2011, 2012, and 2016, we have been focusing our efforts on modelling CO\textsubscript{2} emissions from previous years accurately.
-\end{enumerate}
+\subsection{Model Data}
+\begin{itemize}
+
+\item \textbf{Emission coefficients} \cite{noauthor_electricity_2017}: The following data is in gCO$_2$/kWh (i.e.
+nuclear, solar and wind emissions from construction are averaged over the lifetime of the power-production process):
+
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Electricity source} & \textbf{Emissions coefficient}\\
+\hline
+Coal & 943 \\
+\hline
+Natural Gas & 599 \\
+\hline
+Oil & 738 \\
+\hline
+Solar & 38 \\
+\hline
+Wind & 25 \\
+\hline
+Nuclear & 21 \\
+\hline
+Geothermal & 13 \\
+\hline
+Hydropower & 11 \\
+\hline
+\end{tabular}
+
+\item \textbf{\gls{LCoE}}\cite{noauthor_lazards_2017} : \gls{LCoE} data is appropriate for use in processes where a fixed amount of capacity has already been deployed i.e.
+the initial capacity.
+The following \gls{LCoE} data (in million USD/GWh) was used :\\
+
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Electricity source} & \textbf{LCoE}\\
+\hline
+Coal & 0.06 \\
+\hline
+Natural Gas & 0.08 \\
+\hline
+Oil & 0.39 \\
+\hline
+Solar & 0.161 \\
+\hline
+Wind & 0.144 \\
+\hline
+Nuclear & 0.1 \\
+\hline
+Geothermal & 0(fixed capacity) \\
+\hline
+Hydropower & 0 (fixed capacity) \\
+\hline
+\end{tabular}
+
+\item \textbf{Detailed costs} \cite{noauthor_eia_2019} : While the models with conventional energy sources have part of the following cost structure, these somewhat inaccurate and highly idealized figures need to be revised based on the data in the \gls{ARFC} \gls{I2CNER} repository, especially for offshore and onshore wind(current data is for the US from the \gls{EIA} \cite{noauthor_eia_2019}), and for nuclear (to take construction delays into account).
+
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Electricity} & \textbf{Investment} & \textbf{Fixed \gls{OM}} & \textbf{Variable \gls{OM}}\\
+\textbf{source} & \textbf{Cost (MUSD/GWh)} & \textbf{Cost (MUSD/GW)} & \textbf{Cost (MUSD/GWh)}\\
+\hline
+Coal & 3784 & 51.39 & 0.0072\\
+\hline
+Combined Cycle & 794 & 10.3 & 0.0021\\
+\hline
+Solar & 1783 & 22.46 & 0 \\
+\hline
+Onshore Wind & 2773 & 40.85 & 0\\
+\hline
+Offshore Wind & 8380 & 80.14 & 0\\
+\hline
+Nuclear & 1600 & 0.0165 & 0.00933\\
+\hline
+\end{tabular}
+
+\item \textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016} \cite{gargiulo_documentation_2005}:\\
+
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{Electricity source} & \textbf{Efficiency} & \textbf{Utilization Factor} & \textbf{Lifetime (y)} & \textbf{\gls{PEAK} factor}\\
+\hline
+Coal & 0.6 & 0.95 & 60 & 1.0 \\
+\hline
+Combined Cycle & 0.5 & 0.95 & 60 & 1.0 \\
+\hline
+Solar & 0.20-0.27 & 0.13 & 20-25 & 0.42 \\
+\hline
+Onshore Wind & 0.9 & 0.23-0.25 & 25 & 0.20 \\
+\hline
+Offshore Wind & 0.9 & 0.31-0.32 & 25 & 0.20 \\
+\hline
+Nuclear & 0.9 & 0.95 & 60 & 1.0 \\
+\hline
+\end{tabular}
+
+\end{itemize}
 
@@
 
-Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by \gls{EDMC}:
+Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by \gls{EDMC}.
+\gls{LCoE}-based results for the entire time-period are present in the poster presented at the \gls{I2CNER} symposium \cite{chaube_dynamic_2019}.
 
@@
 \caption{Electricity generated from different sources}
+\label{elcic}
 \end{figure}
@@
 \caption{CO2 emissions from electricity generation compared with actual emissions reported by \gls{MoE}, Japan}
+\label{co2ic}
 \end{figure}
@@
 \caption{Relative error in CO2 emissions.}
+\label{co2err}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{elc-2016}
+\caption{Electricity generated from different sources}
+\label{elcic}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{flat-bug}
+\caption{Erroneous results obtained with discrete investment sizes in \gls{DSCINV} files.}
+\label{flatbug}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{flat-good}
+\caption{Accurate results obtained with semi-discrete investment sizes in \gls{DSCINV} files.}
+\label{flatgood}
 \end{figure}
@@
 
+\item \textbf{Replace \gls{LCoE} in all models with a detailed cost structure:} All models must incorporate investment and \gls{OM} costs.
+
 \item \textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
@@
 
-\item Replace annually averaged capacity factors and/or \gls{C2Peak} factors with seasonal(sumer/winter) and diurnal (day/night) (i.e.
-SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors/\gls{C2Peak} factors.
-The model may then automatically deploy natural gas to supplement wind and solar.
-\textbf{This seems to be a more straightforward solution.}
+\item \textbf{Define load curves for solar and wind:} This is the approach suggested by VEDA developers on their forum.
+However, the details of implementation for this particular approach are lacking in the \gls{TIMES} documentation.
+A successful implementation should incorporate the daily and seasonal variation of these electricity sources, and force the model to deploy natural gas or electricity storage to supplement wind and solar.
 
-\item Define a relationship between the capacities of wind and natural gas.
+\item \textbf{Replace annually averaged capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
+SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
+If seasonal versions of these factors exist, this would be the easiest solution.
+\gls{TIMES} Documentation Part II \cite{loulou_documentation_2005} may offer some insights in this regard.
+
+\item \textbf{Define a direct relationship between the capacities of wind and natural gas}:It might be possible to define a direct equation between the capacity of renewables and natural gas.
 Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the \gls{TIMES} documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and quite possibly the assistance of the VEDA forum.
-\textbf{This is the more challenging fix to this problem.}
 
@@
 The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.
+This data needs to be sifted through and incorporated into our model.
 
-\item \textbf{Revise \gls{CCS} structure:} Simplified \gls{CCS} needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits \cite{kato_energy_2016}.
-In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions.
-Such an implementation should \textbf{not} include retrofitting of \gls{CCS} (i.e.
-adding carbon capture to previously deployed fossil fuel capacity - discussed below).
-While we do not have Japan-specific data for \gls{CCS}, we can simplify our model by using data from the US and do one of the following:
+\item \textbf{Revise \gls{CCS} costs:} Simplified \gls{CCS} electricity generation processes exist in our \gls{I2CNER} models.
+These emit only 10\% of the CO$_2$ that their corresponding fossil fuel technology emits \cite{kato_energy_2016}.
+In the model, these look like any other fossil fuel electricity generation process, except they are more expensive and have a significantly smaller emissions coefficient.
+Such an implementation does \textbf{not} include retrofitting of \gls{CCS} (i.e.
+adding point carbon capture capabilities to previously deployed fossil fuel capacity - discussed below).
+While we do not have Japan-specific data for \gls{CCS}, we can use cost data from the US and do one of the following:
 \begin{itemize}
@@
 
-\item Roughly increase the cost by a small percentage, since the Japanese \gls{CCS} shipping network and offshore storage sites will be more expensive.
+\item Roughly increase the cost by a small percentage, since setting up the Japanese \gls{CCS} shipping network and offshore storage sites will result in an increased cost per unit CO$_2$ captured and stored.
 
-\item Attempt to conduct a rough ab-initio analysis by finding the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites by ship.
+\item Attempt to conduct a rough ab-initio analysis to find the cost of capturing, transporting and storing one ton of CO$_2$.
+The cost of capturing CO$_2$ is more or less uniform and readily available \cite{kato_energy_2016}.
+The cost of transport and storage can be estimated by finding the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites by ship.
+The exact costs for this vary based on the scale of the operation.
 
@@
 \item \textbf{Revise nuclear costs:} Current models include the ideal cost of nuclear, but actual costs are often higher due to delays in construction.
-This is accurately reflected in data from \gls{EIA}, which already exists in our \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs/fossil-ccs-nuc.xlsx}{repository}.
+This is accurately reflected in data from \gls{EIA} \cite{noauthor_eia_2019}, which already exists in our \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs/fossil-ccs-nuc.xlsx}{repository}.
 This needs to be incorporated into our models to reduce over-deployment of nuclear.
@@
 \subsection{Desired Goals}
-These targets are not urgent but are strongly recommended for improving our results.
+These targets are not urgent but are required for improving our results.
 
@@
 
-\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated.
-For example, the \gls{LCoE}for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
+\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated and presented with our results.
+For example, the \gls{LCoE} for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
 
-\item Incorporate more \gls{I$^2$CNER} technology, such as perovskite solar cells, fuel cells for storage etc.
+\item Incorporate more \gls{I2CNER} technology, such as perovskite solar cells, fuel cells for storage etc.
 
@@
 \item \textbf{Implement \gls{CCS} retrofitting:} The modelling process for this is somewhat complicated.
-One would have to track CO$_2$ emitted from different fossil fuels separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum.
+One would have to track CO$_2$ emitted from different fossil fuels separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum, to ensure that CO$_2$ from non-fossil fuel sources is not captured by the model.
 Next, the process that converts this CO$_2$ to captured CO$_2$ and atmospheric CO$_2$ would need to be defined.
-The total amount of CO$_2$ captured may not be greater than the total capacity of the reservoirs around Japan \cite{kato_energy_2016}.\\
+The total amount of CO$_2$ captured may not be greater than the total capacity of the \gls{CCS} reservoirs around Japan \cite{kato_energy_2016}.\\
 The data for retrofitting in Japan is not easily available. Generic \gls{CCS} data from other countries may be used if necessary.\\
 
-\item \textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially \gls{I$^2$CNER} technology, to maximize their efficacy and penetration.
+\item \textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially \gls{I2CNER} technology, to maximize their efficacy and penetration.
 

### 2019-05-14 doc/2019-05-report/acros.tex
edited challenges, progress report
Former-commit-id: 3baa53917e6174d9d3674b37ef31e6861e5be301
Former-commit-id: 13afd68ce7589a0577d245316b37b72315cf5874
added final report
Former-commit-id: 1dba6026135c510c3d164165c9d45c68bf574b47
Former-commit-id: c6913c4087043151330c93b5f7f5f7da86e3005a

@@
 \newacronym{TIMES}{TIMES}{The Integrated Markal-EFOM System}
-\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon-Neutral Energy Research}
+\newacronym{I2CNER}{I$^2$CNER}{International Institute for Carbon-Neutral Energy Research}
 \newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
@@
 \newacronym{MoE}{MoE}{Ministry of Environment}
-\newacronym{METI}{METI}{Ministry of Environment}{Ministry of Economy, Trade and Industry}
+\newacronym{METI}{METI}{Ministry of Economy, Trade and Industry}
 \newacronym{DSCINV}{DSCINV}{Discrete Investment}
-\newacronym{C2Peak}{C2Peak}{Contribution to Peak}
+\newacronym{PEAK}{PEAK}{Contribution to Peak}
 \newacronym{MaxCAP}{MaxCAP}{Maximum Capacity}
+\newacronym{EAD}{EAD}{Energy Analysis Division}
+\newacronym{OM}{O\&M}{operation and maintenance}
+\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
 %\acro{H2O}[$\mathrm{H_2O}$]{water}

### 2019-05-14 doc/2019-05-report/2019-05-i2cner-report.tex
updated report - kdh feedback
Former-commit-id: 4d0e84355a6dc6c797c2461e77fd0183597739c1
Former-commit-id: 9abd5dbbfae83e80c770ef52ba5df61c25a6f0e6

@@
 \usepackage{url}
-\usepackage{hyperref}
+\usepackage{hyperref}[hidelinks]
 \usepackage{float}
@@
 \include{acros}
+\usepackage{amssymb}
+\usepackage{pifont}
+\usepackage{xcolor}
+\newcommand{\greencheck}{{\color{green}\checkmark}}
+\newcommand{\xmark}{{\color{red}\ding{55}}}
 
@@
 The tasks that we performed can be divided into two categories: technical tasks associated with implementation of details and features in our model, and data collection and organization.
-Our accomplishments have been:
+Our accomplishments have been:\\
 
-\begin{itemize}
+\textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} generator.
+We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes.
+Therefore, we took the time to develop our own model files, which we have progressively refined since then.
 
-\item \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005} \cite{gargiulo_documentation_2005} generator.
-We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes.
-Therefore, we took the time to develop our own model files, which we have progressively refined since then.\\
+At the same time, we collected data pertaining to electricity generation and carbon emissions.\\
 
-At the same time, we collected data pertaining to electricity generation and carbon emissions.
-
-\item \textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
+\textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
 \\
@@
 Further, the 2016 data seems slightly inconsistent across different data tables in the \gls{EDMC} databank.
-The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.
+The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.\\
 
-\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from \gls{EDMC} was consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018} \cite{noauthor_iea_2017} \cite{noauthor_japan_2017}.
+\textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from \gls{EDMC} was consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018,noauthor_iea_2017, noauthor_japan_2017}.
 We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
-\cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}
+\cite{publicover_japan_2017, dincer_analysis_2011,noauthor_geothermal_2018,heger_wind_2016,noauthor_operational_2013,noauthor_electricity_2017}\\
 
-\item \textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan.
+\textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan.
 The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
-We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018} \cite{noauthor_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.
+We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018,noauthor_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.\\
 
-\item \textbf{October 2018 – January 2019:}
+\paragraph{October 2018 – January 2019:} ~ \\
 
-\begin{enumerate}
-
-\item \textbf{Changing simulation timeframe to 2013-2100:} As discussed previously, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012.
+\textbf{Changing simulation timeframe to 2013-2100:} As discussed previously, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012.
 Hence the total CO$_2$ emissions for those years were very slightly off the mark.
@@
 
-\item \textbf{Incorporation of the \gls{PEAK} factor \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand.
+\textbf{Incorporation of the \gls{PEAK} factor \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's installed  capacity that is guaranteed to be available during peak demand.
 This introduces a notion of an energy resource's reliability.
@@
 
-\item \textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
+\textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
 However, no \gls{CCS} gets deployed in our models.
@@
 
-\begin{enumerate}
+\begin{itemize}
 
 \item Large amounts of offshore wind can be deployed.
-While we were initially reluctant to hard-code strict capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy due to the unusually deep seabed that is very close to the Japanese coast.
+While we were initially reluctant to hard-code strict installed  capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy due to the unusually deep seabed that is very close to the Japanese coast.
 \gls{JWPA} projections \cite{heger_wind_2016} are already rather ambitious, and our models should be more closely aligned with them, allowing for at-most a 10-20 \% increase in deployment capacities.
@@
 
-\end{enumerate}
+\end{itemize}
 
-\item \textbf{February 2019 – April 2019:}
+\paragraph{February 2019 – April 2019:} ~ \\
 
-\begin{enumerate}
-
-\item \textbf{Gradual collection and replacement of \gls{LCoE} data with accurate cost structure:} The results presented at the \gls{I2CNER} Annual \gls{EAD} workshop \cite{chaube_dynamic_2019} were based entirely on \gls{LCoE} analysis, as \gls{LCoE} data and projections were readily available.
+\textbf{Gradual collection and replacement of \gls{LCOE} data with accurate cost structure:} The results presented at the \gls{I2CNER} Annual \gls{EAD} workshop \cite{chaube_dynamic_2019} were based entirely on \gls{LCOE} analysis, as \gls{LCOE} data and projections were readily available.
 However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, and fixed and variable \gls{OM} costs.
@@
 
-\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
-It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
+\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
+It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete installed  capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
 \ref{flatbug} and fig.
@@
 
-\end{enumerate}
+\section{Model description}
 
-\end{enumerate}
+The objective function \cite{loulou_documentation_2005} for the simulation is the system cost, and the primary constraints are the demand and the CO$_2$ emissions.
+Hence, the simulations determine the energy mix most economically optimal for meeting Japan's future energy needs, when constrained by \gls{I2CNER} CO$_2$ emissions.
 
-\end{itemize}
+\subsection{Key Simulation Parameters}
 
-\section{Model description}
+\begin{tabular}{|c|c|}
+\hline
+Start year & 2013 \\
+\hline
+End Year & 2100 \\
+\hline
+Demand increase rate & +1.7\% p.a. \cite{noauthor_electricity_2017} \\
+\hline
+Conventional sources & Coal, Oil, Natural Gas, Combined Cycle, Nuclear \\
+\hline
+Renewables & Solar, Wind, Geothermal, Hydro \\
+\hline
+Novel tech. & H$_2$(photocatalytic), \gls{CCS} (point-capture)\\
+\hline
+\end{tabular}
+
+\vspace{7mm}
+
+\begin{tabular}{| c | c | c | c | c |}
+\hline
+\textbf{Models}& \textbf{Names}&\textbf{Conventional}&\textbf{Novel}&\textbf{New nuclear}\\
+                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+                  \hline
+1               & conv-free &      \greencheck           &         \xmark       &      \greencheck     \\ 
+2               & conv-nonuc &      \greencheck           &         \xmark       &         \xmark       \\ 
+3               & i2cner-free &      \greencheck           &      \greencheck     &      \greencheck     \\ 
+4               & i2cner-nonuc &      \greencheck           &      \greencheck     &         \xmark       \\
+\hline
+\end{tabular}
 
@@
 
-\item \gls{LCoE} for fossil fuels has been held constant throughout the simulation \cite{chapman_energy_2018} \cite{noauthor_lazards_2017} \cite{noauthor_iea_2017}.
-\gls{LCoE} projections for wind and solar have been incorporated \cite{noauthor_lazards_2017}.
+\item \gls{LCOE} for fossil fuels and nuclear has been held constant throughout the simulation \cite{chapman_energy_2018,noauthor_lazards_2017,noauthor_iea_2017}.
+\gls{LCOE} projections for wind and solar have been incorporated \cite{noauthor_lazards_2017}.
 
@@
 
-\item Nuclear capacity is increased in chunks equivalent to the capacity of GE-Hitachi's \gls{ABWR} \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}.
+\item Nuclear installed  capacity is increased in chunks equivalent to the installed  capacity of GE-Hitachi's \gls{ABWR} \cite{ge_advanced_2007}, which are under consideration for construction \cite{noauthor_electricity_2017}.
 
-\item Solar – Any new solar capacity created by the model has been assumed to be non-tracking type.
+\item Solar – Any new solar installed  capacity created by the model has been assumed to be non-tracking type.
 
@@
 
-\item \textbf{\gls{LCoE}}\cite{noauthor_lazards_2017} : \gls{LCoE} data is appropriate for use in processes where a fixed amount of capacity has already been deployed i.e.
-the initial capacity.
-The following \gls{LCoE} data (in million USD/GWh) was used :\\
+\item \textbf{\gls{LCOE}}\cite{noauthor_lazards_2017} : \gls{LCOE} data is appropriate for use in processes where a fixed amount of installed  capacity has already been deployed i.e.
+the initial installed  capacity.
+The following \gls{LCOE} data (in million USD/GWh) was used :\\
 
@@
 \hline
-\textbf{Electricity source} & \textbf{LCoE}\\
+\textbf{Electricity source} & \textbf{LCOE}\\
 \hline
@@
 \hline
-Geothermal & 0(fixed capacity) \\
+Geothermal & 0(fixed installed  capacity) \\
 \hline
-Hydropower & 0 (fixed capacity) \\
+Hydropower & 0 (fixed installed  capacity) \\
 \hline
@@
 
-\item \textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016} \cite{gargiulo_documentation_2005}:\\
+\item \textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016,gargiulo_documentation_2005}:\\
 
@@
 Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by \gls{EDMC}.
-\gls{LCoE}-based results for the entire time-period are present in the poster presented at the \gls{I2CNER} symposium \cite{chaube_dynamic_2019}.
+\gls{LCOE}-based results for the entire time-period are present in the poster presented at the \gls{I2CNER} symposium \cite{chaube_dynamic_2019}.
 
@@
 \includegraphics[scale=0.6]{co2-2016}
-\caption{CO2 emissions from electricity generation compared with actual emissions reported by \gls{MoE}, Japan}
+\caption{CO2 emissions from electricity generation compared with actual emissions reported by \gls{MOE}, Japan}
 \label{co2ic}
@@
 
-The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers.
+The project has been delayed in part due to limited documentation and customer support available to VEDA users.
 The primitive, black-box like nature of the software inhibits efficient debugging.
@@
 
-\subsection{Critical Goals}
-These targets are urgent and necessary.
+\subsection{Next Steps}
 
-\begin{enumerate}
+\textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
+Current trends support this assumption.
+While a few models already exclude oil-based energy, other models should also replace it with combined-cycle electricity generation for the sake of consistency.\\
 
-\item \textbf{Replace \gls{LCoE} in all models with a detailed cost structure:} All models must incorporate investment and \gls{OM} costs.
+\textbf{Incorporate semi-discrete investment sizes:} As stated previously, all \gls{DSCINV} files must include semi-discrete installed  capacity installation sizes for consistency.\\
 
-\item \textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence.
-Current trends support this assumption.
-While a few models already exclude oil-based energy, other models should also replace it with combined-cycle electricity generation for the sake of consistency.
+\textbf{Restrict maximum wind installed  capacity:} To align the model more closely with JWPA predictions \cite{heger_wind_2016}, the maximum allowed capacities for wind should be reduced in the respective \gls{MaxCAP} files.\\
 
-\item \textbf{Incorporate semi-discrete investment sizes:} As stated previously, all \gls{DSCINV} files must include semi-discrete capacity installation sizes for consistency.
-
-\item \textbf{Restrict maximum wind capacity:} To align the model more closely with JWPA predictions \cite{heger_wind_2016}, the maximum allowed capacities for wind should be reduced in the respective \gls{MaxCAP} files.
-
-\item \textbf{Associate wind (and solar) with natural gas/storage:} There may be two ways to accomplish this:
+\textbf{Associate wind (and solar) with natural gas/storage:} There may be three ways to accomplish this:
 
@@
 
-\item \textbf{Replace annually averaged capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
-SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
+\item \textbf{Replace annually averaged installed  capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
+SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) installed  capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
 If seasonal versions of these factors exist, this would be the easiest solution.
@@
 
-\item \textbf{Define a direct relationship between the capacities of wind and natural gas}:It might be possible to define a direct equation between the capacity of renewables and natural gas.
+\item \textbf{Define a direct relationship between the capacities of wind and natural gas}:It might be possible to define a direct equation between the installed  capacity of renewables and natural gas.
 Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the \gls{TIMES} documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and quite possibly the assistance of the VEDA forum.
@@
 
-\item \textbf{Incorporation of Japan-specific costs for wind:} When incorporating \gls{JWPA} predictions, it will be necessary to split off-shore wind into fixed and floating types.
-The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.
-This data needs to be sifted through and incorporated into our model.
+\textbf{Cost Analysis} - Some metric to compare the transition costs for each scenario should be calculated and presented with our results.
+For example, the \gls{LCOE} for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.\\
 
-\item \textbf{Revise \gls{CCS} costs:} Simplified \gls{CCS} electricity generation processes exist in our \gls{I2CNER} models.
+\textbf{Incorporate more \gls{I2CNER} technology}, such as perovskite solar cells, fuel cells for storage etc.\\
+
+\textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially \gls{I2CNER} technology, to maximize their efficacy and penetration.\\
+
+\subsection{Potential improvements}
+
+\textbf{Revise \gls{CCS} costs:} Simplified \gls{CCS} electricity generation processes exist in our \gls{I2CNER} models.
 These emit only 10\% of the CO$_2$ that their corresponding fossil fuel technology emits \cite{kato_energy_2016}.
@@
 Such an implementation does \textbf{not} include retrofitting of \gls{CCS} (i.e.
-adding point carbon capture capabilities to previously deployed fossil fuel capacity - discussed below).
+adding point carbon capture capabilities to previously deployed fossil fuel installed  capacity - discussed below).
 While we do not have Japan-specific data for \gls{CCS}, we can use cost data from the US and do one of the following:
+
 \begin{itemize}
@@
 
-\item \textbf{Revise nuclear costs:} Current models include the ideal cost of nuclear, but actual costs are often higher due to delays in construction.
+\textbf{Replace \gls{LCOE} in all models with a detailed cost structure:} All models must incorporate investment and \gls{OM} costs.\\
+
+\textbf{Incorporation of Japan-specific costs for wind:} When incorporating \gls{JWPA} predictions, it will be necessary to split off-shore wind into fixed and floating types.
+The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.
+This data needs to be sifted through and incorporated into our model.\\
+
+\textbf{Revise nuclear costs:} Current models include the ideal cost of nuclear, but actual costs are often higher due to delays in construction.
 This is accurately reflected in data from \gls{EIA} \cite{noauthor_eia_2019}, which already exists in our \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs/fossil-ccs-nuc.xlsx}{repository}.
-This needs to be incorporated into our models to reduce over-deployment of nuclear.
+This needs to be incorporated into our models to reduce over-deployment of nuclear.\\
 
-\end{enumerate}
-
-\subsection{Desired Goals}
-These targets are not urgent but are required for improving our results.
-
-\begin{itemize}
-
-\item Make electricity demand process more realistic:
+\paragraph{Make electricity demand process more realistic:}
 
@@
 
-\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated and presented with our results.
-For example, the \gls{LCoE} for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.
-
-\item Incorporate more \gls{I2CNER} technology, such as perovskite solar cells, fuel cells for storage etc.
-
-\end{itemize}
-
-\subsection{Stretch Goals}
-At this time, these targets are neither urgent nor necessary.
-
-\begin{itemize}
-
-\item \textbf{Implement \gls{CCS} retrofitting:} The modelling process for this is somewhat complicated.
+\textbf{Implement \gls{CCS} retrofitting:} The modelling process for this is somewhat complicated.
 One would have to track CO$_2$ emitted from different fossil fuels separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum, to ensure that CO$_2$ from non-fossil fuel sources is not captured by the model.
 Next, the process that converts this CO$_2$ to captured CO$_2$ and atmospheric CO$_2$ would need to be defined.
-The total amount of CO$_2$ captured may not be greater than the total capacity of the \gls{CCS} reservoirs around Japan \cite{kato_energy_2016}.\\
+The total amount of CO$_2$ captured may not be greater than the total installed capacity of the \gls{CCS} reservoirs around Japan \cite{kato_energy_2016}.\\
 The data for retrofitting in Japan is not easily available. Generic \gls{CCS} data from other countries may be used if necessary.\\
-
-\item \textbf{Sensitivity analysis:} To identify optimum thresholds for costs or parameters (like efficiency) of novel technologies, especially \gls{I2CNER} technology, to maximize their efficacy and penetration.
-
-\end{itemize}
 

### 2019-05-15 doc/2019-05-report/old drafts/plot/plotter-el.py
removed old drafts, added report number
Former-commit-id: 28626fa66a45e4a204c974f9175d3074609d40f6
Former-commit-id: eaf61a20d0f5893890ccee8bf22d373ee75c94c3

@@ -1,41 +1,0 @@
-import xlrd
-import numpy as np
-import matplotlib.pyplot as plt
-
-title='Electricity generation from different sources'
-yax='Electricity generated (GWh)'
-format='.png'
-fname='elc-2016'+format
-
-f1='energy2016.xlsx'
-
-wb=xlrd.open_workbook(f1)
-sheet = wb.sheet_by_index(0)
-
-r=int(sheet.nrows)
-c=int(sheet.ncols)
-
-labels=[]
-x=np.zeros(c-1)
-y=np.zeros((r-1,c-1))
-
-for i in range(1,r):
-    labels.append(sheet.cell_value(i,0))
-
-for i in range(1,c):
-    x[i-1]=sheet.cell_value(0,i)
-    for j in range(1,r):
-        y[j-1,i-1]=sheet.cell_value(j,i)
-                              
-fig, ax = plt.subplots()
-ax.stackplot(x,y)
-plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 10})
-ax.set_xlim(2011,2016)
-plt.xlabel('Years',fontsize='12')
-plt.ylabel(yax,fontsize='12')
-plt.title(title,fontsize='16')
-plt.grid(True)
-#plt.show()
-plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
-
-

### 2019-05-15 doc/2019-05-report/old drafts/plot/plotter-err.py

@@ -1,48 +1,0 @@
-import xlrd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import FormatStrFormatter
-
-
-title='CO2 emission values relative error'
-yax='Error (%)'
-format='.png'
-fname='co2-err'+format
-
-f1='co2-error.xlsx'
-
-wb=xlrd.open_workbook(f1)
-sheet = wb.sheet_by_index(0)
-
-r=int(sheet.nrows)
-c=int(sheet.ncols)
-
-#labels=[]
-x=np.zeros(c-1)
-y=np.zeros((r-1,c-1))
-
-#for i in range(1,r):
-#    labels.append(sheet.cell_value(i,0))
-
-for i in range(1,c):
-    x[i-1]=sheet.cell_value(0,i)
-    for j in range(1,r):
-        y[j-1,i-1]=sheet.cell_value(j,i)
-                              
-fig = plt.figure()
-ax1=fig.add_subplot(111)
-
-ax1.scatter(x.astype(int),y[0,:],marker='o',color='red')
-plt.plot(x.astype(int),y[0,:],linestyle='dashed',color='blue')
-ax1.xaxis.set_major_formatter(FormatStrFormatter('%.0f'))
-#ax1.scatter(x,y[1,:],marker='o',color='red')
-#plt.plot(x,y[1,:],linestyle='dashed',color='red')
-#plt.legend(labels,loc='center left',bbox_to_anchor=(1,0.5),prop={'size': 14})
-plt.xlabel('Years',fontsize='14')
-plt.ylabel(yax,fontsize='14')
-plt.title(title,fontsize='16')
-#plt.grid(True)
-#plt.show()
-plt.savefig(fname, format='png', dpi=1000,bbox_inches='tight')
-
-

### 2019-05-20 doc/2019-05-report/2019-05-i2cner-report.tex
corrected hidlinks typo
Former-commit-id: eb42b27e88cb10eb01e90e3fc123754f1cbe1a69
Former-commit-id: 518af30738a25753cc1991b854d8dcb68ad5fa46
removed old drafts, added report number
Former-commit-id: 28626fa66a45e4a204c974f9175d3074609d40f6
Former-commit-id: eaf61a20d0f5893890ccee8bf22d373ee75c94c3
Actually commits changes that close #81
Former-commit-id: ccc518192d8a2fdba183c84dffcbac7c61354edf
Former-commit-id: e2a6f63afb2fcb08822af4f2324b1a9e25d073d2

@@
 \usepackage{url}
-\usepackage{hyperref}[hidelinks]
+\usepackage[hidelinks]{hyperref}
 \usepackage{float}
@@
 \textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} generator.
-We found the format of the developer-prescribed model files restrictive and unsuitable for our purposes.
-Therefore, we took the time to develop our own model files, which we have progressively refined since then.
+Using the simplest VEDA input files from the VEDA tutorial \cite{gargiulo_documentation_2005} as a starting point, we developed our own model files, which we have been progressively refining since then.
 
@@
 
-\textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting the recent trends in electricity demand in Japan.
+\textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting recent trends in electricity demand in Japan.
 \\
 
-While collecting this data, we noticed that the \gls{EDMC} databank that we have been relying on has no data for the amount of electricity generated from individual fossil fuels for the years 2011-12.
-Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category titled "thermal".
-Further, the 2016 data seems slightly inconsistent across different data tables in the \gls{EDMC} databank.
+While collecting these data, we noticed that the \gls{EDMC} databank that we have been relying on has no data for the amount of electricity generated from individual fossil fuels for the years 2011-12.
+Instead, the amount of electricity generated from coal, oil, and natural gas is lumped together in one category entitled "thermal".
+Further, the 2016 data seem slightly inconsistent across different data tables in the \gls{EDMC} databank.
 The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.\\
 
-\textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from \gls{EDMC} was consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018,noauthor_iea_2017, noauthor_japan_2017}.
+\textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to that for previously mentioned energy sources but simpler, since the data obtained for these energy sources from \gls{EDMC} were consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018,noauthor_iea_2017, noauthor_japan_2017}.
 We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
@@
 
-\textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity processes, it was only after incorporating all conventional energy sources that we could move on to fine-tuning CO\textsubscript{2} emission values to ensure they match the actual emissions from Japan.
+\textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity generation processes, it was only after incorporating all conventional energy sources that we could move on to aligning the model's CO\textsubscript{2} emission values with actual emissions from Japan.
 The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
-We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018,noauthor_national_2018} and arrived at reasonable estimates of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.\\
+We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018,noauthor_national_2018} and obtained reasonable approximations of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.\\
 
@@
 Its incorporation reduced excessive deployment of wind and solar.
-The \gls{PEAK} factor values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as the factor is annually averaged.\\
+However, the \gls{PEAK} factor values in the model \cite{kato_energy_2016} neglect the daily or seasonal variation of wind and solar, as the factor is annually averaged.\\
 
-\textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
+\textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  were incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
 However, no \gls{CCS} gets deployed in our models.
@@
 \item Large amounts of offshore wind can be deployed.
-While we were initially reluctant to hard-code strict installed  capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy due to the unusually deep seabed that is very close to the Japanese coast.
-\gls{JWPA} projections \cite{heger_wind_2016} are already rather ambitious, and our models should be more closely aligned with them, allowing for at-most a 10-20 \% increase in deployment capacities.
+While we were initially reluctant to hard-code strict installed  capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy in Japan.
+This is due to the unusually deep seabed that is very close to the Japanese coast.
+\gls{JWPA} projections \cite{heger_wind_2016} are already ambitious, and our models should be closely aligned with them.
 
-\item Wind and solar are treated as any other energy source, with their daily or seasonal variance not truly taken into account (discussed below).
+\item Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
 Their installed capacity should be matched by storage or natural gas.
@@
 However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, and fixed and variable \gls{OM} costs.
-This is due to the fact that when there is no investment cost associated with an energy source, the deployment or premature retirement has no cost-penalty.
-This causes resource deployments for unreasonably brief periods (see fig.
+We believe that when there is no investment cost associated with an energy source, the deployment or premature retirement has no cost-penalty.
+This may cause resource deployments for unrealistically brief periods (see fig.
 \ref{flatgood} ).
 
-\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}.
+\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model} (see table \ref{tab:models}).
 It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete installed  capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
@@
 
-The objective function \cite{loulou_documentation_2005} for the simulation is the system cost, and the primary constraints are the demand and the CO$_2$ emissions.
+The objective function \cite{loulou_documentation_2005} for the simulation is the system cost, and the primary constraints are the demand and the limit on CO$_2$ emissions based on \gls{I2CNER} goals.
 Hence, the simulations determine the energy mix most economically optimal for meeting Japan's future energy needs, when constrained by \gls{I2CNER} CO$_2$ emissions.
@@
 
+The basic features of all simulations are described in the table below.
+The models include some combination of the technologies mentioned in table \ref{tab:basic}; the exact combination for each model is described in table \ref{tab:models}.
+
+\begin{table}[htb]
+\centering
+\caption{\label{tab:basic} Main simulation parameters and features.}
 \begin{tabular}{|c|c|}
@@
 \end{tabular}
+\end{table}
 
-\vspace{7mm}
-
-\begin{tabular}{| c | c | c | c | c |}
+\begin{table}[htb]
+\centering
+\caption{\label{tab:models} Model description.}
+\begin{tabular}{| c | c | c | c |}
 \hline
-\textbf{Models}& \textbf{Names}&\textbf{Conventional}&\textbf{Novel}&\textbf{New nuclear}\\
-                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+\textbf{Model Name}&\textbf{Conventional}&\textbf{Novel}&\textbf{New nuclear}\\
+            &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
                   \hline
-1               & conv-free &      \greencheck           &         \xmark       &      \greencheck     \\ 
-2               & conv-nonuc &      \greencheck           &         \xmark       &         \xmark       \\ 
-3               & i2cner-free &      \greencheck           &      \greencheck     &      \greencheck     \\ 
-4               & i2cner-nonuc &      \greencheck           &      \greencheck     &         \xmark       \\
+conv-free &      \greencheck           &         \xmark       &      \greencheck     \\ 
+conv-nonuc &      \greencheck           &         \xmark       &         \xmark       \\ 
+i2cner-free &      \greencheck           &      \greencheck     &      \greencheck     \\ 
+i2cner-nonuc &      \greencheck           &      \greencheck     &         \xmark       \\
 \hline
 \end{tabular}
+\end{table}
 
@@
 \item All the energy generated by a given process is transferred to the grid without losses.
-Since the \gls{EDMC} data has values in terms of units of electrical energy produced (GWh), we have had no need for incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors for the initially deployed electricity generation sources.
+Since the \gls{EDMC} data have units of electrical energy produced (GWh), we have no need of incorporating data about raw fossil fuel consumption, plant efficiency, and utilization factors for the initially deployed electricity generation sources.
 
@@
 \subsection{Model Data}
-\begin{itemize}
 
-\item \textbf{Emission coefficients} \cite{noauthor_electricity_2017}: The following data is in gCO$_2$/kWh (i.e.
+\textbf{Emission coefficients} \cite{noauthor_electricity_2017}: The following data are in gCO$_2$/kWh (i.e.
 nuclear, solar and wind emissions from construction are averaged over the lifetime of the power-production process):
 
+\begin{table}[htb]
+\centering
+\caption{\label{tab:emi} List of emission coefficients used in the model.}
+\vspace{2mm}
 \begin{tabular}{|c|c|}
@@
 \end{tabular}
+\end{table}
 
-\item \textbf{\gls{LCOE}}\cite{noauthor_lazards_2017} : \gls{LCOE} data is appropriate for use in processes where a fixed amount of installed  capacity has already been deployed i.e.
+\textbf{\gls{LCOE}}\cite{noauthor_lazards_2017} : \gls{LCOE} data are appropriate for use in processes in which a fixed amount of installed  capacity has already been deployed i.e.
 the initial installed  capacity.
-The following \gls{LCOE} data (in million USD/GWh) was used :\\
+The following \gls{LCOE} data (in million USD/GWh) were used :\\
 
+\begin{table}[htb]
+\centering
+\caption{\label{tab:lcoe} \gls{LCOE} data used in the simulation.}
+\vspace{2mm}
 \begin{tabular}{|c|c|}
@@
 \end{tabular}
+\end{table}
 
-\item \textbf{Detailed costs} \cite{noauthor_eia_2019} : While the models with conventional energy sources have part of the following cost structure, these somewhat inaccurate and highly idealized figures need to be revised based on the data in the \gls{ARFC} \gls{I2CNER} repository, especially for offshore and onshore wind(current data is for the US from the \gls{EIA} \cite{noauthor_eia_2019}), and for nuclear (to take construction delays into account).
+\textbf{Detailed costs} \cite{noauthor_eia_2019} : While the models with conventional energy sources have part of the following cost structure, these somewhat inaccurate and highly idealized figures need to be revised based on the data in the \gls{ARFC} \gls{I2CNER} repository, especially for offshore and onshore wind(current data are for the US from the \gls{EIA} \cite{noauthor_eia_2019}), and for nuclear (to take construction delays into account).
 
+\begin{table}[htb]
+\centering
+\caption{\label{tab:costs} Detailed cost structure incorporated in some models.}
+\vspace{2mm}
 \begin{tabular}{|c|c|c|c|}
@@
 \end{tabular}
+\end{table}
 
-\item \textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016,gargiulo_documentation_2005}:\\
-
+\textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016,gargiulo_documentation_2005}: These are the remaining parameters used in the models: \\
+\begin{table}[htb]
+\centering
+\caption{\label{tab:misc} Miscellaneous simulation parameters.}
+\vspace{2mm}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-
-\end{itemize}
+\end{table}
 
@@
 
-Based on these assumptions, the model yields the following results for the years 2011-16, which are very close to the actual electricity generation figures supplied by \gls{EDMC}.
+Based on these assumptions, the model yields the following results for the years 2011-16, which are  close to the actual electricity generation figures supplied by \gls{EDMC}.
 \gls{LCOE}-based results for the entire time-period are present in the poster presented at the \gls{I2CNER} symposium \cite{chaube_dynamic_2019}.
@@
 The primitive, black-box like nature of the software inhibits efficient debugging.
-Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule.
+Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of these data into the model has been behind schedule.
 \\
@@
 The \gls{EDMC} is constantly being revised and updated, for both earlier (2010-2013) and later years(2016-).
-Hence, this data is not always consistent or complete, and often secondary sources must be used for verification.
+Hence, these data are often inconsistent or incomplete, and hence secondary sources must be used for verification.
 \section{Future Work}
@@
 \item \textbf{Define load curves for solar and wind:} This is the approach suggested by VEDA developers on their forum.
-However, the details of implementation for this particular approach are lacking in the \gls{TIMES} documentation.
+However, the details for implementation of this particular approach are lacking in the \gls{TIMES}/VEDA documentation.
 A successful implementation should incorporate the daily and seasonal variation of these electricity sources, and force the model to deploy natural gas or electricity storage to supplement wind and solar.
 
-\item \textbf{Replace annually averaged installed  capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
-SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) installed  capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
+\item \textbf{Replace annually averaged  capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
+SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
 If seasonal versions of these factors exist, this would be the easiest solution.
@@
 \item \textbf{Define a direct relationship between the capacities of wind and natural gas}:It might be possible to define a direct equation between the installed  capacity of renewables and natural gas.
-Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the \gls{TIMES} documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and quite possibly the assistance of the VEDA forum.
+Since no straightforward way to do this is described in the VEDA documentation \cite{gargiulo_documentation_2005}, this would require utilization of the \gls{TIMES} documentation \cite{loulou_documentation_2005}, the VEDA attributes table, and  possibly the assistance of the VEDA forum.
 
@@
 These emit only 10\% of the CO$_2$ that their corresponding fossil fuel technology emits \cite{kato_energy_2016}.
-In the model, these look like any other fossil fuel electricity generation process, except they are more expensive and have a significantly smaller emissions coefficient.
+In the model, these look like any other fossil fuel electricity generation process, except they are more expensive and have a significantly smaller emission coefficient.
 Such an implementation does \textbf{not} include retrofitting of \gls{CCS} (i.e.
-adding point carbon capture capabilities to previously deployed fossil fuel installed  capacity - discussed below).
+adding point carbon capture capabilities to previously deployed fossil fuel plants ).
 While we do not have Japan-specific data for \gls{CCS}, we can use cost data from the US and do one of the following:
@@
 \textbf{Incorporation of Japan-specific costs for wind:} When incorporating \gls{JWPA} predictions, it will be necessary to split off-shore wind into fixed and floating types.
-The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exists in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.
-This data needs to be sifted through and incorporated into our model.\\
+The \href{https://github.com/arfc/i2cner/tree/master/data/japan_costs}{cost data} for this already exist in our repository thanks to Akari Minami, an undergraduate from Kyushu University who assisted with data collection and simulation during March 2019.
+These data need to be sifted through and incorporated into our model.\\
 
@@
 
-\paragraph{Make electricity demand process more realistic:}
-
-\begin{itemize}
-\item At the very least, demand should increase at +1.7 \% per year until 2030 as per \gls{METI} projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.
-
-\item More accurate data for 2030-2050 should be sought to further improve upon this, if possible.
-
-\end{itemize}
+\paragraph{Make electricity demand process more realistic:} Demand should increase at +1.7 \% per year until 2030 as per \gls{METI} projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.
+More accurate data for 2030-2050 can be sought to further improve upon this, if possible.\\
 
 \textbf{Implement \gls{CCS} retrofitting:} The modelling process for this is somewhat complicated.
-One would have to track CO$_2$ emitted from different fossil fuels separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum, to ensure that CO$_2$ from non-fossil fuel sources is not captured by the model.
+CO$_2$ emitted from different fossil fuels would have to be tracked separately by creating \gls{TIMES}  CO$_2$ commodities for coal, oil and petroleum, to ensure that CO$_2$ from non-fossil fuel sources is not captured by the model.
 Next, the process that converts this CO$_2$ to captured CO$_2$ and atmospheric CO$_2$ would need to be defined.
-The total amount of CO$_2$ captured may not be greater than the total installed capacity of the \gls{CCS} reservoirs around Japan \cite{kato_energy_2016}.\\
-The data for retrofitting in Japan is not easily available. Generic \gls{CCS} data from other countries may be used if necessary.\\
+The total amount of CO$_2$ captured should be less than the total capacity of the \gls{CCS} reservoirs around Japan \cite{kato_energy_2016}.\\
+The data for retrofitting in Japan are not easily available. Generic \gls{CCS} data from other countries may be used if necessary.\\
 

### 2019-05-21 doc/2019-05-report/2019-05-i2cner-report.tex
corrected table/figures, revised text
Former-commit-id: 326be0b30deb3db1b94cc4cfebf473cb716c379a
Former-commit-id: d33a5173ffbd03c81fa0e388d0a259d7198e192b

@@
 \newcommand{\xmark}{{\color{red}\ding{55}}}
+\usepackage{ragged2e}
 
@@
 
-\textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} generator.
+\textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} shell.
 Using the simplest VEDA input files from the VEDA tutorial \cite{gargiulo_documentation_2005} as a starting point, we developed our own model files, which we have been progressively refining since then.
@@
 The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
-We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018,noauthor_national_2018} and obtained reasonable approximations of electricity generation, which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most.\\
+We estimated the missing figures based on previous years' trends \cite{noauthor_energy_2018,noauthor_national_2018} and obtained reasonable approximations of electricity generation (see fig.
+\ref{elcic}), which result in CO\textsubscript{2} emission values that differ from actual values by about 5\% at most (see fig.
+\ref{co2ic} and \ref{co2err}).\\
 
-\paragraph{October 2018 – January 2019:} ~ \\
+\begin{flushleft}
+\textbf{October 2018 – January 2019:}
+\end{flushleft}
 
@@
 We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only \gls{CCS} can provide reliable, clean energy in conjunction with renewables.
-We have identified a few shortcomings in our model, some of which contribute to this problem:
+We have identified a few shortcomings in our model, some of which contribute to this problem:\\
 
@@
 
-\item Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
-Their installed capacity should be matched by storage or natural gas.
+\item \justify Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
+Their installed capacity should be matched by electricity storage or natural gas.
 Possible ways to implement this are discussed later.
 
-\item We may be overestimating \gls{CCS} costs.
+\item \justify We may be overestimating \gls{CCS} costs.
 The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
@@
 
-\paragraph{February 2019 – April 2019:} ~ \\
+\begin{flushleft}
+\textbf{February 2019 – April 2019:}
+\end{flushleft}
 
@@
 This may cause resource deployments for unrealistically brief periods (see fig.
-\ref{flatgood} ).
+\ref{flatgood}).\\
 
-\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model} (see table \ref{tab:models}).
+\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model} (see Table \ref{tab:models}).
 It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete installed  capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
 \ref{flatbug} and fig.
-\ref{flatgood} ).\\
+\ref{flatgood}).\\
 
@@
 
-The basic features of all simulations are described in the table below.
-The models include some combination of the technologies mentioned in table \ref{tab:basic}; the exact combination for each model is described in table \ref{tab:models}.
+The models include some combination of the technologies mentioned in Table \ref{tab:basic}; the exact combination for each model is described in Table \ref{tab:models}.
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 
-\textbf{Emission coefficients} \cite{noauthor_electricity_2017}: The following data are in gCO$_2$/kWh (i.e.
-nuclear, solar and wind emissions from construction are averaged over the lifetime of the power-production process):
+\textbf{Emission coefficients} \cite{noauthor_electricity_2017}: The emission coefficients are listed in Table \ref{tab:emi}.
+The data are in gCO$_2$/kWh.
+Hence, nuclear, solar and wind emissions from construction are averaged over the lifetime of the generation facility.
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 
-\textbf{\gls{LCOE}}\cite{noauthor_lazards_2017} : \gls{LCOE} data are appropriate for use in processes in which a fixed amount of installed  capacity has already been deployed i.e.
-the initial installed  capacity.
-The following \gls{LCOE} data (in million USD/GWh) were used :\\
+\textbf{\gls{LCOE}}\cite{noauthor_lazards_2017} : \gls{LCOE} data are appropriate for use in processes in which a fixed amount of installed capacity has already been deployed, i.e.
+the initial installed capacity, and where only the relative cost is important.
+The \gls{LCOE} data (in million USD/GWh) are listed in Table \ref{tab:lcoe}.
+\\
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 
-\textbf{Detailed costs} \cite{noauthor_eia_2019} : While the models with conventional energy sources have part of the following cost structure, these somewhat inaccurate and highly idealized figures need to be revised based on the data in the \gls{ARFC} \gls{I2CNER} repository, especially for offshore and onshore wind(current data are for the US from the \gls{EIA} \cite{noauthor_eia_2019}), and for nuclear (to take construction delays into account).
+\textbf{Detailed costs} \cite{noauthor_eia_2019} : While the models with conventional energy sources have part of the cost structure listed in Table \ref{tab:costs}, these somewhat inaccurate and highly idealized figures need to be revised based on the data in the \gls{ARFC} \gls{I2CNER} repository, especially for offshore and onshore wind(current data are for the US from the \gls{EIA} \cite{noauthor_eia_2019}), and for nuclear (to take construction delays into account).
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 
-\textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016,gargiulo_documentation_2005}: These are the remaining parameters used in the models: \\
-\begin{table}[htb]
+\textbf{Miscellaneous VEDA Parameters} \cite{kato_energy_2016,gargiulo_documentation_2005}: The remaining TIMES parameters used in the models are listed in Table \ref{tab:misc}.
+\begin{table}[H]
 \centering
@@
 
-Based on these assumptions, the model yields the following results for the years 2011-16, which are  close to the actual electricity generation figures supplied by \gls{EDMC}.
+Based on these assumptions and data(\gls{LCOE}), the model yields the following results for the years 2011-16 (see figure \ref{elcic}), which are within 5\% of the actual electricity generation figures obtained from \gls{EDMC}.
 \gls{LCOE}-based results for the entire time-period are present in the poster presented at the \gls{I2CNER} symposium \cite{chaube_dynamic_2019}.
@@
 \includegraphics[scale=0.6]{elc-2016}
-\caption{Electricity generated from different sources}
+\caption{Electricity generation profile for the model's initial conditions.}
 \label{elcic}
@@
 
-The emitted CO\textsubscript{2} values for the period 2011-16 are as follows.
-The error is at most 5.7\% \ref{co2err}, which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.
+The CO\textsubscript{2} emissions for the period 2011-16 are shown in figure \ref{co2ic}.
+The maximum error is 5.7\% (see figure \ref{co2err}), which is due to the aforementioned absence of accurate data for 2011, 2012 and 2016.
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.6]{elc-2016}
-\caption{Electricity generated from different sources}
-\label{elcic}
-\end{figure}
+As mentioned previously, the importance of incorporating semi-discrete installed capacity investment intervals is demonstrated by figures \ref{flatbug} and \ref{flatgood}.
+As seen in fig.
+\ref{flatbug}, production exceeds demand if semi-discrete investment intervals are not used in \gls{DSCINV} files.
+This issue is resolved if semi-discrete intervals are incorporated instead (see fig.
+\ref{flatgood}).
 
@@
 \centering
-\includegraphics[scale=0.6]{flat-bug}
+\includegraphics[scale=0.45]{flat-bug}
 \caption{Erroneous results obtained with discrete investment sizes in \gls{DSCINV} files.}
@@
 \centering
-\includegraphics[scale=0.6]{flat-good}
+\includegraphics[scale=0.45]{flat-good}
 \caption{Accurate results obtained with semi-discrete investment sizes in \gls{DSCINV} files.}
@@
 \item \textbf{Replace annually averaged  capacity factors and/or \gls{PEAK} factors with seasonal (summer/winter) and diurnal (day/night) (i.e.
-SN,SD, WN, WD \cite{gargiulo_documentation_2005} ) capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
+SN,SD, WN, WD \cite{gargiulo_documentation_2005}) capacity factors} : The model may then automatically deploy natural gas to supplement wind and solar.
 If seasonal versions of these factors exist, this would be the easiest solution.
@@
 Such an implementation does \textbf{not} include retrofitting of \gls{CCS} (i.e.
-adding point carbon capture capabilities to previously deployed fossil fuel plants ).
+adding point carbon capture capabilities to previously deployed fossil fuel plants).
 While we do not have Japan-specific data for \gls{CCS}, we can use cost data from the US and do one of the following:

### 2019-05-21 doc/2019-05-report/2019-05-i2cner-report.tex
text edits
Former-commit-id: 28f5edf2db0b3770b57800448c14cbdb2d271d8d
Former-commit-id: c6ad2cdc3b7c77ed9b8a78a7c005aec0f827648b

@@
 \newcommand{\xmark}{{\color{red}\ding{55}}}
-\usepackage{ragged2e}
 
@@
 This is due to the unusually deep seabed that is very close to the Japanese coast.
-\gls{JWPA} projections \cite{heger_wind_2016} are already ambitious, and our models should be closely aligned with them.
+\gls{JWPA} projections \cite{heger_wind_2016} are already ambitious, and our models should be closely aligned with them.\\
 
-\item \justify Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
+\item Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
 Their installed capacity should be matched by electricity storage or natural gas.
-Possible ways to implement this are discussed later.
+Possible ways to implement this are discussed later.\\
 
-\item \justify We may be overestimating \gls{CCS} costs.
+\item We may be overestimating \gls{CCS} costs.
 The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
 While this would make \gls{CCS} plants more expensive in Japan, we cannot arrive at an exact figure.
-Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.
+Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.\\
 

### 2019-05-23 doc/2019-05-report/2019-05-i2cner-report.tex
replaced bullets with subsections
Former-commit-id: 7799d1e43013ec08b8251e1c002c77de73d00174
Former-commit-id: 307d2c50ee9d73f3eedccfccf46b4942c82c2a89

--- 2019-05-21 doc/2019-05-report/2019-05-i2cner-report.tex
@@
 \usepackage{pifont}
+\usepackage{ragged2e}
 \usepackage{xcolor}
@@
 The tasks that we performed can be divided into two categories: technical tasks associated with implementation of details and features in our model, and data collection and organization.
-Our accomplishments have been:\\
+Our accomplishments have been:
 
-\textbf{Installation of and familiarization with VEDA} (January – March 2018) : To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} shell.
+\subsection{Installation of and familiarization with VEDA (January – March 2018)}
+To model Japan's energy industry, we chose VEDA, a \gls{TIMES} \cite{loulou_documentation_2005,gargiulo_documentation_2005} shell.
 Using the simplest VEDA input files from the VEDA tutorial \cite{gargiulo_documentation_2005} as a starting point, we developed our own model files, which we have been progressively refining since then.
 
-At the same time, we collected data pertaining to electricity generation and carbon emissions.\\
+At the same time, we collected data pertaining to electricity generation and carbon emissions.
 
-\textbf{Incorporation of fossil fuel-related data} (April – May 2018): We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting recent trends in electricity demand in Japan.
-\\
+\subsection{Incorporation of fossil fuel-related data(April – May 2018)}
+We incorporated data for electricity generation from fossil fuels from the \gls{EDMC} databank\cite{noauthor_energy_2018}, along with creating a simplified demand process reflecting recent trends in electricity demand in Japan.\\
 
@@
 Further, the 2016 data seem slightly inconsistent across different data tables in the \gls{EDMC} databank.
-The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.\\
+The source of variation in these numbers is likely to be the changes in the electricity distribution system of Japan since 2016.
 
-\textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to that for previously mentioned energy sources but simpler, since the data obtained for these energy sources from \gls{EDMC} were consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018,noauthor_iea_2017, noauthor_japan_2017}.
+\subsection{Incorporation of nuclear, hydropower and renewables into the model(June – August 2018)}
+The process of incorporating these into the model was similar to that for previously mentioned energy sources but simpler, since the data obtained for these energy sources from \gls{EDMC} were consistent across \gls{EDMC} data tables and secondary sources \cite{noauthor_energy_2018,noauthor_iea_2017, noauthor_japan_2017}.
 We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles.
-\cite{publicover_japan_2017, dincer_analysis_2011,noauthor_geothermal_2018,heger_wind_2016,noauthor_operational_2013,noauthor_electricity_2017}\\
+\cite{publicover_japan_2017, dincer_analysis_2011,noauthor_geothermal_2018,heger_wind_2016,noauthor_operational_2013,noauthor_electricity_2017}
 
-\textbf{Refining CO\textsubscript{2} emission processes} (August – September 2018) : While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity generation processes, it was only after incorporating all conventional energy sources that we could move on to aligning the model's CO\textsubscript{2} emission values with actual emissions from Japan.
+\subsection{Refining CO\textsubscript{2} emission processes(August – September 2018)}
+While we had been modelling CO\textsubscript{2} emission processes in parallel with the electricity generation processes, it was only after incorporating all conventional energy sources that we could move on to aligning the model's CO\textsubscript{2} emission values with actual emissions from Japan.
 The major obstacle we faced was the absence of data pertaining to electricity generation from individual fossil fuels, with each fossil fuel's energy cycle having different emission coefficients.
@@
 
-\begin{flushleft}
-\textbf{October 2018 – January 2019:}
-\end{flushleft}
+\subsection{October 2018 – January 2019}
 
-\textbf{Changing simulation timeframe to 2013-2100:} As discussed previously, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012.
+\subsubsection{Changing simulation timeframe to 2013-2100}
+As discussed previously, it became impossible to find exact data for fossil fuels for the years 2010,2011 and 2012.
 Hence the total CO$_2$ emissions for those years were very slightly off the mark.
-We sidestepped this problem by changing the initial year to 2013, for which we have exact data from \gls{EDMC} \cite{noauthor_energy_2018}.\\
+We sidestepped this problem by changing the initial year to 2013, for which we have exact data from \gls{EDMC} \cite{noauthor_energy_2018}.
 
-\textbf{Incorporation of the \gls{PEAK} factor \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's installed capacity that is guaranteed to be available during peak demand.
+\subsubsection{Incorporation of the \gls{PEAK} factor \cite{gargiulo_documentation_2005} factor}
+This parameter is defined as the fraction of a resource's installed capacity that is guaranteed to be available during peak demand.
 This introduces a notion of an energy resource's reliability.
 Its incorporation reduced excessive deployment of wind and solar.
-However, the \gls{PEAK} factor values in the model \cite{kato_energy_2016} neglect the daily or seasonal variation of wind and solar, as the factor is annually averaged.\\
+However, the \gls{PEAK} factor values in the model \cite{kato_energy_2016} neglect the daily or seasonal variation of wind and solar, as the factor is annually averaged.
 
-\textbf{Basic \gls{CCS} Implementation} : Some \gls{CCS} data \cite{kato_energy_2016}  were incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
+\subsubsection{Basic \gls{CCS} Implementation}
+Some \gls{CCS} data \cite{kato_energy_2016}  were incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}.
 However, no \gls{CCS} gets deployed in our models.
 We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only \gls{CCS} can provide reliable, clean energy in conjunction with renewables.
-We have identified a few shortcomings in our model, some of which contribute to this problem:\\
+We have identified a few shortcomings in our model, some of which contribute to this problem:
 
-\begin{itemize}
-
-\item Large amounts of offshore wind can be deployed.
-While we were initially reluctant to hard-code strict installed  capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy in Japan.
+\paragraph{Large amounts of offshore wind can be deployed:} While we were initially reluctant to hard-code strict installed  capacity limits into our model, we have since realized that Japan's underdeveloped offshore wind industry will not reach its full potential for a very long time, as offshore wind is extremely expensive to deploy in Japan.
 This is due to the unusually deep seabed that is very close to the Japanese coast.
@@
 
-\item \justify Wind and solar are treated as any other energy source, with their daily and seasonal variance neglected.
+\paragraph{Wind and solar's daily and seasonal variance neglected:} Their capacity factor is annually averaged.
 Their installed capacity should be matched by electricity storage or natural gas.
@@
 
-\item \justify We may be overestimating \gls{CCS} costs.
-The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
+\paragraph{We may be overestimating \gls{CCS} costs:} The costs associated with \gls{CCS} for Japan have been hard to find as Japan, instead of building \gls{CCS} pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$.
 While this would make \gls{CCS} plants more expensive in Japan, we cannot arrive at an exact figure.
@@
 
-\end{itemize}
+\subsection{February 2019 – April 2019:}
 
-\begin{flushleft}
-\textbf{February 2019 – April 2019:}
-\end{flushleft}
-
-\textbf{Gradual collection and replacement of \gls{LCOE} data with accurate cost structure:} The results presented at the \gls{I2CNER} Annual \gls{EAD} workshop \cite{chaube_dynamic_2019} were based entirely on \gls{LCOE} analysis, as \gls{LCOE} data and projections were readily available.
+\subsubsection{Gradual collection and replacement of \gls{LCOE} data with accurate cost structure}
+The results presented at the \gls{I2CNER} Annual \gls{EAD} workshop \cite{chaube_dynamic_2019} were based entirely on \gls{LCOE} analysis, as \gls{LCOE} data and projections were readily available.
 However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, and fixed and variable \gls{OM} costs.
@@
 This may cause resource deployments for unrealistically brief periods (see fig.
-\ref{flatgood}).\\
+\ref{flatgood}).
 
-\textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model} (see Table \ref{tab:models}).
+\subsubsection{Incorporation of semi-discrete investment sizes}
+Discrete investment sizes were incorporated in most scenarios' \gls{DSCINV} files\cite{gargiulo_documentation_2005}, whereas the slightly improved semi-discrete installed  capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model} (see Table \ref{tab:models}).
 It is desired that all \gls{DSCINV} files in the remaining three models include a similar semi-discrete installed  capacity installation structure, as this helps eliminate the production-exceeding-demand bug (see fig.
 \ref{flatbug} and fig.
-\ref{flatgood}).\\
+\ref{flatgood}).
 

### 2019-06-25 doc/2019-06-poster/poster.tex
create 2019-06 poster
Former-commit-id: ba686428cc0b1fa12e7475019f7f55e6146bca4f
Former-commit-id: 36bdb7d2c23bf78f0f8b39da8b00347719649c76

--- 2019-01-15 doc/2019-01-poster/poster.tex
@@
 \begin{frame}[t] % The whole poster is enclosed in one beamer frame
-
-\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
-
+\begin{columns}
 %=======================================================
@@
 %=========================================================
-
-\begin{column}{\twocolwid} % The first two columns, two cols wide
-\begin{columns}[t,totalwidth=\twocolwid] % Split up the first column into two, 
 \begin{column}{\onecolwid} % The first column, one col wide
@@
 
-%----------------------------------------------------------------------------------------
-%	METHODOLOGY
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.1]{./plots/convNuc_ele.png}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
+\label{s1e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.1]{./plots/convNuc_co2.png}
+\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
+\label{s1c}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.1]{./plots/convNoNuc_ele.png}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
+\label{s2e}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\includegraphics[scale=1.1]{./plots/convNoNuc_co2.png}
+\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
+\label{s2c}
+\end{figure}
+
 %----------------------------------------------------------------------------------------
 
+\end{column} % End of the first column
+%===========================================================================================
+% SECOND COLUMN BEGINS
+%=============================================================================================
+\begin{column}{\onecolwid} % The second column
 \begin{block}{Introduction}
@@
 \end{block}
-
-%\vspace{77mm}
+\begin{tabular}{| c | c | c | c | c |}
+\hline
+\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{I$^2$CNER}&\textbf{New nuclear}\\
+                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+                  \hline
+1               & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
+2               & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
+3               & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
+4               & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
+\hline
+\end{tabular}
 
@@
 \centering
-\includegraphics[scale=1.1]{legend}
-%\caption{Legend}
-\label{legend}
+\includegraphics[scale=1.1]{./plots/i2cnerNuc_ele.png}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
+\label{s3e}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1.51]{conv_nuc_elc}
-\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
-\label{s1e}
+\includegraphics[scale=1.1]{./plots/i2cnerNuc_co2.png}
+\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
+\label{s3c}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1.51]{conv_nuc_co2}
-\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
-\label{s1c}
+\includegraphics[scale=1.1]{./plots/i2cnerNoNuc_ele.png}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
+\label{s4e}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1.51]{conv_nonuc_elc}
-\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
-\label{s2e}
+\includegraphics[scale=1.1]{./plots/i2cnerNoNuc_co2.png}
+\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
+\label{s4c}
 \end{figure}
 
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.51]{conv_nonuc_co2}
-\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
-\label{s2c}
-\end{figure}
+\end{column} % End of column 2, top half
+%=======================================================
+% Double Wide Figure Column 
+%=========================================================
+%\input{model-fig}
 
+\begin{column}{\onecolwid} % The third column
+%----------------------------------------------------------------------------------------
+%	TAKE AWAY
 %----------------------------------------------------------------------------------------
 
-\end{column} % End of the first column
-
-%===========================================================================================
-% SECOND COLUMN BEGINS
-%=============================================================================================
-
-%----------------------------------------------------------------------------------------
-\begin{column}{\onecolwid} % The second column
-%----------------------------------------------------------------------------------------
 \begin{block}{Methodology}
@@
 \begin{itemize}
-        \item\textbf{Objective function:} System cost \ref{cost}.
+        \item\textbf{Objective function:} System cost.
 
@@
 
-\begin{tabular}{| c | c | c | c | c |}
-\hline
-\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{I$^2$CNER}&\textbf{New nuclear}\\
-                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
-                  \hline
-1               & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
-2               & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
-3               & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
-4               & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
-\hline
-\end{tabular}
 \end{block}
 
-%\vspace{65 mm}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nuc_elc}
-\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
-\label{s3e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nuc_co2}
-\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
-\label{s3c}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nonuc_elc}
-\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
-\label{s4e}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.62]{i2cner_nonuc_co2}
-\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
-\label{s4c}
-\end{figure}
-
-\end{column} % End of column 2, top half
-\end{columns}
-%=======================================================
-% Double Wide Figure Column 
-%=========================================================
-%\input{model-fig}
-
-\end{column} % End of wide column, total length
-
-\begin{column}{\onecolwid} % The third column
-
-%----------------------------------------------------------------------------------------
-%	TAKE AWAY
-%----------------------------------------------------------------------------------------
-\begin{figure}[H] 
-\centering
-\includegraphics[scale=1.6]{cost}
-\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
-\label{cost}
-\end{figure}
 \begin{alertblock}{Take Aways}
@@
 \begin{tabular}{cccc}
-\includegraphics[scale=0.7]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
+\includegraphics[scale=0.6]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
 %\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
@@
 \end{columns}
+
 \end{frame} % End of the enclosing frame
@@
 \end{document}
+\grid

### 2019-06-25 doc/2019-06-poster/plots/plot.py

@@ -1,0 +1,69 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+def eleplot(filepath, savepath):
+    df = pd.read_excel(filepath,index_col=1, header=None).fillna(0).T.drop(0)
+    x = [2013 + x for x in range(88)]
+    Sources = ['Combined Cycle Plant', 'Solar', 'Coal', 'Oil',
+               'Hydro', 'Wind', 'Nuclear', 'Geothermal',
+               'Natural Gas','Hydrogen',
+              ]
+    Colors = ['tab:blue', 'tab:orange', 'tab:green', 'tab:red',
+              'tab:purple', 'tab:brown', 'tab:pink', 'tab:gray',
+              'tab:olive', 'tab:cyan']
+    y = []
+    colors = []
+    labels = []
+    for s, c in zip(Sources, Colors):
+        if s in df.columns:
+            labels.append(s)
+            y.append(df[s].values)
+            colors.append(c)
+    y = np.vstack(y)
+    y = np.array(y, dtype=float)
+    fig, ax = plt.subplots(figsize=(10,6))
+    ax.stackplot(x, y, labels=labels, colors=colors)
+    ax.legend(loc='upper left')
+    ax.set_xlabel('Years', fontsize=16)
+    ax.set_ylabel('Electricity Generated / GWh', fontsize=16)
+    ax.set_xlim((2013, 2100))
+    fig.savefig(savepath, dpi=600)
+
+def co2plot(filepath, savepath):
+    df = pd.read_excel(filepath,index_col=1, header=None).fillna(0).T.drop(0)
+    x = [2013 + x for x in range(88)]
+    Sources = ['Combined Cycle Plant', 'Solar', 'Coal', 'Oil', 
+               'Hydro', 'Wind', 'Nuclear', 'Geothermal', 
+               'Natural Gas','Hydrogen',
+              ]
+    Colors = ['tab:blue', 'tab:orange', 'tab:green', 'tab:red',
+              'tab:purple', 'tab:brown', 'tab:pink', 'tab:gray', 
+              'tab:olive', 'tab:cyan']
+    y = []
+    colors = []
+    labels = []
+    for s, c in zip(Sources, Colors):
+        if s in df.columns:
+            labels.append(s)
+            y.append(df[s].values)
+            colors.append(c)
+    y = np.vstack(y)
[…]

### 2019-07-29 doc/2019-06-poster/poster.tex
report number should be uiuc-arfc-2019-02
Former-commit-id: 304edca77791e54db5b311770da181c3965cbcea
Former-commit-id: 0e5fc92118854e29c169bbdf8573e65b66ae1ec3

@@
 
-\title{Dynamic Transition Analysis with TIMES}
+\title{%
+  \texorpdfstring{%
+    \makebox[\linewidth]{%
+      \makebox[0pt][l]{%
+        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
+          {\includegraphics[height=3\baselineskip]{i2cner_logo}}% Left logo
+      }\hfill
+      \makebox[0pt]{I$^2$CNER-Enabled Transitions to a Reduced Carbon Future}%
+      \hfill\makebox[0pt][r]{%
+        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
+          {\includegraphics[height=3\baselineskip]{wpi_logo}}% Right logo
+      }%
+    }%
+  }
+  {I$^2$CNER-Enabled Transitions to a Reduced Carbon Future}} % Poster title
 
@@
        % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
-        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
+        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, Huan Yan \inst{1}, Kathryn Huff\inst{1}}
 \institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
@@
 emissions in Japan to 80\% of 1990 levels by 2050.
-Our model has conventional and I$^2$CNER technologies (\textbf{carbon capture(CCS)} \& \textbf{H$_2$} production).
+Our model has conventional and I$^2$CNER technologies (\textbf{carbon capture(CCS)} \& \textbf{H$_2$} production). We have modeled \textbf{four scenarios}.
 \end{block}
@@
  \end{itemize}
-
-We have modeled \textbf{four scenarios}:\hfill \break
 

### 2020-03-27 doc/2020-03-paper/Appendix.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\section{Feed rates for all cases} \label{Appendix}
Appendix

### 2020-03-27 doc/2020-03-paper/acks.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\section{Acknowledgments}

Osama Ashraf would like to thank the Egyptian Ministry of Higher Education (MoHE), as well as MEPhI's Competitiveness Program for providing financial support for this research. The facility and tools needed to conduct this work were supported by MEPhI.

The authors contributed to this work as described below.

Osama Ashraf conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper.

Andrei Rykhlevskii conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper. Andrei Rykhlevskii 
is supported by  DOE ARPA-E MEITNER program award DE-AR0000983.

G. V. Tikhomirov directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper. Prof. Tikhomirov is Deputy Director of the Institute of Nuclear Physics and Engineering MEPhI. Board member of Nuclear society of Russia.

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

This research is part of the Blue Waters sustained-petascale computing 
project, which is supported by the National Science Foundation (awards 
OCI-0725070 and ACI-1238993) and the state of Illinois. Blue Waters is a joint 
effort of the University of Illinois at Urbana-Champaign and its National 
Center for Supercomputing Applications.

The authors thank members of the Advanced Reactors and Fuel Cycles (ARFC) 
group at the University of Illinois at Urbana-Champaign for helpful 
discussions relating to this paper. Finally, the authors would like to thank 
Matthew Kozak for constructive criticism of the manuscript.

### 2020-03-27 doc/2020-03-paper/acros.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\newacronym{<++>}{<++>}{<++>}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon Neutral Energy Research}
\newacronym{MARKAL}{MARKAL}{MARKet ALlocation}
\newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
%\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-03-27 doc/2020-03-paper/conclusion.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\section{Conclusion} \label{Conclusion}
Conclusion
\section{Future work}
FUTURE WORK

\section{Declaration of Competing Interest}

NECESARY?

### 2020-03-27 doc/2020-03-paper/methods.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\section{Model description} \label{Model-description}

\subsection{TIMES Model Description}
Objective function.
Constraints.
CO2 constraint interpolation.
\subsection{Initial condition}

\begin{tabular}{| c | c | c | c | c |}
\hline
\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{Emerging technologies}&\textbf{New nuclear}\\
                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
                  \hline
1               &   &      \greencheck           &         \xmark       &      \greencheck     \\ 
2               &   &      \greencheck           &         \xmark       &         \xmark       \\ 
3               &  &      \greencheck           &      \greencheck     &      \greencheck     \\ 
4               &  &      \greencheck           &      \greencheck     &         \xmark       \\
\hline

\subsection{Existing technology}

\subsection{Emerging technologies}

\subsection{Base scenarios}
%approach, goal, what are we hoping to learn
\subsection{Sensitivity analysis}
%approach, goal, what are we hoping to learn

\end{tabular}

### 2020-03-27 doc/2020-03-paper/results.tex
cleanup
Former-commit-id: 58322421ef92fff10ab24b0e4c52512d81771895
Former-commit-id: e387f21dccdfc3dd76f67082f9b0cf791fe07277

\section{Results and discussion} \label{Results-and-discussion}
RESULTS

### 2020-04-02 doc/2020-03-paper/methods.tex
recalculate cfs
Former-commit-id: cc8ec4c78536283719df2eb736f8a025c7d36d77
Former-commit-id: 7b549f3f08aef305bc3927ae2e8b7c853c161385

@@
 Objective function.
-Constraints.
-CO2 constraint interpolation.
-\subsection{Initial condition}
+Constraints - CO2 emissions reduction targets, increasing demand, CO2 tax.
+Important parameters.
+\subsection{Initial condition and constraints}
+The initial condition is based on energy generation data from EDMC(-> GLS) for the years 2013 , and emission data for electricity generation from National Carbon Trust.
+
+\begin{tabular}{ c c c c c c c c c c}
+\textbf{Year} & \textbf{Coal} & \textbf{LNG} & \textbf{Oil} & \textbf{Nuclear} & \textbf{Hydro} & \textbf{Solar} & \textbf{Wind} & \textbf{Geo} & \textbf{Total} \\
+ & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} \\
+2013 & 259,514 & 449,271 & 108,135 & 9,302 & 84,885 & 162 & 85 & 2,435 & 913,792 \\
+\end{tabular}
+
+\begin{tabular}{ c c c }
+\textbf{Year} &  \textbf{Model Emissions} & \textbf{Actual Emissions} \\
+ &  \textbf{Mt-CO$_2$-eq.} & \textbf{Mt-CO$_2$-eq.} \\
+2013 & 593.6 & 592.4 \\
+2013 & 593.6 & 592.4 \\
+2013 & 593.6 & 592.4 \\
+2013 & 593.6 & 592.4 \\
+\end{tabular}
 
@@
 \hline
-\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{Emerging technologies}&\textbf{New nuclear}\\
-                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
+                 & \textbf{enabled} & \textbf{enabled} \\
                   \hline
-1               &   &      \greencheck           &         \xmark       &      \greencheck     \\ 
-2               &   &      \greencheck           &         \xmark       &         \xmark       \\ 
-3               &  &      \greencheck           &      \greencheck     &      \greencheck     \\ 
-4               &  &      \greencheck           &      \greencheck     &         \xmark       \\
+1               &   \xmark       &      \greencheck     \\ 
+2               & \xmark       &         \xmark       \\ 
+3               &   \greencheck     &      \greencheck     \\ 
+4               &   \greencheck     &         \xmark       \\
 \hline
-
+\end{tabular}
 \subsection{Existing technology}
@@
 %approach, goal, what are we hoping to learn
-
-\end{tabular}

### 2020-04-06 doc/2020-03-paper/methods.tex
cleanup, added section 3 text
Former-commit-id: fcbb2d2478504439efa3afcf874bcf8fae6bd2f3
Former-commit-id: 7f203aacef92cb574a86b988059c9dad3d6e97ef

--- 2020-03-27 doc/2020-03-paper/methods.tex
@@
 Objective function.
-Constraints.
-CO2 constraint interpolation.
-\subsection{Initial condition}
+Constraints - CO2 emissions reduction targets, increasing demand, CO2 tax.
+Important parameters.
+\subsection{Initial condition and common constraints}
+The initial condition is based on energy generation data from \gls{EDMC} for the years 2013-2016 , and emission data for electricity generation from National Carbon Trust (see Fig.
+\ref{ic-elc}).
+As the \gls{EDMC} database has been evolving over the course of this work, the focus of our model was to recreate the 2013-2016 emission levels with low error, instead of recreating the \gls{EDMC} electricity generation data.
+A tolerance of 1\% was allowed for each electricity generation technology in order to avoid specifying an overly rigorous initial condition that slows the model down.
+The error in the CO$_2$ emission levels is minimal, as seen in Table \ref{ic-co2}.
 
-\begin{tabular}{| c | c | c | c | c |}
+All existing fossil fuels are gradually retired by 2025.
+This aggressive retirement is enabled to simulate the necessary premature retirement required to meet the challenging CO$_2$ constraints, and to not saddle the model with technologies that make the CO$_2$ constraints unattainable.
+As mentioned in the next section, if the model still feels the need to deploy fossil fuel-based technology, it can deploy natural gas and coal with a 10 year lifetime (to simulate premature retirement).
+In practice, this would represent premature retirement of fossil fuel plants or retrofitting them with \gls{CCS} technology.
+
+\begin{figure}[h] 
+\centering
+\label{ic-elc}
+\includegraphics[scale=0.5]{figures/IC}
+\caption{Electricity generation that defines the initial condition of the model.}
+\end{figure}
+
+\begin{table}[!ht]
+	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
 		\hline
-\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{Emerging technologies}&\textbf{New nuclear}\\
-                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
+\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
+  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
 \hline
-1               &   &      \greencheck           &         \xmark       &      \greencheck     \\ 
-2               &   &      \greencheck           &         \xmark       &         \xmark       \\ 
-3               &  &      \greencheck           &      \greencheck     &      \greencheck     \\ 
-4               &  &      \greencheck           &      \greencheck     &         \xmark       \\
+2013 & 603.62 & 592.4 & 1.89 \% \\
+2014 & 582.27 & 572.6 & 1.69 \% \\
+2015 & 572.53 & 560.3 & 2.18 \% \\
+2016 & 565.94 & 552.8 & 2.38 \% \\
 \hline 
+	\end{tabularx}
+\label{ic-co2}
+\end{table}
+The electricity demand in the near term is expected to increase by 1.7\% per year (cite electricity review).
+However, in the long run, the demand should eventually plateau, if not decrease altogether, due to the ageing population of Japan.
+In the absence of long term projections, our model approximates the gradual reduction in the annual demand increase rate, and its eventual reduction to 0\% per year, as shown in table \ref{demand}.
+The demand increases linearly for all intermediate years.
 
-\subsection{Existing technology}
+\begin{table}[!ht]
+	\caption{Demand increase over time.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+		\hline
+\textbf{Year} & \textbf{Annual demand increase} \\
+\hline
+2017-2030 & 1.7 \% \\
+2031-2050 & 1.0 \% \\
+2051-2070 & 0.5 \% \\
+2070-2100 & 0.0 \% \\
+\hline 
+	\end{tabularx}
+\label{demand}
+\end{table}
+The CO$_2$ constraints common to all the models are as shown in table \ref{co2-limits}. The CO$_2$ limit for intervening years is linearly interpolated to ensure gradual transitions. 
+\begin{table}[!ht]
+	\caption{CO$_2$ constraints.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.5\textwidth}p{0.1\textwidth} p{0.2\textwidth}}
+		\hline
+\textbf{Year} & \textbf{Absolute Emission limit} & \textbf{Base Year} & \textbf{Reduction from Based Year} \\
+\hline
+2030 & 438 Mt CO$_2$-eq. & 2013 & 26 \% \\
+2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
+2100 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
+\hline 
+	\end{tabularx}
+\label{co2-limits}
+\end{table}
+
+\subsection{Existing technologies}
+
+For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies.
+The economic data and growth rates for these technologies are defined in tables \ref{existing-eco} and .
+The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector.
+
+\begin{table}[!ht]
+	\caption{Economic data for existing technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.2\textwidth} p{0.16\textwidth} p{0.16\textwidth} p{0.16\textwidth}  p{0.1\textwidth} p{0.1\textwidth}}
+		\hline
+\textbf{Technology} & \textbf{Investment Cost} & \textbf{Fixed \gls{OM} costs} & \textbf{Variable \gls{OM} costs} & \textbf{Lifetime} & \textbf{Capacity Factor}\\
+  & USD/kW & USD/kW & USD/MWh & Years & \\
+\hline
+Nuclear & 6317 & 121.13 & 2.36 & 60 & 0.90\\
+Solar & 1307 (2017) & 15.19 & 0 & 25 & 0.14\\
+Onshore Wind & 3454 (2017) & 136.37 & 0 & 25 & 0.4\\
+Offshore Wind(Fixed) & 7772.73 & 341 & 0 & 25 & 0.44\\
+Offshore Wind(Floating) & 12897 & 423 & 0 & 25 & 0.44\\
+Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & 4h/24h \\
+Natural Gas &  1079 & 14 & 2.54 & 10 & 0.55 \\
+\gls{USC} & 3661 & 40.41 & 4.48 & 10 & 0.55 \\
+\hline 
+\end{tabularx}
+\label{existing-eco}
+\end{table}
 
@@
 %approach, goal, what are we hoping to learn
+\begin{table}[!ht]
+	\caption{Scenario definition.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.33\textwidth} p{0.33\textwidth} p{0.33\textwidth}}
+\hline 
+\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
+                 & \textbf{enabled} & \textbf{enabled} \\
+                  \hline
+%1               &   \xmark       &      \greencheck     \\ 
+%2               & \xmark       &         \xmark       \\ 
+%3               &   \greencheck     &      \greencheck     \\ 
+%4               &   \greencheck     &         \xmark       \\
+1               &   No       &      Yes     \\ 
+2               &  No       &         No       \\ 
+3               &   Yes     &      Yes     \\ 
+4               &   Yes     &         No       \\
+
+\hline
+	\end{tabularx}
+\label{scen-table}
+\end{table}
 \subsection{Sensitivity analysis}
 %approach, goal, what are we hoping to learn
-
-\end{tabular}

### 2020-04-07 doc/2020-03-paper/acks.tex
updates to paper
Former-commit-id: 1fff218c908a2ec1610b116ab213625083a8c178
Former-commit-id: 649db3cb4c71aa18e09ad8a46da4b1e629c4efa6

@@
 \section{Acknowledgments}
-
-Osama Ashraf would like to thank the Egyptian Ministry of Higher Education (MoHE), as well as MEPhI's Competitiveness Program for providing financial support for this research.
-The facility and tools needed to conduct this work were supported by MEPhI.
 
@@
 is supported by  DOE ARPA-E MEITNER program award DE-AR0000983.
-
-G.
-V.
-Tikhomirov directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper.
-Prof.
-Tikhomirov is Deputy Director of the Institute of Nuclear Physics and Engineering MEPhI.
-Board member of Nuclear society of Russia.
 

### 2020-04-07 doc/2020-03-paper/acros.tex
cleanup, added section 3 text
Former-commit-id: fcbb2d2478504439efa3afcf874bcf8fae6bd2f3
Former-commit-id: 7f203aacef92cb574a86b988059c9dad3d6e97ef
updates to paper
Former-commit-id: 1fff218c908a2ec1610b116ab213625083a8c178
Former-commit-id: 649db3cb4c71aa18e09ad8a46da4b1e629c4efa6

@@
 \newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
+\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
+\newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
+\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
+\newacronym{USC}{USC}{Ultra Supercritical Coal}
+\newacronym{OM}{O\&M}{Operation and Maintenance Cost}
+\newacronym{PEMFC}{PEM Fuel Cells}{Polymer Electrolyte Membrane Fuel Cells}
+\newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
+\newacronym{lng}{LNG}{Liquified Natural Gas}
 %\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-04-07 doc/2020-03-paper/methods.tex
updates to paper
Former-commit-id: 1fff218c908a2ec1610b116ab213625083a8c178
Former-commit-id: 649db3cb4c71aa18e09ad8a46da4b1e629c4efa6

@@
 Important parameters.
-\subsection{Initial condition and common constraints}
+
+\subsection{Common Features - Initial condition and constraints}
+
 The initial condition is based on energy generation data from \gls{EDMC} for the years 2013-2016 , and emission data for electricity generation from National Carbon Trust (see Fig.
@@
 
+The economic data for initially deployed capacity is associated with the respective \gls{lcoe} of each electricity supply source, substituted for variable \gls{OM} costs.
+The \gls{lcoe} data and the emission factors for the technologies used in defining the initial condition are listed in table \ref{init-eco}.
 All existing fossil fuels are gradually retired by 2025.
@@
 In practice, this would represent premature retirement of fossil fuel plants or retrofitting them with \gls{CCS} technology.
+
+\begin{table}[!ht]
+	\caption{Data for initial condition.}
+	\vspace{0.1in}
+	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
+		\hline
+\textbf{Technology} & \textbf{\gls{lcoe}} & \textbf{Emission} & \textbf{Year of total}\\
+  & (USD/kWh) & \textbf{Coefficients} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
+\hline
+Coal & 0.06 & 943 & 2030 \\
+\gls{lng} & 0.08 & 599 & 2030 \\
+Oil & 0.39 & 738 & 2030 \\
+Nuclear & 0.11 & 21 & 2069 \\
+Hydro & 0.05 & 11 & N.A. \\
+Geothermal & 0.12 & 13 & N.A. \\
+Wind & 0.11 & 25 & 2040 \\
+Solar & 0.15 & 37 & 2040 \\
+\hline 
+\end{tabularx}
+\label{init-eco}
+\end{table}
 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.5\textwidth}p{0.1\textwidth} p{0.2\textwidth}}
+	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.22\textwidth}p{0.16\textwidth} p{0.4\textwidth}}
 		\hline
-\textbf{Year} & \textbf{Absolute Emission limit} & \textbf{Base Year} & \textbf{Reduction from Based Year} \\
+\textbf{Year} & \textbf{Emission limit} & \textbf{Base Year} & \textbf{Reduction from base year} \\
 \hline
@@
 For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies.
-The economic data and growth rates for these technologies are defined in tables \ref{existing-eco} and .
+The economic data, such as capital costs, \gls{OM} costs, lifetime and capacity factors have been compiled from data sources into table \ref{existing-eco}.
+Dynamic trends are incorporated where available.
 The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector.
+Upper limits for growth rates are based on existing data, but with a generous margin of 5-20\%, as the trends in growth seen in the recent past may not represent the growth rates required to achieve the dramatic reduction in emissions we are aiming for.
 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.2\textwidth} p{0.16\textwidth} p{0.16\textwidth} p{0.16\textwidth}  p{0.1\textwidth} p{0.1\textwidth}}
+	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
 		\hline
-\textbf{Technology} & \textbf{Investment Cost} & \textbf{Fixed \gls{OM} costs} & \textbf{Variable \gls{OM} costs} & \textbf{Lifetime} & \textbf{Capacity Factor}\\
-  & USD/kW & USD/kW & USD/MWh & Years & \\
+\textbf{Technology} & \textbf{Investment} & \textbf{Fixed \gls{OM}} & \textbf{Variable \gls{OM}} \\
+  & \textbf{cost}(USD/kW) & \textbf{costs}(USD/kW) & \textbf{costs}(USD/MWh)\\
 \hline
-Nuclear & 6317 & 121.13 & 2.36 & 60 & 0.90\\
-Solar & 1307 (2017) & 15.19 & 0 & 25 & 0.14\\
-Onshore Wind & 3454 (2017) & 136.37 & 0 & 25 & 0.4\\
-Offshore Wind(Fixed) & 7772.73 & 341 & 0 & 25 & 0.44\\
-Offshore Wind(Floating) & 12897 & 423 & 0 & 25 & 0.44\\
-Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & 4h/24h \\
-Natural Gas &  1079 & 14 & 2.54 & 10 & 0.55 \\
-\gls{USC} & 3661 & 40.41 & 4.48 & 10 & 0.55 \\
+Nuclear(2027 onwards) & 6317 & 121.13 & 2.36  \\
+Solar & 1307(2017) & 15.19 & 0 \\
+  & 1086(2040) &  &  \\
+  & 615(2050) & &  \\
+Onshore Wind & 3454(2017) & 136.37 & 0 \\
+ & 3110(2040) &  &   \\
+ & 2800(2050) & &   \\
+Offshore Wind(Fixed) & 7772(2017) & 341 & 0 \\
+ & 5438(2040) & & \\
+Offshore Wind(Floating) & 12897(2017) & 423 & 0 \\
+ & 9023(2040) &  &   \\
+Li-ion Storage & 1876 (2017) & 10 & 0.3  \\
+& 1446 (2025) &  &  \\
+Natural Gas &  1079 & 14 & 2.54 \\
+\gls{USC} & 3661 & 40.41 & 4.48 \\
 \hline 
@@
 
+\begin{table}[!ht]
+	\caption{Miscellaneous \gls{TIMES} data for existing technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.10\textwidth} p{0.25\textwidth} p{0.2\textwidth}  p{0.2\textwidth}}
+		\hline
+\textbf{Technology} &  \textbf{Lifetime} & \textbf{Capacity Factor/}  & \textbf{Availability} & \textbf{Emission}\\
+  & (years) &  \textbf{Efficiency} & \textbf{Factor} & \textbf{Coefficient}(gCO$_2$-eq./kWh)\\
+\hline
+Nuclear & 60 & 0.90 (CF) & 1 & 21\\
+Solar & 25 & 0.14 (CF) & 1 & 37\\
+Onshore Wind & 25 & 0.4 (CF) & 1 & 25\\
+Offshore Wind (Fixed) & 25 & 0.44 (CF) & 1 & 25\\
+Offshore Wind (Floating) & 25 & 0.44 (CF) & 1 & 25\\
+Li-ion Storage & 10 & 0.688 (Eff.) & 4h/24h & 50 \\
+Natural Gas &  10 & 0.55 (CF) & 1 & 599  \\
+\gls{USC} & 10 & 0.55 (CF) & 1 & 943  \\
+\hline 
+\end{tabularx}
+\label{existing-misc}
+\end{table}
+
+\begin{table}[!ht]
+	\caption{Installed capacity growth rate limits and capacity limits for existing technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
+		\hline
+\textbf{Technology} & \textbf{Annual Growth} & \textbf{Net Capacity} \\
+  & \textbf{Rate}  & \textbf{Limit} (GW) \\
+\hline
+Nuclear (2027 onwards) & +5 reactors & 60 GW \\
+Solar & 30\% per year & None  \\
+Onshore Wind & 50\% & 3.75 (2017) \\
+ &  & 15.3 (2020) \\
+ &  & 39.9 (2030) \\
+ &  & 57.0 (2040) \\
+ &  & 114.0 (2100) \\
+Offshore Wind(Fixed) & 50\% & 1 (2017) \\
+ &  & 8.70 (2030) \\
+ &  & 22.50 (2040) \\
+ &  & 28.50 (2050) \\
+ &  & 57.00 (2100) \\
+Offshore Wind(Floating) & 50\% & 1 (2017) \\
+ &  & 5.70 (2030) \\
+ &  & 19.35 (2040) \\
+ &  & 27.00 (2050) \\
+ &  & 54.00 (2100) \\
+Li-ion Storage & 100\% (2017-2029) & None  \\
+ & 30\% (2030-2100) & None  \\
+Natural Gas &  100\% & None \\
+\gls{USC} & 50\% & None \\
+\hline 
+\end{tabularx}
+\label{existing-gro}
+\end{table}
+
 \subsection{Emerging technologies}
+
+\begin{table}[!ht]
+	\caption{Economic data for emerging technologies.}
+	\vspace{0.1in}
+\centering
+	\begin{tabularx}{1.3\textwidth}{p{0.35\textwidth} p{0.15\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth} }
+		\hline
+\textbf{Technology} & \textbf{First} & \textbf{Investment} & \textbf{Fixed \gls{OM}} & \textbf{Variable \gls{OM}} \\
+  & \textbf{Deployment}& \textbf{Cost}(USD/kW) & \textbf{Costs}(USD/kW) & \textbf{Costs}(USD/MWh)\\
+\hline
+CCS-LNG(90\%) & 2025 & 2569 & 27.48 & 5.82 \\
+CCS-\gls{USC}(90\%) & 2025 & 5997 & 59.29 & 10.93 \\
+Perovskite & 2022 & 1307 (2022) & 27.48 & 15.19 \\
+& & 1086 (2040) &  &  \\
+& & 615 (2050) &  &  \\
+\gls{PEMFC} & 2025 & 7399 & 30.65 & 0.59 \\
+LNG steam reforming & 2025 & 491 & 6.14 & 40.4 \\
+LNG steam reforming with CCS(90\%) & 2025 & 848.5 & 5.704 & 55.7 \\
+Electrolysis & 2025 & 1100 & 6.87 & 0.9 \\
+\hline 
+\end{tabularx}
+\label{emerging-eco}
+\end{table}
+
+\begin{table}[!ht]
+	\caption{Miscellaneous \gls{TIMES} data for emerging technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{1.2\textwidth}{p{0.3\textwidth} p{0.10\textwidth} p{0.25\textwidth} p{0.2\textwidth}  p{0.2\textwidth}}
+		\hline
+\textbf{Technology} &  \textbf{Lifetime} & \textbf{Capacity Factor/}  & \textbf{Availability} & \textbf{Emission}\\
+  & (years) &  \textbf{Efficiency} & \textbf{Factor} & \textbf{Coefficient}(gCO$_2$-eq./kWh)\\
+\hline
+CCS-LNG(90\%) & 40 & 0.45 (CF) & 1 & 59.9\\
+CCS-\gls{USC}(90\%) & 40 & 0.45 (CF) & 1 & 94.3\\
+Perovskite & 20 & 0.14 (CF) & 1 & 37\\
+\gls{PEMFC} & 10 & 0.5 (Eff.) & 0.5 & 0.57(2025),0.34(2030)\\
+LNG steam reforming & 20 & 0.44 (CF) & 1 & 313.2\\
+LNG steam reforming with CCS(90\%) & 20 & 0.55(Eff.) & 1 & 31.32  \\
+Electrolysis & 10 & 0.65 (Eff.) & 1 &  39.4(2025),16.31 (2030) \\
+\hline 
+\end{tabularx}
+\label{emerging-misc}
+\end{table}
+
+\begin{table}[!ht]
+	\caption{Installed capacity growth rate limits and capacity limits for emerging technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
+		\hline
+\textbf{Technology} & \textbf{Annual Growth} & \textbf{Net Capacity} \\
+  & \textbf{Rate}  & \textbf{Limit} (GW) \\
+\hline
+Perovskite & 100\% (2022-2029) & None \\
+ & 80\% (2030-2034) &  \\
+ & 50\% (2035-2039) & \\
+ & 30\% (2040-2100) & \\
+All CCS, H$_2$ & 100\% (2025-29) & None \\
+technologies & 80\% (2030-2034) &  \\
+ & 50\% (2035-2039) & \\
+ & 30\% (2040-2100) & \\
+\hline 
+\end{tabularx}
+\label{emerging-gro}
+\end{table}
 
@@
 %approach, goal, what are we hoping to learn
+
 \begin{table}[!ht]
@@
 \end{table}
+
 \subsection{Sensitivity analysis}

### 2020-06-07 doc/2020-03-paper/acros.tex
added data + references
Former-commit-id: d21d3fa43c141a146410ddc02c412e9aeb411b66
Former-commit-id: 5dd078789f042d8cb1db3ad9cced13317e75feb5

@@
 \newacronym{OM}{O\&M}{Operation and Maintenance Cost}
-\newacronym{PEMFC}{PEM Fuel Cells}{Polymer Electrolyte Membrane Fuel Cells}
+\newacronym{PEMFC}{PEMFC}{Polymer Electrolyte Membrane Fuel Cells}
 \newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
 \newacronym{lng}{LNG}{Liquified Natural Gas}
+\newacronym{AEC}{AEC}{Alkaline Electrolyzer Cell}
+\newacronym{PEMEC}{PEMEC}{Polymer Electrolyte Membrane Electrolyzer Cell}
+\newacronym{SOEC}{SOEC}{Solid Oxide Electrolyzer Cell}
+\newacronym{SOFC}{SOFC}{Solid Oxide Fuel Cell}
+\newacronym{PWS}{PWS}{Photochemical Water Splitting}
 %\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-06-07 doc/2020-03-paper/methods.tex
added data + references
Former-commit-id: d21d3fa43c141a146410ddc02c412e9aeb411b66
Former-commit-id: 5dd078789f042d8cb1db3ad9cced13317e75feb5

--- 2020-04-06 doc/2020-03-paper/methods.tex
@@
 For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies.
-The economic data and growth rates for these technologies are defined in tables \ref{existing-eco} and .
+The economic data, such as capital costs, \gls{OM} costs, lifetime and capacity factors have been compiled from data sources into table \ref{existing-eco}.
+Dynamic trends are incorporated where available.
 The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector.
+Upper limits for growth rates are based on existing data, but with a generous margin of 5-20\%, as the trends in growth seen in the recent past may not represent the growth rates required to achieve the dramatic reduction in emissions we are aiming for.
+
+\gls{PEMFC} \gls{PEMEC} \gls{AEC} \gls{USC} \gls{SOEC} \gls{SOFC} \gls{PWS}.
+
+\begin{landscape}
+\begin{longtable}{ |*{8}{c|} }
+\caption{Economic data for modelled technologies.}\\
+\hline
+\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
+\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
+ & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
+\hline
+\endhead  % header material
+\hline
+\endfoot  % footer material
+\hline
+\endlastfoot
+\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
+\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
+Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
+Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
+ & 1446 (2025) &  &  &  &  & &  \\
+Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+ & 1086(2040) & & & & &  & \\
+ & 615(2050) & & & & & &  \\
+Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
+ & 3110(2040) &  &  &  & CF=0.3(2040) & 7(2040) &  \\
+ & 2800(2050) &  &  &  & CF=0.35(2050) &  &  \\
+Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
+ & 5438(2040) &  &  & & CF=0.35(2040) & 11(2040) &  \\
+ &  &  &  & & CF=0.4(2050) &  &  \\
+Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
+ & 9023(2040) &  &  &  & CF=0.4(2040) & 11(2040)  &  \\
+ &  &  &  &  & CF=0.45(2050) &  &  \\
+CCS-LNG(90\%) & 5088(2022) & 33(2022) & 0.0631(2022) & 30 & CF=0.12-0.4(2017) & 42(2022) & 2022 \\
+ & 2313(2050) & 14(2050) & 0.044(2050) &  & CF=0.35(2017) &  & \\
+CCS-USC(90\%) & 6816(2023) & 84(2023) & 0.093(2023) & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
+ & 3552(2050) & 69(2050) & 0.058(2050) &  &  &  & \\
+Emerging Solar & 4600(2017) & 15.19(2017) & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
+ & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
+ & 3822(2030) &  &  &  & Eff=0.25(2025) &  13(2040) &  \\
+ & 2164(2035) &  &  &  & Eff=0.3(2030) &  &  \\
+  & 1086(2040) &  &  &  &  &  &  \\
+ & 615(2050) &  &  &  &  &  &  \\
+  & 600(2051) &  &  &  &  &  &  \\
+\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.6 & 0.408(2022) & 2022\\
+ & 4000(2030) &  &  &  &  & 0.245(2030) &  \\
+ & 3000(2030) &  &  &  &  & 0.245(2030) &  \\
+\gls{AEC} & 1500(2022) & 6.87 & 0.0009 & 10(CF=0.9) & Eff=0.82 & 3.19 & 2022\\
+ & 850(2030) &  &  &  &  & &  \\
+\gls{PEMEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2022\\
+ & 2200(2025) &  &  &  &  & 16(2050) &  \\
+ & 1500(2030) &  &  &  &  &  &  \\
+ & 1000(2035) &  &  &  &  &  &  \\
+ & 500(2040) &  &  &  &  &  &  \\
+\gls{SOEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
+\gls{SOFC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2030\\
+\gls{PWS} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
+\label{eco}
+\end{longtable}
+\end{landscape}
 
 \begin{table}[!ht]
-	\caption{Economic data for existing technologies.}
+%\begin{minipage}{\textwidth} 
+	\caption{Installed capacity growth rate limits and capacity limits for existing technologies.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.2\textwidth} p{0.16\textwidth} p{0.16\textwidth} p{0.16\textwidth}  p{0.1\textwidth} p{0.1\textwidth}}
+	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
 		\hline
-\textbf{Technology} & \textbf{Investment Cost} & \textbf{Fixed \gls{OM} costs} & \textbf{Variable \gls{OM} costs} & \textbf{Lifetime} & \textbf{Capacity Factor}\\
-  & USD/kW & USD/kW & USD/MWh & Years & \\
+\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
+  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
 \hline
-Nuclear & 6317 & 121.13 & 2.36 & 60 & 0.90\\
-Solar & 1307 (2017) & 15.19 & 0 & 25 & 0.14\\
-Onshore Wind & 3454 (2017) & 136.37 & 0 & 25 & 0.4\\
-Offshore Wind(Fixed) & 7772.73 & 341 & 0 & 25 & 0.44\\
-Offshore Wind(Floating) & 12897 & 423 & 0 & 25 & 0.44\\
-Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & 4h/24h \\
-Natural Gas &  1079 & 14 & 2.54 & 10 & 0.55 \\
-\gls{USC} & 3661 & 40.41 & 4.48 & 10 & 0.55 \\
+Nuclear (2027 onwards) & +5 reactors & 50 GW (with new tech)  \\
+ & & 100 GW (without new tech)  \\
+  & & (see Sec. \ref{scendef} ) \\
+Solar & 40\% & 300 \\
+Onshore Wind & 25\% & 3.75 (2017) \\
+ &  & 15.3 (2020) \\
+ &  & 39.9 (2030) \\
+ &  & 57.0 (2040) \\
+ &  & 114.0 (2100) \\
+Offshore Wind(Fixed) & 20\% & 1 (2017) \\
+ &  & 8.70 (2030) \\
+ &  & 22.50 (2040) \\
+ &  & 28.50 (2050) \\
+ &  & 57.00 (2100) \\
+Offshore Wind(Floating) & 20\% & 1 (2017) \\
+ &  & 5.70 (2030) \\
+ &  & 19.35 (2040) \\
+ &  & 27.00 (2050) \\
+ &  & 54.00 (2100) \\
+Li-ion Storage & 30\% & None  \\
+Natural Gas &  50\% & None \\
+\gls{USC} & 50\% & None \\
 \hline 
 \end{tabularx}
-\label{existing-eco}
+\label{existing-gro}
+%\end{minipage}
 \end{table}
@@
 
-\subsection{Base scenarios}
+\begin{table}[!ht]
+	\caption{Installed capacity growth rate limits and capacity limits for emerging technologies.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
+		\hline
+\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
+  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
+\hline
+Emerging Solar & 40\% & None \\
+All CCS, H$_2$ & 40\% (Year 1-5) & None \\
+technologies & 60\% (Year 6-10) &  \\
+ & 40\% (Year 11-15) & \\
+ & 30\% (Year 16-) & \\
+\hline 
+\end{tabularx}
+\label{emerging-gro}
+\end{table}
+
+\subsection{Base scenarios} \label{scendef}
 %approach, goal, what are we hoping to learn
+
 \begin{table}[!ht]

### 2020-06-17 doc/2020-03-paper/methods.tex
completed economic data table (first draft)
Former-commit-id: 11d12709b9a7acbddcc4268ef9157a0b7255b47b
Former-commit-id: 1fd4530b8cc901f3c87c966b8dd760ec7c84af26

@@
 Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
- & 1086(2040) & & & & &  & \\
  & 615(2050) & & & & & &  \\
 Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
- & 3110(2040) &  &  &  & CF=0.3(2040) & 7(2040) &  \\
- & 2800(2050) &  &  &  & CF=0.35(2050) &  &  \\
+ & 2406(2050) &  &  &  & CF=0.35(2050) &  &  \\
 Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
- & 5438(2040) &  &  & & CF=0.35(2040) & 11(2040) &  \\
- &  &  &  & & CF=0.4(2050) &  &  \\
+ & 3381(2050) &  &  & & CF=0.40(2050) &  &  \\
 Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
- & 9023(2040) &  &  &  & CF=0.4(2040) & 11(2040)  &  \\
- &  &  &  &  & CF=0.45(2050) &  &  \\
-CCS-LNG(90\%) & 5088(2022) & 33(2022) & 0.0631(2022) & 30 & CF=0.12-0.4(2017) & 42(2022) & 2022 \\
- & 2313(2050) & 14(2050) & 0.044(2050) &  & CF=0.35(2017) &  & \\
-CCS-USC(90\%) & 6816(2023) & 84(2023) & 0.093(2023) & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
- & 3552(2050) & 69(2050) & 0.058(2050) &  &  &  & \\
-Emerging Solar & 4600(2017) & 15.19(2017) & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
- & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
- & 3822(2030) &  &  &  & Eff=0.25(2025) &  13(2040) &  \\
- & 2164(2035) &  &  &  & Eff=0.3(2030) &  &  \\
-  & 1086(2040) &  &  &  &  &  &  \\
- & 615(2050) &  &  &  &  &  &  \\
-  & 600(2051) &  &  &  &  &  &  \\
-\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.6 & 0.408(2022) & 2022\\
- & 4000(2030) &  &  &  &  & 0.245(2030) &  \\
- & 3000(2030) &  &  &  &  & 0.245(2030) &  \\
-\gls{AEC} & 1500(2022) & 6.87 & 0.0009 & 10(CF=0.9) & Eff=0.82 & 3.19 & 2022\\
+ & 5610(2050) &  &  &  & CF=0.45(2050) &  &  \\
+CCS-LNG(90\%) & 2626(2022) & 27.484 & 0.0531 & 30 & CF=0.12-0.4(2017) & WHA & 2022 \\
+ & 1422(2050) &  & &  &  &  & \\
+CCS-USC(90\%) & 5252(2023) & 59 & 0.094 & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
+ & 4091(2050) &  &  &  &  &  & \\
+Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
+  & 600(2050) &  &  & Eff=0.3(2030) &  & 13(2040) &  \\
+\gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
  & 850(2030) &  &  &  &  & &  \\
-\gls{PEMEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2022\\
- & 2200(2025) &  &  &  &  & 16(2050) &  \\
- & 1500(2030) &  &  &  &  &  &  \\
- & 1000(2035) &  &  &  &  &  &  \\
- & 500(2040) &  &  &  &  &  &  \\
-\gls{SOEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
-\gls{SOFC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2030\\
-\gls{PWS} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
+\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
+ & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
+ & 400(2050) &  &  &  & &  &  \\
+\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
+ & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
+ & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
+Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 400 & 2022\\
+Gas Reforming w/ CCS & 1200 & 8 & 0.077 & 30 & Eff=0.5 & 120 & 2022\\
+\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
+ & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
+ & 3000(2035) &  &  &  &  &  &  \\
+\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
+ & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
+ & 3000(2040) &  &  &  &  & &  \\
+\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
 \label{eco}

### 2020-06-17 doc/2020-03-paper/methods.tex
added ccs lifecycle emissions
Former-commit-id: 56b5d9172b37cf64a13fbcc80652f57bff9a985d
Former-commit-id: 359488cfa9d96e1f7b3cf386ef39c04ab7db0d62

@@
 \endlastfoot
-\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
-\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
-Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
-Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
- & 1446 (2025) &  &  &  &  & &  \\
+\gls{USC} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
+ & 1446 (2025) &  &  &  &  & 87 (2025) &  \\
 Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
@@
 Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
- & 2406(2050) &  &  &  & CF=0.35(2050) &  &  \\
+ & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
- & 3381(2050) &  &  & & CF=0.40(2050) &  &  \\
+ & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
- & 5610(2050) &  &  &  & CF=0.45(2050) &  &  \\
-CCS-LNG(90\%) & 2626(2022) & 27.484 & 0.0531 & 30 & CF=0.12-0.4(2017) & WHA & 2022 \\
+ & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 170 & 2022 \\
  & 1422(2050) &  & &  &  &  & \\
-CCS-USC(90\%) & 5252(2023) & 59 & 0.094 & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
+USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 220 & 2023 \\
  & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
-  & 600(2050) &  &  & Eff=0.3(2030) &  & 13(2040) &  \\
+  & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
 \gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
@@
  & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
-Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 400 & 2022\\
-Gas Reforming w/ CCS & 1200 & 8 & 0.077 & 30 & Eff=0.5 & 120 & 2022\\
+Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
+Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
 \gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\

### 2020-06-19 doc/2020-03-paper/Appendix.tex
added intro and litreview draft
Former-commit-id: 9e8d3fb3816dc710a72af07e4eefa25d914aceb5
Former-commit-id: 65e2ca89214491e667fb2548c45b9cb86e03f1ff

@@
-\section{Feed rates for all cases} \label{Appendix}
-Appendix
+\section{Data and assumptions for scenarios} \label{Appendix}
+\begin{table}[!ht]
+	\caption{Data for initial condition.}
+	\vspace{0.1in}
+	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
+		\hline
+\textbf{Technology} & \textbf{\gls{lcoe}} & \textbf{Emission} & \textbf{Year of total}\\
+  & (USD/kWh) & \textbf{Coefficients} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
+\hline
+Coal & 0.06 & 943 & 2030 \\
+\gls{lng} & 0.08 & 599 & 2030 \\
+Oil & 0.39 & 738 & 2030 \\
+Nuclear & 0.11 & 21 & 2069 \\
+Hydro & 0.05 & 11 & N.A. \\
+Geothermal & 0.12 & 13 & N.A. \\
+Wind & 0.11 & 25 & 2040 \\
+Solar & 0.15 & 37 & 2040 \\
+\hline 
+\end{tabularx}
+\label{init-eco}
+\end{table}
+
+\begin{figure}[h] 
+\centering
+\label{ic-elc}
+\includegraphics[scale=0.5]{figures/IC}
+\caption{Electricity generation that defines the initial condition of the model.}
+\end{figure}
+
+\begin{table}[!ht]
+	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
+		\hline
+\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
+  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
+\hline
+2013 & 603.62 & 592.4 & 1.89 \% \\
+2014 & 582.27 & 572.6 & 1.69 \% \\
+2015 & 572.53 & 560.3 & 2.18 \% \\
+2016 & 565.94 & 552.8 & 2.38 \% \\
+\hline 
+	\end{tabularx}
+\label{ic-co2}
+\end{table}
+\begin{landscape}
+\begin{longtable}{ |*{8}{c|} }
+\caption{Economic data for modelled technologies.}\\
+\hline
+\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
+\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
+ & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
+\hline
+\endhead  % header material
+\hline
+\endfoot  % footer material
+\hline
+\endlastfoot
+\gls{USC} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
+ & 1446 (2025) &  &  &  &  & 87(2050) &  \\
+Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+ & 615(2050) & & & & & &  \\
+Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
+ & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
+ & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
+ & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
+ & 1422(2050) &  & &  &  &  & \\
+USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
+ & 4091(2050) &  &  &  &  &  & \\
+Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
+  & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
+\gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
+ & 850(2030) &  &  &  &  & &  \\
+\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
+ & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
+ & 400(2050) &  &  &  & &  &  \\
+\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
+ & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
+ & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
+Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
+Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
+\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
+ & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
+ & 3000(2035) &  &  &  &  &  &  \\
+\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
+ & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
+ & 3000(2040) &  &  &  &  & &  \\
+\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
+\label{eco}
+\end{longtable}
+\end{landscape}
+
+\begin{table}[!ht]
+	\caption{Capacity limits.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
+		\hline
+\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
+\hline
+Photovoltaic & 332 \\
+Onshore wind & 332 \\
+Offshore wind (fixed) & 332 \\
+Offshore wind (floating) & 332 \\
+Nuclear & 332 \\
+\hline 
+\end{tabularx}
+\label{emerging-gro}
+\end{table}
+
+\begin{table}[!ht]
+%\begin{minipage}{\textwidth} 
+	\caption{Capacity growth rates.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+		\hline
+\textbf{Technology} & \textbf{Max. Annual} \\
+  & \textbf{Growth Rate}   \\
+\hline
+Nuclear (2027 onwards) & +5 reactors \\
+Solar & 40\%  \\
+Onshore Wind & 25\% \\
+Offshore Wind(Fixed) & 20\% \\
+Offshore Wind(Floating) & 20\% \\
+Li-ion Storage & 30\% \\
+Natural Gas &  50\% \\
+\gls{USC} & 50\% \\
+All CCS, H$_2$ & 40\% (Year 1-5) \\
+technologies & 60\% (Year 6-10) \\
+ & 40\% (Year 11-15) \\
+ & 30\% (Year 16-) \\
+\hline 
+\end{tabularx}
+\label{tech-gro}
+%\end{minipage}
+\end{table}

### 2020-06-19 doc/2020-03-paper/introduction.tex
added intro and litreview draft
Former-commit-id: 9e8d3fb3816dc710a72af07e4eefa25d914aceb5
Former-commit-id: 65e2ca89214491e667fb2548c45b9cb86e03f1ff

\section{Introduction} \label{Introduction}
In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements (UNFCCC, 2015). The largest contribution to global greenhouse gas (GHG) emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors (WRI, 2020). For developed economy nations rich in natural resources, switching to natural gas or implementing carbon capture and storage (CCS) on fossil fuel plants is one option to reduce GHG emissions, however for developing nations, these options are not always economically feasible, leading to increased emissions (through greater coal use) for rapidly developing nations (IEA, 2019). For Japan, a developed economy nation with no fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment (IEA, 2019).
Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 (METI, 2018). The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018). The Plan reaffirms the Japanese benchmarks for evaluating the energy system as, first and foremost within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid). Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met. This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies (Matsuo et al., 2018). For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies (Ashina et al., 2012). It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan. The current candidates include a reinvigoration of the nuclear contribution to final energy demand, deploying CCS to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad (Ashina et al., 2012; Matsuo et al., 2018; METI, 2017). 
The aim of this research is to investigate the likely suite of technologies and their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using the TIMES framework. Our dynamic simulations of transition scenarios, by focusing on minimizing the cost of the transition while satisfying CO2 emission constraints, suggest potential economically feasible decarbonization pathways while meeting the increasing near-term electricity demand. Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters of each technology and hence guide research and development efforts focused on these technologies.

### 2020-06-19 doc/2020-03-paper/litreview.tex
added intro and litreview draft
Former-commit-id: 9e8d3fb3816dc710a72af07e4eefa25d914aceb5
Former-commit-id: 65e2ca89214491e667fb2548c45b9cb86e03f1ff

\section{Background and literature review} \label{litreview}
The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism (UNFCCC, 2019). Japan, as a signatory to the Paris Agreements has submitted an INDC with the following goals and timelines: by 2030, to reduce GHG emissions by 26\% compared to 2013 levels, and by 2050 to reduce overall GHG emissions by 80\% or more, through the “development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure” (UNFCCC, 2015). Cognizant of these targets, a numfgber of authors have evaluated Japan,s future energy system using a variety of modeling approaches. Using the MARKAL model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and carbon capture and storage (CCS) to reduce electricity sector emissions to nearly zero by 2050 (2018). Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al. explored the role of hydrogen as a storage medium through power to gas (P2G) approaches in Kyushu, Japan. Their study identified that P2G can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (2019). Cognizant of the Japanese government,s strategic approach to carbon reduction out to 2050 via energy system reform, Chapman & Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018). Considering economic conditions and demographic trends such as moderate GDP growth and rapid aging which are occurring in Japan, Kuriyama et al., suggest that 2030 targets can be met or exceeded (i.e. up to 42\% GHG reduction) with limited renewable energy growth at a 15\% contribution from nuclear, or even without nuclear, under a renewable growth scenario (2019). It appears that these trends and energy system changes will be insufficient to meet the more ambitious 2050 targets. Taking a more holistic view, in line with the Japanese government,s 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also have a large influence on modeling outcomes for the  Low Carbon Navigator assessing Japanese energy and emission options out to 2050 (Moinuddin & Kuriyama, 2019). A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan,s long term (i.e. to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models (2019). Model results are contrasted under six scenarios which incorporate a baseline and a range of emissions reductions (50-80\%) and regional obligations for global models (ibid.). under the Paris Agreement target of an 80\% reduction, each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro & Masui, 2015; Sugiyama et al., 2019). Many studies consider hydrogen a critical part of Japan,s low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida & Sakata, 2019). Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by fuel cell passenger and freight vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 (Ishimoto et al., 2017). From a policy standpoint, Japan has committed to achieving a hydrogen society with the primary goal of cost parity of hydrogen with competing fuels, requiring a three-fold reduction in cost by 2030, and further reductions into the future (Nagashima, 2018). Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility and industry, develop international supply chains to ensure stable supply, expand renewable deployment and revitalize regional areas and develop hydrogen related technologies (METI, 2017). The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges (Nagashima, 2018). A common thread across previous research is that the uncertainty surrounding carbon capture and storage (particularly with regard to scaling up and public acceptance issues) and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 (Oshiro et al., 2019). 
The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050. By modeling the Japanese energy system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction goals against the backdrop of a long time-scale that incorporates the effects of the retirement of existing fossil fuel, nuclear and renewable generation capacity. This work also leverages the dynamic simulation capabilities of TIMES <CITE LOULOU> by incorporating time varying trends for economic parameters such as investment and o&m costs, efficiency, deployment dates, scalability, growth rates, and emission coefficients. Our model also does not neglect life-cycle emissions from nuclear, renewables or any of the emerging CCS or hydrogen technologies, as the emissions associated with the construction of these technologies, while insignificant compared to fossil fuels, are significant when considering emission levels associated with an 80\% emission reduction. This also allows for a more meaningful analysis when assessing the carbon neutrality of the energy mix, and the effect of a carbon tax.

### 2020-06-19 doc/2020-03-paper/methods.tex
added intro and litreview draft
Former-commit-id: 9e8d3fb3816dc710a72af07e4eefa25d914aceb5
Former-commit-id: 65e2ca89214491e667fb2548c45b9cb86e03f1ff

--- 2020-06-17 doc/2020-03-paper/methods.tex
@@
 
-\begin{table}[!ht]
-	\caption{Data for initial condition.}
-	\vspace{0.1in}
-	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
-		\hline
-\textbf{Technology} & \textbf{\gls{lcoe}} & \textbf{Emission} & \textbf{Year of total}\\
-  & (USD/kWh) & \textbf{Coefficients} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
-\hline
-Coal & 0.06 & 943 & 2030 \\
-\gls{lng} & 0.08 & 599 & 2030 \\
-Oil & 0.39 & 738 & 2030 \\
-Nuclear & 0.11 & 21 & 2069 \\
-Hydro & 0.05 & 11 & N.A. \\
-Geothermal & 0.12 & 13 & N.A. \\
-Wind & 0.11 & 25 & 2040 \\
-Solar & 0.15 & 37 & 2040 \\
-\hline 
-\end{tabularx}
-\label{init-eco}
-\end{table}
-
-\begin{figure}[h] 
-\centering
-\label{ic-elc}
-\includegraphics[scale=0.5]{figures/IC}
-\caption{Electricity generation that defines the initial condition of the model.}
-\end{figure}
-
-\begin{table}[!ht]
-	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust.}
-	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
-		\hline
-\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
-  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
-\hline
-2013 & 603.62 & 592.4 & 1.89 \% \\
-2014 & 582.27 & 572.6 & 1.69 \% \\
-2015 & 572.53 & 560.3 & 2.18 \% \\
-2016 & 565.94 & 552.8 & 2.38 \% \\
-\hline 
-	\end{tabularx}
-\label{ic-co2}
-\end{table}
 The electricity demand in the near term is expected to increase by 1.7\% per year (cite electricity review).
@@
 
-\begin{landscape}
-\begin{longtable}{ |*{8}{c|} }
-\caption{Economic data for modelled technologies.}\\
-\hline
-\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
-\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
- & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
-\hline
-\endhead  % header material
-\hline
-\endfoot  % footer material
-\hline
-\endlastfoot
-\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
-\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
-Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
-Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
- & 1446 (2025) &  &  &  &  & &  \\
-Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
- & 615(2050) & & & & & &  \\
-Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
- & 2406(2050) &  &  &  & CF=0.35(2050) &  &  \\
-Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
- & 3381(2050) &  &  & & CF=0.40(2050) &  &  \\
-Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
- & 5610(2050) &  &  &  & CF=0.45(2050) &  &  \\
-CCS-LNG(90\%) & 2626(2022) & 27.484 & 0.0531 & 30 & CF=0.12-0.4(2017) & WHA & 2022 \\
- & 1422(2050) &  & &  &  &  & \\
-CCS-USC(90\%) & 5252(2023) & 59 & 0.094 & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
- & 4091(2050) &  &  &  &  &  & \\
-Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
-  & 600(2050) &  &  & Eff=0.3(2030) &  & 13(2040) &  \\
-\gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
- & 850(2030) &  &  &  &  & &  \\
-\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
- & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
- & 400(2050) &  &  &  & &  &  \\
-\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
- & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
- & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
-Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 400 & 2022\\
-Gas Reforming w/ CCS & 1200 & 8 & 0.077 & 30 & Eff=0.5 & 120 & 2022\\
-\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
- & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
- & 3000(2035) &  &  &  &  &  &  \\
-\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
- & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
- & 3000(2040) &  &  &  &  & &  \\
-\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
-\label{eco}
-\end{longtable}
-\end{landscape}
-
-\begin{table}[!ht]
-%\begin{minipage}{\textwidth} 
-	\caption{Installed capacity growth rate limits and capacity limits for existing technologies.}
-	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
-		\hline
-\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
-  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
-\hline
-Nuclear (2027 onwards) & +5 reactors & 50 GW (with new tech)  \\
- & & 100 GW (without new tech)  \\
-  & & (see Sec. \ref{scendef} ) \\
-Solar & 40\% & 300 \\
-Onshore Wind & 25\% & 3.75 (2017) \\
- &  & 15.3 (2020) \\
- &  & 39.9 (2030) \\
- &  & 57.0 (2040) \\
- &  & 114.0 (2100) \\
-Offshore Wind(Fixed) & 20\% & 1 (2017) \\
- &  & 8.70 (2030) \\
- &  & 22.50 (2040) \\
- &  & 28.50 (2050) \\
- &  & 57.00 (2100) \\
-Offshore Wind(Floating) & 20\% & 1 (2017) \\
- &  & 5.70 (2030) \\
- &  & 19.35 (2040) \\
- &  & 27.00 (2050) \\
- &  & 54.00 (2100) \\
-Li-ion Storage & 30\% & None  \\
-Natural Gas &  50\% & None \\
-\gls{USC} & 50\% & None \\
-\hline 
-\end{tabularx}
-\label{existing-gro}
-%\end{minipage}
-\end{table}
-
 \subsection{Emerging technologies}
-
-\begin{table}[!ht]
-	\caption{Installed capacity growth rate limits and capacity limits for emerging technologies.}
-	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
-		\hline
-\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
-  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
-\hline
-Emerging Solar & 40\% & None \\
-All CCS, H$_2$ & 40\% (Year 1-5) & None \\
-technologies & 60\% (Year 6-10) &  \\
- & 40\% (Year 11-15) & \\
- & 30\% (Year 16-) & \\
-\hline 
-\end{tabularx}
-\label{emerging-gro}
-\end{table}
 

### 2020-06-19 doc/2020-03-paper/litreview.tex
added litreview, alkaline ec emissions
Former-commit-id: 81773bfdbeecdc359b7a7412964d263f0e91909e
Former-commit-id: 0f7abe6bc99effe150dff7bfb589ed72662fb65a

@@
 Japan, as a signatory to the Paris Agreements has submitted an INDC with the following goals and timelines: by 2030, to reduce GHG emissions by 26\% compared to 2013 levels, and by 2050 to reduce overall GHG emissions by 80\% or more, through the “development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure” (UNFCCC, 2015).
-Cognizant of these targets, a numfgber of authors have evaluated Japan,s future energy system using a variety of modeling approaches.
+Cognizant of these targets, a number of authors have evaluated Japan’s future energy system using a variety of modeling approaches.
 Using the MARKAL model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and carbon capture and storage (CCS) to reduce electricity sector emissions to nearly zero by 2050 (2018).
@@
 Their study identified that P2G can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (2019).
-Cognizant of the Japanese government,s strategic approach to carbon reduction out to 2050 via energy system reform, Chapman & Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
+Cognizant of the Japanese government’s strategic approach to carbon reduction out to 2050 via energy system reform, Chapman & Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
 Considering economic conditions and demographic trends such as moderate GDP growth and rapid aging which are occurring in Japan, Kuriyama et al., suggest that 2030 targets can be met or exceeded (i.e.
@@
 It appears that these trends and energy system changes will be insufficient to meet the more ambitious 2050 targets.
-Taking a more holistic view, in line with the Japanese government,s 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
+Taking a more holistic view, in line with the Japanese government’s 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
 Consensus on policy options and priorities also have a large influence on modeling outcomes for the  Low Carbon Navigator assessing Japanese energy and emission options out to 2050 (Moinuddin & Kuriyama, 2019).
-A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan,s long term (i.e.
+A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan’s long term (i.e.
 to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models (2019).
@@
 Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro & Masui, 2015; Sugiyama et al., 2019).
-Many studies consider hydrogen a critical part of Japan,s low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida & Sakata, 2019).
+Many studies consider hydrogen a critical part of Japan’s low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida & Sakata, 2019).
 Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by fuel cell passenger and freight vehicles and power generation, via both mixed and direct combustion.
@@
 A common thread across previous research is that the uncertainty surrounding carbon capture and storage (particularly with regard to scaling up and public acceptance issues) and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 (Oshiro et al., 2019).
+
+This work leverages the dynamic simulation capabilities of TIMES <CITE LOULOU> by incorporating learning curves for parameters such as investment and o&m costs, efficiency, and emission coefficients.
+Our model also incorporates life-cycle emissions of all conventional and emerging technologies.
+This allows for a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\%.
 The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050.
-By modeling the Japanese energy system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction goals against the backdrop of a long time-scale that incorporates the effects of the retirement of existing fossil fuel, nuclear and renewable generation capacity.
-This work also leverages the dynamic simulation capabilities of TIMES <CITE LOULOU> by incorporating time varying trends for economic parameters such as investment and o&m costs, efficiency, deployment dates, scalability, growth rates, and emission coefficients.
-Our model also does not neglect life-cycle emissions from nuclear, renewables or any of the emerging CCS or hydrogen technologies, as the emissions associated with the construction of these technologies, while insignificant compared to fossil fuels, are significant when considering emission levels associated with an 80\% emission reduction.
-This also allows for a more meaningful analysis when assessing the carbon neutrality of the energy mix, and the effect of a carbon tax.
+By modeling the Japanese energy system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2020-06-21 doc/2020-03-paper/introduction.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205

@@
 For Japan, a developed economy nation with no fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment (IEA, 2019).
+
 Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 (METI, 2018).
@@
 The current candidates include a reinvigoration of the nuclear contribution to final energy demand, deploying CCS to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad (Ashina et al., 2012; Matsuo et al., 2018; METI, 2017).
-The aim of this research is to investigate the likely suite of technologies and their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using the TIMES framework.
+
+The aim of this research is to investigate the likely suite of electricity generation and storage technologies and their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using the TIMES framework.
 Our dynamic simulations of transition scenarios, by focusing on minimizing the cost of the transition while satisfying CO2 emission constraints, suggest potential economically feasible decarbonization pathways while meeting the increasing near-term electricity demand.

### 2020-06-21 doc/2020-03-paper/litreview.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205

@@
 The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism (UNFCCC, 2019).
-Japan, as a signatory to the Paris Agreements has submitted an INDC with the following goals and timelines: by 2030, to reduce GHG emissions by 26\% compared to 2013 levels, and by 2050 to reduce overall GHG emissions by 80\% or more, through the “development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure” (UNFCCC, 2015).
-Cognizant of these targets, a number of authors have evaluated Japan’s future energy system using a variety of modeling approaches.
+Japan, as a signatory to the Paris Agreements has submitted an INDC with the following goals and timelines: by 2030, to reduce GHG emissions by 26\% compared to 2013 levels, and by 2050 to reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" (UNFCCC, 2015).
+Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
 Using the MARKAL model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and carbon capture and storage (CCS) to reduce electricity sector emissions to nearly zero by 2050 (2018).
@@
 Their study identified that P2G can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (2019).
-Cognizant of the Japanese government’s strategic approach to carbon reduction out to 2050 via energy system reform, Chapman & Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
+Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
 Considering economic conditions and demographic trends such as moderate GDP growth and rapid aging which are occurring in Japan, Kuriyama et al., suggest that 2030 targets can be met or exceeded (i.e.
@@
 It appears that these trends and energy system changes will be insufficient to meet the more ambitious 2050 targets.
-Taking a more holistic view, in line with the Japanese government’s 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
-Consensus on policy options and priorities also have a large influence on modeling outcomes for the  Low Carbon Navigator assessing Japanese energy and emission options out to 2050 (Moinuddin & Kuriyama, 2019).
-A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan’s long term (i.e.
+Taking a more holistic view, in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
+Consensus on policy options and priorities also have a large influence on modeling outcomes for the  Low Carbon Navigator assessing Japanese energy and emission options out to 2050 (Moinuddin \& Kuriyama, 2019).
+A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan's long term (i.e.
 to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models (2019).
@@
 under the Paris Agreement target of an 80\% reduction, each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
-Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro & Masui, 2015; Sugiyama et al., 2019).
-Many studies consider hydrogen a critical part of Japan’s low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida & Sakata, 2019).
+Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro \& Masui, 2015; Sugiyama et al., 2019).
+Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida \& Sakata, 2019).
 Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by fuel cell passenger and freight vehicles and power generation, via both mixed and direct combustion.
@@
 
-This work leverages the dynamic simulation capabilities of TIMES <CITE LOULOU> by incorporating learning curves for parameters such as investment and o&m costs, efficiency, and emission coefficients.
+This work leverages the dynamic simulation capabilities of TIMES (Loulou et al., 2005) by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
 Our model also incorporates life-cycle emissions of all conventional and emerging technologies.
@@
 The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050.
-By modeling the Japanese energy system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
+By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2020-06-21 doc/2020-03-paper/methods.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205

@@
-\section{Model description} \label{Model-description}
+\section{Methodology} \label{method}
 
 \subsection{TIMES Model Description}
-Objective function.
-Constraints - CO2 emissions reduction targets, increasing demand, CO2 tax.
-Important parameters.
+The \gls{TIMES} model generator is designed to model dynamic energy systems and simulate transition scenarios as a mixed-integer programming linear optimization problem that is subject to a primary objective function and additional constraints.
+The generation, trade, refinement, storage, and supply of energy commodities across multiple sectors and multiple regions is modeled using a wide variety of in-built commodity and process types.
+Emissions can be associated with energy commodities or processes as emission coefficient per unit commodity produced or consumed.
 
-\subsection{Common Features - Initial condition and constraints}
+The objective function in our simulations is the overall cost of the transition, hence the primary objective of the solver is to minimize said cost.The major constrains in our simulations are the overall demand for electricity, emission constraints based on Japan's \gls{NDC}, and feasible nameplate capacity deployment limits.
 

### 2020-06-22 doc/2020-03-paper/acks.tex
added plots for base scen 1-4
Former-commit-id: 3d0d846c0d9516d8f3e77a5968cef48b21b24b62
Former-commit-id: b13122957eda23ef887beeafd327aaf3b6cddf4d

@@
 The authors contributed to this work as described below.
-
-Osama Ashraf conceived and designed the simulations, wrote the paper, prepared figures 
-and/or tables, performed the computation work, and reviewed drafts of the paper.
-
-Andrei Rykhlevskii conceived and designed the simulations, wrote the paper, prepared figures 
-and/or tables, performed the computation work, and reviewed drafts of the paper. Andrei Rykhlevskii 
-is supported by  DOE ARPA-E MEITNER program award DE-AR0000983.
 
@@
 sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.
-
-This research is part of the Blue Waters sustained-petascale computing 
-project, which is supported by the National Science Foundation (awards 
-OCI-0725070 and ACI-1238993) and the state of Illinois. Blue Waters is a joint 
-effort of the University of Illinois at Urbana-Champaign and its National 
-Center for Supercomputing Applications.
-
-The authors thank members of the Advanced Reactors and Fuel Cycles (ARFC) 
-group at the University of Illinois at Urbana-Champaign for helpful 
-discussions relating to this paper. Finally, the authors would like to thank 
-Matthew Kozak for constructive criticism of the manuscript.

### 2020-06-22 doc/2020-03-paper/acros.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205
added plots for base scen 1-4
Former-commit-id: 3d0d846c0d9516d8f3e77a5968cef48b21b24b62
Former-commit-id: b13122957eda23ef887beeafd327aaf3b6cddf4d

@@
 \newacronym{lng}{LNG}{Liquified Natural Gas}
-\newacronym{AEC}{AEC}{Alkaline Electrolyzer Cell}
-\newacronym{PEMEC}{PEMEC}{Polymer Electrolyte Membrane Electrolyzer Cell}
-\newacronym{SOEC}{SOEC}{Solid Oxide Electrolyzer Cell}
+\newacronym{AEC}{AEC}{Alkaline Electrolyser Cell}
+\newacronym{PEMEC}{PEMEC}{Polymer Electrolyte Membrane Electrolyser Cell}
+\newacronym{SOEC}{SOEC}{Solid Oxide Electrolyser Cell}
 \newacronym{SOFC}{SOFC}{Solid Oxide Fuel Cell}
 \newacronym{PWS}{PWS}{Photochemical Water Splitting}
+\newacronym{INDC}{INDC}{Intended Nationally Determined Contribution}
+\newacronym{GHG}{GHG}{greenhouse gas}
 %\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-06-22 doc/2020-03-paper/methods.tex
added plots for base scen 1-4
Former-commit-id: 3d0d846c0d9516d8f3e77a5968cef48b21b24b62
Former-commit-id: b13122957eda23ef887beeafd327aaf3b6cddf4d

@@
 \section{Methodology} \label{method}
-
+% what is TIMES, what are we doing, common features of all scenarios(obj, constraints, time frame, technology details, how are results presented/assessed
 \subsection{TIMES Model Description}
@@
 
-The objective function in our simulations is the overall cost of the transition, hence the primary objective of the solver is to minimize said cost.The major constrains in our simulations are the overall demand for electricity, emission constraints based on Japan's \gls{NDC}, and feasible nameplate capacity deployment limits.
+The objective function in our simulations is the overall cost of the transition.
+The major constrains in our simulations are the demand for electricity (see table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see table \ref{caplim}).
+Hence each simulation is focused on minimizing the transition cost while attempting to meet the increasing electricity demand and achieving the required emission cuts using, a combination of technologies of various readiness levels.
 
-The initial condition is based on energy generation data from \gls{EDMC} for the years 2013-2016 , and emission data for electricity generation from National Carbon Trust (see Fig.
-\ref{ic-elc}).
-As the \gls{EDMC} database has been evolving over the course of this work, the focus of our model was to recreate the 2013-2016 emission levels with low error, instead of recreating the \gls{EDMC} electricity generation data.
-A tolerance of 1\% was allowed for each electricity generation technology in order to avoid specifying an overly rigorous initial condition that slows the model down.
-The error in the CO$_2$ emission levels is minimal, as seen in Table \ref{ic-co2}.
-
-The economic data for initially deployed capacity is associated with the respective \gls{lcoe} of each electricity supply source, substituted for variable \gls{OM} costs.
-The \gls{lcoe} data and the emission factors for the technologies used in defining the initial condition are listed in table \ref{init-eco}.
-All existing fossil fuels are gradually retired by 2025.
-This aggressive retirement is enabled to simulate the necessary premature retirement required to meet the challenging CO$_2$ constraints, and to not saddle the model with technologies that make the CO$_2$ constraints unattainable.
-As mentioned in the next section, if the model still feels the need to deploy fossil fuel-based technology, it can deploy natural gas and coal with a 10 year lifetime (to simulate premature retirement).
-In practice, this would represent premature retirement of fossil fuel plants or retrofitting them with \gls{CCS} technology.
-
-The electricity demand in the near term is expected to increase by 1.7\% per year (cite electricity review).
-However, in the long run, the demand should eventually plateau, if not decrease altogether, due to the ageing population of Japan.
-In the absence of long term projections, our model approximates the gradual reduction in the annual demand increase rate, and its eventual reduction to 0\% per year, as shown in table \ref{demand}.
-The demand increases linearly for all intermediate years.
+While electricity demand in the near term is expected to grow, long term electricity demand is expected to plateau, or even decrease, due to Japan's aging population.
+However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
+Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification resulting in increasing demand for electricity, but the demand eventually plateaus due to the aging population.
+The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016.
+Long term impacts of factors such as the retirement of the existing nuclear fleet and the new deployment of emerging, potentially disruptive technology is assessed by simulating the system until 2100.
+The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire lifetime output) for every technology, as applicable.
 
@@
 \end{table}
-The CO$_2$ constraints common to all the models are as shown in table \ref{co2-limits}. The CO$_2$ limit for intervening years is linearly interpolated to ensure gradual transitions. 
+
 \begin{table}[!ht]
@@
 
-\subsection{Existing technologies}
+To explore possible pathways to curbing \gls{GHG} emissions, we simulated different transition scenarios with different combinations of technologies enabled for deployment.
+The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
+New deployments of oil-fuelled power plants are disabled due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence under the Basic Energy Plan.
+The second set of technologies considered includes emerging carbon-neutral technologies, namely \gls{CCS} and utility-scale hydrogen power.
+Based on their technological readiness and scalability, \gls{CCS}-based coal and natural gas,\gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation.
+It is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables.
+However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain.
+Hence, scenarios where new nuclear reactor deployment is enabled and disabled must be juxtaposed to assess the potential role of nuclear in decarbonization of the electricity generation sector.
+Finally, the long-term impact of nascent technologies on the hydrogen economy is considered in an additional scenario.
+In this scenario, the potential of the commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
 
-For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies.
-The economic data, such as capital costs, \gls{OM} costs, lifetime and capacity factors have been compiled from data sources into table \ref{existing-eco}.
-Dynamic trends are incorporated where available.
-The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector.
-Upper limits for growth rates are based on existing data, but with a generous margin of 5-20\%, as the trends in growth seen in the recent past may not represent the growth rates required to achieve the dramatic reduction in emissions we are aiming for.
+ADD TECH PARAMS,ASSUMPTIONS.
 
-\gls{PEMFC} \gls{PEMEC} \gls{AEC} \gls{USC} \gls{SOEC} \gls{SOFC} \gls{PWS}.
-
-\subsection{Emerging technologies}
-
-\subsection{Base scenarios} \label{scendef}
 %approach, goal, what are we hoping to learn

### 2020-06-22 doc/2020-03-paper/discussion.tex
added results
Former-commit-id: 4c3b33b13ba2639f7649dce115d0832e5f3badac
Former-commit-id: 5c0328da46f31d8f48794b2dba882d21e6c30d7b

\section{Discussion}
% This should explore the significance of the results of the work, not repeat
% them. A combined Results and Discussion section is often appropriate. Avoid
% extensive citations and discussion of published literature.

### 2020-06-23 doc/2020-03-paper/Appendix.tex
added plots for base scen 1-4
Former-commit-id: 3d0d846c0d9516d8f3e77a5968cef48b21b24b62
Former-commit-id: b13122957eda23ef887beeafd327aaf3b6cddf4d
added results
Former-commit-id: 4c3b33b13ba2639f7649dce115d0832e5f3badac
Former-commit-id: 5c0328da46f31d8f48794b2dba882d21e6c30d7b
capacity limits, scenarios details
Former-commit-id: 29a6326e0b47ebd541575ad240b7e271cbccf2d3
Former-commit-id: 0d103945a43a523462de42764e8ff5969a844d8f

@@
 \end{table}
+
 \begin{landscape}
@@
 Photovoltaic & 332 \\
-Onshore wind & 332 \\
-Offshore wind (fixed) & 332 \\
-Offshore wind (floating) & 332 \\
-Nuclear & 332 \\
+Onshore wind & 180 \\
+Offshore wind (fixed) & 130 \\
+Offshore wind (floating) & 260 \\
+Nuclear & 50 (with new tech.) \\
+Nuclear & 100 (without new tech.) \\
+\gls{PWS} & 100 (without new tech.) \\
 \hline 
 \end{tabularx}
-\label{emerging-gro}
+\label{caplim}
 \end{table}
@@
 Nuclear (2027 onwards) & +5 reactors \\
-Solar & 40\%  \\
+Solar and Emerging Solar & 40\%  \\
 Onshore Wind & 25\% \\
@@
 \gls{USC} & 50\% \\
-All CCS, H$_2$ & 40\% (Year 1-5) \\
-technologies & 60\% (Year 6-10) \\
- & 40\% (Year 11-15) \\
- & 30\% (Year 16-) \\
+All emerging technologies & 40\% (Years 1-5) \\
+& 60\% (Years 6-10) \\
+ & 40\% (Years 11-15) \\
+ & 30\% (Years 16-) \\
 \hline 
 \end{tabularx}
-\label{tech-gro}
+\label{growrate}
 %\end{minipage}

### 2020-06-23 doc/2020-03-paper/methods.tex
added results
Former-commit-id: 4c3b33b13ba2639f7649dce115d0832e5f3badac
Former-commit-id: 5c0328da46f31d8f48794b2dba882d21e6c30d7b
capacity limits, scenarios details
Former-commit-id: 29a6326e0b47ebd541575ad240b7e271cbccf2d3
Former-commit-id: 0d103945a43a523462de42764e8ff5969a844d8f

@@
 In this scenario, the potential of the commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
+Thus, five scenarios are simulated to explore possible transition pathways under the aforementioned conditions, and these are detailed in table \ref{scen-table}.
 
-ADD TECH PARAMS,ASSUMPTIONS.
+ADD TECH PARAMS,ASSUMPTIONS, FIX TABLE.
+The economic data, emission coefficients, nameplate capacity limits and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.33\textwidth} p{0.33\textwidth} p{0.33\textwidth}}
+	\begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.25\textwidth} p{0.25\textwidth} p{0.35\textwidth}}
 \hline 
-\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
-                 & \textbf{enabled} & \textbf{enabled} \\
+\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} & \textbf{Nascent tech.}\\
+                 & \textbf{enabled} & \textbf{enabled} & \textbf{enabled}\\
                   \hline
@@
 %4               &   \greencheck     &         \xmark       \\
-1               &   No       &      Yes     \\ 
-2               &  No       &         No       \\ 
-3               &   Yes     &      Yes     \\ 
-4               &   Yes     &         No       \\
-
+1               &  No       &         No     &     No  \\ 
+2               &   No       &      Yes     &     No  \\ 
+3               &   Yes     &         No      &     No   \\
+4               &   Yes     &      Yes     &     No  \\ 
+5               &   Yes     &      Yes     &     Yes  \\ 
 \hline

### 2020-06-23 doc/2020-03-paper/acks.tex
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

@@
 
-The authors contributed to this work as described below.
-
-Kathryn D.
+%The authors contributed to this work as described below.
+%
+%
+%Kathryn D.
 Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
@@
 Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER),
-sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.
+%sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2020-06-23 doc/2020-03-paper/conclusion.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

@@
 \section{Conclusion} \label{Conclusion}
-Conclusion
+Notes for Ansh:
+Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
+Urgency of transition : scenarios + sensitivity analysis.
+Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements.
+AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
+SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).
 \section{Future work}
-FUTURE WORK
 
 \section{Declaration of Competing Interest}
-
-NECESARY?

### 2020-06-23 doc/2020-03-paper/methods.tex
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

@@
 The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
-New deployments of oil-fuelled power plants are disabled due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence under the Basic Energy Plan.
-The second set of technologies considered includes emerging carbon-neutral technologies, namely \gls{CCS} and utility-scale hydrogen power.
-Based on their technological readiness and scalability, \gls{CCS}-based coal and natural gas,\gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation.
-It is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables.
+New deployments of oil-fuelled power plants are not considered due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence as per the Basic Energy Plan.
+The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS} and utility-scale hydrogen power.
+For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation based on their technological.
+Along with these two technology groups, it is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables.
 However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain.
 Hence, scenarios where new nuclear reactor deployment is enabled and disabled must be juxtaposed to assess the potential role of nuclear in decarbonization of the electricity generation sector.
-Finally, the long-term impact of nascent technologies on the hydrogen economy is considered in an additional scenario.
-In this scenario, the potential of the commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
-Thus, five scenarios are simulated to explore possible transition pathways under the aforementioned conditions, and these are detailed in table \ref{scen-table}.
+Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario.
+In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
+Thus, five scenarios are simulated to explore possible transition pathways under a wide variety of conditions, and these are detailed in table \ref{scen-table}.
 
-ADD TECH PARAMS,ASSUMPTIONS, FIX TABLE.
 The economic data, emission coefficients, nameplate capacity limits and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Learning curves for costs and life-cycle emissions are compiled from existing data about cost projections, scale-up of manufacturing, availability of manufacturing materials (especially rare earth materials) and the use of clean energy for manufacturing.
+These learning curves modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for said parameter, as detailed in table \ref{eco}.
+Capacity limits on renewables and \gls{PWS} are based on their land-use requirements, whereas the assumed capacity limits for nuclear are based on the minimum requirement for nuclear in different scenarios.
+The land use footprint of other technologies is considered negligible.
+Maximum annual capacity growth rates for existing technologies are constant.
+The growth rate of nuclear power based on historic trends and current pressure vessel manufacturing limitations.
+The reactor size assumed in this study is 1165 MWe.
+The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate maximum growth rate.
+One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
+We believe that these technologies, some of which are already commercialized or close to commercialization,  will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
+Hence they could be deployed as rapidly as solar photovoltaic.
 

### 2020-06-23 doc/2020-03-paper/discussion.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

@@
 % extensive citations and discussion of published literature.
+Notes for Ansh:
+Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
+Urgency of transition : scenarios + sensitivity analysis.
+Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements.
+AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
+SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).

### 2020-06-23 doc/2020-03-paper/methods.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

@@
 The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire lifetime output) for every technology, as applicable.
+The daily and seasonal variability of renewables is incorporated using day-night and seasonal time periods.
+The availability of renewables varies during these time periods (for instance, solar output drops to zero at night, and a similar notion of days without wind is incorporated) based on the annually averaged capacity factors of renewables in Japan (cite).
 
@@
 2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
-2100 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
+2100 & 75 Mt CO$_2$-eq. & 2050 & 0 \% \\
 \hline 
@@
 
+All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years).
+Our assumptions about the reduction in the investment costs of life-cycle emissions are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries.
+All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following.
+Long-term storage of hydrogen is also available using hydrogen tanks with appropriate losses (cite IEA).
+For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the nature of the hydrogen facility and the source of energy used for electrolysis (eg: wind, biomass, solar photovoltaic etc.)
+
 %approach, goal, what are we hoping to learn

### 2020-06-23 doc/2020-03-paper/results.tex
added results
Former-commit-id: 4c3b33b13ba2639f7649dce115d0832e5f3badac
Former-commit-id: 5c0328da46f31d8f48794b2dba882d21e6c30d7b
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

@@
-\section{Results and discussion} \label{Results-and-discussion}
-RESULTS
+\section{Results} \label{Results-and-discussion}
+\subsection{Transition Scenarios}
+Notes for Ansh: electricity diverted to storage could be reduced to text with percentages i.e.
+"total amount of electricity diverted to storage=, electricity for storage came from nuclear (50\%), solar(30\%),wind(20\%) over 2017-2100".
+Same for H2 (total GWh generated, amount).
+
+Scenario 1 results (fig.
+\ref{scen1}) demonstrate our model's attempt at decarbonization using existing technologies without deploying new nuclear power.
+Under these conditions, coal and oil must be retired by 2030, and natural gas by 2050.
+All existing nuclear power plants must restarted by <YEAR> at full operating capacity.
+With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium ion storage are necessary.
+The presence of a large share of renewables results in significant overgeneration of electricity during some years.
+Due to reduced flexibility caused by the retirement of natural gas and an increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model.
+The plot displaying the electricity supplied to the end-user shows a high degree of variability as excess electricity from renewables, hydropower, and nuclear power is often diverted to lithium-ion storage as appropriate, instead of being directly supplied to the \gls{TIMES} process.
+Despite the deployment of a large amount of renewables, the model fails to achieve the 2030 and 2050 emission reduction goals by <AMT1> and <AMT2> respectively.
+Furthermore, emissions continue to rise after 2050 primarily due to life-cycle emissions of lithium-ion batteries.
+The total cost of this transition is \textbf{insert number here.}
+
+With the option of deploying new nuclear reactors available in Scenario 2 (fig.
+\ref{scen2}) , the model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions.
+Coal and oil are again retired rapidly, but due to the reduction in emissions by nuclear power, natural gas power plants can continue to operate.
+The amount of renewables required for decarbonization is reduced dramatically.
+This combined with the load following capabilities of natural gas plants and nuclear reactors drastically reduces the amount of lithium ion storage.
+The model is able to achieve its 2030 and 2050 decarbonization goals, and automatically decarbonizes more than the required limit by 2100.
+The total transition cost is \textbf{insert number here.}
+\begin{figure}[h] 
+\centering
+\label{scen1}
+\includegraphics[scale=0.25]{figures/conv_nonuc}
+\caption{Conventional technologies, no new nuclear.}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\label{scen2}
+\includegraphics[scale=0.25]{figures/conv_nuc}
+\caption{Conventional technologies, with new nuclear.}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\label{scen3}
+\includegraphics[scale=0.2]{figures/newtechs_nonuc}
+\caption{Emerging technologies, no new nuclear.}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\label{scen4}
+\includegraphics[scale=0.2]{figures/newtechs_nuc}
+\caption{Emerging technologies, no new nuclear.}
+\end{figure}
+
+\subsection{Sensitivity analysis}

### 2020-06-24 doc/2020-03-paper/methods.tex
added scenaario results description
Former-commit-id: 2d5aecee148ca1908aea8bad4b823693d0b14a8b
Former-commit-id: 3a70cd2d8df0cf14b57e554377c76c209071b20f

@@
 
-All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years).
+All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, a depth of discharge of 80\%, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years).
 Our assumptions about the reduction in the investment costs of life-cycle emissions are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries.

### 2020-06-24 doc/2020-03-paper/results.tex
added scenaario results description
Former-commit-id: 2d5aecee148ca1908aea8bad4b823693d0b14a8b
Former-commit-id: 3a70cd2d8df0cf14b57e554377c76c209071b20f

@@
 \ref{scen1}) demonstrate our model's attempt at decarbonization using existing technologies without deploying new nuclear power.
-Under these conditions, coal and oil must be retired by 2030, and natural gas by 2050.
-All existing nuclear power plants must restarted by <YEAR> at full operating capacity.
+In all scenarios, coal and oil must be retired by 2030.
+Natural gas sees rapid growth in the near-term, and complete retirement by 2055.
+Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards.
+All existing nuclear power plants must restarted by 2022 at full operating capacity.
 With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium ion storage are necessary.
@@
 Furthermore, emissions continue to rise after 2050 primarily due to life-cycle emissions of lithium-ion batteries.
+The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
 The total cost of this transition is \textbf{insert number here.}
@@
 \ref{scen2}) , the model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions.
-Coal and oil are again retired rapidly, but due to the reduction in emissions by nuclear power, natural gas power plants can continue to operate.
+Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100.
 The amount of renewables required for decarbonization is reduced dramatically.
-This combined with the load following capabilities of natural gas plants and nuclear reactors drastically reduces the amount of lithium ion storage.
+This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the amount of lithium ion storage deployed.
 The model is able to achieve its 2030 and 2050 decarbonization goals, and automatically decarbonizes more than the required limit by 2100.
+The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
 The total transition cost is \textbf{insert number here.}
+
+Using emerging technologies without new nuclear power (fig.
+\ref{scen3}), the model needs to restart Japan's existing nuclear power plants at full capacity by 2030.
+The deep emission cuts achieved through renewables, hydrogen and \gls{CCS} leave room for emissions from \gls{lng}, hence natural gas plants continue to operate until 2100.
+Expansion of solar and onshore wind, along with a modest deployment of lithium ion batteries, helps the model meet 2030 emission goals.
+After that, the model relies primarily on renewables and hydrogen to curb emissions while supplying power.
+Investment in hydrogen allows effective utilization of renewables and precludes investment in offshore floating wind power.
+\gls{lng}-based \gls{CCS} plays a modest role between <YEAR1-YEAR2> as an intermediate technology before the model can complete the transition to utility scale hydrogen.
+The model deploys <X> GW of \gls{CCS} technology that results in <Y> amount of CO$_2$ captured.
+As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace current solar power, benefiting from the existing solar manufacture and supply chains.
+The model is able to hold the emissions constant until 2100, but addition decarbonization as in scenario 2 is not achieved.
+The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
+The amount of hydrogen generated is < > GWh, from <SOURCES>.
+The cost of this transition is <insert number here>.
+
+Using emerging technologies with new nuclear power deployment results in rapid decarbonization that continues until 2100.
+The model achieves an additional <X> Mt of CO$_2$ reduction by 2050.
+The deployment of around 50 MW nuclear obviates the need to invest in offshore wind, lithium ion storage, and \gls{CCS}.
+Hydrogen plays a significant role in decarbonization, but it is deployed from <YEAR> instead.
+The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
+The amount of hydrogen generated is < > GWh, from <SOURCES>.
+The cost of this transition is <insert number here>.
+
 \begin{figure}[h] 

### 2020-06-25 doc/2020-03-paper/results.tex
image, plotting script cleanup
Former-commit-id: 732c4439d7ab78701e8bb97066bd3151f04ec0a0
Former-commit-id: 05c78ecd4f27e617b14ecdb85b654f822e1dea4d

@@
 Same for H2 (total GWh generated, amount).
+
+Talk about description of plots, common features, oscillations, storage,
 
@@
 Furthermore, emissions continue to rise after 2050 primarily due to life-cycle emissions of lithium-ion batteries.
-The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
+The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
 The total cost of this transition is \textbf{insert number here.}
@@
 The model is able to achieve its 2030 and 2050 decarbonization goals, and automatically decarbonizes more than the required limit by 2100.
-The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
+The amount of electricity diverted to storage technologies is 12,220 TWh, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
 The total transition cost is \textbf{insert number here.}
@@
 The model is able to hold the emissions constant until 2100, but addition decarbonization as in scenario 2 is not achieved.
-The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
-The amount of hydrogen generated is < > GWh, from <SOURCES>.
+The amount of electricity diverted to storage technologies is 43,879 TWh, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%),and onshore wind (20\%).
+The amount of hydrogen generated is 35,478 TWh, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%).
 The cost of this transition is <insert number here>.
@@
 Hydrogen plays a significant role in decarbonization, but it is deployed from <YEAR> instead.
-The amount of electricity diverted to storage technologies is <X>, primarily from <list of contributors>.
-The amount of hydrogen generated is < > GWh, from <SOURCES>.
+The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%).
+The amount of hydrogen generated is 24,264 TWh, produced entirely from PEM electrolysis.
 The cost of this transition is <insert number here>.
 
-\begin{figure}[h] 
+\begin{figure}[htb] 
 \centering
 \label{scen1}
-\includegraphics[scale=0.25]{figures/conv_nonuc}
+\includegraphics[scale=0.3]{figures/conv_nonuc}
 \caption{Conventional technologies, no new nuclear.}
@@
 \label{scen2}
-\includegraphics[scale=0.25]{figures/conv_nuc}
+\includegraphics[scale=0.3]{figures/conv_nuc}
 \caption{Conventional technologies, with new nuclear.}
@@
 \label{scen3}
-\includegraphics[scale=0.2]{figures/newtechs_nonuc}
+\includegraphics[scale=0.3]{figures/newtechs_nonuc}
 \caption{Emerging technologies, no new nuclear.}
@@
 \label{scen4}
-\includegraphics[scale=0.2]{figures/newtechs_nuc}
+\includegraphics[scale=0.3]{figures/newtechs_nuc}
 \caption{Emerging technologies, no new nuclear.}

### 2020-06-25 doc/2020-03-paper/Appendix.tex
adjusted plot width and legends
Former-commit-id: c5e2c31a189fc816638987eebdc40e010fba5b20
Former-commit-id: 86035ec06681e1d9b2daf96a89475c5d4832517a

@@
 Offshore wind (floating) & 260 \\
-Nuclear & 50 (with new tech.) \\
-Nuclear & 100 (without new tech.) \\
-\gls{PWS} & 100 (without new tech.) \\
+Nuclear & 50 (Scenarios 3 \& 4) \\
+ & 100 (Scenario 2) \\
+\gls{PWS} & 100 (Scenario 5) \\
 \hline 

### 2020-06-25 doc/2020-03-paper/litreview.tex
minor corrections
Former-commit-id: 73fa67ae7dfdd55dc9ca0475bcfdd9cec707fa25
Former-commit-id: 37a6fe9c80ddc0b9080cf1e4d4e034e7c6c4cdd7

@@
 
+The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050.
 This work leverages the dynamic simulation capabilities of TIMES (Loulou et al., 2005) by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
-Our model also incorporates life-cycle emissions of all conventional and emerging technologies.
-This allows for a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\%.
-The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050.
+Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities considering the highly globalized manufacture and supply chain of existing and emerging technologies.
+This accounts for a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from recent emission levels.
 By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2020-06-25 doc/2020-03-paper/methods.tex
minor corrections
Former-commit-id: 73fa67ae7dfdd55dc9ca0475bcfdd9cec707fa25
Former-commit-id: 37a6fe9c80ddc0b9080cf1e4d4e034e7c6c4cdd7

--- 2020-06-23 doc/2020-03-paper/methods.tex
@@
 \section{Methodology} \label{method}
-% what is TIMES, what are we doing, common features of all scenarios(obj, constraints, time frame, technology details, how are results presented/assessed
+% what is TIMES
 \subsection{TIMES Model Description}
-The \gls{TIMES} model generator is designed to model dynamic energy systems and simulate transition scenarios as a mixed-integer programming linear optimization problem that is subject to a primary objective function and additional constraints.
+The \gls{TIMES} model generator is designed to model dynamic energy systems and simulate transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints.
 The generation, trade, refinement, storage, and supply of energy commodities across multiple sectors and multiple regions is modeled using a wide variety of in-built commodity and process types.
@@
 
-The objective function in our simulations is the overall cost of the transition.
+%basic features of model
+The objective function in our single-region model is the overall cost of the transition.
 The major constrains in our simulations are the demand for electricity (see table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see table \ref{caplim}).
-Hence each simulation is focused on minimizing the transition cost while attempting to meet the increasing electricity demand and achieving the required emission cuts using, a combination of technologies of various readiness levels.
+Hence each simulation is focused on minimizing the transition cost, while attempting to meet the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
 
-While electricity demand in the near term is expected to grow, long term electricity demand is expected to plateau, or even decrease, due to Japan's aging population.
+While electricity demand in the near future is expected to grow, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
 However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
-Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification resulting in increasing demand for electricity, but the demand eventually plateaus due to the aging population.
+Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification, but the demand gradually plateaus due to the aging population.
 The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016.
-Long term impacts of factors such as the retirement of the existing nuclear fleet and the new deployment of emerging, potentially disruptive technology is assessed by simulating the system until 2100.
-The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire lifetime output) for every technology, as applicable.
+Long term impacts of factors such as the retirement of the existing nuclear fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
+The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire operating lifetime) for every technology, as applicable.
+The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods (cite Loulou).
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan (cite).
 
@@
 
+%scenario description
 To explore possible pathways to curbing \gls{GHG} emissions, we simulated different transition scenarios with different combinations of technologies enabled for deployment.
 The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
-New deployments of oil-fuelled power plants are not considered due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence as per the Basic Energy Plan.
+New deployments of oil-fuelled power plants are not considered due to the declining use of oil for electricity generation in Japan due to Japan's goal of energy security and independence as per the Basic Energy Plan.
 The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS} and utility-scale hydrogen power.
-For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation based on their technological.
-Along with these two technology groups, it is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables.
+For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC}s,\gls{PEMEC}s,\gls{PEMFC}s, and \gls{SOFC}s were selected for simulation based on their technological.
+Along with these two technology groups, it is also important to consider the impact of nuclear energy due to its extremely long operational lifetimes, and consequently extremely low life-cycle emissions, and a high capacity factor.
+These factors grant nuclear power significant advantages over renewables.
 However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain.
-Hence, scenarios where new nuclear reactor deployment is enabled and disabled must be juxtaposed to assess the potential role of nuclear in decarbonization of the electricity generation sector.
+Hence, transition scenarios with and without new nuclear reactor deployment must be juxtaposed to assess the importance of the role of nuclear in emission reduction.
 Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario.
 In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
-Thus, five scenarios are simulated to explore possible transition pathways under a wide variety of conditions, and these are detailed in table \ref{scen-table}.
+Thus, a total of five transition scenarios of varying likelihood are simulated, and these are detailed in table \ref{scen-table}.
 
-The economic data, emission coefficients, nameplate capacity limits and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Learning curves for costs and life-cycle emissions are compiled from existing data about cost projections, scale-up of manufacturing, availability of manufacturing materials (especially rare earth materials) and the use of clean energy for manufacturing.
-These learning curves modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for said parameter, as detailed in table \ref{eco}.
-Capacity limits on renewables and \gls{PWS} are based on their land-use requirements, whereas the assumed capacity limits for nuclear are based on the minimum requirement for nuclear in different scenarios.
-The land use footprint of other technologies is considered negligible.
-Maximum annual capacity growth rates for existing technologies are constant.
-The growth rate of nuclear power based on historic trends and current pressure vessel manufacturing limitations.
+%misc assumptions
+The economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Learning curves for costs and life-cycle emissions are compiled from existing data based on scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
+These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in table \ref{eco}.
+Capacity limits of renewables and \gls{PWS} are based on their land-use requirements.
+The maximum annual capacity growth rates for existing technologies are held constant.
+The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations.
 The reactor size assumed in this study is 1165 MWe.
-The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate maximum growth rate.
+Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors.
+The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate growth rate.
 One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
 We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
-Hence they could be deployed as rapidly as solar photovoltaic.
+Hence they could be deployed as rapidly as conventional solar photovoltaic.
+
+All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, a depth of discharge of 80\%, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years).
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries.
+All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following.
+Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors (cite IEA).
+For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
 

### 2020-06-25 doc/2020-03-paper/results.tex
minor corrections
Former-commit-id: 73fa67ae7dfdd55dc9ca0475bcfdd9cec707fa25
Former-commit-id: 37a6fe9c80ddc0b9080cf1e4d4e034e7c6c4cdd7

@@
 \section{Results} \label{Results-and-discussion}
+
 \subsection{Transition Scenarios}
-Notes for Ansh: electricity diverted to storage could be reduced to text with percentages i.e.
-"total amount of electricity diverted to storage=, electricity for storage came from nuclear (50\%), solar(30\%),wind(20\%) over 2017-2100".
-Same for H2 (total GWh generated, amount).
 
-Talk about description of plots, common features, oscillations, storage,
+The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology.
+Due to natural variations in renewables' output, the ability of some electricity sources to load-follow, and the increasing deployment of storage, the first plot shows a large degree of variation, as generated electricity is diverted from multiple sources to storage technologies, instead of being supplied directly to the end user.
+The second plot describes the transitions in terms of capacities, and highlights the effect of the capacity factor of intermittent versus base-load technologies.
+The third plot details the sources of direct and averaged life-cycle emissions from each source.
 
-Scenario 1 results (fig.
-\ref{scen1}) demonstrate our model's attempt at decarbonization using existing technologies without deploying new nuclear power.
-In all scenarios, coal and oil must be retired by 2030.
+In scenario 1 (fig.
+\ref{scen1}), the model is able to meet 2030 emission goals but fails to meet 2050 emission goals by a margin of 25 Mt.
+Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium ion storage.
+As in all other scenarios, coal and oil must be retired by 2030.
 Natural gas sees rapid growth in the near-term, and complete retirement by 2055.
-Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards.
+Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards due to its load-following capabilities.
 All existing nuclear power plants must restarted by 2022 at full operating capacity.
@@
 The presence of a large share of renewables results in significant overgeneration of electricity during some years.
-Due to reduced flexibility caused by the retirement of natural gas and an increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model.
-The plot displaying the electricity supplied to the end-user shows a high degree of variability as excess electricity from renewables, hydropower, and nuclear power is often diverted to lithium-ion storage as appropriate, instead of being directly supplied to the \gls{TIMES} process.
-Despite the deployment of a large amount of renewables, the model fails to achieve the 2030 and 2050 emission reduction goals by <AMT1> and <AMT2> respectively.
-Furthermore, emissions continue to rise after 2050 primarily due to life-cycle emissions of lithium-ion batteries.
 The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
-The total cost of this transition is \textbf{insert number here.}
+The total cost of this transition is \textbf{3,513,941 MUSD} (in 2015 USD).
 
-With the option of deploying new nuclear reactors available in Scenario 2 (fig.
-\ref{scen2}) , the model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions.
+With the availability new nuclear reactors in Scenario 2 (fig.
+\ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100.
+The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions.
 Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100.
@@
 This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the amount of lithium ion storage deployed.
-The model is able to achieve its 2030 and 2050 decarbonization goals, and automatically decarbonizes more than the required limit by 2100.
 The amount of electricity diverted to storage technologies is 12,220 TWh, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
-The total transition cost is \textbf{insert number here.}
+The total transition cost of this scenario is the lowest, at \textbf{2,664,207 MUSD.}
 
 Using emerging technologies without new nuclear power (fig.
-\ref{scen3}), the model needs to restart Japan's existing nuclear power plants at full capacity by 2030.
+\ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonization occurs after 2050.
+The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario.
 The deep emission cuts achieved through renewables, hydrogen and \gls{CCS} leave room for emissions from \gls{lng}, hence natural gas plants continue to operate until 2100.
-Expansion of solar and onshore wind, along with a modest deployment of lithium ion batteries, helps the model meet 2030 emission goals.
+Expansion of solar and onshore wind, along with a modest deployment of lithium ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals.
 After that, the model relies primarily on renewables and hydrogen to curb emissions while supplying power.
-Investment in hydrogen allows effective utilization of renewables and precludes investment in offshore floating wind power.
-\gls{lng}-based \gls{CCS} plays a modest role between <YEAR1-YEAR2> as an intermediate technology before the model can complete the transition to utility scale hydrogen.
-The model deploys <X> GW of \gls{CCS} technology that results in <Y> amount of CO$_2$ captured.
+Significant investment in hydrogen from 2034 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power.
+\gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility scale hydrogen.
+Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame.
+This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan (cite Kato 2016).
 As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace current solar power, benefiting from the existing solar manufacture and supply chains.
-The model is able to hold the emissions constant until 2100, but addition decarbonization as in scenario 2 is not achieved.
 The amount of electricity diverted to storage technologies is 43,879 TWh, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%),and onshore wind (20\%).
 The amount of hydrogen generated is 35,478 TWh, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%).
-The cost of this transition is <insert number here>.
+The cost of this transition is \textbf{3,187,940 MUSD}.
 
-Using emerging technologies with new nuclear power deployment results in rapid decarbonization that continues until 2100.
-The model achieves an additional <X> Mt of CO$_2$ reduction by 2050.
+Using both emerging technologies with new nuclear reactors (fig.
+\ref{scen4}) results in rapid decarbonization.
+Both 2030 and 2050 emission targets met, and an additional emissions reduction of 32 Mt occurs by 2100.
 The deployment of around 50 MW nuclear obviates the need to invest in offshore wind, lithium ion storage, and \gls{CCS}.
-Hydrogen plays a significant role in decarbonization, but it is deployed from <YEAR> instead.
+Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared to scenario 3, from 2037 instead.
 The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%).
 The amount of hydrogen generated is 24,264 TWh, produced entirely from PEM electrolysis.
-The cost of this transition is <insert number here>.
+The cost of this transition is \textbf{2,804,753 MUSD}.
 
@@
 \centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nonuc}
+\caption{Conventional technologies, no new nuclear.}
 \label{scen1}
-\includegraphics[scale=0.3]{figures/conv_nonuc}
-\caption{Conventional technologies, no new nuclear.}
 \end{figure}
@@
 \centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nuc}
+\caption{Conventional technologies, with new nuclear.}
 \label{scen2}
-\includegraphics[scale=0.3]{figures/conv_nuc}
-\caption{Conventional technologies, with new nuclear.}
 \end{figure}
@@
 \centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nonuc}
+\caption{Emerging technologies, no new nuclear.}
 \label{scen3}
-\includegraphics[scale=0.3]{figures/newtechs_nonuc}
-\caption{Emerging technologies, no new nuclear.}
 \end{figure}
@@
 \centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nuc}
+\caption{Emerging technologies, no new nuclear.}
 \label{scen4}
-\includegraphics[scale=0.3]{figures/newtechs_nuc}
-\caption{Emerging technologies, no new nuclear.}
 \end{figure}

### 2020-06-26 doc/2020-03-paper/methods.tex
minor corrections
Former-commit-id: 76e77b1523eb618e7a780869cbc0305d62999327
Former-commit-id: 1a828357956bc6fcf50c50c37814155968f6391b

@@
 %misc assumptions
-The economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+The model uses MUSD(2015) as the default currency unit, and a 5\% discount rate.
+Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
 Learning curves for costs and life-cycle emissions are compiled from existing data based on scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.

### 2020-06-30 doc/2020-03-paper/methods.tex
minor assumptions update
Former-commit-id: 0471d955cf790eb1b68d9e8687d64ec42158d098
Former-commit-id: 1df54404b36efd55ff190c48b94e7ea02d89a535
minor corrections
Former-commit-id: 6b7680c3388d633325db12cb64212204aa1f9a66
Former-commit-id: f18dc2281f14e3f12a9db789578ac17ad633cfd5

@@
 The model uses MUSD(2015) as the default currency unit, and a 5\% discount rate.
+The transmission efficiency is assumed to be 90\%.
 Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Prices and projections for fossil fuels and nuclear fuel were incorporated.
 Learning curves for costs and life-cycle emissions are compiled from existing data based on scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
@@
 The reactor size assumed in this study is 1165 MWe.
-Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors.
+Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors' range of capacity factors.
 The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate growth rate.

### 2020-07-01 doc/2020-03-paper/methods.tex
minor edits
Former-commit-id: d6edc638a459eb9c40c1e86d88715c92474ee6ee
Former-commit-id: 53262b3a3a1fdbe1e41f4720e63dfa8eda7f585e

@@
 The major constrains in our simulations are the demand for electricity (see table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see table \ref{caplim}).
+Miscellaneous assumptions are summarized in table \ref{misc-assump}.
 Hence each simulation is focused on minimizing the transition cost, while attempting to meet the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
@@
 The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016.
-Long term impacts of factors such as the retirement of the existing nuclear fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
+Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
 The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire operating lifetime) for every technology, as applicable.
 The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods (cite Loulou).
-The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan (cite).
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan.
 
@@
 %misc assumptions
-The model uses MUSD(2015) as the default currency unit, and a 5\% discount rate.
-The transmission efficiency is assumed to be 90\%.
 Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Prices and projections for fossil fuels and nuclear fuel were incorporated.
+Prices and projections for fossil fuels and nuclear fuel were incorporated (add references).
 Learning curves for costs and life-cycle emissions are compiled from existing data based on scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
@@
 
-All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, a depth of discharge of 80\%, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years).
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries.
 All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following.
@@
 For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries respectively.
 

### 2020-08-28 doc/2020-03-paper/introduction.tex
minor corrections to introduction
Former-commit-id: 0e63083aad4554e5492e763db4113e29405f1904
Former-commit-id: e9403800b58991baa518f612851e4293f8b2ce61

--- 2020-06-19 doc/2020-03-paper/introduction.tex
@@
 In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements (UNFCCC, 2015).
-The largest contribution to global greenhouse gas (GHG) emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors (WRI, 2020).
-For developed economy nations rich in natural resources, switching to natural gas or implementing carbon capture and storage (CCS) on fossil fuel plants is one option to reduce GHG emissions, however for developing nations, these options are not always economically feasible, leading to increased emissions (through greater coal use) for rapidly developing nations (IEA, 2019).
-For Japan, a developed economy nation with no fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment (IEA, 2019).
+The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors (WRI, 2020).
+For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions.
+However for developing nations, these options are not always economically feasible, leading to increased emissions through greater coal use by rapidly developing nations (IEA, 2019).
+For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment (IEA, 2019).
+
 Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 (METI, 2018).
 The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018).
-The Plan reaffirms the Japanese benchmarks for evaluating the energy system as, first and foremost within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).
+The Plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).
 Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met.
@@
 It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan.
-The current candidates include a reinvigoration of the nuclear contribution to final energy demand, deploying CCS to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad (Ashina et al., 2012; Matsuo et al., 2018; METI, 2017).
-The aim of this research is to investigate the likely suite of technologies and their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using the TIMES framework.
-Our dynamic simulations of transition scenarios, by focusing on minimizing the cost of the transition while satisfying CO2 emission constraints, suggest potential economically feasible decarbonization pathways while meeting the increasing near-term electricity demand.
+The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad (Ashina et al., 2012; Matsuo et al., 2018; METI, 2017).
+
+The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using \gls{TIMES} framework.
+Our dynamic simulations of transition scenarios, by focusing on minimizing the cost of the transition while satisfying CO2 emission constraints, suggest potential economically feasible decarbonization pathways that meet the increasing near-term electricity demand.
 Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters of each technology and hence guide research and development efforts focused on these technologies.

### 2020-08-28 doc/2020-03-paper/litreview.tex
lit review corrections
Former-commit-id: 4f44fc931963a354bcb5e74b1219f87f407636f2
Former-commit-id: 249f1c80ef74feb3134bb71a245fda4f1a107c33

--- 2020-06-21 doc/2020-03-paper/litreview.tex
@@
 The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism (UNFCCC, 2019).
-Japan, as a signatory to the Paris Agreements has submitted an INDC with the following goals and timelines: by 2030, to reduce GHG emissions by 26\% compared to 2013 levels, and by 2050 to reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" (UNFCCC, 2015).
+Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" (UNFCCC, 2015).
 Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
-Using the MARKAL model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and carbon capture and storage (CCS) to reduce electricity sector emissions to nearly zero by 2050 (2018).
+Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 (Ozawa 2018).
 Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al.
-explored the role of hydrogen as a storage medium through power to gas (P2G) approaches in Kyushu, Japan.
-Their study identified that P2G can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (2019).
-Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
-Considering economic conditions and demographic trends such as moderate GDP growth and rapid aging which are occurring in Japan, Kuriyama et al., suggest that 2030 targets can be met or exceeded (i.e.
-up to 42\% GHG reduction) with limited renewable energy growth at a 15\% contribution from nuclear, or even without nuclear, under a renewable growth scenario (2019).
-It appears that these trends and energy system changes will be insufficient to meet the more ambitious 2050 targets.
-Taking a more holistic view, in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment appears to be necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
-Consensus on policy options and priorities also have a large influence on modeling outcomes for the  Low Carbon Navigator assessing Japanese energy and emission options out to 2050 (Moinuddin \& Kuriyama, 2019).
-A seminal work by Sugiyama et al., brings together a number of modeling approaches for Japan's long term (i.e.
+explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan.
+Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (Li et.
+al.
+2019).
+Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
+Considering Japan's economic conditions and demographic trends such as moderate GDP growth and rapid aging, Kuriyama et al.
+suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario (2019).
+However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.
+Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
+Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 (Moinuddin \& Kuriyama, 2019).
+A seminal work by Sugiyama et al.
+harmonizes a number of modeling approaches for Japan's long term (i.e.
 to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models (2019).
-Model results are contrasted under six scenarios which incorporate a baseline and a range of emissions reductions (50-80\%) and regional obligations for global models (ibid.).
-under the Paris Agreement target of an 80\% reduction, each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
+Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction.
+Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
 Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro \& Masui, 2015; Sugiyama et al., 2019).
-Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, specifically toward improving energy security, its ability to be produced from multiple sources and lack of emissions when combusted (Iida \& Sakata, 2019).
-Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by fuel cell passenger and freight vehicles and power generation, via both mixed and direct combustion.
+Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion (Iida \& Sakata, 2019).
+Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \gls{FCV}s and power generation, via both mixed and direct combustion.
 Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 (Ishimoto et al., 2017).
-From a policy standpoint, Japan has committed to achieving a hydrogen society with the primary goal of cost parity of hydrogen with competing fuels, requiring a three-fold reduction in cost by 2030, and further reductions into the future (Nagashima, 2018).
-Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility and industry, develop international supply chains to ensure stable supply, expand renewable deployment and revitalize regional areas and develop hydrogen related technologies (METI, 2017).
+From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future (Nagashima, 2018).
+Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies (METI, 2017).
 The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges (Nagashima, 2018).
-A common thread across previous research is that the uncertainty surrounding carbon capture and storage (particularly with regard to scaling up and public acceptance issues) and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 (Oshiro et al., 2019).
+A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 (Oshiro et al., 2019).
 
-This work leverages the dynamic simulation capabilities of TIMES (Loulou et al., 2005) by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
-Our model also incorporates life-cycle emissions of all conventional and emerging technologies.
-This allows for a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\%.
-The model and approach proposed in this research is unique, as it builds on the works and modeling consensus outlined in the literature review and expands the consideration of technologies beyond conventional and recent technologies to also include emerging and disruptive technologies post-2050.
-By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid and long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
+The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review, and expand the consideration of technologies beyond  conventional options to also include emerging near-term alternatives, and potentially disruptive technologies post-2050.
+This work leverages the dynamic simulation capabilities of \gls{TIMES} (Loulou et al., 2005) by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
+Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities.
+This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels.
+By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2020-08-28 doc/2020-03-paper/methods.tex
methodology minor corrections
Former-commit-id: bb5704f9059dd6be7778d735aea63348d7012923
Former-commit-id: 216117c713e2cf9f6af0e1b9954b547e6853bd45

@@
 \subsection{TIMES Model Description}
-The \gls{TIMES} model generator is designed to model dynamic energy systems and simulate transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints.
-The generation, trade, refinement, storage, and supply of energy commodities across multiple sectors and multiple regions is modeled using a wide variety of in-built commodity and process types.
-Emissions can be associated with energy commodities or processes as emission coefficient per unit commodity produced or consumed.
+\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints.
+The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types.
+Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.
 
@@
 The objective function in our single-region model is the overall cost of the transition.
-The major constrains in our simulations are the demand for electricity (see table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see table \ref{caplim}).
+The major constrains in our simulations are the demand for electricity (see Table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see Table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see Table \ref{caplim}).
 Miscellaneous assumptions are summarized in table \ref{misc-assump}.
-Hence each simulation is focused on minimizing the transition cost, while attempting to meet the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
+Hence each simulation is focused on minimizing the transition cost, while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
 
@@
 However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
-Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification, but the demand gradually plateaus due to the aging population.
+Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification driving increasing demand, but the demand eventually plateaus due to the aforementioned expected demographic changes.
 The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016.
 Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
-The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire operating lifetime) for every technology, as applicable.
+The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for every technology, as applicable.
 The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods (cite Loulou).
@@
 %scenario description
-To explore possible pathways to curbing \gls{GHG} emissions, we simulated different transition scenarios with different combinations of technologies enabled for deployment.
-The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
-New deployments of oil-fuelled power plants are not considered due to the declining use of oil for electricity generation in Japan due to Japan's goal of energy security and independence as per the Basic Energy Plan.
-The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS} and utility-scale hydrogen power.
-For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC}s,\gls{PEMEC}s,\gls{PEMFC}s, and \gls{SOFC}s were selected for simulation based on their technological.
-Along with these two technology groups, it is also important to consider the impact of nuclear energy due to its extremely long operational lifetimes, and consequently extremely low life-cycle emissions, and a high capacity factor.
-These factors grant nuclear power significant advantages over renewables.
+To explore possible pathways to curbing \gls{GHG} emissions, we simulated a total of five transition scenarios of varying likelihood, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}.
+The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
+New deployments of oil-fuelled power plants are neglected due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan.
+The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS}, and utility-scale hydrogen power.
+For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC}s,\gls{PEMEC}s,\gls{PEMFC}s, and \gls{SOFC}s were incoporated based on their technological potential.
+Along with these two technology groups, we also explore the potential impact of nuclear energy.
+Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions, and a high capacity factor.
 However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain.
@@
 Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario.
-In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored.
-Thus, a total of five transition scenarios of varying likelihood are simulated, and these are detailed in table \ref{scen-table}.
+In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored in the absence of new nuclear power.
 
 %misc assumptions
-Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
 Prices and projections for fossil fuels and nuclear fuel were incorporated (add references).
-Learning curves for costs and life-cycle emissions are compiled from existing data based on scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
-These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in table \ref{eco}.
+Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
+These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}.
 Capacity limits of renewables and \gls{PWS} are based on their land-use requirements.
@@
 Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors' range of capacity factors.
-The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate growth rate.
+The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
 One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
 We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
-Hence they could be deployed as rapidly as conventional solar photovoltaic.
+Therefore, they could be deployed as rapidly as conventional solar photovoltaic.
 
@@
 For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries respectively.
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively (cite).
 

### 2020-08-28 doc/2020-03-paper/results.tex
final corrections, closes #95
Former-commit-id: 3629b1917866685026c37863b4b819802bb93f0f
Former-commit-id: 902178e98715af08e374e21f5e92de05a2c42eaf

@@
 The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology.
-Due to natural variations in renewables' output, the ability of some electricity sources to load-follow, and the increasing deployment of storage, the first plot shows a large degree of variation, as generated electricity is diverted from multiple sources to storage technologies, instead of being supplied directly to the end user.
-The second plot describes the transitions in terms of capacities, and highlights the effect of the capacity factor of intermittent versus base-load technologies.
+Due to natural variations in renewables' output, the ability of some electricity sources to load-follow, and the increasing deployment of storage, the first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies, instead of being supplied directly to the end user.
+The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies.
 The third plot details the sources of direct and averaged life-cycle emissions from each source.
 
-In scenario 1 (fig.
-\ref{scen1}), the model is able to meet 2030 emission goals but fails to meet 2050 emission goals by a margin of 25 Mt.
-Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium ion storage.
+In Scenario 1 (Fig.
+\ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt.
+Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage.
 As in all other scenarios, coal and oil must be retired by 2030.
-Natural gas sees rapid growth in the near-term, and complete retirement by 2055.
+Natural gas sees rapid growth in the near-term, but complete retirement by 2055.
 Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards due to its load-following capabilities.
-All existing nuclear power plants must restarted by 2022 at full operating capacity.
-With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium ion storage are necessary.
+All existing nuclear power plants must be restarted by 2022 at full operating capacity.
+With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary.
 The presence of a large share of renewables results in significant overgeneration of electricity during some years.
@@
 
-With the availability new nuclear reactors in Scenario 2 (fig.
+With the availability of new nuclear reactors in Scenario 2 (Fig.
 \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100.
-The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions.
+The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions.
 Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100.
-The amount of renewables required for decarbonization is reduced dramatically.
-This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the amount of lithium ion storage deployed.
-The amount of electricity diverted to storage technologies is 12,220 TWh, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
+The share of renewables deployed during this transition is reduced dramatically.
+This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the capacity of lithium-ion storage deployed.
+12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
 The total transition cost of this scenario is the lowest, at \textbf{2,664,207 MUSD.}
 
-Using emerging technologies without new nuclear power (fig.
+Using emerging technologies without new nuclear power (Fig.
 \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonization occurs after 2050.
 The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario.
-The deep emission cuts achieved through renewables, hydrogen and \gls{CCS} leave room for emissions from \gls{lng}, hence natural gas plants continue to operate until 2100.
-Expansion of solar and onshore wind, along with a modest deployment of lithium ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals.
+The deep emission cuts achieved through renewables, hydrogen, and \gls{CCS} allow the model to keep using \gls{lng} until 2100.
+Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals.
 After that, the model relies primarily on renewables and hydrogen to curb emissions while supplying power.
 Significant investment in hydrogen from 2034 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power.
-\gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility scale hydrogen.
+\gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen.
 Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame.
 This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan (cite Kato 2016).
-As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace current solar power, benefiting from the existing solar manufacture and supply chains.
-The amount of electricity diverted to storage technologies is 43,879 TWh, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%),and onshore wind (20\%).
-The amount of hydrogen generated is 35,478 TWh, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%).
+As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains.
+A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%).
+Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%).
 The cost of this transition is \textbf{3,187,940 MUSD}.
 
-Using both emerging technologies with new nuclear reactors (fig.
+Using both emerging technologies with new nuclear reactors (Fig.
 \ref{scen4}) results in rapid decarbonization.
-Both 2030 and 2050 emission targets met, and an additional emissions reduction of 32 Mt occurs by 2100.
-The deployment of around 50 MW nuclear obviates the need to invest in offshore wind, lithium ion storage, and \gls{CCS}.
-Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared to scenario 3, from 2037 instead.
+Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100.
+The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}.
+Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared with Scenario 3, from 2037 instead.
 The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%).
-The amount of hydrogen generated is 24,264 TWh, produced entirely from PEM electrolysis.
+From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3.
 The cost of this transition is \textbf{2,804,753 MUSD}.

### 2020-09-11 doc/2020-03-paper/introduction.tex
added some references
Former-commit-id: 8b3495d5fc0df75ffb6d8a991d3550e22fa72bb8
Former-commit-id: a395f202b2ba19a53a822e8437ae48f3000e1cc0

@@
 \section{Introduction} \label{Introduction}
-In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements (UNFCCC, 2015).
-The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors (WRI, 2020).
+In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors \cite{ge_4_2020}.
 For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions.
-However for developing nations, these options are not always economically feasible, leading to increased emissions through greater coal use by rapidly developing nations (IEA, 2019).
-For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment (IEA, 2019).
+However for developing nations, these options are not always economically feasible, leading to increased emissions through greater coal use by rapidly developing nations \cite{international_energy_agency_latest_2019}.
+For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
 
-Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 (METI, 2018).
+Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}.
 The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018).
@@
 Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met.
-This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies (Matsuo et al., 2018).
-For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies (Ashina et al., 2012).
+This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies \cite{matsuo_quantitative_2018}.
+For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies \cite{ashina_roadmap_2012}.
 It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan.
-The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad (Ashina et al., 2012; Matsuo et al., 2018; METI, 2017).
+The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
 

### 2020-09-11 doc/2020-03-paper/litreview.tex
added some references
Former-commit-id: 8b3495d5fc0df75ffb6d8a991d3550e22fa72bb8
Former-commit-id: a395f202b2ba19a53a822e8437ae48f3000e1cc0

@@
 \section{Background and literature review} \label{litreview}
-The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism (UNFCCC, 2019).
-Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" (UNFCCC, 2015).
+The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
 Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
-Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 (Ozawa 2018).
+Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
 Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al.
 explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan.
-Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues (Li et.
-al.
-2019).
-Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach (2018).
+Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}.
+Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
 Considering Japan's economic conditions and demographic trends such as moderate GDP growth and rapid aging, Kuriyama et al.
-suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario (2019).
+suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}.
 However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.
 Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
-Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 (Moinuddin \& Kuriyama, 2019).
+Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}.
 A seminal work by Sugiyama et al.
 harmonizes a number of modeling approaches for Japan's long term (i.e.
-to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models (2019).
+to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}.
 Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction.
 Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
-Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role (Sato, 2005; Akimoto et al., 2010; Matsuo et al., 2013; Fujii and Komiyama, 2015; Oshiro \& Masui, 2015; Sugiyama et al., 2019).
-Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion (Iida \& Sakata, 2019).
+Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{sato_consideration_2005, akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
+Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}.
 Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \gls{FCV}s and power generation, via both mixed and direct combustion.
-Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 (Ishimoto et al., 2017).
-From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future (Nagashima, 2018).
-Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies (METI, 2017).
-The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges (Nagashima, 2018).
-A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 (Oshiro et al., 2019).
+Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}.
+From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future \cite{nagashima_japans_2018}.
+Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
+The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.
+A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 \cite{oshiro_mid-century_2019}.
 
 The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review, and expand the consideration of technologies beyond  conventional options to also include emerging near-term alternatives, and potentially disruptive technologies post-2050.
-This work leverages the dynamic simulation capabilities of \gls{TIMES} (Loulou et al., 2005) by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
+This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
 Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities.

### 2020-09-11 doc/2020-03-paper/methods.tex
added some references
Former-commit-id: 8b3495d5fc0df75ffb6d8a991d3550e22fa72bb8
Former-commit-id: a395f202b2ba19a53a822e8437ae48f3000e1cc0

@@
 The objective function in our single-region model is the overall cost of the transition.
-The major constrains in our simulations are the demand for electricity (see Table \ref{demand}), emission constraints based on Japan's \gls{INDC} (see Table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see Table \ref{caplim}).
+The major constrains in our simulations are the demand for electricity (see Table \ref{demand}), emission constraints on the electricity-generation sector based on Japan's \gls{INDC} (see Table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see Table \ref{caplim}).
 Miscellaneous assumptions are summarized in table \ref{misc-assump}.
-Hence each simulation is focused on minimizing the transition cost, while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
+Therefore, our model minimizes the transition cost, while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
 
-While electricity demand in the near future is expected to grow, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
+While electricity demand in the near future is expected to grow \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
 However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
 Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification driving increasing demand, but the demand eventually plateaus due to the aforementioned expected demographic changes.
-The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016.
+The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
 Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
 The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for every technology, as applicable.
-The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods (cite Loulou).
-The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan.
+The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}.
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018} cite IRENA.
 
@@
 \hline
-2017-2030 & 1.7 \% \\
+2017-2030 & 1.7 \% \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019} \\
 2031-2050 & 1.0 \% \\

### 2020-09-16 doc/2020-03-paper/Appendix.tex
minor edits
Former-commit-id: d6edc638a459eb9c40c1e86d88715c92474ee6ee
Former-commit-id: 53262b3a3a1fdbe1e41f4720e63dfa8eda7f585e
added pws capacity factor
Former-commit-id: ef1132612ec949e6d38c329589843b014e6f8087
Former-commit-id: 23dd5676499da8d401ff9bfab0308be51139a606
methodology minor corrections
Former-commit-id: bb5704f9059dd6be7778d735aea63348d7012923
Former-commit-id: 216117c713e2cf9f6af0e1b9954b547e6853bd45
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

@@
 \section{Data and assumptions for scenarios} \label{Appendix}
+
 \begin{table}[!ht]
@@
 		\hline
-\textbf{Technology} & \textbf{\gls{lcoe}} & \textbf{Emission} & \textbf{Year of total}\\
-  & (USD/kWh) & \textbf{Coefficients} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
+\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
+  & (USD/kWh) & \textbf{Coefficients} \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
 \hline
@@
 \begin{table}[!ht]
-	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust.}
+	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
 	\vspace{0.1in}
@@
 \textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
-\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
+ & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
  & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
@@
 \endlastfoot
-\gls{USC} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
-\gls{lng} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
-Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
-Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
+\gls{USC} \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
-Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
  & 615(2050) & & & & & &  \\
 Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
- & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
- & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
- & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
 LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
- & 1422(2050) &  & &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\
 USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
- & 4091(2050) &  &  &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
-  & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
+ \cite{irena_solar_2012,peng_review_2013} & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
 \gls{AEC}  & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
- & 850(2030) &  &  &  &  & &  \\
+\cite{iea_technology_2015, bhandari_life_2014, cetinkaya_life_2012, burkhardt_hydrogen_2016} & 850(2030) &  &  &  &  & &  \\
 \gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
- & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
+\cite{iea_technology_2015, bareis_life_2019, carmo_comprehensive_2013,ayers_research_2010,siracusano_influence_2017,schmidt_future_2017,mayyas_manufacturing_2019} & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
  & 400(2050) &  &  &  & &  &  \\
 \gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
- & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
+\cite{iea_technology_2015,schmidt_future_2017,hafele_life_2016} & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
  & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
 Gas Reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
+\cite{iea_technology_2015,mehmeti_life_2018,keipi_economic_2018} & & & & & &  & \\
 Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
-\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
+\cite{iea_technology_2015,keipi_economic_2018,cormos_ana-maria_economic_2018} &  &  &  &  &  &  & \\
+\gls{PEMFC} \cite{iea_technology_2015,simons_life-cycle_2015,kannan_life_2007} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
  & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
  & 3000(2035) &  &  &  &  &  &  \\
-\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
+\gls{SOFC} \cite{iea_technology_2015,simons_life-cycle_2015,rillo_life_2017,tu_advances_2004} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
  & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
  & 3000(2040) &  &  &  &  & &  \\
-\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
+\gls{PWS} \cite{pinaud_technical_2013} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
 \label{eco}
@@
 \hline
-Photovoltaic & 332 \\
-Onshore wind & 180 \\
-Offshore wind (fixed) & 130 \\
-Offshore wind (floating) & 260 \\
+Photovoltaic \cite{isep_53_2018} & 332 \\
+Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
+Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
+Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
 Nuclear & 50 (Scenarios 3 \& 4) \\
  & 100 (Scenario 2) \\
-\gls{PWS} & 100 (Scenario 5) \\
+\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
 \hline 
@@
 Nuclear (2027 onwards) & +5 reactors \\
-Solar and Emerging Solar & 40\%  \\
-Onshore Wind & 25\% \\
-Offshore Wind(Fixed) & 20\% \\
-Offshore Wind(Floating) & 20\% \\
+Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
+Onshore Wind \cite{irena_renewable_2020} & 25\% \\
+Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
+Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
 Li-ion Storage & 30\% \\
@@
 \end{table}
+
+\begin{table}[!ht]
+	\caption{Miscellaneous model parameters and assumptions.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+		\hline
+\textbf{Parameter} & \textbf{Value} \\
+\hline
+Currency & MUSD 2015 \\
+Activity unit & GWh\\
+Discount rate & 5\% \\
+Transmission efficiency & 90 \% \\
+Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
+Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
+Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
+Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
+\hline 
+	\end{tabularx}
+\label{misc-assump}
+\end{table}

### 2020-09-16 doc/2020-03-paper/litreview.tex
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

@@
 Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
-Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{sato_consideration_2005, akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
+Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
 Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}.

### 2020-09-16 doc/2020-03-paper/methods.tex
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

@@
 Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Prices and projections for fossil fuels and nuclear fuel were incorporated (add references).
+Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_group_commodity_2016, international_energy_agency_world_2019}.
 Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
@@
 The maximum annual capacity growth rates for existing technologies are held constant.
-The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations.
+The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}.
 The reactor size assumed in this study is 1165 MWe.
-Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors' range of capacity factors.
+Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow to a certain extent, which is simulated in a limited way in our model based on French reactors' range of capacity factors.
 The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
@@
 All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following.
-Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors (cite IEA).
+Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
 For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively (cite).
-
-%approach, goal, what are we hoping to learn
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
 

### 2020-09-16 doc/2020-03-paper/Appendix.tex
added figures
Former-commit-id: 397fc5a3eb6bd05763c89c592904ed924036023e
Former-commit-id: ed765d313eda47c8f62f47644dc28d64032fd6a0

@@
 \textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
-  & (USD/kWh) & \textbf{Coefficients} \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
+  & (USD/kWh) & \textbf{Coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
 \hline
@@
 \endlastfoot
-\gls{USC} \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
-\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
-Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+\gls{USC} \cite{eia_cost_2020,ipcc_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng}\cite{eia_cost_2020,ipcc_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear \cite{eia_cost_2020,ipcc_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
 Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
-Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+Solar \cite{eia_cost_2020,ipcc_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
  & 615(2050) & & & & & &  \\
 Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
-\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
 LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
- \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\
+ \cite{eia_cost_2020,ipcc_2014} & 1422(2050) &  & &  &  &  & \\
 USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
- \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\
+ \cite{eia_cost_2020,ipcc_2014} & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\

### 2020-09-16 doc/2020-03-paper/methods.tex
added figures
Former-commit-id: 397fc5a3eb6bd05763c89c592904ed924036023e
Former-commit-id: ed765d313eda47c8f62f47644dc28d64032fd6a0

@@
 
-While electricity demand in the near future is expected to grow \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
+While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
 However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
@@
 \hline
-2017-2030 & 1.7 \% \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019} \\
+2017-2030 & 1.7 \% \cite{noauthor_electricity_2019} \\
 2031-2050 & 1.0 \% \\
@@
 Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_group_commodity_2016, international_energy_agency_world_2019}.
+Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
 Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.

### 2020-09-16 doc/2020-03-paper/results.tex
added figures
Former-commit-id: 397fc5a3eb6bd05763c89c592904ed924036023e
Former-commit-id: ed765d313eda47c8f62f47644dc28d64032fd6a0

@@
 \subsection{Sensitivity analysis}
+
+\begin{figure}[h] 
+\centering
+\hspace*{-3cm}
+\includegraphics[scale=0.14]{figures/techs}
+\caption{Sensitivity analysis of selected model parameters.
+Red dots indicate points that are zero values, while blue dots indicate non-zero values.
+Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
+PEM FC and CCS Coal).
+}
+\label{sa-techs}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\hspace*{-3cm}
+\includegraphics[scale=0.14]{figures/syscost}
+\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.
+Red dots indicate points that are zero values, while blue dots indicate non-zero values.
+Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
+PEM FC and CCS Coal).}
+\label{sa-syscost}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\hspace*{-3cm}
+\includegraphics[scale=0.14]{figures/co2emi}
+\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters.
+Red dots indicate points that are zero values, while blue dots indicate non-zero values.
+Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
+PEM FC and CCS Coal).
+}
+\label{sa-co2}
+\end{figure}

### 2020-09-17 doc/2020-03-paper/methods.tex
added SA methodology
Former-commit-id: 7b3865d600a114cbe94bf0c23cca5ace962431cf
Former-commit-id: 889fc4b6ca18a197aeaf54da0094dcec8ccc1c96

@@
 4               &   Yes     &      Yes     &     No  \\ 
-5               &   Yes     &      Yes     &     Yes  \\ 
+5               &   Yes     &      No     &     Yes  \\ 
 \hline
@@
 %approach, goal, what are we hoping to learn
+%variables, sampling approach, median, range, which variables, which base case scenario, why
+While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, we have to acknowledge that many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain.
+This is especially true for nascent technologies that have not been commercialized, like \gls{CCS}, hydrogen generation and conversion technologies.
+Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost and cumulative emissions over the entire simulation time-frame.
+
+While there is significant uncertainty in the investment cost of nuclear power plants, it varies for individual plants and not for the technology as a whole.
+Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions.
+Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster.
+Therefore,in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis.
+10 model parameters were sampled 30 times from appropriate distributions (see Table \ref{sa-vars}).
+The parameter value at the first year of deployment (see Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios.
+For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.
+These parameters were randomly co-varied in 30 simulations.
+The share of each electricity generation technology (as the ratio cumulative technology output to the cumulative electricity demand) or output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
+A similar approach was also used to correlate these parameters with the system's transition cost, and net emissions over the entire simulation.
+
+\begin{table}[!ht]
+	\caption{Scenario definition.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.25\textwidth} p{0.25\textwidth} p{0.25\textwidth}p{0.25\textwidth}}
+\hline 
+\textbf{Technology} \textbf{Parameter} & \textbf{Sampled Distribution} & \textbf{Distribution Mean}& \textbf{Distribution Range}\\
+\hline
+\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% around the mean. \\                  
+\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% around the mean. \\
+\gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  
+\gls{SOEC} Emission Coefficient & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\
+\gls{PWS} Efficiency            & Triangular  & 0.525 & 0.5-0.58. \\                               
+\hline
+	\end{tabularx}
+\label{sa-vars}
+\end{table}

### 2020-09-17 doc/2020-03-paper/results.tex
added 5th scenario text
Former-commit-id: b5d9e1780d0f4060074e878d725c382be900daa7
Former-commit-id: 1c02e10ccb10f21f0f0858db27963f6d5f6bf642

@@
 
-Using both emerging technologies with new nuclear reactors (Fig.
+Deploying both emerging technologies with new nuclear reactors (Fig.
 \ref{scen4}) results in rapid decarbonization.
@@
 
+The fifth scenario's results (Fig.
+\ref{scen5}) closely resemble those of the third scenario (Fig.
+\ref{scen3}).
+However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s.
+Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost.
+Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050.
+The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%).
+From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%).
+\gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%.
+The cost of this transition is \textbf{3,180,613 MUSD}.
+
 \begin{figure}[htb] 
@@
 \includegraphics[scale=0.42]{figures/conv_nonuc}
-\caption{Conventional technologies, no new nuclear.}
+\caption{Scenario 1 - Conventional technologies, no new nuclear.}
 \label{scen1}
@@
 \includegraphics[scale=0.42]{figures/conv_nuc}
-\caption{Conventional technologies, with new nuclear.}
+\caption{Scenario 2 - Conventional technologies, with new nuclear.}
 \label{scen2}
@@
 \includegraphics[scale=0.41]{figures/newtechs_nonuc}
-\caption{Emerging technologies, no new nuclear.}
+\caption{Scenario 3 - Emerging technologies, no new nuclear.}
 \label{scen3}
@@
 \includegraphics[scale=0.41]{figures/newtechs_nuc}
-\caption{Emerging technologies, no new nuclear.}
+\caption{Scenario 4 - Emerging technologies, with new nuclear.}
 \label{scen4}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
+\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
+\label{scen5}
 \end{figure}

### 2020-09-18 doc/2020-03-paper/discussion.tex
added figures
Former-commit-id: 397fc5a3eb6bd05763c89c592904ed924036023e
Former-commit-id: ed765d313eda47c8f62f47644dc28d64032fd6a0
adds clean results for syscost, net emissions
Former-commit-id: 5a0d7dd093d146c65fbf51a7f4887799ed403066
Former-commit-id: 8d484390baa9c26c0788b9cfa933ef94f0c1e0fc

--- 2020-06-22 doc/2020-03-paper/discussion.tex
@@
 % extensive citations and discussion of published literature.
+
+%Notes for Ansh:
+%Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
+%Urgency of transition : scenarios + sensitivity analysis.
+%Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements. Say Li is okay.
+%AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
+%SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).
+%pemecs still part of cost optimal solutions
+%identify key techs, same fcs needed always
+%nuclear is key
+%pws will have to be cheaper/cost competitive with electrolyzers to have a role
+%main H2, role of CCS LNG - secondary alternative to H2 - as shown by correlation with SOFC inv cost. Not good on its own. Supplement to H2.
+%H2 non trivial despite large range of perturbation
+% FC flexibility, more storage/H2 less flex for CCS, nuclear
+
+%urgency
+As the results of all base case scenarios (Figs.
+\ref{scen1}-\ref{scen5}) indicate, rapid retirement of fossil fuels and deployment of carbon neutral technologies is urgently required to achieve emission reduction targets.
+All coal and oil plants must be shut down between 2025-2030, and natural gas use must be reduced dramatically.
+Japan must restart all of its existing reactors at full operating capacity by 2022.
+Since hydrogen plays a key role in zero to moderate nuclear deployment scenarios (Figs.
+\ref{scen3}and \ref{scen4}), it is prudent to invest in hydrogen power.
+As our model uses learning curves for technology prices and our objective function is the transition cost, our model deploys hydrogen technologies as late as possible in order to minimize  costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals.
+Therefore, our results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale utility-scale hydrogen by 2030 at the latest, in the absence of new nuclear, or by 2035, with new nuclear.
+
+%nuclear
+The scenario with the most nuclear deployment, Scenario 2, also has the lowest transition cost.
+When used with hydrogen, 50 MW of nuclear new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios.
+It also reduces the cost of the transition from 3,187,940 MUSD in Scenario 3 to 2,804,753 MUSD in Scenario 4.
+This is a difference of 383,187 MUSD.
+The estimated savings due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen through tankers or pipelines.
+Furthermore, the large emission reductions achieved with the help of nuclear allow natural gas to continue operating until 2100 while also meeting emission goals.
+As natural gas is excellent for peaking and load-following, when coupled with flexible fuel cell technology, it should result in an extremely stable energy system.
+Thus, in all scenarios, nuclear plays a key role in reducing emissions.
+Japan should strongly consider reinvigorating its nuclear energy sector by restarting existing plants, constructing new plants, and investing in advanced reactor research.
+To minimize the environmental impact from their life cycle emissions, it is vital that all existing and any new reactors be operated for a lifetime of 60 years or more at high capacity factors.
+Premature decommissioning due to operational problems or lack of public acceptance need to be avoided.
+Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, and increasing public awareness of nuclear's vital role in emission mitigation are key to achieving 2030 and 2050 emission targets.
+
+%renewables and flexibility
+In all scenarios, solar and wind supply a large part of the electricity demand.
+Unless large numbers of nuclear power plants are constructed, Japan must also invest in offshore wind farms by 2030 (Figs.
+\ref{scen1,scen3,scen4,scen5}).
+If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also necessary (\ref{scen1}).
+With such a large share of renewables, grid flexibility is extremely important.
+This requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive.
+As natural gas is the only extant option for load-following, it is important to incorporate nuclear as in Scenarios 2 and 4 (Figs.
+\ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following.
+Additionally, nuclear power plants and CCS power plants must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store their excess electricity for peak demand.
+Any fuel cell technology utilized must also be extremely flexible and responsive.
+Since our model prefers \gls{SOFC}s to \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.
+
+%batteries
+Lithium ion is the preferred storage medium in the absence of hydrogen.
+However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts.
+While lithium and cobalt may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium ion storage if it is relied upon as the primary storage medium.
+It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals.
+The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing.
+If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3,scen4,scen5}).
+
+%hydrogen - key players, key parameters, path forward?
+After nuclear, hydrogen power emerges as the second most important technology for achieving 2050 emission goals.
+As seen in the sensitivity analysis results, it maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector.
+While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s respectively to recreate similar energy mixes.
+Key technologies that aid in decarbonization in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation.
+Steam reforming, with or without CCS, does not get utilized in our simulations due to its high emission coefficient.
+At the lower end of the technology readiness scale, \gls{SOEC}s emerge as tremendously disruptive due to their high efficiency.
+However, their lifetime must be increased significantly, their life cycle emissions must be kept low, and they must become cost-competitive with \gls{PEMEC}s to realize their potential.
+\gls{PWS} plays a marginal role as it is not cost-competitive with electrolysis.
+From the simulation output data, the investment cost of \gls{SOFC}s emerges as an obviously important parameter.
+Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible.
+However, low response times and high availability factors are other key factors that are implicit in our assumptions.
+If \gls{SOFC}s are not as flexible as we have assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and are closer to commercialization.
+In Scenarios 3 and 4, solar, wind, and nuclear are used to generate hydrogen.
+Therefore it would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants.
+Waste heat from nuclear could also be used to produce hydrogen, and would reduce reliance on renewables for electrolysis.
+As mentioned previously, more flexible and responsive fuel cells and electrolyzers are likely to be the dominant technology in such a system.
+
+%ccs
+CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen.
+Its share is found to be largely insensitive to its own investment cost in our sensitivity analysis.
+This is mainly due to its large emission coefficient.
+Marginal gains are expected in its penetration if the efficiency of CCS is increased to reduce its direct emissions.
+Reducing indirect emissions is likely to have a greater impact.
+This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.

### 2020-09-18 doc/2020-03-paper/methods.tex
adds clean results for syscost, net emissions
Former-commit-id: 5a0d7dd093d146c65fbf51a7f4887799ed403066
Former-commit-id: 8d484390baa9c26c0788b9cfa933ef94f0c1e0fc

@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.25\textwidth} p{0.25\textwidth} p{0.25\textwidth}p{0.25\textwidth}}
+	\begin{tabularx}{1.1\textwidth}{p{0.3\textwidth} p{0.25\textwidth} p{0.25\textwidth}p{0.3\textwidth}}
 \hline 
-\textbf{Technology} \textbf{Parameter} & \textbf{Sampled Distribution} & \textbf{Distribution Mean}& \textbf{Distribution Range}\\
+\textbf{Technology}  & \textbf{Sampled} & \textbf{Distribution}& \textbf{Distribution}\\
+\textbf{Parameter} & \textbf{Distribution} & \textbf{Mean}& \textbf{Range}\\
 \hline
-\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% around the mean. \\                  
-\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% around the mean. \\
+\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% of mean. \\                  
+\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% of mean.\\                  
+\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% of mean.\\                  
+\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
+\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
+\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% of mean.\\                  
+\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% of mean.\\
 \gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  

### 2020-09-18 doc/2020-03-paper/results.tex
adds clean results for syscost, net emissions
Former-commit-id: 5a0d7dd093d146c65fbf51a7f4887799ed403066
Former-commit-id: 8d484390baa9c26c0788b9cfa933ef94f0c1e0fc

@@
 \subsection{Transition Scenarios}
+
+\begin{figure}[htb] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nonuc}
+\caption{Scenario 1 - Conventional technologies, no new nuclear.}
+\label{scen1}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nuc}
+\caption{Scenario 2 - Conventional technologies, with new nuclear.}
+\label{scen2}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nonuc}
+\caption{Scenario 3 - Emerging technologies, no new nuclear.}
+\label{scen3}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nuc}
+\caption{Scenario 4 - Emerging technologies, with new nuclear.}
+\label{scen4}
+\end{figure}
+
+\begin{figure}[h] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
+\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
+\label{scen5}
+\end{figure}
 
@@
 \ref{scen3}).
-However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s.
+However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055.
 Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost.
@@
 The cost of this transition is \textbf{3,180,613 MUSD}.
-
-\begin{figure}[htb] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nonuc}
-\caption{Scenario 1 - Conventional technologies, no new nuclear.}
-\label{scen1}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nuc}
-\caption{Scenario 2 - Conventional technologies, with new nuclear.}
-\label{scen2}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nonuc}
-\caption{Scenario 3 - Emerging technologies, no new nuclear.}
-\label{scen3}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nuc}
-\caption{Scenario 4 - Emerging technologies, with new nuclear.}
-\label{scen4}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
-\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
-\label{scen5}
-\end{figure}
 
@@
 Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).
-}
+PEM FC and CCS Coal).}
 \label{sa-co2}
 \end{figure}
+
+As the first set of sensitivity analysis results (Fig.
+\ref{sa-techs}) indicate, \gls{PEMFC}s are never utilized due to their efficiency being lower than that of \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient.
+\gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period, as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh.
+The share of \gls{PWS} was found to be strongly correlated to its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be deployed.
+It's deployment is also weakly correlated with the splitting efficiency, wherein values greater than 21\% seem most favourable for its deployment.
+The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment.
+\gls{SOEC}'s share is most strongly correlated with their investment cost, however they play a non-trivial role over the range of perturbation applied to said parameter.
+Their deployment is largely insensitive to their emission coefficient as their cost and high efficiency trumps any increase in emissions due to their deployment, which is likely to be small due to their small emission coefficient.
+\gls{PEMEC} and \gls{SOFC} deployment is also most noticeably affected by their respective investment costs.
+The share of \gls{CCS}-Gas is relatively small, about 2-3\%, due to its emission coefficient being much larger than that of all hydrogen technologies.
+Its deployment is most strongly correlated with the investment cost of \gls{SOFC}s as a reduction in the deployment of fuel cells forces the model to marginally increase CCS Gas deployment to achieve its emission goals.
+
+The second set of results (Fig.
+\ref{sa-syscost} and \ref{sa-co2}) indicate that system's total transition cost and total emissions are tightly correlated with the investment cost of \gls{SOFC}s.
+This follows from the large share of \gls{SOFC}s, and the fact that they are the most important technology in the model in terms of reducing emissions and converting excess power from renewables into electricity, yet they are the most expensive technology available to the model.

### 2020-09-18 doc/2020-03-paper/Appendix.tex
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

@@
-\section{Data and assumptions for scenarios} \label{Appendix}
+\section{Model data, assumptions, and secondary results} \label{Appendix}
 
@@
 \end{table}
-
 \begin{landscape}
@@
 \endlastfoot
-\gls{USC} \cite{eia_cost_2020,ipcc_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
-\gls{lng}\cite{eia_cost_2020,ipcc_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
-Nuclear \cite{eia_cost_2020,ipcc_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
 Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
-Solar \cite{eia_cost_2020,ipcc_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+Solar \cite{eia_cost_2020,ipcc_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
  & 615(2050) & & & & & &  \\
 Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
 LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
- \cite{eia_cost_2020,ipcc_2014} & 1422(2050) &  & &  &  &  & \\
+ \cite{eia_cost_2020,ipcc_climate_2014} & 1422(2050) &  & &  &  &  & \\
 USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
- \cite{eia_cost_2020,ipcc_2014} & 4091(2050) &  &  &  &  &  & \\
+ \cite{eia_cost_2020,ipcc_climate_2014} & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
@@
 \end{table}
+
+\begin{figure}[h] 
+\centering
+\hspace*{-3cm}
+\includegraphics[scale=0.07]{figures/useless}
+\caption{Sensitivity analysis results for \gls{PEMFC} and \gls{CCS} coal.}
+\label{sa-useless}
+\end{figure}

### 2020-09-18 doc/2020-03-paper/discussion.tex
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

@@
 Unless large numbers of nuclear power plants are constructed, Japan must also invest in offshore wind farms by 2030 (Figs.
-\ref{scen1,scen3,scen4,scen5}).
+\ref{scen1},\ref{scen3}-\ref{scen5}).
 If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also necessary (\ref{scen1}).
@@
 The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing.
-If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3,scen4,scen5}).
+If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3}-\ref{scen5}).
 

### 2020-09-18 doc/2020-03-paper/results.tex
adjusted figure sizes
Former-commit-id: 723ebece9a628c30d3a45cc8f4c7a86d323348be
Former-commit-id: 47cda099c10c589ad1f8afdd651f55678e5aa3c7
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

--- 2020-09-17 doc/2020-03-paper/results.tex
@@
 \subsection{Transition Scenarios}
+
+\begin{figure}[H] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nonuc}
+\caption{Scenario 1 - Conventional technologies, no new nuclear.}
+\label{scen1}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.42]{figures/conv_nuc}
+\caption{Scenario 2 - Conventional technologies, with new nuclear.}
+\label{scen2}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nonuc}
+\caption{Scenario 3 - Emerging technologies, no new nuclear.}
+\label{scen3}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/newtechs_nuc}
+\caption{Scenario 4 - Emerging technologies, with new nuclear.}
+\label{scen4}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+\vspace*{-3cm}
+\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
+\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
+\label{scen5}
+\end{figure}
 
@@
 
-\begin{figure}[htb] 
+\subsection{Sensitivity analysis}
+
+\begin{figure}[H] 
 \centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nonuc}
-\caption{Scenario 1 - Conventional technologies, no new nuclear.}
-\label{scen1}
+\hspace*{-1cm}
+\includegraphics[scale=0.09]{figures/pws}
+\caption{Sensitivity analysis of Photochemical Water Splitting. Red dots indicate points that are zero values, while blue dots indicate non-zero values.}
+\label{pws}
 \end{figure}
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nuc}
-\caption{Scenario 2 - Conventional technologies, with new nuclear.}
-\label{scen2}
+%\hspace*{-3cm}
+\includegraphics[scale=0.12]{figures/satechsh2}
+\caption{Sensitivity analysis of hydrogen generation technologies \gls{SOEC} and \gls{PEMEC}}.
+\label{satechs-h2}
 \end{figure}
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nonuc}
-\caption{Scenario 3 - Emerging technologies, no new nuclear.}
-\label{scen3}
+%\hspace*{-3cm}
+\includegraphics[scale=0.12]{figures/satechselc}
+\caption{Sensitivity analysis of electricity generation technologies \gls{SOFC} and \gls{CCS} gas.}
+\label{satechs-elc}
 \end{figure}
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nuc}
-\caption{Scenario 4 - Emerging technologies, with new nuclear.}
-\label{scen4}
+%\hspace*{-3cm}
+\includegraphics[scale=0.15]{figures/syscost}
+\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.}
+\label{syscost}
 \end{figure}
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
-\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
-\label{scen5}
+%\hspace*{-3cm}
+\includegraphics[scale=0.15]{figures/co2emi}
+\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters.}
+\label{co2emi}
 \end{figure}
 
-\subsection{Sensitivity analysis}
+Preliminary assessment of our sensitivity analysis data (Fig.
+\ref{sa-useless}) indicates that \gls{PEMFC}s are never utilized due to their efficiency being lower than that of \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient.
+\gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Fig.
+\ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh.
+The share of \gls{PWS} was found to be strongly correlated to its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be deployed.
+It's deployment is also weakly correlated with the splitting efficiency, wherein values greater than 21\% seem most favourable for its deployment.
+The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment.
+Since \gls{PEMFC}s, \gls{CCS} coal, and \gls{PWS} are not deployed in quantities significant enough to affect the model's performance, they are omitted as potential dependent variables for the rest of the sensitivity analysis.
 
-\begin{figure}[h] 
-\centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/techs}
-\caption{Sensitivity analysis of selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).
-}
-\label{sa-techs}
-\end{figure}
+\gls{SOEC}'s share is most strongly correlated with their investment cost, however they play a non-trivial role over the range of perturbation applied to said parameter (Fig.
+\ref{satechs-h2}).
+Their deployment is largely insensitive to their emission coefficient as their cost and high efficiency trumps any increase in emissions due to their deployment, which will be negligible due to their small emission coefficient.
+\gls{PEMEC} (Fig.
+\ref{satechs-elc}) and \gls{SOFC} (Fig.
+\ref{satechs-elc}) deployment is also most noticeably affected by their respective investment costs.
+The share of \gls{CCS}-Gas (Fig.
+\ref{satechs-elc}) is relatively small, about 2-3\%, due to its emission coefficient being much larger than that of all hydrogen technologies.
+Its deployment is most strongly correlated with the investment cost of \gls{SOFC}s as a reduction in the deployment of fuel cells forces the model to marginally increase CCS Gas deployment to achieve its emission goals.
 
-\begin{figure}[h] 
-\centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/syscost}
-\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).}
-\label{sa-syscost}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/co2emi}
-\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).
-}
-\label{sa-co2}
-\end{figure}
+The final set of results (Fig.
+\ref{syscost} and \ref{co2emi}) indicate that system's total transition cost and total emissions are tightly correlated with the investment cost of \gls{SOFC}s.
+This follows from the large share of \gls{SOFC}s, and the fact that they are the most important technology in the model in terms of reducing emissions and converting excess power from renewables into electricity, yet they are the most expensive technology available to the model.

### 2020-10-11 doc/2020-03-paper/discussion.tex
minor corrections
Former-commit-id: 995bda384d92316cc2e51b7cf8653667b3f6ab5a
Former-commit-id: 8768ef4142084c1e247f6295df7b84a7b955a4d9

--- 2020-06-23 doc/2020-03-paper/discussion.tex
@@
 % extensive citations and discussion of published literature.
-Notes for Ansh:
-Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
-Urgency of transition : scenarios + sensitivity analysis.
-Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements.
-AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
-SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).
+
+%Notes for Ansh:
+%Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
+%Urgency of transition : scenarios + sensitivity analysis.
+%Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements. Say Li is okay.
+%AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
+%SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).
+%pemecs still part of cost optimal solutions
+%identify key techs, same fcs needed always
+%nuclear is key
+%pws will have to be cheaper/cost competitive with electrolyzers to have a role
+%main H2, role of CCS LNG - secondary alternative to H2 - as shown by correlation with SOFC inv cost. Not good on its own. Supplement to H2.
+%H2 non trivial despite large range of perturbation
+% FC flexibility, more storage/H2 less flex for CCS, nuclear
+
+%urgency
+As the results of all base case scenarios indicate, rapid retirement of fossil fuels and deployment of carbon neutral technologies is urgently required to achieve emission reduction targets in Japan.
+All coal and oil plants need to be shut down between 2025-2030, and natural gas use must be reduced dramatically.
+It is also imperative that the existing nuclear reactors be operated at full capacity by 2022.
+Since hydrogen plays a key role in zero to moderate nuclear deployment scenarios (Figs.
+\ref{scen3}and \ref{scen4}), it appears prudent to invest in hydrogen power.
+As the model uses learning curves for technology prices and our objective function is transition cost, hydrogen technologies are deployed as late as possible in order to minimize costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals.
+Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen deployment by 2030 at the latest, in the absence of new nuclear, or by 2035, with new nuclear.
+
+%nuclear
+The scenario with the largest nuclear deployment, Scenario 2, also has the lowest transition cost.
+When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios.
+It also reduces the cost of the transition from 3,187,940 MUSD in Scenario 3 to 2,804,753 MUSD in Scenario 4, a difference of 12\% of the system cost.
+The estimated savings due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines.
+Further, the large emission reductions achieved with the help of nuclear allow natural gas to continue operating until 2100 while also meeting emission goals.
+As natural gas is well suited to peaking and load-following, when coupled with flexible fuel cell technologies, it could engender in an extremely stable energy system.
+
+For the transitioning energy system in Japan, under all scenarios investigated, nuclear plays a key role in reducing emissions.
+A potential strategy for Japan could include the reinvigoration of its nuclear energy sector by restarting existing plants, and if politically feasible, constructing new plants, and investing in advanced reactor research.
+To minimize the environmental impact from life cycle emissions, it is necessary that all existing and any new reactors be operated for a lifetime of 60 years or more at a high capacity factor.
+Premature decommissioning due to operational problems or lack of public acceptance need to be avoided.
+Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, increasing public awareness of nuclear's vital role in  mitigating carbon emission is key to achieving 2030 and 2050 emission targets.
+
+%renewables and flexibility
+In all scenarios, solar and wind supply a large portion of the electricity demand.
+Unless large numbers of nuclear power plants are constructed, Japan will need to invest heavily in offshore wind farms by 2030 (Figs.
+\ref{scen1},\ref{scen3}-\ref{scen5}).
+If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (\ref{scen1}).
+Under a scenario with a relatively large share of renewables, grid flexibility becomes extremely important.
+such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive.
+As natural gas is the only extant option for load-following, Japan will face a critical choice - whether to incorporate nuclear as in Scenarios 2 and 4 (Figs.
+\ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following.
+Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand.
+Any fuel cell technology utilized must also be extremely flexible and responsive.
+Since the model prioritizes \gls{SOFC}s over \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.
+
+%batteries
+Lithium-ion is the preferred storage medium in the absence of hydrogen.
+However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts.
+While lithium may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium-ion storage if it is relied upon as the primary storage medium.
+It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals.
+The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing.
+If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3}-\ref{scen5}).
+
+%hydrogen - key players, key parameters, path forward?
+After nuclear, hydrogen power emerges as the second most efficacious technology for achieving 2050 emission goals.
+As seen in the sensitivity analysis results, hydrogen maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector.
+While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s respectively to recreate similar energy mixes.
+Key technologies that aid in decarbonization in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation.
+Steam reforming, with or without CCS, does not get utilized in our simulations due to its high emission coefficient.
+At the lower end of the technology readiness scale, \gls{SOEC}s emerge as tremendously disruptive due to their high efficiency.
+However, their operational lifetimes need to be increased significantly, life cycle emissions must be kept low, and cost-competitiveness with \gls{PEMEC}s must be achieved in order to realize their potential.
+\gls{PWS} plays a marginal role as it is not cost-competitive with electrolysis.
+From the simulation output data, the investment cost of \gls{SOFC}s emerges as a critical parameter.
+Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible.
+However, low response times and high availability are two key factors that are implicit in our assumptions.
+If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and closer to commercialization.
+In Scenarios 3 and 4, solar, wind, and nuclear are used to generate hydrogen.
+Therefore it would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants.
+Waste heat from nuclear could also be used to produce hydrogen, and would reduce reliance on renewables for electrolysis.
+As mentioned previously, more flexible and responsive fuel cells and electrolyzers are likely to be the dominant technology in such a system.
+
+%ccs
+CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen.
+Its share is found to be largely insensitive to  investment costs as evidenced by the sensitivity analysis.
+This is mainly due to its large emission coefficient.
+Marginal gains are expected in its penetration if the efficiency of CCS is increased to reduce its direct emissions.
+Reducing indirect emissions is likely to have a greater impact.
+This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.

### 2020-11-26 doc/2020-03-paper/Appendix.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 	\caption{Data for initial condition.}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 	\caption{Capacity limits.}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 %\begin{minipage}{\textwidth} 
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 	\caption{Miscellaneous model parameters and assumptions.}
@@
 
+\pagebreak
+
+\subsection{Sensitivity analysis secondary results}
+
+\begin{figure}[H] 
+\centering
+\hspace*{-1cm}
+\includegraphics[scale=0.09]{figures/pws}
+\caption{Sensitivity analysis of Photochemical Water Splitting. Red dots indicate points that are zero values, while blue dots indicate non-zero values.}
+\label{pws}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\hspace*{-3cm}
+\includegraphics[scale=0.12]{figures/satechsh2}
+\caption{Sensitivity analysis of hydrogen generation technologies \gls{SOEC} and \gls{PEMEC}}.
+\label{satechs-h2}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\hspace*{-3cm}
+\includegraphics[scale=0.12]{figures/satechselc}
+\caption{Sensitivity analysis of electricity generation technologies \gls{SOFC} and \gls{CCS} gas.}
+\label{satechs-elc}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\hspace*{-3cm}
+\includegraphics[scale=0.15]{figures/syscost}
+\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.}
+\label{syscost}
+\end{figure}
+
 \begin{figure}[h] 
@@
 \label{sa-useless}
+
 \end{figure}

### 2020-11-26 doc/2020-03-paper/abstract.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

\begin{abstract}

We simulated five possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model. Key features of our simulations include the incorporation of novel technologies like hydrogen electrolyzers, carbon caputre, photochemical water splitting, and emerging solar technologies, long-term impact assessment up to 2100, and inclusion of life-cycle emission and learning curves for novel technologies. Results indicate that a hybrid approach using hydrogen from renewable energy-based electrolysis and nuclear power, is cost-effective and provides long-term emission reduction along with energy security. Hydrogen from renewables, nuclear power, wind, and novel solar technologies emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.

\end{abstract}

### 2020-11-26 doc/2020-03-paper/acks.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

--- 2020-06-22 doc/2020-03-paper/acks.tex
@@
 
+The author(s) gratefully acknowledge the support of the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.
+We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.
+
 The authors contributed to this work as described below.
+
+Anshuman Chaube designed simulation models, conducted sensitivity analysis, and wrote the original draft of the paper.
+
+Andrew Chapman conceived and contributed to conception of the simulations, designed simulation models, and wrote the original draft of the paper.
+
+Akari Minami translated data from Japanese to English, and assisted with testing and performing simulations.
+
+James Stubbins supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
 
@@
 Prof.
-Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER),
-sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.
+Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2020-11-26 doc/2020-03-paper/conclusion.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba
adds clean results for syscost, net emissions
Former-commit-id: 5a0d7dd093d146c65fbf51a7f4887799ed403066
Former-commit-id: 8d484390baa9c26c0788b9cfa933ef94f0c1e0fc
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

--- 2020-03-27 doc/2020-03-paper/conclusion.tex
@@
 \section{Conclusion} \label{Conclusion}
-Conclusion
-\section{Future work}
-FUTURE WORK
+%what we did. sum up key technologies, what needs to happen for technologies that are not "key", importance of rapid change/suggested timeline.
 
+We simulated five transition scenarios, assessing potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system, and their long-term impact upto 2100.
+Scenario 1 (Fig.
+\ref{scen1}), proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure.
+The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Fig.
+\ref{scen2}), investing heavily in hydrogen (Fig.
+\ref{scen3} and \ref{scen5}), or using a combination of both (Fig.
+\ref{scen4}).
+Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050.
+Key technologies that emerge from our results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role.
+CCS with coal, steam reforming with our without CCS, new coal, and new oil are not utilized due to their high direct and life-cycle emissions.
+Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction.
+Such a multifaceted approach to emission reduction is also likely to improve decarbonization outcomes since the commercialization and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.
+
+Future work should incorporate synergistic assessment of hydrogen across multiple sectors such as transportation and industry.
+The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating.
+Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonization strategies, improve social outcomes, and delineate investment goals for the energy sector.
+
+%\section{Future work}
+%grid resilience - analysis of grid stability of similar mixes at the resolution of minutes. Maybe in TIMES (ugh).
 \section{Declaration of Competing Interest}
-
-NECESARY?
+The authors declare no conflict of interest.

### 2020-11-26 doc/2020-03-paper/discussion.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

@@
 Since hydrogen plays a key role in zero to moderate nuclear deployment scenarios (Figs.
-\ref{scen3}and \ref{scen4}), it appears prudent to invest in hydrogen power.
+\ref{scen3} and \ref{scen4}), it appears prudent to invest in hydrogen power.
 As the model uses learning curves for technology prices and our objective function is transition cost, hydrogen technologies are deployed as late as possible in order to minimize costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals.
-Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen deployment by 2030 at the latest, in the absence of new nuclear, or by 2035, with new nuclear.
+Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen power by 2030 at the latest in the absence of new nuclear, or by 2035 with new nuclear.
 
@@
 When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios.
-It also reduces the cost of the transition from 3,187,940 MUSD in Scenario 3 to 2,804,753 MUSD in Scenario 4, a difference of 12\% of the system cost.
-The estimated savings due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines.
-Further, the large emission reductions achieved with the help of nuclear allow natural gas to continue operating until 2100 while also meeting emission goals.
+It also reduces the cost of the transition from 3.18 Trillion USD in Scenario 3 to 2.80 Trillion USD in Scenario 4, a difference of 12\% of the system cost.
+The estimated savings in cost and emissions due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines.
+The large emission cuts achieved with the help of nuclear also allow natural gas to continue operating until 2100, while meeting emission goals.
 As natural gas is well suited to peaking and load-following, when coupled with flexible fuel cell technologies, it could engender in an extremely stable energy system.
@@
 Premature decommissioning due to operational problems or lack of public acceptance need to be avoided.
-Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, increasing public awareness of nuclear's vital role in  mitigating carbon emission is key to achieving 2030 and 2050 emission targets.
+Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, and increasing public awareness of nuclear's vital role in mitigating carbon emission is key to achieving 2030 and 2050 emission targets.
 
@@
 \ref{scen1},\ref{scen3}-\ref{scen5}).
-If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (\ref{scen1}).
+If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (Fig.
+\ref{scen1}).
 Under a scenario with a relatively large share of renewables, grid flexibility becomes extremely important.
-such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive.
-As natural gas is the only extant option for load-following, Japan will face a critical choice - whether to incorporate nuclear as in Scenarios 2 and 4 (Figs.
-\ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following.
+Such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive.
+As natural gas is the only extant option for load-following, it is necessary to invest in nuclear or hydrogen to achieve emission cuts while simultaneously keeping natural gas operational for load-following.
 Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand.
@@
 The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing.
-If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3}-\ref{scen5}).
+If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (Figs.
+\ref{scen3}-\ref{scen5}).
 
@@
 Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible.
-However, low response times and high availability are two key factors that are implicit in our assumptions.
+However, low response times and high availability are two other key factors that are implicit in our assumptions.
 If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and closer to commercialization.
@@
 CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen.
-Its share is found to be largely insensitive to  investment costs as evidenced by the sensitivity analysis.
+Its share is found to be largely insensitive to its investment costs as evidenced by the sensitivity analysis.
 This is mainly due to its large emission coefficient.
@@
 This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.
+
+Although our analysis relies on optimal solutions and scenarios and is technologically agnostic, policy makers in Japan will face difficult future decisions as to the long-term nature of the low-carbon energy system.
+One approach could be to prioritize nuclear energy and to reap the benefits of inexpensive, low-carbon energy, at the cost of achieving consensus from the public for its long-term deployment and use.
+Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilizing hydrogen as a storage medium to engender significant deployment of renewable energy.
+The hydrogen pathway also provides more energy security, obviating the use of coal and oil and mitigating the use of natural gas.
+As social opposition to nuclear is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely.
+However, our results indicate that these two approaches are not mutually exclusive.
+The cost of transitioning to a hydrogen energy system without deploying any new nuclear is much higher than that of any of the nuclear-inclusive options.
+Deploying nuclear in tandem with hydrogen provides a cost-effective compromise.
+An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as at the time of writing, the timely success of the Japanese hydrogen plan is far from certain.
+At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a "bridging" option, providing a low-carbon pathway in the short term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for longer-term deployment timelines.
+If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets.
+Policy which is cognizant of these economic, environmental, and social aspects of energy systems is required to deliver a low-cost, low-carbon energy future for Japan which is socially acceptable.

### 2020-11-26 doc/2020-03-paper/introduction.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

@@
 Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}.
-The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018).
+The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies \cite{noauthor_annual_2018}.
 The Plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).

### 2020-11-26 doc/2020-03-paper/methods.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

@@
 \subsection{TIMES Model Description}
-\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints.
+\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}.
 The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types.
@@
 While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
-However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors.
-Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification driving increasing demand, but the demand eventually plateaus due to the aforementioned expected demographic changes.
+However, precisely quantifying this rate of decrease is challenging as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
+Hence, post-2030, we have assumed a conservative demand curve based on increased electrification driving increasing demand, with the demand eventually plateauing due to the aforementioned expected demographic changes.
 The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
@@
 The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}.
-The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018} cite IRENA.
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.
 
@@
 To explore possible pathways to curbing \gls{GHG} emissions, we simulated a total of five transition scenarios of varying likelihood, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}.
-The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage.
+The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed, and offshore-floating considered separately), and utility-scale lithium-ion battery storage.
 New deployments of oil-fuelled power plants are neglected due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan.
-The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS}, and utility-scale hydrogen power.
-For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC}s,\gls{PEMEC}s,\gls{PEMFC}s, and \gls{SOFC}s were incoporated based on their technological potential.
+The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe), \gls{CCS}, and utility-scale hydrogen power.
+For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \glspl{AEC}, \glspl{PEMEC}, \glspl{PEMFC}, and \glspl{SOFC} were incoporated based on their technological potential.
 Along with these two technology groups, we also explore the potential impact of nuclear energy.
@@
 One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
-We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
+We assume that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
 Therefore, they could be deployed as rapidly as conventional solar photovoltaic.
@@
 For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
 
@@
 %variables, sampling approach, median, range, which variables, which base case scenario, why
-While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, we have to acknowledge that many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain.
-This is especially true for nascent technologies that have not been commercialized, like \gls{CCS}, hydrogen generation and conversion technologies.
-Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost and cumulative emissions over the entire simulation time-frame.
+While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain.
+This is especially true for developing technologies like \gls{CCS}, and hydrogen generation and conversion technologies.
+Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost.
 
@@
 Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster.
-Therefore,in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis.
+Therefore, in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis.
 10 model parameters were sampled 30 times from appropriate distributions (see Table \ref{sa-vars}).
@@
 For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.
+This makes learning-based cost-reductions proportionate across all sensitivity analysis runs.
 These parameters were randomly co-varied in 30 simulations.
 The share of each electricity generation technology (as the ratio cumulative technology output to the cumulative electricity demand) or output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
-A similar approach was also used to correlate these parameters with the system's transition cost, and net emissions over the entire simulation.
+A similar approach was also used to correlate these parameters with the system's transition cost.
 

### 2020-11-26 doc/2020-03-paper/results.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

--- 2020-09-17 doc/2020-03-paper/results.tex
@@
 
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+%\hspace{-3cm}
+\includegraphics[scale=0.5]{figures/conv_nonuc}
+\caption{Scenario 1 - Conventional technologies, no new nuclear.}
+\label{scen1}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/conv_nuc}
+\caption{Scenario 2 - Conventional technologies, with new nuclear.}
+\label{scen2}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/newtechs_nonuc}
+\caption{Scenario 3 - Emerging technologies, no new nuclear.}
+\label{scen3}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/newtechs_nuc}
+\caption{Scenario 4 - Emerging technologies, with new nuclear.}
+\label{scen4}
+\end{figure}
+
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
+\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
+\label{scen5}
+\end{figure}
+
 The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology.
-Due to natural variations in renewables' output, the ability of some electricity sources to load-follow, and the increasing deployment of storage, the first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies, instead of being supplied directly to the end user.
+The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user.
+The output of some technologies also varies due to their ability to load-follow.
 The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies.
@@
 Natural gas sees rapid growth in the near-term, but complete retirement by 2055.
-Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards due to its load-following capabilities.
+Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities.
 All existing nuclear power plants must be restarted by 2022 at full operating capacity.
@@
 The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
-The total cost of this transition is \textbf{3,513,941 MUSD} (in 2015 USD).
+The total cost of this transition is \textbf{3.51 Trillion USD} (in 2015 USD).
 
@@
 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
-The total transition cost of this scenario is the lowest, at \textbf{2,664,207 MUSD.}
+The total transition cost of this scenario is the lowest, at \textbf{2.66 Trillion USD.}
 
@@
 Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals.
-After that, the model relies primarily on renewables and hydrogen to curb emissions while supplying power.
-Significant investment in hydrogen from 2034 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power.
+After that, the model relies primarily on renewables and hydrogen to curb emissions.
+Rapid investment in hydrogen storage from 2030 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power.
 \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen.
 Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame.
-This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan (cite Kato 2016).
+This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan \cite{kato_energy_2016}.
 As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains.
 A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%).
-Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%).
-The cost of this transition is \textbf{3,187,940 MUSD}.
+Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness.
+The cost of this transition is \textbf{3.19 Trillion USD}.
 
@@
 The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}.
-Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared with Scenario 3, from 2037 instead.
+Hydrogen plays a significant role in decarbonization, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3.
 The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%).
 From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3.
-The cost of this transition is \textbf{2,804,753 MUSD}.
+The cost of this transition is \textbf{2.80 Trillion USD}.
 
@@
 \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%.
-The cost of this transition is \textbf{3,180,613 MUSD}.
-
-\begin{figure}[htb] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nonuc}
-\caption{Scenario 1 - Conventional technologies, no new nuclear.}
-\label{scen1}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.42]{figures/conv_nuc}
-\caption{Scenario 2 - Conventional technologies, with new nuclear.}
-\label{scen2}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nonuc}
-\caption{Scenario 3 - Emerging technologies, no new nuclear.}
-\label{scen3}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/newtechs_nuc}
-\caption{Scenario 4 - Emerging technologies, with new nuclear.}
-\label{scen4}
-\end{figure}
-
-\begin{figure}[h] 
-\centering
-\vspace*{-3cm}
-\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
-\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
-\label{scen5}
-\end{figure}
+The cost of this transition is \textbf{3.18 Trillion USD}.
 
@@
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/techs}
-\caption{Sensitivity analysis of selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).
-}
-\label{sa-techs}
+\hspace*{-1cm}
+\includegraphics[scale=0.7]{figures/syscost_abbrv}
+\caption{Sensitivity analysis for overall transition cost vs. SOFC capital costs.}
+\label{syscost-smol}
 \end{figure}
 
-\begin{figure}[h] 
+\begin{figure}[H] 
 \centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/syscost}
-\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).}
-\label{sa-syscost}
+%\hspace*{-3cm}
+\includegraphics[scale=0.7]{figures/satechselc_abbrv}
+\caption{Sensitivity analysis results for electricity supply shares of SOFCs and CCS Gas plants vs SOFC capital costs.}
+\label{satechs-smol}
 \end{figure}
 
-\begin{figure}[h] 
-\centering
-\hspace*{-3cm}
-\includegraphics[scale=0.14]{figures/co2emi}
-\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters.
-Red dots indicate points that are zero values, while blue dots indicate non-zero values.
-Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e.
-PEM FC and CCS Coal).
-}
-\label{sa-co2}
-\end{figure}
+Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figures \ref{pws}-\ref{sa-useless}).
+The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Fig.
+\ref{satechs-smol}).
+This follows from the large share of \gls{SOFC}s, as they are the most important low-carbon technology for storing renewable power, yet they are the most expensive technology available to the model.
+Hence, in the absence of nuclear, they are irreplaceable, and their share is largely fixed.
+In analyzing the sensitivity of the output of electricity generation technologies (Fig.
+\ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs.
+However, the output of \gls{CCS} with natural gas was also most strongly correlated with the investment cost of \gls{SOFC}s, rather than the investment cost of CCS gas itself.
+Its share is also relatively small (indicated by the y-values in Fig.
+\ref{satechs-smol}), about 2-3\%.
+This is because CCS gas deployment increases marginally as fuel cells deployment decreases due to increasing fuel cell cost.
+Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonization alternatives are uneconomical.
+This is due to the large life-cycle and direct emissions of CCS gas compared to renewables and hydrogen technologies.
+
+Remaining results indicate that \gls{PEMFC}s are never utilized due to their low efficiency compared to \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient (Fig.
+\ref{sa-useless}).
+\gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Fig.
+\ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh.
+The share of \gls{PWS} was found to be strongly correlated with its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be cost-competitive (Fig.
+\ref{pws}).
+Its deployment is also weakly correlated with the splitting efficiency; values over 21\% seem most favourable.
+The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment.
+Since \gls{PEMFC}s, \gls{CCS} coal, and \gls{PWS} are not deployed in quantities significant enough to affect the model's performance, they are omitted as potential dependent variables for the rest of the sensitivity analysis.
+
+For hydrogen generating technologies (Fig.
+\ref{satechs-h2}), the \gls{SOEC} output is most strongly correlated with the SOEC investment cost.
+However, their output is affected insignificantly by the perturbation applied to their investment cost.
+Their deployment is largely insensitive to their emission coefficient as their contribution to overall emissions is negligible.
+This highlights their vital role in the transition.
+\gls{PEMEC} (Fig.
+\ref{satechs-elc}) deployment is also most noticeably affected by their respective investment costs, but also by the investment cost of SOECs - as SOECs become more expensive, \gls{PEMEC}s emerge as the natural replacement.

### 2020-12-09 doc/2020-03-paper/abstract.tex
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e

@@
 
-We simulated five possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model.
-Key features of our simulations include the incorporation of novel technologies like hydrogen electrolyzers, carbon caputre, photochemical water splitting, and emerging solar technologies, long-term impact assessment up to 2100, and inclusion of life-cycle emission and learning curves for novel technologies.
-Results indicate that a hybrid approach using hydrogen from renewable energy-based electrolysis and nuclear power, is cost-effective and provides long-term emission reduction along with energy security.
-Hydrogen from renewables, nuclear power, wind, and novel solar technologies emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.
+We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model.
+Key features of our simulations include the incorporation of novel technologies, like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emission and learning curves for technology costs and emission coefficients.
+Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security.
+Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.
 

### 2020-12-09 doc/2020-03-paper/introduction.tex
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e

--- 2020-09-11 doc/2020-03-paper/introduction.tex
@@
 In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption, consisting mainly of the transportation, electricity and heat, buildings, manufacturing and construction sectors \cite{ge_4_2020}.
+The largest contribution to global \gls{GHG} emissions, some 73\%, comes from largely from energy consumption of the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
 For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions.
-However for developing nations, these options are not always economically feasible, leading to increased emissions through greater coal use by rapidly developing nations \cite{international_energy_agency_latest_2019}.
-For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
+However these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
+For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
 
 Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}.
-The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018).
-The Plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).
-Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met.
-This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies \cite{matsuo_quantitative_2018}.
-For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies \cite{ashina_roadmap_2012}.
+The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
+The plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).
+Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not detail how the 2050 emission reduction target of 80\% is to be met.
+This vagueness may be due to uncertainty regarding the economical feasibility of GHG emissions reduction in each sector.
+It has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}.
+For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delayed action in preference for future technologies \cite{ashina_roadmap_2012}.
 It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan.
-The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
+The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in the hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
 
-The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, cognizant of energy policy, resource limitations, demand growth, emerging technologies and economic constraints using \gls{TIMES} framework.
-Our dynamic simulations of transition scenarios, by focusing on minimizing the cost of the transition while satisfying CO2 emission constraints, suggest potential economically feasible decarbonization pathways that meet the increasing near-term electricity demand.
-Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters of each technology and hence guide research and development efforts focused on these technologies.
+The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework.
+Our dynamic simulations of transition scenarios, which focus on minimizing the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonization pathways that meet the increasing near-term electricity demand.
+Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2020-12-09 doc/2020-03-paper/litreview.tex
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e

@@
 The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
+Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
 Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
-Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al.
+Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al.
 explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan.
@@
 Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
-Considering Japan's economic conditions and demographic trends such as moderate GDP growth and rapid aging, Kuriyama et al.
+Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid aging, Kuriyama et al.
 suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}.
 However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.
-Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future.
+Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future.
 Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}.
 A seminal work by Sugiyama et al.
-harmonizes a number of modeling approaches for Japan's long term (i.e.
-to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}.
+harmonizes a number of modeling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}.
 Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction.
-Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
-Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
+Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
+Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
 Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}.
-Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \gls{FCV}s and power generation, via both mixed and direct combustion.
-Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}.
-From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future \cite{nagashima_japans_2018}.
+Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \glspl{FCV} and power generation, via both mixed and direct combustion.
+Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}.
+From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}.
 Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
 The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.
-A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 \cite{oshiro_mid-century_2019}.
+A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.
 
-The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review, and expand the consideration of technologies beyond  conventional options to also include emerging near-term alternatives, and potentially disruptive technologies post-2050.
-This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
+The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
+This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and operation and maintenance (O\&M) costs, efficiency, and emission coefficients.
 Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities.

### 2020-12-09 doc/2020-03-paper/methods.tex
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e

@@
 Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
-For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
 Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

### 2020-12-10 doc/2020-03-paper/Appendix.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
-\section{Model data, assumptions, and secondary results} \label{Appendix}
+\section{Model data and assumptions} \label{Appendix}
 
 \begin{table}[H]
-	\caption{Data for initial condition.}
+	\caption{Data for defining the initial condition across all simulations.}
 	\vspace{0.1in}
@@
 \textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
-  & (USD/kWh) & \textbf{Coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
+  & (USD/kWh) & \textbf{coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
 \hline
@@
 \includegraphics[scale=0.5]{figures/IC}
-\caption{Electricity generation that defines the initial condition of the model.}
+\caption{Electricity generation between 2013-2016 that defines the initial condition across all simulations.}
 \end{figure}
@@
 \begin{table}[H]
-	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
+	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
 	\vspace{0.1in}
@@
 		\hline
-\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
-  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
+\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
+  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
 \hline
@@
 \hline
-\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
- & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
- & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
+\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity factor/} & \textbf{Emission} & \textbf{Year} \\
+ & \textbf{cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{efficiency} & \textbf{coefficient} & \textbf{available} \\
+ & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\
 \hline
@@
 Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
-Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
+Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
@@
  & 615(2050) & & & & & &  \\
-Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
+Onshore wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
 \cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
-Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
+Offshore wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
 \cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
-Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
+Offshore wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
 \cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
@@
  & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
-Gas Reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
+Gas reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
 \cite{iea_technology_2015,mehmeti_life_2018,keipi_economic_2018} & & & & & &  & \\
-Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
+Gas reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
 \cite{iea_technology_2015,keipi_economic_2018,cormos_ana-maria_economic_2018} &  &  &  &  &  &  & \\
@@
 \begin{table}[H]
-	\caption{Capacity limits.}
+	\caption{Nameplate capacity deployment limits.}
 	\vspace{0.1in}
@@
 %\begin{minipage}{\textwidth} 
-	\caption{Capacity growth rates.}
+	\caption{Nameplate capacity growth rates.}
 	\vspace{0.1in}
@@
 		\hline
-\textbf{Technology} & \textbf{Max. Annual} \\
-  & \textbf{Growth Rate}   \\
+\textbf{Technology} & \textbf{Maximum Annual Growth Rate} \\
+%  & \textbf{Growth Rate}   \\
 \hline
 Nuclear (2027 onwards) & +5 reactors \\
-Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
-Onshore Wind \cite{irena_renewable_2020} & 25\% \\
-Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
-Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
-Li-ion Storage & 30\% \\
-Natural Gas &  50\% \\
+Solar and emerging solar \cite{irena_renewable_2020} & 40\%  \\
+Onshore wind \cite{irena_renewable_2020} & 25\% \\
+Offshore wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
+Offshore wind(Floating) \cite{irena_renewable_2020} & 20\% \\
+Li-ion storage & 30\% \\
+Natural gas &  50\% \\
 \gls{USC} & 50\% \\
@@
 
-\subsection{Sensitivity analysis secondary results}
+\section{Sensitivity analysis secondary results}
 

### 2020-12-10 doc/2020-03-paper/abstract.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
 We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model.
-Key features of our simulations include the incorporation of novel technologies, like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emission and learning curves for technology costs and emission coefficients.
+Key features of our simulations include the incorporation of novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emissions, and learning curves for parameters such as investment cost, efficiency, and emission coefficient.
 Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security.

### 2020-12-10 doc/2020-03-paper/acros.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba
minor corrections
Former-commit-id: 73fa67ae7dfdd55dc9ca0475bcfdd9cec707fa25
Former-commit-id: 37a6fe9c80ddc0b9080cf1e4d4e034e7c6c4cdd7
lit review corrections
Former-commit-id: 4f44fc931963a354bcb5e74b1219f87f407636f2
Former-commit-id: 249f1c80ef74feb3134bb71a245fda4f1a107c33
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e
NP edits to sections 3-app

--- 2020-04-07 doc/2020-03-paper/acros.tex
@@
 \newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
-\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
+%\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
 \newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
-\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
-\newacronym{USC}{USC}{Ultra Supercritical Coal}
-\newacronym{OM}{O\&M}{Operation and Maintenance Cost}
-\newacronym{PEMFC}{PEM Fuel Cells}{Polymer Electrolyte Membrane Fuel Cells}
-\newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
-\newacronym{lng}{LNG}{Liquified Natural Gas}
+\newacronym{CCS}{CCS}{carbon capture and sequestration}
+\newacronym{USC}{USC}{ultra-supercritical coal}
+\newacronym{OM}{O\&M}{operation and maintenance}
+\newacronym{PEMFC}{PEMFC}{polymer electrolyte membrane fuel cell}
+\newacronym{lcoe}{LCOE}{levelized cost of electricity}
+\newacronym{lng}{LNG}{liquified natural gas}
+\newacronym{AEC}{AEC}{alkaline electrolyser cell}
+\newacronym{PEMEC}{PEMEC}{polymer electrolyte membrane electrolyser cell}
+\newacronym{SOEC}{SOEC}{solid oxide electrolyser cell}
+\newacronym{SOFC}{SOFC}{solid oxide fuel cell}
+\newacronym{PWS}{PWS}{photochemical water splitting}
+\newacronym{INDC}{INDC}{Intended Nationally Determined Contribution}
+\newacronym{GHG}{GHG}{greenhouse gas}
+\newacronym{BOP}{BOP}{balance of plant}
+\newacronym{P2G}{P2G}{power-to-gas}
+\newacronym{FCV}{FCV}{fuel cell vehicle}
 %\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-12-10 doc/2020-03-paper/introduction.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
 \section{Introduction} \label{Introduction}
-In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
 The largest contribution to global \gls{GHG} emissions, some 73\%, comes from largely from energy consumption of the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
 For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions.
-However these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
+However, these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
 For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
@@
 The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
-The plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid).
+The plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarised as '3E+S'; ibid).
 Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not detail how the 2050 emission reduction target of 80\% is to be met.
-This vagueness may be due to uncertainty regarding the economical feasibility of GHG emissions reduction in each sector.
+This vagueness may be due to uncertainty regarding the economic feasibility of GHG emissions reduction in each sector.
 It has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}.
-For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delayed action in preference for future technologies \cite{ashina_roadmap_2012}.
+For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}.
 It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan.
@@
 The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework.
-Our dynamic simulations of transition scenarios, which focus on minimizing the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonization pathways that meet the increasing near-term electricity demand.
+Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand.
 Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2020-12-10 doc/2020-03-paper/litreview.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
 Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches.
+Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modelling approaches.
 Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
-Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al.
+Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al.
 explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan.
-Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}.
+Their study identified that \gls{P2G} can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}.
 Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
@@
 Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future.
-Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}.
+Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}.
 A seminal work by Sugiyama et al.
-harmonizes a number of modeling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}.
+harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}.
 Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction.
-Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
+Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
 Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
@@
 From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}.
-Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
-The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.
+Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
+The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.
 A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.
 
-The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
-This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and operation and maintenance (O\&M) costs, efficiency, and emission coefficients.
+The model and the approach proposed in this research are unique, as they build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
+This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
 Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities.
 This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels.
-By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
+By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2020-12-10 doc/2020-03-paper/methods.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
 \subsection{TIMES Model Description}
-\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}.
+\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}.
 The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types.
@@
 The objective function in our single-region model is the overall cost of the transition.
-The major constrains in our simulations are the demand for electricity (see Table \ref{demand}), emission constraints on the electricity-generation sector based on Japan's \gls{INDC} (see Table \ref{co2-limits}), and feasible nameplate capacity deployment limits (see Table \ref{caplim}).
-Miscellaneous assumptions are summarized in table \ref{misc-assump}.
-Therefore, our model minimizes the transition cost, while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
+The major constraints in our simulations are the demand for electricity (Table \ref{demand}), emission constraints on the electricity-generation sector based on Japan's \gls{INDC} (Table \ref{co2-limits}), and feasible nameplate capacity deployment limits (Table \ref{caplim}).
+Miscellaneous assumptions are summarised in Table \ref{misc-assump}.
+In other words, our model minimises the transition cost while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
 
-While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
-However, precisely quantifying this rate of decrease is challenging as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
-Hence, post-2030, we have assumed a conservative demand curve based on increased electrification driving increasing demand, with the demand eventually plateauing due to the aforementioned expected demographic changes.
-The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
-Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100.
-The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for every technology, as applicable.
+While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
+However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
+Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, with the demand eventually plateauing due to the aforementioned expected demographic changes.
+The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
+Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100.
+The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology, as applicable.
 The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}.
@@
 \begin{table}[!ht]
-	\caption{Demand increase over time.}
+	\caption{Electricity demand increase over the simulation time frame.}
 	\vspace{0.1in}
@@
 \begin{table}[!ht]
-	\caption{CO$_2$ constraints.}
+	\caption{Emission constraints.}
 	\vspace{0.1in}
@@
 		\hline
-\textbf{Year} & \textbf{Emission limit} & \textbf{Base Year} & \textbf{Reduction from base year} \\
+\textbf{Year} & \textbf{Emission limit} & \textbf{Base year} & \textbf{Reduction from base year} \\
 \hline
@@
 %scenario description
-To explore possible pathways to curbing \gls{GHG} emissions, we simulated a total of five transition scenarios of varying likelihood, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}.
-The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed, and offshore-floating considered separately), and utility-scale lithium-ion battery storage.
-New deployments of oil-fuelled power plants are neglected due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan.
-The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe), \gls{CCS}, and utility-scale hydrogen power.
+To explore possible pathways to curbing \gls{GHG} emissions, we simulated five transition scenarios of varying likelihoods, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}.
+The first set includes conventional technologies such as  \gls{USC}, \gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed, and offshore-floating considered separately), and utility-scale lithium-ion battery storage.
+New deployments of oil-fuelled power plants are disabled due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan.
+The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialised or close to commercialisation, namely emerging solar photovoltaic (modelled as a composite of perovskites and CdTe solar cells), \gls{CCS}, and utility-scale hydrogen power.
 For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \glspl{AEC}, \glspl{PEMEC}, \glspl{PEMFC}, and \glspl{SOFC} were incoporated based on their technological potential.
 Along with these two technology groups, we also explore the potential impact of nuclear energy.
-Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions, and a high capacity factor.
-However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain.
+Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions and a high capacity factor.
+However, nuclear power faces extremely low public acceptance in Japan after the Fukushima-Daiichi accident, therefore its future in Japan is highly uncertain.
 Hence, transition scenarios with and without new nuclear reactor deployment must be juxtaposed to assess the importance of the role of nuclear in emission reduction.
 Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario.
-In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored in the absence of new nuclear power.
+In this scenario, the potential commercialisation of \gls{SOEC} and \gls{PWS} post-2050 is explored in the absence of new nuclear power.
 
 %misc assumptions
-Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
+Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in Tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Prices and projections for fossil fuels and nuclear fuel are incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
 Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
@@
 The reactor size assumed in this study is 1165 MWe.
-Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow to a certain extent, which is simulated in a limited way in our model based on French reactors' range of capacity factors.
-The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
+Due to a projected increase in the share of renewables, nuclear power plants must be able to load-follow to a certain extent, which is approximated in our model based on French reactors' range of capacity factors.
+The growth rates of all emerging technologies are modelled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
 One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
-We assume that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
+We assume that these technologies, some of which are already commercialised or close to commercialisation, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
 Therefore, they could be deployed as rapidly as conventional solar photovoltaic.
 
-All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following.
+All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load-following.
 Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
 For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
 
 \begin{table}[!ht]
-	\caption{Scenario definition.}
+	\caption{Electricity supply transition scenario definition.}
 	\vspace{0.1in}
@@
 %variables, sampling approach, median, range, which variables, which base case scenario, why
-While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain.
-This is especially true for developing technologies like \gls{CCS}, and hydrogen generation and conversion technologies.
-Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost.
+While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, many parameters, such as the investment cost, life cycle emissions, and lifetimes, are highly uncertain for novel technologies like \gls{CCS} and hydrogen generation and conversion technologies.
+Therefore, our sensitivity analysis is focused on investigating the impact of such parameters (Table \ref{sa-vars}).
+We analyse the sensitivity of the share of each of these technologies in the electricity-generation mix, and of the system transition cost with respect to these variables.
 
@@
 Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions.
+Consequently, we eliminated nuclear power's investment cost as a candidate for sensitivity analysis.
 Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster.
-Therefore, in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis.
-10 model parameters were sampled 30 times from appropriate distributions (see Table \ref{sa-vars}).
-The parameter value at the first year of deployment (see Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios.
+In order to assess these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose Scenario 5 (Table \ref{scen-table}) as our base scenario for sensitivity analysis.
+Ten model parameters were sampled 30 times from appropriate distributions (Table \ref{sa-vars}).
+The parameter value at the first year of deployment (Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios.
 For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.
@@
 These parameters were randomly co-varied in 30 simulations.
-The share of each electricity generation technology (as the ratio cumulative technology output to the cumulative electricity demand) or output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
+The share of each electricity generation technology (as the ratio of cumulative technology output to the cumulative electricity demand) and output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
 A similar approach was also used to correlate these parameters with the system's transition cost.
@@
 \begin{table}[!ht]
-	\caption{Scenario definition.}
+	\caption{Candidate parameters and their variation in our sensitivity analysis.}
 	\vspace{0.1in}

### 2020-12-10 doc/2020-03-paper/results.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

@@
 \includegraphics[scale=0.5]{figures/conv_nonuc}
-\caption{Scenario 1 - Conventional technologies, no new nuclear.}
+\caption{Scenario 1 results (conventional technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
 \label{scen1}
@@
 \includegraphics[scale=0.5]{figures/conv_nuc}
-\caption{Scenario 2 - Conventional technologies, with new nuclear.}
+\caption{Scenario 2 results (conventional technologies with new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
 \label{scen2}
@@
 \includegraphics[scale=0.5]{figures/newtechs_nonuc}
-\caption{Scenario 3 - Emerging technologies, no new nuclear.}
+\caption{Scenario 3 results (emerging technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
 \label{scen3}
@@
 \includegraphics[scale=0.5]{figures/newtechs_nuc}
-\caption{Scenario 4 - Emerging technologies, with new nuclear.}
+\caption{Scenario 4 results (emerging technologies with new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
 \label{scen4}
@@
 \includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
-\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
+\caption{Scenario 5 results (emerging technologies and nascent hydrogen technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
 \label{scen5}
@@
 
-The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology.
+The results of each scenario (Table \ref{scen-table} for scenario definitions) are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology.
 The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user.
@@
 
-In Scenario 1 (Fig.
-\ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt.
+In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt.
 Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage.
@@
 All existing nuclear power plants must be restarted by 2022 at full operating capacity.
-With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary.
+With renewable energy as the only option for decarbonisation, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary.
 The presence of a large share of renewables results in significant overgeneration of electricity during some years.
 The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
-The total cost of this transition is \textbf{3.51 Trillion USD} (in 2015 USD).
+The total cost of this transition is \textbf{3.51 trillion USD} (in 2015 USD).
 
-With the availability of new nuclear reactors in Scenario 2 (Fig.
-\ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100.
+With the availability of new nuclear reactors in Scenario 2 (Figure \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100.
 The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions.
-Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100.
-The share of renewables deployed during this transition is reduced dramatically.
-This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the capacity of lithium-ion storage deployed.
+This nuclear-driven reduction in emissions allows natural gas power plants to operate until 2100.
+The share of renewables deployed during this transition reduces dramatically.
+This, combined with the load-following capabilities of natural gas plants and nuclear reactors, drastically decreases the capacity of lithium-ion storage deployed.
 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
-The total transition cost of this scenario is the lowest, at \textbf{2.66 Trillion USD.}
+The total transition cost of this scenario is the lowest, at \textbf{2.66 trillion USD.}
 
-Using emerging technologies without new nuclear power (Fig.
-\ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonization occurs after 2050.
+Using emerging technologies without new nuclear power (Figure \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonisation occurs after 2050.
 The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario.
@@
 After that, the model relies primarily on renewables and hydrogen to curb emissions.
-Rapid investment in hydrogen storage from 2030 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power.
+Rapid investment in hydrogen storage from 2030 onwards allows effective utilisation of renewables and precludes investment in offshore floating wind power.
 \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen.
-Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame.
+Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time frame.
 This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan \cite{kato_energy_2016}.
@@
 Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness.
-The cost of this transition is \textbf{3.19 Trillion USD}.
+The cost of this transition is \textbf{3.19 trillion USD}.
 
-Deploying both emerging technologies with new nuclear reactors (Fig.
-\ref{scen4}) results in rapid decarbonization.
+Deploying both emerging technologies with new nuclear reactors (Figure \ref{scen4}) results in rapid decarbonisation.
 Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100.
 The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}.
-Hydrogen plays a significant role in decarbonization, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3.
-The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%).
+Hydrogen plays a significant role in decarbonisation, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3.
+The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies (62\%), onshore wind (20\%), and nuclear (13\%).
 From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3.
-The cost of this transition is \textbf{2.80 Trillion USD}.
+The cost of this transition is \textbf{2.80 trillion USD}.
 
-The fifth scenario's results (Fig.
-\ref{scen5}) closely resemble those of the third scenario (Fig.
-\ref{scen3}).
+The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}).
 However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055.
@@
 Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050.
-The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%).
-From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%).
+The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies (48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%).
+From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), and \gls{PEMEC} (43\%).
 \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%.
-The cost of this transition is \textbf{3.18 Trillion USD}.
+The cost of this transition is \textbf{3.18 trillion USD}.
 
@@
 \includegraphics[scale=0.7]{figures/syscost_abbrv}
-\caption{Sensitivity analysis for overall transition cost vs. SOFC capital costs.}
+\caption{Sensitivity analysis for overall transition cost vs. solid oxide fuel cell capital costs.}
 \label{syscost-smol}
@@
 \includegraphics[scale=0.7]{figures/satechselc_abbrv}
-\caption{Sensitivity analysis results for electricity supply shares of SOFCs and CCS Gas plants vs SOFC capital costs.}
+\caption{Sensitivity analysis results for electricity supply shares of solid oxide fuel cells (top) and carbon capture and sequestration natural gas plants (bottom) vs solid oxide fuel cell capital costs.}
 \label{satechs-smol}
@@
 
-Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figures \ref{pws}-\ref{sa-useless}).
-The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Fig.
-\ref{satechs-smol}).
+Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figs.
+\ref{pws}-\ref{sa-useless}).
+The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Figure \ref{satechs-smol}).
 This follows from the large share of \gls{SOFC}s, as they are the most important low-carbon technology for storing renewable power, yet they are the most expensive technology available to the model.
-Hence, in the absence of nuclear, they are irreplaceable, and their share is largely fixed.
-In analyzing the sensitivity of the output of electricity generation technologies (Fig.
-\ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs.
+In the absence of new nuclear deployments, \glspl{SOFC} are irreplaceable, and their share is largely fixed.
+In analysing the sensitivity of the output of electricity generation technologies (Figure \ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs.
 However, the output of \gls{CCS} with natural gas was also most strongly correlated with the investment cost of \gls{SOFC}s, rather than the investment cost of CCS gas itself.
-Its share is also relatively small (indicated by the y-values in Fig.
-\ref{satechs-smol}), about 2-3\%.
-This is because CCS gas deployment increases marginally as fuel cells deployment decreases due to increasing fuel cell cost.
-Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonization alternatives are uneconomical.
+The share of \gls{CCS} with natural gas is also relatively small (indicated by the y-values in Figure \ref{satechs-smol}), about 2-3\%.
+This is because CCS gas deployment increases only marginally as fuel cells deployment decreases due to increasing fuel cell cost.
+Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonisation alternatives are uneconomical.
 This is due to the large life-cycle and direct emissions of CCS gas compared to renewables and hydrogen technologies.
 
-Remaining results indicate that \gls{PEMFC}s are never utilized due to their low efficiency compared to \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient (Fig.
-\ref{sa-useless}).
-\gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Fig.
-\ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh.
-The share of \gls{PWS} was found to be strongly correlated with its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be cost-competitive (Fig.
-\ref{pws}).
-Its deployment is also weakly correlated with the splitting efficiency; values over 21\% seem most favourable.
-The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment.
+Remaining results indicate that \gls{PEMFC}s are never utilised because of their low efficiency compared to \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient (Figure \ref{sa-useless}).
+\gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Figure \ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh, and \gls{PEMEC}s, which generate 12,000-16,000 TWh of hydrogen, respectively.
+The share of \gls{PWS} was found to be strongly correlated with its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be cost-competitive (Figure \ref{pws}).
+\gls{PWS} deployment is also weakly correlated with the splitting efficiency; values over 21\% seem most favourable.
+The \gls{PWS} emission coefficient is too small to have an impact on the overall emissions of the system considering \gls{PWS}'s small deployment.
+Hence its emission coefficient does not appreciably affect \gls{PWS} deployment.
 Since \gls{PEMFC}s, \gls{CCS} coal, and \gls{PWS} are not deployed in quantities significant enough to affect the model's performance, they are omitted as potential dependent variables for the rest of the sensitivity analysis.
 
-For hydrogen generating technologies (Fig.
-\ref{satechs-h2}), the \gls{SOEC} output is most strongly correlated with the SOEC investment cost.
-However, their output is affected insignificantly by the perturbation applied to their investment cost.
-Their deployment is largely insensitive to their emission coefficient as their contribution to overall emissions is negligible.
-This highlights their vital role in the transition.
-\gls{PEMEC} (Fig.
-\ref{satechs-elc}) deployment is also most noticeably affected by their respective investment costs, but also by the investment cost of SOECs - as SOECs become more expensive, \gls{PEMEC}s emerge as the natural replacement.
+For hydrogen generating technologies (Figure \ref{satechs-h2}), the \gls{SOEC} output is most strongly correlated with the SOEC investment cost.
+However, \gls{SOEC} output is affected insignificantly by the perturbation applied to its investment cost.
+\gls{SOEC} deployment is largely insensitive to its emission coefficient as its contribution to overall emissions is negligible.
+This highlights \gls{SOEC}'s vital role in the transition.
+\gls{PEMEC} (Figure \ref{satechs-elc}) deployment is also most noticeably affected by its respective investment costs, but also by the investment cost of SOECs - as SOECs become more expensive, \gls{PEMEC}s emerge as the natural replacement.

### 2020-12-14 publications/2020-03-paper/revisions/review-responses.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Strategies for thorium fuel cycle transition in the SD-TMSR\\
\large Response to Review Comments}
\author{O. Ashraf, Andrei Rykhlevskii, G. V. Tikhomirov, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which certainly improved the paper.

\begin{questions}
        \section*{Reviewer 1}

        \question This work investigates the fuel cycle and neutronics performance of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different fissile material based on an extended SERPENT-2 code. The whole paper states clearly.

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
        \begin{solution}

        		  Thank you for the excellent point.

        		  About depletion regions definition: we used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material
        		  is treated as a single depletion zone. The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.

        		  About burnup time step definition: it is time interval given in days. During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). We started our calculations by 30 days' time step but we do not find significant changes in $k_{eff}$ when we increased the time step to 365 days. The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.

        		  We changed the paragraph as follows:\\

        		  The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump. We used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material is treated as a single depletion zone.

        		  We changed the paragraph as follows:\\
        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in $k_{eff}$ became significant. The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}

		          Thank you for your insightful comment. We used total fuel 
		          salt inventory in the primary loop to define the fuel 
		          material in the SERPENT input. Moreover, we accordingly 
		          adjusted power density in SERPENT burnup calculations 
		          because fission takes place only in the core region. But we did not consider processes, such as decay, which occurs outside of the core. Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in Zhang et al. (2018) \cite{zhang2018review}.

		          We changed the paragraph as follows:\\

		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region. But we did not consider processes, such as decay, which occurs outside of the core. Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.     
        \end{solution}

        %---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question Strategies for thorium fuel cycle transition by employing different startup fissile material and feed mechanisms were investigated for the single-fluid double-zoned thorium-based molten salt reactor (SD-TMSR) in this study, and some specific conclusions were obtained. While, realizing thorium fuel cycle transition by using different startup fissile material has already been well studied in the previous studies for different types of MSR, including SD-TMSR. The motivation (e.g., improvement from previous studies) for conducting this study is not clear. In addition, some statements in the paper are inaccurate and more interpretations should be provided to explain some obtained results. Therefore, a major revision is required to improve the manuscript.

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question SD-TMSR concept development does not correctly described in the section "introduction", where it states that the SD-TMSR was introduced by the Chinese Academy of Sciences. Actually, SD-TMSR concept was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) (see Ref.: Tech. Rep. ORNL-4541). In addition, the study of reference 7 which was cited to illustrate SD-TMSR concept actually adopted the single-flow single-zone MSR rather than SD-TMSR.

        \begin{solution}
                 Thank you for catching this. Just small correction: this ORNL 
                 concept was called \emph{Molten Salt Breeder Reactor (MSBR)}. 
                 The whole statement has been 
                 modified to read:\\

                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
                 MW$_{th}$ was proposed for the first time by ORNL as early as 
                 in the 1960s, which was called Molten Salt Breeder Reactor 
                 (MSBR) \cite{robertson_conceptual_1971}.

                 Thank you for catching this. Reference 7 has been removed from the paragraph.

        \end{solution}

        %---------------------------------------------------------------------

        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept. Cui. et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium. Progress in Nuclear Energy 104 (2018) 75-84). The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
        \begin{solution}
                Thank you for your helpful review. The statement "For the SD-TMSR 
                concept, simulating the fissile core startup and fuel cycle 
                transition with other fissile materials (except$^{233}$U) has 
                not studied before" in page 3, has been removed. 
                The following paragraphs have been added to the manuscript:\\

                The research effort described in \cite{cui2017transition} and
                \cite{cui2018possible} is most similar to the work
                presented in this paper. Cui \emph{et al.} analyzed the fuel 
                transition from 
                enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the 
                MSBR-like design. Cui 
                \emph{et al.} found that the fuel transition can be achieved 
                by using: (1) 
                enriched uranium with greater than 40\% enrichment 
                \cite{cui2018possible}; (2) 
                Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel 
                \cite{cui2017transition, 
                	cui2018possible}.

                However, a few major differences follow: 
                (1) Cui \emph{et al.} employed an in-house tool named MSR 
                Reprocessing 
                Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE 
                and employs a 
                batch-wise approach while we used built-in truly continuous 
                fuel depletion 
                capabilities in SERPENT-2 \cite{aufiero2013extended}; 
                (2) Cui \emph{et al.} studied a high-enriched uranium ($>$40\% 
                of $^{235}$U) 
                and plutonium partitioned from light water reactors spent fuel 
                as the startup 
                fissile materials while we considered different loading cases: 
                HALEU, Pu 
                mixed with HALEU, reactor-grade plutonium, TRU and $^{233}$U;
                (3) we adopted the SD-TMSR core geometry optimized by Li 
                \emph{et al.} 
                \cite{li_optimization_2018} which is different from the 
                MSBR-like geometry by 
                Mathieu \emph{et al.} \cite{mathieu_possible_2009} adopted by 
                Cui \emph{et 
                	al.}; 
                (4) Cui \emph{et al.} introduced two scenarios for thorium 
                fuel cycle 
                transition: a Breeding and Burning (B\&B) scenario and a 
                Pre-breeding scenario 
                while we adopting different approach by introducing two 
                different feed 
                mechanisms: thorium and non-thorium.

                Comparing with Cui \emph{et al.}, we used different reactor 
                design (geometry, 
                volumes, densities, fuel salt compositions) and computation 
                method (continuous 
                online reprocessing instead of batch-wise approach). In Cui's 
                scenarios, the 
                amount of thorium is kept constant. $^{233}$U is fed only in 
                (B\&B) scenario 
                and extra fissile materials would have to be added into the 
                core if the 
                produced $^{233}$U is not enough to maintain the reactor 
                criticality. In the 
                Pre-breeding scenario, all the $^{233}$U produced from the 
                decay of the 
                extracted $^{233}$Pa stored outside the core until it reaches 
                the required 
                startup mass for a new reactor. Thus, the criticality of the 
                core is 
                maintained by refueling external fissile material. In the 
                current work, using 
                the thorium feed mechanism, we simultaneously feed thorium and 
                all or fraction 
                of produced $^{233}$U from the \texttt{Pa-decay tank} into the 
                core. The 
                excess $^{233}$U (if exists) is stored outside the core. In 
                the non-thorium 
                feed mechanism, we continuously inject external heavy metals 
                (HALEU, Pu mixed 
                with HALEU, reactor-grade Pu, or TRU) and fraction of produced 
                $^{233}$U from 
                the \texttt{Pa-decay tank}. For the non-thorium mechanism, we 
                feed a part of 
                produced $^{233}$U because in some cases (e.g., TRU) refueling 
                only external 
                heavy metals failed to maintain the core criticality 
                (limitation is 
                dm$_{salt}$ $\leq$ 0.1\%).

        \end{solution}

        %---------------------------------------------------------------------

        \question More details should be provided to illustrate the heavy metal addition for the thorium feed mechanism and non-thorium feed mechanism in page 11. It is hard to understand why the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Pa.
        \begin{solution}
               Thank you for the comment. Actually, in page 11, we mention 
               that the mass of Th / external heavy metals is approximately 
               equal to the mass of extracted Fission products (FPs) and not 
               Pa. Because in both feed mechanisms (thorium and non-thorium) 
               we continuously added $^{233}$U and the mass of injected 
               $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa 
               decays to $^{233}$U after $\approx$ 27 d). To keep the total 
               fuel mass almost constant, for \textbf{thorium feed mechanism}, 
               the mass of injected thorium must be equal to the mass of 
               extracted FPs and for \textbf{non-thorium feed mechanism}, the 
               mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, 
               reactor-grade Pu, or TRU) must be equal to the mass of 
               extracted FPs. We rewrite the paragraph on page 11 to clarify 
               this point:\\

               \begin{enumerate}
               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected 
               	$^{233}$U $\approx$ mass of extracted Pa and mass of injected 
               	$^{232}$Th $\approx$ mass of extracted FPs to maintain the 
               	total fuel mass constant.
               	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
               \end{enumerate}
               In both feed mechanisms (thorium and non-thorium) we 
               continuously added $^{233}$U and the mass of injected $^{233}$U 
               is equal to the mass of extracted Pa ($^{233}$Pa decays to 
               $^{233}$U after $\approx$ 27 d). To keep the total fuel mass 
               almost constant, for \textbf{thorium feed mechanism}, the mass 
               of injected thorium must be equal to the mass of extracted FPs 
               and for \textbf{non-thorium feed mechanism}, the mass of 
               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
               Pu, or TRU) must be equal to the mass of extracted FPs.

        \end{solution}

        %--------------------------------------------------------------------

        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
        \begin{solution}
                 Thank you for your insightful comment. Phenomenons presented 
                 in Figure 3 have been described in the manuscript.
                 The following paragraph and additional Figure~4 has been added to the manuscript:\\

                 For the Pu+HALEU case, $k_{eff}$ firstly increases during the 
                 first $\approx$ $3$ EFPY and then gradually decreases. This 
                 is due to the conversion of $^{238}$U from HALEU into fissile 
                 plutonium, which often produces the majority of the neutrons 
                 until the transition to Th/$^{233}$U fuel cycle. Figure~4 
                 shows the variation in fissile plutonium isotopes ($^{239}$Pu 
                , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
                 operation. For TRU and reactor-grade Pu, the fissile 
                 plutonium isotopes are gradually depleted, during operating 
                 (the fissile material is dominated by Pu in these cases). For 
                 the HALEU case, the fissile material is dominated by 
                 $^{235}$U, 
                 however, $^{238}$U is converted into fissile plutonium. 
                 Therefore, the mass of fissile plutonium increases during 
                 operating but its value still relatively low. For the 
                 Pu+HALEU case, the mass of the fissile plutonium isotopes 
                 increases 
                 within the first $\approx$ $3$ EFPY and then decreases. The 
                 reactivity from the produced Pu is much greater than the 
                 depletion of the initial reactivity (due to the depletion of 
                 initial fissile isotopes), consequently, $k_{eff}$ increases 
                 during the first $\approx$ $3$ years and then decreases; the 
                 amount of $^{233}$U generated in the Pu+HALEU case is 
                 insufficient to maintain the reactor criticality and 
                 counteract neutron absorption in non-fissile isotopes.\\

                 Figure~3 shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U. Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.

        \end{solution}

        %--------------------------------------------------------------------
        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
        \begin{solution}
                  Thank you for the question. Specifically, Pa is removed from the fuel by chemical reprocessing into the \texttt{Pa-decay tank} to decay and produce $^{233}$U. The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime. Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).

                  The following paragraph and additional Figure~8 has been added to the manuscript:\\

                  The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime. Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
        \end{solution}

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The statement has been removed from the text.
                Moreover, we rewrite the paragraph to clarify this point:\\

                Figure~11 demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Harder neutron spectrum enhance $^{233}$U breeding from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to Figure 10, reasons should be provided to explain why the time achieving Pu solubility limit for the case of TRU is shorter than that of the case of reactor-grade Pu.
        \begin{solution}
                 This has now been clarified in the text.
                 We rewrite the paragraph to clarify this point:\\

                 Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case. The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table 5).

        \end{solution}

        %--------------------------------------------------------------------
        \question It is hard to understand that the neutron spectrum of TRU case at BOL is softer than U-233 case since TRU has a greater amount of thermal neutron absorbers and the fissile material is dominated by Pu which would generate hard neutron spectrum.

        \begin{solution}
                 We appreciate your detailed review.                   
                 The following paragraph has been added to the manuscript:\\

                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx$ $10^2$ b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~14).

        \end{solution}

        %--------------------------------------------------------------------
        \question More details should be provided to explain the radial 
        neutron flux distribution for the cases of Pu reactor-grade and TRU 
        presented in Fig.13 and 14. For both the radial fast and thermal 
        neutron flux change from BOL to EOL, why it is much larger for Pu 
        reactor-grade case compared with TRU case. In addition, the state "In 
        contrast, for the reactor-grade Pu and TRU cases, significant changes 
        are observed for thermal neutron flux in the outer core zone and 
        reactor" is inaccurate, apparently from Figure 14, it can be seen that 
        the Pu reactor-grade (initial) case has a small change in the outer 
        core zone and reflector. 
        \begin{solution}
				Thank you for pointing it out. 
				At the EOL the fuel salt composition is more or less the same 
				(``equilibrium'' composition), hence, both fast and thermal 
				fluxes looks very similar for plutonium and TRU cases.
				At the BOL, this difference is caused by different $^{232}$Th 
				inventory at BOL for Pu reactor-grade (67.5t) and TRU (54.4t). 
				 $^{232}$Th is a strong absorber in the thermal and 
				 intermediate energy range, so, it causes such a significant  
				 difference in the flux: reactor-grade Pu composition provides 
				 much harder spectrum (see Figure~14) at BOL.

                Figure 15 shows 
				significant changes \textbf{during reactor operation} in the 
				outer core zone for the Pu (green line) and almost no changes 
				for the TRU (orange). However, we are agree that thermal flux 
				drop in the reflector is more dramatic for the TRU (initial 
				and equilibrium compositions) and the Pu (equilibrium) cases 
				than for the U-233 case. We think it happens because of 
				non-optimal geometry of the core for the Pu and TRU initial 
				loading.

				The following paragraphs have been added to the manuscript for 
				clarification:\\

				Notably, the neutron flux change for both the fast and thermal 
				energies is much larger for the reactor-grade Pu case than for 
				TRU case (Figures~15 and 16). The reason is the much softer 
				neutron spectrum for the TRU initial loading compared with the 
				reactor-grade Pu as shown in Figure~14: peak thermal neutron 
				flux is about 4 times larger for the TRU case. The neutron 
				spectrum in the SD-TMSR core initially loaded by TRU is much 
				softer than the reactor-grade Pu case and even than the U-233 
				case because $^{232}$Th inventory is the lowest for the TRU 
				case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the reactor-grade  
				Pu and U-233 cases, respectively (Table~5). $^{232}$Th greatly 
				affects the neutron energy spectrum due to its large 
				absorption cross section in the thermal energy range and 
				resonance region between $10^{-5}$ and $10^{-3}$. Finally, 
				when the TRU and the reactor-grade Pu cases reached 
				equilibrium fuel salt composition ($\approx 30$ years after 
				startup), the radial fast and thermal neutron flux 
				distribution became similar in both shape and magnitude.

				More changes in thermal neutron flux shape and magnitude 
				during the reactor operation for the $^{233}$U case are 
				observed in the inner core zone ($R\lesssim150$) than in the 
				outer core zone. In the outer core zone, significant changes 
				during reactor operation are observed for the thermal 
				neutron flux for the reactor-grade Pu case. In contrast, for 
				the TRU case, thermal neutron flux change in the outer core 
				zone is almost negligible. Additionally, 
				Figure~16 shows relatively significant changes in thermal flux 
				leakage from the core for the Pu (equilibrium composition) and 
				TRU (initial and equilibrium composition) cases. The SD-TMSR 
				core design was optimized for $^{233}$U  				
				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
				channel lattice pitch) must be re-optimized for another type 
				of fuel to obtain better neutronics performance.
        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to the FTC for three different cases, reasons should be provided to explain why spectrum softening will positively affects the FTC since generally harder neutron spectrum would benefit FTC.
        \begin{solution}
                Thank you for your insightful comment.  Indeed, the Doppler 
                effect coefficient ($\alpha_{D,F}$) is usually stronger for 
                harder spectrum (see Table~8, ``Fuel salt temperature''), so, 
                spectrum softening negatively affects $\alpha_{D,F}$ (it is 
                decreasing by value but still negative). But we additionally 
                considered the fuel salt density coefficient 
                ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
                (e.g., $+1.09$ $pcm/K$ for the \gls{MSBR}           
                \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
                spectrum benefit $\alpha_{\rho,F}$ \cite{li_effects_2018-1, 
                rykhlevskii2019modeling}. More analysis on this topic:
            Li, X., Ma, Y., Yu, C. et al. Effects of fuel salt composition on 
            fuel salt temperature coefficient (FSTC) for an under-moderated 
            molten salt reactor (MSR). NUCL SCI TECH 29, 110 (2018). 
            https://doi.org/10.1007/s41365-018-0458-1.

	            The following paragraphs have been added to the manuscript:\\

	            The \gls{FTC} is a combination of the Doppler effect 
	            coefficient ($\alpha_{D,F}$) and density coefficient 
	            ($\alpha_{\rho,F}$) and significantly affected by the neutron 
	            spectrum. Li \emph{et al.} reported that 	            
	            $\alpha_{D,F}$ in thermal \gls{MSR} is always negative and 
	            increases by magnitude when spectrum hardening (see Table~8, 
	            first raw). In contrast, $\alpha_{\rho,F}$ is a combination of 
	            moderator-to-fuel volume ratio, absorption cross section of 
	            heavy metal, and the core leakage. When the fuel salt 
	            temperature increases, the salt becomes less dense, 
	            causing a reduction in the fuel concentration and the neutron 
	            spectrum become softer. Such spectrum softening is leading to 
	            a rise in macroscopic absorption cross section of the fissile 
	            isotopes. Moreover, the spectrum softening may leads to 
	            a larger fast fission reaction rate \cite{li_effects_2018-1}. 
	            Thus, spectrum softening positively affects the density 
	            coefficient ($\alpha_{\rho,F}$): $+1.54$ $pcm/K$ and $-1.58$ 
	            $pcm/K$ at the startup and equilibrium for the 
	            reactor-grade Pu case, respectively. More discussion about 
	            effects of fuel salt composition in the \gls{FTC} can be found 
	            elsewhere 
	            \cite{li_effects_2018-1}.
        \end{solution}

        %--------------------------------------------------------------------
        \question It seems unclear why (what is the purpose) to conduct the study of six factor analysis.
        \begin{solution}
                 Thank you for bringing our attention to the point. Usually, 
                 six factor analysis helps to understand reasons of changes in 
                 TCs and control rod worths during reactor operation. But in 
                 this case, considering many various cases, such analysis is 
                 outmoded.           
                  The section has been removed from the manuscript completely.
        \end{solution}

        %--------------------------------------------------------------------
        \question Making the full definition for abbreviation through the whole paper is not necessary, such as SD-TMSR, first time is enough.

        \begin{solution}
                Thank you for the information. The full definition for abbreviation through the whole paper has been removed as requested.
        \end{solution}

        %--------------------------------------------------------------------

\end{questions}
\bibliographystyle{elsarticle-num}
\bibliography{../2019-Scenarios}
\end{document}

%
% End of file `elsarticle-template-num.tex'.

### 2020-12-14 publications/2019-02-presentation/assums.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

\begin{frame}
  \frametitle{Assumptions}

  \begin{itemize}

  \item New Nuclear = Advanced Boiling Water Reactors \cite{rothwell_real_2006}.

  \item Simplistic, conservative assumption about demand growth = +1.7\% per year\cite{noauthor_electricity_2017}.

  \item Nuclear, wind, solar annual growth rate \textbf{limits} based on trends in USA, China, Japan \cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}.

  \item CCS: Available for deployment in 2030, costs reduce by 2050 \cite{kato_energy_2016}.

  \item Offshore and onshore wind capacity limited to theoretical potential (about 450 GW and 200 GW respectively).

  \item H$_2$: Steam reforming available in 2030, photocatalytic conversion in 2050 (assumed cost-competitive with other generation methods) \cite{kato_energy_2016} \cite{acar_comparative_2014}.

  \item Hydropower, geothermal capacity held constant \cite{noauthor_energy_2018}.

  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{Levelized cost projections for solar and wind}
  \begin{figure}[htbp!]
    \begin{center}
      \includegraphics[scale=0.5]{./images/cost}
    \end{center}
          \caption{Levelized cost projections from Lazard \cite{noauthor_lazards_2017} and Acar \& Dincer \cite{acar_comparative_2014}}
    \label{cost}
  \end{figure}
\end{frame}

\begin{frame}
\frametitle{Contribution to peak factor (C2P factor)}
This is a TIMES parameter that defines what fraction of a energy source's capacity is guaranteed to be available during peak demand \cite{loulou_etsap-tiam:_2008}.\\

\begin{tabular}{|c|c|}
\hline 
\textbf{Energy source} & \textbf{C2P factor} \\
\hline 
Fossil fuels & 1 \\
Nuclear power & 1 \\
Solar power & 0.42 \cite{kato_energy_2016}\\
Wind & 0.20 \cite{nguyen_factors_2016}\\
\hline 
\end{tabular}

This factor is reduced for solar and wind with increasing penetration \cite{nguyen_factors_2016}.
\end{frame}

### 2020-12-14 publications/2019-02-presentation/motivation.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

--- 2019-01-24 doc/2019-02-presentation/motivation.tex
@@
 
-   \item \textbf{I$^2$CNER goal:} Reduce emissions by 80\% from 1990 levels by 2050,
+   \item \textbf{I$^2$CNER goal:} Reduce emissions by 80\% from 1990 levels by 2050.
 
@@
 
-   \item Using The Integrated MARKAL-EFOM System (TIMES).
+   \item Using The Integrated MARKAL-EFOM System (TIMES) \cite{loulou_documentation_2005}.
    \end{itemize}
-%        Frames (slides) can have ``blocks.'' 
-%        \begin{block}{This one is about a cat}
-%                A cat in a hat.
-%        \end{block}
-%        \begin{block}{A cat}
-%                In a hat.
-%
-%                \includegraphics[height=0.2\textheight]{./images/catinhat}
-%        \end{block}
 

### 2020-12-14 publications/2019-05-report/2019-05-i2cner-report.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

--- 2019-05-23 doc/2019-05-report/2019-05-i2cner-report.tex
@@
             Kathryn D. \textsc{Huff} % Supervisor's name
+            \vspace{4mm}\\
+            \textit{Co-Principal Investigator}\\
+            James \textsc{Stubbins} % Supervisor's name
+            \vspace{4mm}\\
+            \textit{Contributing Collaborators}\\
+            Kenshi \textsc{Itaoka} \\% Supervisor's name
+            Andrew \textsc{Chapman} \\% Supervisor's name
+            Hadi \textsc{Faradi} \\% Supervisor's name
         \end{flushright}
@@
     \vspace{1cm}
-    \textsc{\LARGE\bfseries UIUC-ARFC-2018-00} \textit{work in progress} % Replace YYYY with the year, NN with report index
+    \textsc{\LARGE\bfseries UIUC-ARFC-2019-02} % Replace YYYY with the year, NN with report index
     \vspace{0.5cm}
@@
     \vspace{0.5cm} % Position the date further down the remaining page
-    {\large\today} % Date, change the \today to a set date if you want to be precise
+    {\large May 29, 2019} % Date, change the \today to a set date if you want to be precise
     \vspace{0.5cm}

### 2020-12-14 publications/2019-09-report/2019-09-i2cner-report.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

\documentclass[14pt,a4paper]{article} %openany
\usepackage[affil-it]{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{rotating}
%\usepackage{bibtex}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{courier}
\usepackage{verbatim}
\usepackage{url}
\usepackage{float}
\usepackage{array}
\usepackage{breakcites}
\usepackage{gensymb}
%\usepackage[backend=biber]{biblatex}
\usepackage{booktabs,tabularx}
\usepackage{listings}
\usepackage{appendix}
\usepackage{cite}
\usepackage{blindtext}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Palatino font
\usepackage{graphicx} % For the logo
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

%\bibliographystyle{numeric}

\begin{document}

%----------------------------------------------------------------------------------------
%    TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
    \newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here

    \center % Centre everything on the page

    %------------------------------------------------
    %    Title
    %------------------------------------------------

    \HRule\\[0.2cm]

     \begin{minipage}{0.4\textwidth}
        \includegraphics[width=\textwidth]{arfc-logo}
        \end{minipage}%
        \begin{minipage}{0.6\textwidth}
        {\begin{flushright}\huge\bfseries Dynamic Transition Analysis With TIMES\end{flushright}}
        {\begin{flushright}\large\textit{I\textsuperscript{2}CNER Project Report}\end{flushright}}

        \end{minipage}

    \vspace{0.2cm}
    \HRule
    \vspace{0.5cm}

    %------------------------------------------------
    %    Author(s)
    %------------------------------------------------

    \begin{minipage}{0.4\textwidth}
        \begin{flushleft}
            \large
            \textit{Author}\\
            Huan \textsc{Yan}\\
        \end{flushleft}
    \end{minipage}
    ~
    \begin{minipage}{0.4\textwidth}
        \begin{flushright}
            \large
            \textit{Principal Investigator}\\
            Kathryn D. \textsc{Huff} % Supervisor's name
        \end{flushright}
    \end{minipage}

    % If you don't want a supervisor, uncomment the two lines below and comment the code above
    %{\large\textit{Author}}\\
    %John \textsc{Smith} % Your name

    %------------------------------------------------
    %    Report Number
    %------------------------------------------------
    \vspace{1cm}
    \textsc{\LARGE\bfseries UIUC-ARFC-2019-09} \textit{work in progress} % Replace YYYY with the year, NN with report index
    \vspace{0.5cm}

    %------------------------------------------------
    %    Date
    %------------------------------------------------

    \vspace{0.5cm} % Position the date further down the remaining page
    {\large\today} % Date, change the \today to a set date if you want to be precise
    \vspace{0.5cm}

%------------------------------------------------
    %    Headings
    %------------------------------------------------

    \textsc{\LARGE Advanced Reactors and Fuel Cycles}\\[0.25cm] % Research Group

    \textsc{\large Dept. of Nuclear, Plasma, \& Radiological Engineering}\\% Department

    \textsc{\large University of Illiois at Urbana-Champaign}\\ % University

    %------------------------------------------------
    %    Logo
    %------------------------------------------------

    \vspace{0.5cm}
    \includegraphics[scale=0.2]{arfc-logo}
    \includegraphics[scale=0.3]{i2cner_logo}
    \includegraphics[scale=0.2]{wpi_logo}
    \includegraphics[scale=0.04]{ku_logo}\\[1cm] % Include a department/university logo - this will require the graphicx package

    %----------------------------------------------------------------------------------------

    %------------------------------------------------
    %   Funding 
    %------------------------------------------------
    % For this section, either use \vfill to fill the space 
    % or insert funding acknowledgement
    \textit{The authors gratefully acknowledge the support of the International Institute for Carbon
Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.}

\end{titlepage}

\section{Introduction}
This report summarizes the summer working progress made on TIMES model for Japan energy transition analysis, including major model changes that facilitates the analysis of the impact of I$^2$CNER technology.

\section{Progress Summary}
\subsection{Availability Factors of Renewable Energy}
TIMES analysis framework allows users to explicitly define the availability factor of processes in each time invervals. With this function, the intermittent feature of renewable energy can be modeled in a relistic way. In this model, solar and wind power are two major intermittent power generation processes considered.\\
There are four time levels in TIMES framework and currently in this model we consider "Annual" and "Daynite", with the later can be arbitrarily divided. To model the availability of solar and wind energy, time-slices where each process is available are created and the availability factors are defined close to 1, while in other time-slices this value is zero. The hierarchy of the time-slices used in this model is shown in Figure \ref{fig:time}. The length of each time-slices is calculated based on the average sunshine duration in Japan and also inferred from the availability factor of wind power. It is assumed that the availability of these two processes are independent. 
The purpose of explicitly modeling availability factor in each time-slice is to enforce the backup power deployment for renewable energy. In reality the supply from solar and wind power is intermittent while the demand is not, large capacity of backup power or energy storage is required to fully exploit the benefit of renewable energy.

\begin{figure}[H]
  \centering
    \includegraphics[width=1\textwidth]{./plot/timeslices.jpg}
  \caption{Hierarchical structure of time slices and corresponding duration }
  \label{fig:time}
\end{figure}

\subsection{Time-dependent Power Demand}
The power demand is strongly time-dependent. Usually the demand is higher in the daytime and summer. It could affect the deployment of energy storage device considering the availability of solar energy follows the similar pattern. So it would be beneficial to make the demand in each time-slice follow a realistic pattern. The time-dependent power demand is enabled after 2017. The percentage of power demand for each period is shown in Figure.\ref{fig:demand}.

\begin{figure}[H]
  \centering
    \includegraphics[width=0.8\textwidth]{./plot/demand.jpg}
  \caption{Percentage of total demand by time periods.}
  \label{fig:demand}
\end{figure}

\subsection{Hydrogen Economy}
To model the effect of development of hydrogen economy, it is required to explicitly consider the cost of different types of fuel. In the current model only two processes involving natural gas and oil are restructured to include fuel cost. Nominal prices of natural gas and oil are assumed and added to the corresponding importing processes. And these costs are removed from the variable costs of all processes that consume natural gas and oil.

\subsubsection{Refinery Process}
Modeling hydrogen production is the first step of modeling the hydrogen economy. Currently the hydrogen mass production is through steam reforming of natural gas. This process results in net reduction of energy and is reflected in efficiency\cite{sheet2005hydrogen}. Note that two types of steam reforming are considered, either with or without CCS. We assumed that without CCS the carbon emission is equivalent to directly using natural gas in electricity production. CCS steam reforming is available after 2030 and the emission is reduced to zero. Note that for simplicity only the fuel cost is considered in the hydrogen production process.
Besides steam reforming, electrolysis and photocatalysis are also considered as alternative for hydrogen production. Electrolysis is modeled as transforming electricity to hydrogen with some lost of energy and zero emission. There are different electrolysis technologies with different efficiency around 80\%\cite{ursua2011hydrogen}. In current model only one electrolysis process with 80\% efficiency is included.
Photocatalysis is an alternative hydrogen production technology that currently under development and is a part fof I$^2$CNER research portfolio. This technology is envisioned as directly using sunlight to split water, as opposed to PV and electrolysis system. In the model this process is modeled in a similar fashion as solar power, with the same definition of availability factor. Currently in the model the cost data associated with photocatalysis is taken from \cite{pinaud2013technical} as variable cost for unit production of hydrogen.
Also, as stated in the following section, to model the transportation sector which requires different types of fuel, the crude oil refinery is also included. Currently the process is directly borrowed from the VEDA demo model and only gasoline is used. We can further include process such as residential heating or diesel car to use other fuels. Or the extra fuels can be handled by export process to bring down the overall system costs.

\subsubsection{Modeling Transportation Sector}
It is recognized that a major part of I$^2$NER technology contributions is through hydrogen economy. Shifting to hydrogen as energy carrier will have significant impact on transportation sector. In fact, according to the technology roadmap published by Ministry of Economy, Trade and Industry, Japan plans to achieve 800,000 hydrogen fuel cell vehicles on road by 2030, with technology advances bring the cost and performance of FCV to the level that rivals conventional vehicle\cite{japan_fc_roadmap}. It is reasonable to model the demand from transportation sectors to see if the results align with the roadmap.
Currently only passenger transportation is modeled. However the freight transportation also accounts for a large part of carbon emission so it needs to be included as well.
The demand for passenger transportation is expressed in the unit of KPassenger*KM/Year and the data is from OECD database\cite{oecd}. Since the population of Japan is unlike to increase in the future it is assumed that the demand will stay constant. For personal sector, only three types of vehicle are considered: traditional gasoline car, electric car and hydrogen fuel cell car. The efficiency can be inferred from fuel economy data. The availability of each vehicle is expressed in the mileage traveled per year. The parameters are summarized in Table.\ref{tab:car}. Compared to electric vehicle, with easier refueling procedures the hydrogen and gasoline car can travel longer distances per year. Due to the technology advance and increased production of fuel cell, it is assumed that the performance and price of electric car and hydrogen car will be brought down to the same level as conventional gasoline car by 2030. Note that in order to preserve the initial conditions the modeling of transportation sector starts from 2017 rather than 2013.

\begin{table}[htbp]
\small
\setlength\tabcolsep{0.1pt}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Vehicle\\  Type\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mileage \\ (km/year)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Passenger\\ /Car\end{tabular} & \begin{tabular}[c]{@{}c@{}}Investment\\  Cost (\$)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Maintenance\\  Cost \\ (\$/year)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Life \\ (year)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Efficiency\\  (MV*km/GWh)\end{tabular} \\ \hline
Gasoline & 12000 & 1.25 & 15500 & 150 & 10 & 1.152 \\ \hline
Electric & 8000 & 1.25 & 20000 & 150 & 10 & 4.548 \\ \hline
\begin{tabular}[c]{@{}c@{}}Hydrogen\\  Fuel Cell\end{tabular} & 12000 & 1.25 & 70000 & 150 & 10 & 5.776 \\ \hline
\end{tabular}
\caption{Personal vehicle parameters.}
\label{tab:car}
\end{table}

\subsection{Storage Process}
Energy storage is a crucial part of power grid due to the intermittent feature of some renewable energy. In current model two storage processes were added to account for the storage of electricity and hydrogen. The capacity of storage process corresponds to the charging rate of the process while the activity corresponds to the amount of energy it can store. The later can be specified using CAP2ACT.
Currently only one type of battery with total storage capacity of 8GWh per GW was added to the model.The efficiency is assumed to be 80\% (20\% of electricity loss from charging-discharging). The estimated cost for battery from EIA is used\cite{outlook2019technical}. This device can be replaced if detailed data are available.
Hydrogen can be stored in specialized high pressure gas tanks. The cost of storage is inferred from the estimated hydrogen storage volume and pressure of such device\cite{james2016hydrogen}.

\subsection{Refining Model Constraints}

\subsubsection{Growth Rate of Capacity}
In the previous model there's no constraint on the growth rate of capacity except for those explicitly defined lumpy investments. However, in reality the increment of new capacity is limited. Without such limit, the model will deploy renewable energy in a unrealistic pace. In current model it is assumed that new capacity (including vehicles) can only grow by 30\% each year. It might be more appropriate to limit the absolute amount of new capacity each year but TIMES doesn't offer a simple way to implement such constraint.
.
\subsubsection{CO2 Emission Constraint}
In the previous model, the CO$_2$ emission limit is linearly interpolated between the current emission and the objective of the final year.
However, after implementation of the growth rate constraint on the new capacity, the model will be infeasible due to the slower deployment of renewable energy and increasing power demand. It is realized that due to the assumption of increasing demand we have to allow for a period of time where emission increases relative to base year level. The detailed analysis will be shown in the following section.

\subsubsection{Constraint on Wind Power Capacity}
The constraint on the max capacity of wind power is replaced by the estimation of the theoretical max capacity in Japan. \cite{heger_wind_2016}

\section{Results}

In this part some results generated by current model will be presented. Two scenarios, with and without new nuclear reactors, are compared. Note that the new installment of reactors is limited to one reactor per year.

\subsection{Capacity and Power Output}
The installed capacity for the two scenarios are shown in Figure.\ref{fig:nonuccap} and Figure.\ref{fig:nuccap}. The exclusion of new nuclear reactor clearly encourages significantly more installation of renewable energy and earlier introduction of hydrogen fuel cell as a main electricity production method. As revealed in section \ref{sec:hydrogen production}, the deployment of hydrogen fuel cells relies on the highly efficient photocatalytic hydrogen production method. Other pathways, such as PV plus electrolysis, are rejected by model probably due to higher cost and lower system efficiency. Interestingly, the model suggests no need for direct electricity storage, except tiny amount of battery installed near 2100. Most energy will be stored in the form of hydrogen (See section \ref{sec:hydrogen production}). 
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nonuc_cap.png}
  \caption{Installed capacity without new reactors.}
  \label{fig:nonuccap}
\end{figure}
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nuc_cap.png}
  \caption{Installed capacity with new reactors.}
  \label{fig:nuccap}
\end{figure}

The actual electricity generated from different sources in the corresponding cases are shown in Figure.\ref{fig:nonucpower} and Figure.\ref{fig:nucpower}. It's clear that without nuclear energy, hydrogen fuel cell will replace natural gas not only as the back-up for solar and wind power, but also as the main electricity generating technology. Even in the case with new nuclear reactors, hydrogen fuel cells will generate comparable amount of electricity, suggesting the overall efficiency of hydrogen economy rivals nuclear energy, if high efficiency hydrogen production method is available.
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nonuc_power.png}
  \caption{Electricity generated without new reactors.}
  \label{fig:nonucpower}
\end{figure}
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nuc_power.png}
  \caption{Electricity generated with new reactors.}
  \label{fig:nucpower}
\end{figure}

\subsection{Carbon Emission}
The carbon emission from electricity generation sector is shown in Figure.\ref{fig:nonucco2} and Figure.\ref{fig:nucco2}. These two figures illustrate the significance of the definition of carbon reduction pathway. Because of the intermittent characteristics of wind and solar power, part of the energy demand must be met by burning fossil fuel. Under the assumption of increasing power demand by 1.7\% each year and maximum growth rate of new capacity by 30\% each year, it's inevitable that the carbon emission will continue to increase until renewable energy reach some critical level. In the case without new nuclear reactor, the carbon emission will continue to increase at a faster pace until it reach the maximum emission around 2040. By then the emission will be increased by 100\% compared the base year level. In both cases the emission by 2050 will be inceased by 50\%. Comparing two emission profiles side by side, it's clear that the higher emission in the no nuclear case is mainly due to burning coal. Note that there's no new coal capacity. All electricity generated from burning coal is from the exisiting capacity.

\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nonuc_co2.png}
  \caption{Carbon emission in electricity generation sector without new reactors.}
  \label{fig:nonucco2}
\end{figure}
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nuc_co2.png}
  \caption{Carbon emission in electricity generation sector with new reactors.}
  \label{fig:nucco2}
\end{figure}

\subsection{Personal Vehicle Composition}

In the current model, the transportation sector is relatively simple compared to electricity sector. The demand is assumed to be constant and only three types of vehicles is modeled. It is assumed that the performance and cost of these vehicles will converge to the same level by 2030. It turns out that there's no impact from the absence of new nuclear reactor when it comes to composition of personal passenger vehicles. The change of number of passenger vehicle is identical in both cases and is shown in Figure.\ref{fig:nonuccar}.
There are two clear transitions in vehicle composition. The conventional gasoline vehicle will firstly be replaced by electric vehicle. All gasoline vehicles will be completely replaced by electric car and hydrogen fuel cell car by mid 40s. After that electric cars start to retire and will be all replaced by hydrogen fuel cell vehicle after 2060.

\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nonuc_car.png}
  \caption{Total number of personal vehicles.}
  \label{fig:nonuccar}
\end{figure}

\subsection{Hydrogen Production and Storage}
\label{sec:hydrogen production}

Finally the means of hydrogen production will be presented. As shown in Figure.\ref{fig:nonuch2} and Figure.\ref{fig:nuch2}, in both scenarios hydrogen production only increase after photocatalysis is available. The cost of photocatalysis is estimated to be 2.0\$ per kilogram of hydrogen\cite{pinaud2013technical}. Clearly before the introduction of advanced production method, there's no economical advantage of switching to hydrogen economy. The overall system efficiency of converting natural gas to hydrogen is lower than converting it to electricity. The PV-electrolysis system is also of low efficiency so the electrolysis process is not activated by the model. Since photocatalysis is modeled in a similar way as solar power, it requires hydrogen storage device to store the hydrogen produced in the morning. In both cases, all hydrogen usage is either coming from production of photocatalysis or hydrogen storage. Under no nuclear assumption the demand for hydrogen is significantly larger.
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nonuc_h2.png}
  \caption{Total hydrogen output by source without new reactors}
  \label{fig:nonuch2}
\end{figure}
\begin{figure}[H]
  \centering
    \includegraphics[width=0.9\textwidth]{./plot/nuc_h2.png}
  \caption{Total hydrogen output by source with new reactors}
  \label{fig:nuch2}
\end{figure}

\section{Future Work}
The current model have included sufficient TIMES functions to model the energy structure transitions. The future work should focus on data validating and adding detailed processes.

\subsection{Fuel Supply Curve}
Compared to the previous model, the fuel cost is now considered separately. The fuel cost is a crucial part in determining the overall cost of system, along with other factors such as efficiency and pathway. In Japan's case all fuels are imported. Detailed price information including exporting countries and corresponding prices can be included based on Japan's fuel import history.

\subsection{Transportation Sector}
The current transportation sector model only considers personal vehicle and three types of vehicle. More details can be added to the transportation part:
\subsubsection{Personal Passenger Transportation}
More vehicle types can be added to the personal passenger sector. In Japan's case it would be appropriate to add hybrid vehicles and plug-in hybrid electric vehicles. The detailed parameters need to be updated according to the estimations from Japan's strategic plan. 
\subsubsection{Public Passenger Transportation}
Modeling of public transportation sector includes railway and bus. The railway is included in current model but the detailed data regarding the cost and capacity of trains are not verified. Besides, share of hydrogen fuel cell buses is also expected to increase in the future\cite{japan_fc_roadmap}.
\subsubsection{Freight Transportation}
Freight transportation also contributes significant carbon emission and should be included in the model.

\subsection{Hydrogen Production and Storage Process}
More hydrogen production technologies can be included, such as steam reforming from other fuels, biological technology, nuclear reactor hydrogen production. Other hydrogen storage technology can also be added, such as chemical storage. Also, the hydrogen storage loss should be added into model. This can be done by define storage efficiency.

\subsection{Residential Sector}
If data is available, modeling residential sector will help evaluating some I$^2$CNER technologies, such as heat pump.

\bibliographystyle{ieeetr}
%\addbibresource{2018-chaube-i2cner-report-sept}
\bibliography{2019-09-i2cner-report}

%\bibliographystyle{plain}

%\printbibliography

\end{document}

### 2020-12-14 publications/2020-03-paper/acks.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

--- 2020-11-26 doc/2020-03-paper/acks.tex
@@
 Prof.
-Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.
+Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I$^2$CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2020-12-14 publications/2020-03-paper/conclusion.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

\section{Conclusion} \label{Conclusion}
%what we did. sum up key technologies, what needs to happen for technologies that are not "key", importance of rapid change/suggested timeline.

We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100. Scenario 1 (Figure \ref{scen1}) proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Figure \ref{scen2}), investing heavily in hydrogen (Figs. \ref{scen3} and \ref{scen5}), or using a combination of both (Figure \ref{scen4}). Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from are results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with or without CCS, new coal, and new oil are not utilised due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonisation outcomes since the commercialisation and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

Mitigating emissions from the industrial and transportation sector presents unique challenges that may affect the amount of emission reduction required from the electricity supply sector to meet Japan's 2030 and 2050 goals. Future work should incorporate holistic assessment of the entire Japanese energy system when exploring energy transition pathways. The assessment of synergistic utilisation of hydrogen in transportation and industry alongside electricity storage and supply is vital for policy decisions. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

%\section{Future work}
%grid resilience - analysis of grid stability of similar mixes at the resolution of minutes. Maybe in TIMES (ugh).
\section{Declaration of Competing Interest}
The authors declare no conflict of interest.

### 2020-12-14 publications/2020-03-paper/discussion.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

--- 2020-11-26 doc/2020-03-paper/discussion.tex
@@
 \ref{scen3} and \ref{scen4}), it appears prudent to invest in hydrogen power.
-As the model uses learning curves for technology prices and our objective function is transition cost, hydrogen technologies are deployed as late as possible in order to minimize costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals.
-Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen power by 2030 at the latest in the absence of new nuclear, or by 2035 with new nuclear.
+As the model uses learning curves for technology prices, and our objective function is transition cost, hydrogen technologies are deployed as late as possible to minimise costs by utilising technologies at their cheapest, while there is still time to deploy them and achieve emission goals.
+Therefore, results indicate that it is imperative that Japan deploy an increasing amount of renewables, including wind power, between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen power by 2030 at the latest in the absence of new nuclear, or by 2035 with new nuclear.
 
@@
 When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios.
-It also reduces the cost of the transition from 3.18 Trillion USD in Scenario 3 to 2.80 Trillion USD in Scenario 4, a difference of 12\% of the system cost.
-The estimated savings in cost and emissions due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines.
-The large emission cuts achieved with the help of nuclear also allow natural gas to continue operating until 2100, while meeting emission goals.
+It also reduces the cost of the transition from 3.18 trillion USD in Scenario 3 to 2.80 trillion USD in Scenario 4, a difference of 12\% of the system cost.
+The estimated savings in cost and emissions due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilising tankers or pipelines.
+The large emission cuts achieved with the help of nuclear also allow natural gas to continue operating until 2100 while meeting emission goals.
 As natural gas is well suited to peaking and load-following, when coupled with flexible fuel cell technologies, it could engender in an extremely stable energy system.
@@
 For the transitioning energy system in Japan, under all scenarios investigated, nuclear plays a key role in reducing emissions.
-A potential strategy for Japan could include the reinvigoration of its nuclear energy sector by restarting existing plants, and if politically feasible, constructing new plants, and investing in advanced reactor research.
-To minimize the environmental impact from life cycle emissions, it is necessary that all existing and any new reactors be operated for a lifetime of 60 years or more at a high capacity factor.
+A potential strategy for Japan could include the reinvigoration of its nuclear energy sector by restarting existing plants and, if politically feasible, constructing new plants and investing in advanced reactor research.
+To minimise the environmental impact from life cycle emissions, it is necessary that all existing and any new reactors be operated for a lifetime of 60 years or more at a high capacity factor.
 Premature decommissioning due to operational problems or lack of public acceptance need to be avoided.
-Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, and increasing public awareness of nuclear's vital role in mitigating carbon emission is key to achieving 2030 and 2050 emission targets.
+Therefore, prioritising reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, and increasing public awareness of nuclear's vital role in mitigating carbon emission are key to achieving 2030 and 2050 emission targets.
 
@@
 Unless large numbers of nuclear power plants are constructed, Japan will need to invest heavily in offshore wind farms by 2030 (Figs.
-\ref{scen1},\ref{scen3}-\ref{scen5}).
+\ref{scen1}, \ref{scen3}-\ref{scen5}).
 If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (Fig.
 \ref{scen1}).
-Under a scenario with a relatively large share of renewables, grid flexibility becomes extremely important.
-Such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive.
-As natural gas is the only extant option for load-following, it is necessary to invest in nuclear or hydrogen to achieve emission cuts while simultaneously keeping natural gas operational for load-following.
-Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand.
-Any fuel cell technology utilized must also be extremely flexible and responsive.
-Since the model prioritizes \gls{SOFC}s over \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.
+In a scenario with a relatively large share of renewables, grid flexibility becomes extremely important.
+Such a scenario requires significant investment in storage technologies and ensuring that all emerging technologies are flexible and responsive.
+As natural gas is the only extant option for prompt load-following, it is necessary to invest in nuclear or hydrogen to achieve emission cuts while simultaneously keeping natural gas operational.
+Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand, and potentially utilise waste heat for hydrogen generation.
+Any fuel cell technology utilised must also be extremely flexible and responsive.
+Since the model prioritises \gls{SOFC}s over \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.
 
@@
 While lithium may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium-ion storage if it is relied upon as the primary storage medium.
-It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals.
+It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing and improve recycling to increase the recovery rate of rare metals.
 The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing.
-If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (Figs.
+If hydrogen storage is available, battery storage serves as a near-term transition technology after which hydrogen storage dominates (Figs.
 \ref{scen3}-\ref{scen5}).
@@
 As seen in the sensitivity analysis results, hydrogen maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector.
-While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s respectively to recreate similar energy mixes.
-Key technologies that aid in decarbonization in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation.
-Steam reforming, with or without CCS, does not get utilized in our simulations due to its high emission coefficient.
+While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s, respectively, to recreate similar energy mixes.
+Key technologies that aid in decarbonisation in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation.
+Steam reforming, with or without CCS, does not get utilised in our simulations due to its high emission coefficient.
 At the lower end of the technology readiness scale, \gls{SOEC}s emerge as tremendously disruptive due to their high efficiency.
-However, their operational lifetimes need to be increased significantly, life cycle emissions must be kept low, and cost-competitiveness with \gls{PEMEC}s must be achieved in order to realize their potential.
+However, their operational lifetimes need to be increased significantly, life cycle emissions must be kept low, and cost-competitiveness with \gls{PEMEC}s must be achieved in order to realise their potential.
 \gls{PWS} plays a marginal role as it is not cost-competitive with electrolysis.
-From the simulation output data, the investment cost of \gls{SOFC}s emerges as a critical parameter.
+From the sensitivity analysis results, the investment cost of \gls{SOFC}s emerges as a critical parameter.
 Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible.
-However, low response times and high availability are two other key factors that are implicit in our assumptions.
-If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and closer to commercialization.
+Low response times and high availability of fuel cells and electrolysers are two other desirable traits that are implicit in our assumptions.
+If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible.
+Hence, our results show that the more flexible and responsive hydrogen technologies will be dominant in a renewable energy-based transition.
 In Scenarios 3 and 4, solar, wind, and nuclear are used to generate hydrogen.
-Therefore it would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants.
-Waste heat from nuclear could also be used to produce hydrogen, and would reduce reliance on renewables for electrolysis.
-As mentioned previously, more flexible and responsive fuel cells and electrolyzers are likely to be the dominant technology in such a system.
+It would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants.
+The use of waste heat from nuclear to produce hydrogen would reduce reliance on renewables for electrolysis, and mitigate intermittency-related grid-stability issues.
 
 %ccs
-CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen.
-Its share is found to be largely insensitive to its investment costs as evidenced by the sensitivity analysis.
-This is mainly due to its large emission coefficient.
-Marginal gains are expected in its penetration if the efficiency of CCS is increased to reduce its direct emissions.
-Reducing indirect emissions is likely to have a greater impact.
-This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.
+CCS plays a small role in our base case scenarios as a transitional technology.
+Despite being cheaper than hydrogen, its share is found to be largely insensitive to its investment costs as evidenced by the sensitivity analysis.
+This is mainly due to the large emission coefficient of \gls{CCS} with natural gas.
+Marginal gains are expected in \gls{CCS} penetration if the capture efficiency is increased to reduce its direct emissions.
+Reducing indirect emissions is likely to have a greater impact on \gls{CCS} penetration.
+This could be achieved by increased electrification of the industrial sector and the use of hydrogen to produce steel.
 
-Although our analysis relies on optimal solutions and scenarios and is technologically agnostic, policy makers in Japan will face difficult future decisions as to the long-term nature of the low-carbon energy system.
-One approach could be to prioritize nuclear energy and to reap the benefits of inexpensive, low-carbon energy, at the cost of achieving consensus from the public for its long-term deployment and use.
-Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilizing hydrogen as a storage medium to engender significant deployment of renewable energy.
+Although our analysis relies on optimal solutions and scenarios and is technologically agnostic, policy makers in Japan will face difficult decisions as to the long-term nature of the low-carbon energy system.
+One approach could prioritise nuclear energy and reap the benefits of inexpensive, low-carbon energy at the cost of achieving consensus from the public for its long-term deployment and use.
+Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilising hydrogen as a storage medium to engender significant deployment of renewable energy.
 The hydrogen pathway also provides more energy security, obviating the use of coal and oil and mitigating the use of natural gas.
 As social opposition to nuclear is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely.
-However, our results indicate that these two approaches are not mutually exclusive.
+Nonetheless, our results indicate that these two approaches are not mutually exclusive.
 The cost of transitioning to a hydrogen energy system without deploying any new nuclear is much higher than that of any of the nuclear-inclusive options.
 Deploying nuclear in tandem with hydrogen provides a cost-effective compromise.
-An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as at the time of writing, the timely success of the Japanese hydrogen plan is far from certain.
-At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a "bridging" option, providing a low-carbon pathway in the short term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for longer-term deployment timelines.
+An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain.
+At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a "bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment.
 If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets.

### 2020-12-14 publications/2020-03-paper/highlights/highlights.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

\documentclass[review]{elsarticle}

\usepackage{lineno}
\usepackage{xspace}
\modulolinenumbers[5]

\journal{Annals of Nuclear Energy}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%%%% packages and definitions (optional)
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{hhline}
\usepackage{amsmath}

%\usepackage[demo]{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{x}{>{\hsize=.25\hsize}X}

\graphicspath{ {figures/} }

% tikz %
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

% hyperref %
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{frontmatter}
\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Five initial fissile loadings: HALEU, Pu mixed with HALEU, reactor-grade Pu, TRU, and $^{233}$U have been studied for transitioning to the thorium fuel cycle in the SD-TMSR.
	\item The MSR burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the SD-TMSR.
	\item The dynamics of $k_{eff}$, major isotopes mass, and essential safety parameters have been investigated.
	\item The neutron energy spectrum shift during the reactor operation was calculated.
	\item Temperature coefficient of reactivity evolution during SD-TMSR operation are investigated.
\end{itemize}
\end{document}

### 2020-12-14 publications/2020-03-paper/revisions/acros.tex
renamed directories
Former-commit-id: 30fefb4f04f1f6036403e1f5e73c35ff385622ad
Former-commit-id: a33aa4986ff995e14c75db32ec518ae09d9b7412

\newacronym{<++>}{<++>}{<++>}
\newacronym{HALEU}{HALEU}{High Assay Low Enriched Uranium}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{TRU}{TRU}{transuranic elements}
\newacronym{LEU}{LEU}{low-enriched uranium}
\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{ANS}{ANS}{American Nuclear Society}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{BR}{BR}{Breeding Ratio}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CAS}{CAS}{Chinese Academy of Sciences} 
\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDF}{EDF}{Électricité de France}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EFPY}{EFPY}{effective full-power years}
\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EPR}{EPR}{European Pressurized Reactors}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{EU}{EU}{European Union}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{FP}{FP}{Fission Product}
\newacronym{FTC}{FTC}{Fuel Temperature Coefficient}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GIF}{GIF}{Generation IV International Forum}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{IHX}{IHX}{Intermediate Heat Exchanger}
\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
\newacronym{IRP}{IRP}{Integrated Research Project}
\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
\newacronym{ISRG}{ISRG}{Independent Student Research Group}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOSART}{MOSART}{MOlten Salt Actinide Recycler and Transmuter}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MPI}{MPI}{Message Passing Interface}
\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{MTC}{MTC}{Moderator Temperature Coefficient}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NPP}{NPP}{Nuclear Power Plant}
\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWF}{NWF}{Nuclear Waste Fund}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PRIS}{PRIS}{Power Reactor Information System}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PWR}{PWR}{Pressurized Water Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{REE}{REE}{rare earth element}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{ROD}{ROD}{Reactor Optimum Design}
\newacronym{SD-TMSR}{SD-TMSR}{Single-fluid Double-zone Thorium-based Molten Salt Reactor}	
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}
\newacronym{CNRS}{CNRS}{National Center for Scientific Research}		
\newacronym{CRAM}{CRAM}{Chebyshev Rational Approximation Method}
\newacronym{DT}{DT}{Doubling Time}		
\newacronym{Euratom}{Euratom}{European Atomic Energy Community}
\newacronym{FPs}{FPs}{fission products} 
\newacronym{HM}{HM}{heavy metal}
\newacronym{MAs}{MAs}{Minor Actinides}
\newacronym{OpenMP}{OpenMP}{Open Multi-Processing}
\newacronym{TCR}{TCR}{Temperature Coefficient of Reactivity}
\newacronym{3D}{3D}{Three Dimensions}			
\newacronym{TS-MSR}{TS-MSR}{Thermal-Spectrum Molten Salt Reactor}
\newacronym{FS-MSR}{FS-MSR}{Fast-Spectrum Molten Salt Reactor}
\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}
\newacronym{TMSR}{TMSR}{Thorium-based Molten Salt Reactor}

### 2021-01-13 publications/2020-03-paper/cover-letter/cover_letter.tex
adds cover letter draft
Former-commit-id: 51cf05d2f0977e5649586ad8d0ae4866b0007132
Former-commit-id: 8ed31854fbef04f7ca7e0967c806c5db6d33e6ae

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{letter} % Default font size of the document, change to 10pt to fit more text
%\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\usepackage[left=1.25in,right=1.25in,top=1in,bottom=0.5in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
%\usepackage{everypage}
%\usepackage{blindtext}
%\usepackage{eso-pic,graphicx}
 \begin{document}
%\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

%----------------------------------------------------------------------------------------
%       ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Professor Jinyue Yan\\
Editor-in-Chief, Applied Energy.}

%----------------------------------------------------------------------------------------
%       YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\address{Anshuman Chaube\\
achaube2@illinois.edu\\
226 Talbot Laboratory\\
MC-234\\
104 S. Wright Street\\
Urbana, IL 61801}

%----------------------------------------------------------------------------------------
%       LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Professor Yan,}

Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals for Japan'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff, 
are submitting for exclusive consideration for publication as a research 
article in Progress in Nuclear Energy.

Our work uses TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies. This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs. We assess novel technologies’ impact using a rigorous sensitivity analysis.

Our results approach true carbon-neutrality with the incorporation of lifecycle emissions. We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen. Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy with continued emission reduction until 2100. Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.

Our work will offer a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers. Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.

We confirm that we have no conflicts of interest to disclose, and that this work has been reviewed by native speakers of English (Chapman, Stubbins, and Huff). I acknowledge my availability to review 3 or more articles for Applied Energy. Please direct your correspondence apropos this manuscript to me at achaube2@illinois.edu.

\closing{Sincere regards,
%\includegraphics[height=2cm]{signature}\\
\fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
Eng.\\University of Illinois\\achaube2@illinois.edu}
}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2021-01-15 publications/2020-03-paper/abstract.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

--- 2020-12-09 doc/2020-03-paper/abstract.tex
@@
 We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model.
-Key features of our simulations include the incorporation of novel technologies, like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emission and learning curves for technology costs and emission coefficients.
+Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impact up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients.
 Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security.

### 2021-01-15 publications/2020-03-paper/acks.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

@@
+\section{CRediT Statement}
+
+The authors contributed to this work as described below.
+
+\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.
+
+\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.
+
+\textbf{Akari Minami}: data curation, validation.
+
+\textbf{James Stubbins}: writing - review and editing, supervision.
+
+\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
+
 \section{Acknowledgments}
@@
 The author(s) gratefully acknowledge the support of the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology.
-We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.
 
-The authors contributed to this work as described below.
-
-Anshuman Chaube designed simulation models, conducted sensitivity analysis, and wrote the original draft of the paper.
-
-Andrew Chapman conceived and contributed to conception of the simulations, designed simulation models, and wrote the original draft of the paper.
-
-Akari Minami translated data from Japanese to English, and assisted with testing and performing simulations.
-
-James Stubbins supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
-
-Kathryn D.
-Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
 Prof.
 Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I$^2$CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.
+
+We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.

### 2021-01-15 publications/2020-03-paper/discussion.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

@@
 %nuclear
-The scenario with the largest nuclear deployment, Scenario 2, also has the lowest transition cost.
+The scenario with the maximum nuclear deployment, Scenario 2, also has the lowest transition cost.
 When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios.
@@
 %batteries
-Lithium-ion is the preferred storage medium in the absence of hydrogen.
+Lithium-ion batteries are the preferred storage medium in the absence of hydrogen.
 However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts.
@@
 %hydrogen - key players, key parameters, path forward?
-After nuclear, hydrogen power emerges as the second most efficacious technology for achieving 2050 emission goals.
+After nuclear, hydrogen power emerges as the second most effective technology for achieving 2050 emission goals.
 As seen in the sensitivity analysis results, hydrogen maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector.
 While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s, respectively, to recreate similar energy mixes.
-Key technologies that aid in decarbonisation in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation.
+Key technologies that aid in decarbonisation in our simulations are \gls{SOFC}s and \gls{PEMEC}s.
 Steam reforming, with or without CCS, does not get utilised in our simulations due to its high emission coefficient.
@@
 
-Although our analysis relies on optimal solutions and scenarios and is technologically agnostic, policy makers in Japan will face difficult decisions as to the long-term nature of the low-carbon energy system.
-One approach could prioritise nuclear energy and reap the benefits of inexpensive, low-carbon energy at the cost of achieving consensus from the public for its long-term deployment and use.
+Our policy-agnostic analysis relies on optimal solutions and scenarios.
+However, policy makers in Japan are considering two alternatives as to the long-term nature of the low-carbon energy system.
+One approach could prioritise nuclear energy and reap the benefits of inexpensive, low-carbon energy if consensus from the public for its long-term deployment and use can be achieved.
 Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilising hydrogen as a storage medium to engender significant deployment of renewable energy.
-The hydrogen pathway also provides more energy security, obviating the use of coal and oil and mitigating the use of natural gas.
-As social opposition to nuclear is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely.
+The hydrogen pathway also provides more energy security.
+As social opposition to nuclear power is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely.
 Nonetheless, our results indicate that these two approaches are not mutually exclusive.
@@
 An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain.
-At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a "bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment.
+At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a ``bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment.
 If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets.

### 2021-01-15 publications/2020-03-paper/introduction.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition in 2018 \cite{noauthor_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand. Additionally, we assess the significance of key economic parameters of emerging technologies through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2021-01-15 publications/2020-03-paper/litreview.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

--- 2020-12-10 doc/2020-03-paper/litreview.tex
@@
 \section{Background and literature review} \label{litreview}
-The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modelling approaches.
+The Paris Agreement commits individual nations to significant carbon reduction over time through the \gls{INDC} mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the ``development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
+Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below.
 Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
 Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al.
-explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan.
-Their study identified that \gls{P2G} can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}.
+explored the role of hydrogen as a storage medium through power-to-gas approaches in Kyushu, Japan.
+Their study identified that power-to-gas can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}.
 Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
@@
 However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.
+
 Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future.
@@
 Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}.
-Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \glspl{FCV} and power generation, via both mixed and direct combustion.
+Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion.
 Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}.
@@
 
-The model and the approach proposed in this research are unique, as they build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
+The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
 This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
-Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities.
+Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality.
 This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels.

### 2021-01-15 publications/2020-03-paper/methods.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9

--- 2020-12-10 doc/2020-03-paper/methods.tex
@@
 
-While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population.
+While Japanese electricity demand is expected to grow in the near future  \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's ageing population.
 However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
-Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, with the demand eventually plateauing due to the aforementioned expected demographic changes.
-The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
+Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes.
+The model captures the initial condition of the post-Fukushima Japanese electricity supply system using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
 Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100.
-The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology, as applicable.
-The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}.
+We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology.
+Using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}, the daily and seasonal variability of renewables is incorporated.
 The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.
@@
 Along with these two technology groups, we also explore the potential impact of nuclear energy.
-Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions and a high capacity factor.
+Nuclear power has significant advantages over renewables including long operational lifetimes, extremely low life-cycle emissions, and high capacity factors.
 However, nuclear power faces extremely low public acceptance in Japan after the Fukushima-Daiichi accident, therefore its future in Japan is highly uncertain.
@@
 Prices and projections for fossil fuels and nuclear fuel are incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
-Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
-These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}.
+Learning curves for costs and life-cycle emissions are compiled from existing data (Table \ref{eco}) based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
+These learning curves are modelled as piecewise linear functions interpolated between the available data points, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}.
 Capacity limits of renewables and \gls{PWS} are based on their land-use requirements.
@@
 The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}.
-The reactor size assumed in this study is 1165 MWe.
+The reactor size assumed in this study is 1165 MWe, based on Watts-Bar Unit 2 \cite{iaea_pris_nodate-1}.
 Due to a projected increase in the share of renewables, nuclear power plants must be able to load-follow to a certain extent, which is approximated in our model based on French reactors' range of capacity factors.
@@
 We assume that these technologies, some of which are already commercialised or close to commercialisation, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
-Therefore, they could be deployed as rapidly as conventional solar photovoltaic.
+Therefore, they could be deployed as rapidly as conventional solar photovoltaic cells.
 
@@
 Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
-For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
 Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
@@
 %variables, sampling approach, median, range, which variables, which base case scenario, why
-While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, many parameters, such as the investment cost, life cycle emissions, and lifetimes, are highly uncertain for novel technologies like \gls{CCS} and hydrogen generation and conversion technologies.
+While the aforementioned scenarios identify potential pathways that are likely to result in deep emission cuts, many parameters, such as the investment cost, life cycle emissions, and lifetimes, are highly uncertain for novel technologies like \gls{CCS} and hydrogen generation and conversion technologies.
 Therefore, our sensitivity analysis is focused on investigating the impact of such parameters (Table \ref{sa-vars}).
-We analyse the sensitivity of the share of each of these technologies in the electricity-generation mix, and of the system transition cost with respect to these variables.
+We analyse the sensitivity of the share of each of these technologies in the electricity-generation mix and of the system transition cost with respect to these variables.
 
-While there is significant uncertainty in the investment cost of nuclear power plants, it varies for individual plants and not for the technology as a whole.
+While there is significant uncertainty in the investment cost of nuclear power plants \cite{lovering_historical_2016}, it varies for individual plants and not for the technology as a whole.
 Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions.

### 2021-01-15 publications/2020-03-paper/highlights/highlights.tex
adds highlights
Former-commit-id: d81cc9b7b4e78b95d3602c15c5d80f5297fae011
Former-commit-id: d4cf835837583cac16171310086eda753fa38615

@@
 
-\journal{Annals of Nuclear Energy}
+\journal{Applied Energy}
 
@@
 \begin{frontmatter}
-\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
+\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
 \end{frontmatter}
@@
 \begin{itemize}
-	\item Five initial fissile loadings: HALEU, Pu mixed with HALEU, reactor-grade Pu, TRU, and $^{233}$U have been studied for transitioning to the thorium fuel cycle in the SD-TMSR.
-	\item The MSR burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the SD-TMSR.
-	\item The dynamics of $k_{eff}$, major isotopes mass, and essential safety parameters have been investigated.
-	\item The neutron energy spectrum shift during the reactor operation was calculated.
-	\item Temperature coefficient of reactivity evolution during SD-TMSR operation are investigated.
+	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
+	\item Includes long-term assessment up to 2100 
+	\item Dynamic simulations use learning curves for cost and emissions..
+	\item Sensitivity analysis identifies key parameters and thresholds.
 \end{itemize}

### 2021-01-15 publications/2020-03-paper/Appendix.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

--- 2020-12-10 doc/2020-03-paper/Appendix.tex
@@
 Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
-Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
+Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019,oliveira_environmental_2015} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\

### 2021-01-15 publications/2020-03-paper/methods.tex
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+	\begin{tabularx}{0.4\textwidth}{p{0.15\textwidth} p{0.25\textwidth}}
 		\hline
-\textbf{Year} & \textbf{Annual demand increase} \\
+\textbf{Year} & \textbf{Annual demand} \\
+ & \textbf{increase} \\
 \hline
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.22\textwidth}p{0.16\textwidth} p{0.4\textwidth}}
+	\begin{tabularx}{0.6\textwidth}{p{0.05\textwidth} p{0.2\textwidth}p{0.05\textwidth} p{0.3\textwidth}}
 		\hline
-\textbf{Year} & \textbf{Emission limit} & \textbf{Base year} & \textbf{Reduction from base year} \\
+\textbf{Year} & \textbf{Emission limit} & \textbf{Base} & \textbf{Reduction} \\
+ & & \textbf{year} & \textbf{from base year} \\
 \hline
@@
 \begin{table}[!ht]
-	\caption{Electricity supply transition scenario definition.}
+	\caption{Electricity supply transition scenario definition based on enabled technologies.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.25\textwidth} p{0.25\textwidth} p{0.35\textwidth}}
+	\begin{tabularx}{0.65\textwidth}{p{0.1\textwidth} p{0.18\textwidth} p{0.15\textwidth} p{0.18\textwidth}}
 \hline 
-\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} & \textbf{Nascent tech.}\\
-                 & \textbf{enabled} & \textbf{enabled} & \textbf{enabled}\\
+\textbf{Scenario}& \textbf{Emerging} & \textbf{New} & \textbf{Nascent}\\
+ & \textbf{tech.} & \textbf{nuclear} & \textbf{tech.}\\
+
+%                 & \textbf{enabled} & \textbf{enabled} & \textbf{enabled}\\
                   \hline
-%1               &   \xmark       &      \greencheck     \\ 
-%2               & \xmark       &         \xmark       \\ 
-%3               &   \greencheck     &      \greencheck     \\ 
-%4               &   \greencheck     &         \xmark       \\
+%1               &   \xmark       &      \xmark     &   \xmark     \\ 
+%2               &   \xmark       &      \greencheck     &   \xmark     \\ 
+%3               &   \greencheck       &      \xmark     &   \xmark     \\ 
+%4               &   \greencheck       &      \greencheck     &   \xmark     \\ 
+%5               &   \greencheck       &      \xmark     &   \greencheck     \\ 
 1               &  No       &         No     &     No  \\ 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{1.1\textwidth}{p{0.3\textwidth} p{0.25\textwidth} p{0.25\textwidth}p{0.3\textwidth}}
+	\begin{tabularx}{0.9\textwidth}{p{0.3\textwidth} p{0.15\textwidth} p{0.15\textwidth}p{0.3\textwidth}}
 \hline 

### 2021-01-15 publications/2020-03-paper/results.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

--- 2020-12-10 doc/2020-03-paper/results.tex
@@
 
-\begin{figure}[H] 
-\centering
-%\vspace*{-3cm}
-%\hspace{-3cm}
-\includegraphics[scale=0.5]{figures/conv_nonuc}
-\caption{Scenario 1 results (conventional technologies without new nuclear).
-The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
-\label{scen1}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-%\vspace*{-3cm}
-\includegraphics[scale=0.5]{figures/conv_nuc}
-\caption{Scenario 2 results (conventional technologies with new nuclear).
-The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
-\label{scen2}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-%\vspace*{-3cm}
-\includegraphics[scale=0.5]{figures/newtechs_nonuc}
-\caption{Scenario 3 results (emerging technologies without new nuclear).
-The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
-\label{scen3}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-%\vspace*{-3cm}
-\includegraphics[scale=0.5]{figures/newtechs_nuc}
-\caption{Scenario 4 results (emerging technologies with new nuclear).
-The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
-\label{scen4}
-\end{figure}
-
-\begin{figure}[H] 
-\centering
-%\vspace*{-3cm}
-\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
-\caption{Scenario 5 results (emerging technologies and nascent hydrogen technologies without new nuclear).
-The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
-\label{scen5}
-\end{figure}
-
-The results of each scenario (Table \ref{scen-table} for scenario definitions) are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology.
+The transition simulations' results are shown in Figures \ref{scen1}-\ref{scen5}, and summarised in Table \ref{tab:results_summary} (see Table \ref{scen-table} for scenario definitions).
+The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology.
 The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user.
@@
 The third plot details the sources of direct and averaged life-cycle emissions from each source.
+
+\begin{table}[!ht]
+	\caption{Summary of decarbonisation simulations' results.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.2\textwidth}}
+		\hline
+\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
+ & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD 2015) \\
+ &  & \textbf{emission} & \textbf{emission} & \textbf{2050-2100} &  \\
+ &  & \textbf{goals} & \textbf{goals} & &  \\
+\hline
+1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
+2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
+3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
+4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
+5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
+\hline 
+	\end{tabularx}
+\label{tab:results_summary}
+\end{table}
 
@@
 
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+%\hspace{-3cm}
+\includegraphics[scale=0.5]{figures/conv_nonuc}
+\caption{Scenario 1 results (conventional technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
+\label{scen1}
+\end{figure}
+
 With the availability of new nuclear reactors in Scenario 2 (Figure \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100.
@@
 The total transition cost of this scenario is the lowest, at \textbf{2.66 trillion USD.}
+
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/conv_nuc}
+\caption{Scenario 2 results (conventional technologies with new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
+\label{scen2}
+\end{figure}
 
@@
 
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/newtechs_nonuc}
+\caption{Scenario 3 results (emerging technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
+\label{scen3}
+\end{figure}
+
 Deploying both emerging technologies with new nuclear reactors (Figure \ref{scen4}) results in rapid decarbonisation.
@@
 
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/newtechs_nuc}
+\caption{Scenario 4 results (emerging technologies with new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
+\label{scen4}
+\end{figure}
+
 The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}).
-However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055.
+However, \gls{SOEC}s rapidly replace a large fraction of ageing \gls{PEMEC}s, starting from 2055.
 Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost.
@@
 
+\begin{figure}[H] 
+\centering
+%\vspace*{-3cm}
+\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
+\caption{Scenario 5 results (emerging technologies and nascent hydrogen technologies without new nuclear).
+The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
+\label{scen5}
+\end{figure}
+
 \subsection{Sensitivity analysis}
+
+Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figs.
+\ref{pws}-\ref{sa-useless}).
+The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Figure \ref{satechs-smol}).
+This follows from the large share of \gls{SOFC}s, as they are the most important low-carbon technology for storing renewable power, yet they are the most expensive technology available to the model.
+In the absence of new nuclear deployments, \glspl{SOFC} are irreplaceable, and their share is largely fixed.
+In analysing the sensitivity of the output of electricity generation technologies (Figure \ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs.
+However, the output of \gls{CCS} with natural gas was also most strongly correlated with the investment cost of \gls{SOFC}s, rather than the investment cost of CCS gas itself.
+The share of \gls{CCS} with natural gas is also relatively small (indicated by the y-values in Figure \ref{satechs-smol}), about 2-3\%.
+This is because CCS gas deployment increases only marginally as fuel cells deployment decreases due to increasing fuel cell cost.
+Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonisation alternatives are uneconomical.
+This is due to the large life-cycle and direct emissions of CCS gas compared to renewables and hydrogen technologies.
 
@@
 
-Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figs.
-\ref{pws}-\ref{sa-useless}).
-The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Figure \ref{satechs-smol}).
-This follows from the large share of \gls{SOFC}s, as they are the most important low-carbon technology for storing renewable power, yet they are the most expensive technology available to the model.
-In the absence of new nuclear deployments, \glspl{SOFC} are irreplaceable, and their share is largely fixed.
-In analysing the sensitivity of the output of electricity generation technologies (Figure \ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs.
-However, the output of \gls{CCS} with natural gas was also most strongly correlated with the investment cost of \gls{SOFC}s, rather than the investment cost of CCS gas itself.
-The share of \gls{CCS} with natural gas is also relatively small (indicated by the y-values in Figure \ref{satechs-smol}), about 2-3\%.
-This is because CCS gas deployment increases only marginally as fuel cells deployment decreases due to increasing fuel cell cost.
-Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonisation alternatives are uneconomical.
-This is due to the large life-cycle and direct emissions of CCS gas compared to renewables and hydrogen technologies.
-
 Remaining results indicate that \gls{PEMFC}s are never utilised because of their low efficiency compared to \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient (Figure \ref{sa-useless}).

### 2021-01-19 publications/2020-03-paper/introduction.tex
spell check, references corrected
Former-commit-id: 7437cf8ebb93536124042c19b07afd5e525608af
Former-commit-id: eb7ea29474615346eeb1e9bba398b6519a449cb7

@@
 
-Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition in 2018 \cite{noauthor_japans_2018}.
+Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition in 2018 \cite{meti_japans_2018}.
 The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
@@
 For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}.
-The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
+The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.
 

### 2021-01-19 publications/2020-03-paper/litreview.tex
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69
spell check, references corrected
Former-commit-id: 7437cf8ebb93536124042c19b07afd5e525608af
Former-commit-id: eb7ea29474615346eeb1e9bba398b6519a449cb7

@@
 Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
-Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid aging, Kuriyama et al.
+Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid ageing, Kuriyama et al.
 suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}.
@@
 From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}.
-Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
+Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}.
 The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.

### 2021-01-19 publications/2020-03-paper/abstract.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 
-We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model.
+We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region model in \gls{TIMES}.
 Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impact up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients.

### 2021-01-19 publications/2020-03-paper/acks.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 
-We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.
+We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing manuscript drafts.

### 2021-01-19 publications/2020-03-paper/introduction.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
-However, these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
+However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
 Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
 
-Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition in 2018 \cite{meti_japans_2018}.
-The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
+Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
 The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid).
@@
 
-This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework.
+This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using the \gls{TIMES} framework.
 Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand.

### 2021-01-19 publications/2020-03-paper/litreview.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below.
-Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
+Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al.
+found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}.
 Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al.
@@
 Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas.
-Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}.
+Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}.
 Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}.
 Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion.
-Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}.
+Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}.
 From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}.

### 2021-01-19 publications/2020-03-paper/methods.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 \gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}.
-The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types.
+The generation, refinement, supply, storage, and trade of energy commodities are modelled across multiple sectors and multiple regions using a wide variety of in-built commodity and process types.
 Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.
@@
 \hline
-\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% of mean. \\                  
-\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% of mean.\\                  
-\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% of mean.\\                  
-\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
-\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
-\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% of mean.\\                  
-\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% of mean.\\
+\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\%. \\                  
+\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\%.\\                  
+\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\%.\\                  
+\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\%.\\                  
+\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\%.\\                  
+\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\%.\\                  
+\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\%.\\
 \gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  

### 2021-01-19 publications/2020-03-paper/results.tex
table width fix
Former-commit-id: 48bd34588605351dc3be18710626a4a0bd8db887
Former-commit-id: 2a45e7c4708f82a2238db5736b4c5c97a327f318
spell check, references corrected
Former-commit-id: 7437cf8ebb93536124042c19b07afd5e525608af
Former-commit-id: eb7ea29474615346eeb1e9bba398b6519a449cb7
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

@@
 
-\begin{table}[!ht]
-	\caption{Summary of decarbonisation simulations' results.}
-	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.2\textwidth}}
-		\hline
-\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
- & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD 2015) \\
- &  & \textbf{emission} & \textbf{emission} & \textbf{2050-2100} &  \\
- &  & \textbf{goals} & \textbf{goals} & &  \\
-\hline
-1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
-2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
-3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
-4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
-5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
-\hline 
-	\end{tabularx}
-\label{tab:results_summary}
-\end{table}
-
 In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt.
@@
 The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
-The total cost of this transition is \textbf{3.51 trillion USD} (in 2015 USD).
+The total cost of this transition is \textbf{3.51 trillion USD}.
 
-\begin{figure}[H] 
+\begin{figure}[b!] 
 \centering
@@
 
-\begin{figure}[H] 
+\begin{figure}[b!] 
 \centering
@@
 \end{figure}
+
+\begin{table}[!ht]
+	\caption{Summary of decarbonisation simulations' results.}
+	\vspace{0.1in}
+	\begin{tabularx}{0.9\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
+		\hline
+\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
+ & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD) \\
+ &  & \textbf{emission} & \textbf{emission} & \textbf{2050-} &  \\
+ &  & \textbf{goals} & \textbf{goals} & \textbf{2100} &  \\
+\hline
+1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
+2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
+3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
+4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
+5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
+\hline 
+	\end{tabularx}
+\label{tab:results_summary}
+\end{table}
 

### 2021-01-20 publications/2020-03-paper/cover-letter/cover_letter.tex
fixes logo issue
Former-commit-id: cd00320ab496dbea42ee18fb50a9d124186caa5e
Former-commit-id: afe3ac4ca7c6845b83e75aaacd583a6e6051f90c
signature correction
Former-commit-id: b3d6bd2e31e43a454901d072ae65a568eca85a4a
Former-commit-id: 30dac75a5b42023debe49869fffc6bd361c99cf4
adjusts table widths
Former-commit-id: 93ef12ba16bfcc32ee9d78c4b2209be9034e2c6c
Former-commit-id: 182aa7c602d60e40d5de034df1c57fceae38efe1

@@
 %\usepackage{blindtext}
-%\usepackage{eso-pic,graphicx}
+\usepackage{eso-pic}
+\usepackage{graphicx}
+
  \begin{document}
-%\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}
+%\ClearShipoutPicture
+\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}
 
@@
 
-Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals for Japan'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff,
+Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff
 are submitting for exclusive consideration for publication as a research 
-article in Progress in Nuclear Energy.
+article in Applied Energy.
 
-Our work uses TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies.
+Our work uses the TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies.
 This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs.
-We assess novel technologies’ impact using a rigorous sensitivity analysis.
+We assess emerging technologies’ impact using a rigorous sensitivity analysis.
 
@@
 We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen.
-Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy with continued emission reduction until 2100.
+Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy.
 Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.
 
-Our work will offer a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers.
+Our work offers a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers.
 Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.
@@
 
-\closing{Sincere regards,
+\closing{Sincere regards,\\
 %\includegraphics[height=2cm]{signature}\\
 \fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
-Eng.\\University of Illinois\\achaube2@illinois.edu}
+Eng.\\University of Illinois.\\achaube2@illinois.edu}
 }

### 2021-01-22 publications/2020-03-paper/highlights/highlights.tex
chapman corrections
Former-commit-id: 34ff7f9fee444823f431591fdb1c5c7bc67cbaa8
Former-commit-id: 2a9e415a4bda7c1d79adfd494a80e1a73e133505

@@
 \begin{itemize}
-	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
-	\item Includes long-term assessment up to 2100 
-	\item Dynamic simulations use learning curves for cost and emissions..
-	\item Sensitivity analysis identifies key parameters and thresholds.
+	\item Identifies potential transition pathways for Japan using multiple technologies.
+	\item Simulations to the year 2100 identify post-2050 impacts of a stabilizing transition. 
+	\item Dynamic simulations use learning curves for cost and emissions.
+	\item Sensitivity analysis identifies key parameters, thresholds, and trade-offs.
 \end{itemize}

### 2021-02-02 publications/2020-03-paper/credit-statements/credit.tex
separates credit statement, declaration of interest based on applied energy guidelines
Former-commit-id: 15bdec437b737268ef40dcbb97979ba5d996b60a
Former-commit-id: c1132ae75c7fe5215b0927d3a86a69bc7c6786ca

--- 2021-01-15 publications/2020-03-paper/highlights/highlights.tex
@@
 \end{frontmatter}
-\section*{Highlights}
-\begin{itemize}
-	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
-	\item Includes long-term assessment up to 2100 
-	\item Dynamic simulations use learning curves for cost and emissions..
-	\item Sensitivity analysis identifies key parameters and thresholds.
-\end{itemize}
+\section*{CRediT Statement}
+
+The authors contributed to this work as described below.
+
+\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.
+
+\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.
+
+\textbf{Akari Minami}: data curation, validation.
+
+\textbf{James Stubbins}: writing - review and editing, supervision.
+
+\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
 \end{document}

### 2021-02-02 publications/2020-03-paper/declaration-of-interests/declaration.tex
separates credit statement, declaration of interest based on applied energy guidelines
Former-commit-id: 15bdec437b737268ef40dcbb97979ba5d996b60a
Former-commit-id: c1132ae75c7fe5215b0927d3a86a69bc7c6786ca

--- 2021-01-15 publications/2020-03-paper/highlights/highlights.tex
@@
 \end{frontmatter}
-\section*{Highlights}
-\begin{itemize}
-	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
-	\item Includes long-term assessment up to 2100 
-	\item Dynamic simulations use learning curves for cost and emissions..
-	\item Sensitivity analysis identifies key parameters and thresholds.
-\end{itemize}
-\end{document}
+\section*{Declaration of interests}
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.\end{document}

### 2021-06-14 publications/2020-03-paper/revisions/review-responses.tex
adds response to reviewer 2

@@
 
-\title{Strategies for thorium fuel cycle transition in the SD-TMSR\\
+\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals\\
 \large Response to Review Comments}
-\author{O. Ashraf, Andrei Rykhlevskii, G. V. Tikhomirov, Kathryn D. Huff}
+\author{Anshuman Chaube, Andrew Chapman, Akari Minami, James Stubbins, Kathryn Huff}
 
@@
 
-        \question This work investigates the fuel cycle and neutronics performance of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different fissile material based on an extended SERPENT-2 code.
-The whole paper states clearly.
-
-        \begin{solution}
-                Thank you very much for these comments.
-We appreciate your detailed review, which has certainly improved the paper.
-The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
-        \end{solution}
-
-        %---------------------------------------------------------------------
-
-        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
-        \begin{solution}
-
-        		  Thank you for the excellent point.
-
-        		  About depletion regions definition: we used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material
-        		  is treated as a single depletion zone. The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.
-
-        		  About burnup time step definition: it is time interval given in days.
-During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
-We started our calculations by 30 days' time step but we do not find significant changes in $k_{eff}$ when we increased the time step to 365 days.
-The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
-
-        		  We changed the paragraph as follows:\\
-
-        		  The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.
-We used the depletion mode 1 in SERPENT-2 (i.e.
-burn 1), which means that the fuel material is treated as a single depletion zone.
-
-        		  We changed the paragraph as follows:\\
-        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
-To determine the appropriate depletion step size, we conducted a time step refinement study.
-We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in $k_{eff}$ became significant.
-The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
-
-        \end{solution}
-
-        %---------------------------------------------------------------------
-        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere.
-In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time.
-Have you considered this in SERPENT calculation?
-        \begin{solution}
-
-		          Thank you for your insightful comment. We used total fuel 
-		          salt inventory in the primary loop to define the fuel 
-		          material in the SERPENT input. Moreover, we accordingly 
-		          adjusted power density in SERPENT burnup calculations 
-		          because fission takes place only in the core region.
-But we did not consider processes, such as decay, which occurs outside of the core.
-Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in Zhang et al.
-(2018) \cite{zhang2018review}.
-
-		          We changed the paragraph as follows:\\
-
-		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere.
-We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
-Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
-But we did not consider processes, such as decay, which occurs outside of the core.
-Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.
-        \end{solution}
-
         %---------------------------------------------------------------------
@@
         %---------------------------------------------------------------------
-        \question Strategies for thorium fuel cycle transition by employing different startup fissile material and feed mechanisms were investigated for the single-fluid double-zoned thorium-based molten salt reactor (SD-TMSR) in this study, and some specific conclusions were obtained.
-While, realizing thorium fuel cycle transition by using different startup fissile material has already been well studied in the previous studies for different types of MSR, including SD-TMSR.
-The motivation (e.g., improvement from previous studies) for conducting this study is not clear.
-In addition, some statements in the paper are inaccurate and more interpretations should be provided to explain some obtained results.
-Therefore, a major revision is required to improve the manuscript.
+        \question The Paris agreement converged on Intended Nationally Determined Contributions on carbon footprint reduction.
+What are the parameters a country such as Japan consider while determining such targets?
 
         \begin{solution}
-                Thank you very much for these comments.
+                Thank you for these comments.
 We appreciate your detailed review, which has certainly improved the paper.
-The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
+Regarding the parameters that must be considered, we have referenced the Paris Agreements which state the international considerations, and the Japanese Basic Energy Plan and the 3E+S approach, which we have summarised briefly in the introduction chapter.
+Since the focus of our paper is not on energy policy review and analysis, further details of these parameters are left in the references for the sake of brevity.
         \end{solution}
@@
 
-        \question SD-TMSR concept development does not correctly described in the section "introduction", where it states that the SD-TMSR was introduced by the Chinese Academy of Sciences.
-Actually, SD-TMSR concept was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) (see Ref.: Tech.
-Rep.
-ORNL-4541).
-In addition, the study of reference 7 which was cited to illustrate SD-TMSR concept actually adopted the single-flow single-zone MSR rather than SD-TMSR.
+        \question I have some apprehensions regarding the long-term horizon of 2100 for investigating the impact of the technologies.
+Such a long duration will involve many uncertainties.
+Further, the technology growth has been exponential in the last century.
+Therefore, it seems plausible that new technologies will be introduced in the energy mix.
+How the current paper deals with such uncertainties and technology disruptions?
 
         \begin{solution}
-                 Thank you for catching this. Just small correction: this ORNL 
-                 concept was called \emph{Molten Salt Breeder Reactor (MSBR)}. 
-                 The whole statement has been 
-                 modified to read:\\
-
-                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
-                 MW$_{th}$ was proposed for the first time by ORNL as early as 
-                 in the 1960s, which was called Molten Salt Breeder Reactor 
-                 (MSBR) \cite{robertson_conceptual_1971}.
-
-                 Thank you for catching this. Reference 7 has been removed from the paragraph.
+                 Thank you for your comment.
+We have conducted a thorough literature review to identify key technologies that could play a significant role in decarbonisation at scale.
+Likely changes in key technology parameters such as investment cost, emission coefficient etc.
+are incorporated dynamically through learning curves obtained from our references, and using TIMES interpolation features.
+Many of these data sources identify median values and ranges of key parameters in the original references.
+Beyond that, it is true that novel technologies may emerge in the future, and they will be incorporated in any future simulations that we conduct.
+The final paragraph of the Conclusion section has been revised to indicate the same :
 
@@
 
-        %---------------------------------------------------------------------
+                \question Carbon capture and sequestration is not a new technology.
+It has been utilized since long.
+Please highlight the chronological evolution of CCS and Hydrogen technologies to put your contributions in context.
+In fact, a table showing such chronological evolution for all the suggested technologies viz.
+nuclear power, wind, solar must be provided.
 
-        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept.
-Cui.
-et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium.
-Progress in Nuclear Energy 104 (2018) 75-84).
-The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
         \begin{solution}
-                Thank you for your helpful review. The statement "For the SD-TMSR 
-                concept, simulating the fissile core startup and fuel cycle 
-                transition with other fissile materials (except$^{233}$U) has 
-                not studied before" in page 3, has been removed. 
-                The following paragraphs have been added to the manuscript:\\
-
-                The research effort described in \cite{cui2017transition} and
-                \cite{cui2018possible} is most similar to the work
-                presented in this paper. Cui \emph{et al.} analyzed the fuel 
-                transition from 
-                enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the 
-                MSBR-like design. Cui 
-                \emph{et al.} found that the fuel transition can be achieved 
-                by using: (1) 
-                enriched uranium with greater than 40\% enrichment 
-                \cite{cui2018possible}; (2) 
-                Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel 
-                \cite{cui2017transition, 
-                	cui2018possible}.
-
-                However, a few major differences follow: 
-                (1) Cui \emph{et al.} employed an in-house tool named MSR 
-                Reprocessing 
-                Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE 
-                and employs a 
-                batch-wise approach while we used built-in truly continuous 
-                fuel depletion 
-                capabilities in SERPENT-2 \cite{aufiero2013extended}; 
-                (2) Cui \emph{et al.} studied a high-enriched uranium ($>$40\% 
-                of $^{235}$U) 
-                and plutonium partitioned from light water reactors spent fuel 
-                as the startup 
-                fissile materials while we considered different loading cases: 
-                HALEU, Pu 
-                mixed with HALEU, reactor-grade plutonium, TRU and $^{233}$U;
-                (3) we adopted the SD-TMSR core geometry optimized by Li 
-                \emph{et al.} 
-                \cite{li_optimization_2018} which is different from the 
-                MSBR-like geometry by 
-                Mathieu \emph{et al.} \cite{mathieu_possible_2009} adopted by 
-                Cui \emph{et 
-                	al.}; 
-                (4) Cui \emph{et al.} introduced two scenarios for thorium 
-                fuel cycle 
-                transition: a Breeding and Burning (B\&B) scenario and a 
-                Pre-breeding scenario 
-                while we adopting different approach by introducing two 
-                different feed 
-                mechanisms: thorium and non-thorium.
-
-                Comparing with Cui \emph{et al.}, we used different reactor 
-                design (geometry, 
-                volumes, densities, fuel salt compositions) and computation 
-                method (continuous 
-                online reprocessing instead of batch-wise approach). In Cui's 
-                scenarios, the 
-                amount of thorium is kept constant. $^{233}$U is fed only in 
-                (B\&B) scenario 
-                and extra fissile materials would have to be added into the 
-                core if the 
-                produced $^{233}$U is not enough to maintain the reactor 
-                criticality. In the 
-                Pre-breeding scenario, all the $^{233}$U produced from the 
-                decay of the 
-                extracted $^{233}$Pa stored outside the core until it reaches 
-                the required 
-                startup mass for a new reactor. Thus, the criticality of the 
-                core is 
-                maintained by refueling external fissile material. In the 
-                current work, using 
-                the thorium feed mechanism, we simultaneously feed thorium and 
-                all or fraction 
-                of produced $^{233}$U from the \texttt{Pa-decay tank} into the 
-                core. The 
-                excess $^{233}$U (if exists) is stored outside the core. In 
-                the non-thorium 
-                feed mechanism, we continuously inject external heavy metals 
-                (HALEU, Pu mixed 
-                with HALEU, reactor-grade Pu, or TRU) and fraction of produced 
-                $^{233}$U from 
-                the \texttt{Pa-decay tank}. For the non-thorium mechanism, we 
-                feed a part of 
-                produced $^{233}$U because in some cases (e.g., TRU) refueling 
-                only external 
-                heavy metals failed to maintain the core criticality 
-                (limitation is 
-                dm$_{salt}$ $\leq$ 0.1\%).
-
-        \end{solution}
-
-        %---------------------------------------------------------------------
-
-        \question More details should be provided to illustrate the heavy metal addition for the thorium feed mechanism and non-thorium feed mechanism in page 11.
-It is hard to understand why the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Pa.
-        \begin{solution}
-               Thank you for the comment. Actually, in page 11, we mention 
-               that the mass of Th / external heavy metals is approximately 
-               equal to the mass of extracted Fission products (FPs) and not 
-               Pa. Because in both feed mechanisms (thorium and non-thorium) 
-               we continuously added $^{233}$U and the mass of injected 
-               $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa 
-               decays to $^{233}$U after $\approx$ 27 d). To keep the total 
-               fuel mass almost constant, for \textbf{thorium feed mechanism}, 
-               the mass of injected thorium must be equal to the mass of 
-               extracted FPs and for \textbf{non-thorium feed mechanism}, the 
-               mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, 
-               reactor-grade Pu, or TRU) must be equal to the mass of 
-               extracted FPs. We rewrite the paragraph on page 11 to clarify 
-               this point:\\
-
-               \begin{enumerate}
-               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
-               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
-               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
-               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected 
-               	$^{233}$U $\approx$ mass of extracted Pa and mass of injected 
-               	$^{232}$Th $\approx$ mass of extracted FPs to maintain the 
-               	total fuel mass constant.
-               	\subitem 3b.
-\textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
-               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
-               \end{enumerate}
-               In both feed mechanisms (thorium and non-thorium) we 
-               continuously added $^{233}$U and the mass of injected $^{233}$U 
-               is equal to the mass of extracted Pa ($^{233}$Pa decays to 
-               $^{233}$U after $\approx$ 27 d). To keep the total fuel mass 
-               almost constant, for \textbf{thorium feed mechanism}, the mass 
-               of injected thorium must be equal to the mass of extracted FPs 
-               and for \textbf{non-thorium feed mechanism}, the mass of 
-               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
-               Pu, or TRU) must be equal to the mass of extracted FPs.
+                 Thank you for your comment.
+While carbon capture technology has been available in some form for a variety of applications since early 2000s, high-efficiency utility-scale carbon capture and sequestration plants have not been developed beyond the pilot stage in any nation, including Japan.
+This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022.
+We have amended the initial reference to "carbon capture and sequestration" to "utility-scale carbon capture and sequestration" for further clarity.
 
@@
 
-        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
+                        \question It has been argued that the life cycle cost associated with wind and photovoltaic power may far outweigh  their benefits.
+For example, what about the disposal of the used wind turbine blades and their environmental impact?
+How have you considered such impacts in the time horizon?
+Also, provide a tabular summary of the expected environmental impact of the suggested technologies.
+
         \begin{solution}
-                 Thank you for your insightful comment. Phenomenons presented 
-                 in Figure 3 have been described in the manuscript.
-                 The following paragraph and additional Figure~4 has been added to the manuscript:\\
 
-                 For the Pu+HALEU case, $k_{eff}$ firstly increases during the 
-                 first $\approx$ $3$ EFPY and then gradually decreases. This 
-                 is due to the conversion of $^{238}$U from HALEU into fissile 
-                 plutonium, which often produces the majority of the neutrons 
-                 until the transition to Th/$^{233}$U fuel cycle. Figure~4 
-                 shows the variation in fissile plutonium isotopes ($^{239}$Pu 
-                , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
-                 operation. For TRU and reactor-grade Pu, the fissile 
-                 plutonium isotopes are gradually depleted, during operating 
-                 (the fissile material is dominated by Pu in these cases). For 
-                 the HALEU case, the fissile material is dominated by 
-                 $^{235}$U, 
-                 however, $^{238}$U is converted into fissile plutonium. 
-                 Therefore, the mass of fissile plutonium increases during 
-                 operating but its value still relatively low. For the 
-                 Pu+HALEU case, the mass of the fissile plutonium isotopes 
-                 increases 
-                 within the first $\approx$ $3$ EFPY and then decreases. The 
-                 reactivity from the produced Pu is much greater than the 
-                 depletion of the initial reactivity (due to the depletion of 
-                 initial fissile isotopes), consequently, $k_{eff}$ increases 
-                 during the first $\approx$ $3$ years and then decreases; the 
-                 amount of $^{233}$U generated in the Pu+HALEU case is 
-                 insufficient to maintain the reactor criticality and 
-                 counteract neutron absorption in non-fissile isotopes.\\
-
-                 Figure~3 shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
-Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.
+                 Thank you for your comment.
+One form of environmental impact, namely the direct and lifecycle CO$_2$ emissions, has been incorporated for all methods of electricity generation and storage using TIMES's emission coefficient feature.
+For all energy sources including renewables like wind and solar, the references for lifecycle emissions include the carbon cost of materials, manufacturing, and disposable as and when applicable.
+Since the focus of our paper is on modelling energy systems while focussing on \textbf{carbon emissions}, other forms of environmental impact such as recycling, acidification, human toxicity etc.
+are beyond the scope of our paper.
 
@@
         %--------------------------------------------------------------------
-        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
-        \begin{solution}
-                  Thank you for the question.
-Specifically, Pa is removed from the fuel by chemical reprocessing into the \texttt{Pa-decay tank} to decay and produce $^{233}$U.
-The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
-Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
-The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime.
-Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$.
-The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
-Therefore, we selected the RP = $30$ $s$.
-This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
-For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
-
-                  The following paragraph and additional Figure~8 has been added to the manuscript:\\
-
-                  The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
-Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
-The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime.
-Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$.
-The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
-Therefore, we selected the RP = $30$ $s$.
-This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
-For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
-        \end{solution}
-
-        %--------------------------------------------------------------------
-        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.
+                        \question In a country such as Japan, which has been badly impacted by nuclear disasters, how can nuclear power be part of the suggested energy mix for carbon neutral future?
+Line no.
+18-19 in P-2 directly contradicts line no 34-36 in the abstract page.
 
         \begin{solution}
-                Thank you for the excellent point. The statement has been removed from the text.
-                Moreover, we rewrite the paragraph to clarify this point:\\
 
-                Figure~11 demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
-For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL.
-For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases.
-The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt.
-Harder neutron spectrum enhance $^{233}$U breeding from $^{232}$Th.
-For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th).
-However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.
+                 Thank you for your comment.
+We have touched upon this issue in our discussion, by identifying a need for improving safety standards within the Japanese regulatory framework, and for the need of engendering public acceptance by creating trust in nuclear power.
+Since the focus of our paper is not on policy and creating public acceptance, further discussion on this issue is beyond the scope of our paper.
+
+                 The lines 18-19 in page 2 have been revised as follows for further clarity:
 
@@
         %--------------------------------------------------------------------
-        \question Regarding to Figure 10, reasons should be provided to explain why the time achieving Pu solubility limit for the case of TRU is shorter than that of the case of reactor-grade Pu.
+
+        %--------------------------------------------------------------------
+                        \question  Should not the 3E+S benchmark be 3E+SS where the second S stands for social acceptance?
+I believe social acceptance is the first requirement of any energy systems expected for countries governed by dictatorial methods.
+
         \begin{solution}
-                 This has now been clarified in the text.
-                 We rewrite the paragraph to clarify this point:\\
 
-                 Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case.
-The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table 5).
+                 Thank you for your comment.
+We have simply referenced the policy as named by the Japanese government.
+We are not responsible for the nomenclature and are unable to modify its name for the sake of precision.
+We have referenced the need for social acceptance in the Discussion section, especially when discussing nuclear power.
 
@@
                %--------------------------------------------------------------------
-        \question It is hard to understand that the neutron spectrum of TRU case at BOL is softer than U-233 case since TRU has a greater amount of thermal neutron absorbers and the fissile material is dominated by Pu which would generate hard neutron spectrum.
+                        \question   Please provide enumerated lists for research gaps, contributions and novelty of the paper at the end of section 2 under a subsection 2.1 Research gaps and contributions.
 
         \begin{solution}
-                 We appreciate your detailed review.                   
-                 The following paragraph has been added to the manuscript:\\
 
-                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
-$^{232}$Th has a very high absorption cross section in the thermal region ($\approx$ $10^2$ b).
-Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~14).
+                 Thank you for your comment.
+We have identified research gaps by highlighting the lack of clarity in the transition pathway, the emergence of new technologies, the incorporation of carbon emission coefficients for all technologies, and the use of sensitivity analysis in determining key parameters across our abstract, introduction, and conclusion.
+A separate section has not been added for brevity.
 
@@
               %--------------------------------------------------------------------
-        \question More details should be provided to explain the radial 
-        neutron flux distribution for the cases of Pu reactor-grade and TRU 
-        presented in Fig.13 and 14. For both the radial fast and thermal 
-        neutron flux change from BOL to EOL, why it is much larger for Pu 
-        reactor-grade case compared with TRU case. In addition, the state "In 
-        contrast, for the reactor-grade Pu and TRU cases, significant changes 
-        are observed for thermal neutron flux in the outer core zone and 
-        reactor" is inaccurate, apparently from Figure 14, it can be seen that 
-        the Pu reactor-grade (initial) case has a small change in the outer 
-        core zone and reflector. 
-        \begin{solution}
-				Thank you for pointing it out. 
-				At the EOL the fuel salt composition is more or less the same 
-				(``equilibrium'' composition), hence, both fast and thermal 
-				fluxes looks very similar for plutonium and TRU cases.
-				At the BOL, this difference is caused by different $^{232}$Th 
-				inventory at BOL for Pu reactor-grade (67.5t) and TRU (54.4t). 
-				 $^{232}$Th is a strong absorber in the thermal and 
-				 intermediate energy range, so, it causes such a significant  
-				 difference in the flux: reactor-grade Pu composition provides 
-				 much harder spectrum (see Figure~14) at BOL.
-
-                Figure 15 shows 
-				significant changes \textbf{during reactor operation} in the 
-				outer core zone for the Pu (green line) and almost no changes 
-				for the TRU (orange). However, we are agree that thermal flux 
-				drop in the reflector is more dramatic for the TRU (initial 
-				and equilibrium compositions) and the Pu (equilibrium) cases 
-				than for the U-233 case. We think it happens because of 
-				non-optimal geometry of the core for the Pu and TRU initial 
-				loading.
-
-				The following paragraphs have been added to the manuscript for 
-				clarification:\\
-
-				Notably, the neutron flux change for both the fast and thermal 
-				energies is much larger for the reactor-grade Pu case than for 
-				TRU case (Figures~15 and 16). The reason is the much softer 
-				neutron spectrum for the TRU initial loading compared with the 
-				reactor-grade Pu as shown in Figure~14: peak thermal neutron 
-				flux is about 4 times larger for the TRU case. The neutron 
-				spectrum in the SD-TMSR core initially loaded by TRU is much 
-				softer than the reactor-grade Pu case and even than the U-233 
-				case because $^{232}$Th inventory is the lowest for the TRU 
-				case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the reactor-grade  
-				Pu and U-233 cases, respectively (Table~5). $^{232}$Th greatly 
-				affects the neutron energy spectrum due to its large 
-				absorption cross section in the thermal energy range and 
-				resonance region between $10^{-5}$ and $10^{-3}$. Finally, 
-				when the TRU and the reactor-grade Pu cases reached 
-				equilibrium fuel salt composition ($\approx 30$ years after 
-				startup), the radial fast and thermal neutron flux 
-				distribution became similar in both shape and magnitude.
-
-				More changes in thermal neutron flux shape and magnitude 
-				during the reactor operation for the $^{233}$U case are 
-				observed in the inner core zone ($R\lesssim150$) than in the 
-				outer core zone. In the outer core zone, significant changes 
-				during reactor operation are observed for the thermal 
-				neutron flux for the reactor-grade Pu case. In contrast, for 
-				the TRU case, thermal neutron flux change in the outer core 
-				zone is almost negligible. Additionally, 
-				Figure~16 shows relatively significant changes in thermal flux 
-				leakage from the core for the Pu (equilibrium composition) and 
-				TRU (initial and equilibrium composition) cases. The SD-TMSR 
-				core design was optimized for $^{233}$U  				
-				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
-				channel lattice pitch) must be re-optimized for another type 
-				of fuel to obtain better neutronics performance.
-        \end{solution}
-
-        %--------------------------------------------------------------------
-        \question Regarding to the FTC for three different cases, reasons should be provided to explain why spectrum softening will positively affects the FTC since generally harder neutron spectrum would benefit FTC.
-        \begin{solution}
-                Thank you for your insightful comment.  Indeed, the Doppler 
-                effect coefficient ($\alpha_{D,F}$) is usually stronger for 
-                harder spectrum (see Table~8, ``Fuel salt temperature''), so, 
-                spectrum softening negatively affects $\alpha_{D,F}$ (it is 
-                decreasing by value but still negative). But we additionally 
-                considered the fuel salt density coefficient 
-                ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
-                (e.g., $+1.09$ $pcm/K$ for the \gls{MSBR}           
-                \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
-                spectrum benefit $\alpha_{\rho,F}$ \cite{li_effects_2018-1, 
-                rykhlevskii2019modeling}. More analysis on this topic:
-            Li, X., Ma, Y., Yu, C. et al. Effects of fuel salt composition on 
-            fuel salt temperature coefficient (FSTC) for an under-moderated 
-            molten salt reactor (MSR). NUCL SCI TECH 29, 110 (2018). 
-            https://doi.org/10.1007/s41365-018-0458-1.
-
-	            The following paragraphs have been added to the manuscript:\\
-
-	            The \gls{FTC} is a combination of the Doppler effect 
-	            coefficient ($\alpha_{D,F}$) and density coefficient 
-	            ($\alpha_{\rho,F}$) and significantly affected by the neutron 
-	            spectrum. Li \emph{et al.} reported that 	            
-	            $\alpha_{D,F}$ in thermal \gls{MSR} is always negative and 
-	            increases by magnitude when spectrum hardening (see Table~8, 
-	            first raw). In contrast, $\alpha_{\rho,F}$ is a combination of 
-	            moderator-to-fuel volume ratio, absorption cross section of 
-	            heavy metal, and the core leakage. When the fuel salt 
-	            temperature increases, the salt becomes less dense, 
-	            causing a reduction in the fuel concentration and the neutron 
-	            spectrum become softer. Such spectrum softening is leading to 
-	            a rise in macroscopic absorption cross section of the fissile 
-	            isotopes. Moreover, the spectrum softening may leads to 
-	            a larger fast fission reaction rate \cite{li_effects_2018-1}. 
-	            Thus, spectrum softening positively affects the density 
-	            coefficient ($\alpha_{\rho,F}$): $+1.54$ $pcm/K$ and $-1.58$ 
-	            $pcm/K$ at the startup and equilibrium for the 
-	            reactor-grade Pu case, respectively. More discussion about 
-	            effects of fuel salt composition in the \gls{FTC} can be found 
-	            elsewhere 
-	            \cite{li_effects_2018-1}.
-        \end{solution}
-
-        %--------------------------------------------------------------------
-        \question It seems unclear why (what is the purpose) to conduct the study of six factor analysis.
-        \begin{solution}
-                 Thank you for bringing our attention to the point. Usually, 
-                 six factor analysis helps to understand reasons of changes in 
-                 TCs and control rod worths during reactor operation. But in 
-                 this case, considering many various cases, such analysis is 
-                 outmoded.           
-                  The section has been removed from the manuscript completely.
-        \end{solution}
-
-        %--------------------------------------------------------------------
-        \question Making the full definition for abbreviation through the whole paper is not necessary, such as SD-TMSR, first time is enough.
+                        \question   Start section 4.2 provide a table detailing a summary of parameters and range of their variations for which the sensitivity analysis is performed.
 
         \begin{solution}
-                Thank you for the information. The full definition for abbreviation through the whole paper has been removed as requested.
+
+                 Thank you for your comment.
+The same table is present in the draft at the end of Section 4.2.
+We have not placed the table at the beginning of the section for the sake of readability, specifically so that the reader may first be introduced to the concept and scope of our sensitivity analysis and the parameters therein, before diving into the detailed ranges of variation.
+
         \end{solution} 
+                      %--------------------------------------------------------------------
+                        \question   The Acknowledgement section mentions the funding source as the ministry of culture and others.
+What about the impact of suggested technologies on the culture and tradition of the country.
+Sustainable energy goals must meet social, economic, environmental and technological sustainability.
+Culture is an integral part of social sustainability of any energy resource.
 
+        \begin{solution}
+
+                 Thank you for your comment.
+We have simply referenced a source of funding.
+The focus of the paper is on modelling the electricity supply sector using TIMES while reducing carbon emissions.
+Cultural impacts are beyond the scope of our paper.
+
+        \end{solution} 
                               %--------------------------------------------------------------------
+                        \question   Finally, I appreciate the authors for writing such a  thought provoking paper.
+I personally believe Nuclear Power is the only energy source which can provide sustainable energy for a long-time horizon like 2100.
+Starting from small energy sources such as nuclear battery to GW size generators, nuclear power has all in it.
+It would be great if the authors investigate the major impediments to a nuclear dominated energy scenario.
+Can the political and social constructs of the nation and for that matter the whole world accept nuclear power?
+Since Reliability theory says that all systems eventually fail, should not we give nuclear power a fair chance?
 
+        \begin{solution}
+
+                 Thank you for your comment.
+We appreciate the depth of your question.
+We have referenced nuclear-specific challenges throughout the paper in discussing the associated cost, the safety concerns especially after Fukushima-Daiichi, and the lack of public acceptance.
+However, the focus of the paper is on modelling the electricity supply sector using TIMES while reducing carbon emissions.
+Investigating impediments to any specific technology and proposing solutions to such impediments is beyond the scope of our paper, which aims to conduct an technologically-impartial analysis into decarbonisation transition scenarios.
+
+        \end{solution} 
 \end{questions}
-\bibliographystyle{elsarticle-num}
-\bibliography{../2019-Scenarios}
+%\bibliographystyle{elsarticle-num}
+%\bibliography{../2019-Scenarios}
 \end{document}

### 2021-06-14 publications/2020-03-paper/revisions/abstract.tex
adds response to reviewer 2

--- 2021-01-19 publications/2020-03-paper/abstract.tex
@@
 We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region model in \gls{TIMES}.
-Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impact up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients.
+Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impacts up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients.
 Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security.
-Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.
+Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role in achieving emission reduction targets.
 

### 2021-06-14 publications/2020-03-paper/revisions/introduction.tex
adds response to reviewer 2

--- 2021-01-19 publications/2020-03-paper/introduction.tex
@@
 In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
+The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
 Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.

### 2021-06-14 publications/2020-03-paper/revisions/methods.tex
adds response to reviewer 2

--- 2021-01-19 publications/2020-03-paper/methods.tex
@@
 %basic features of model
+We outline salient features of our model in this section, while the data used for our simulations are in \ref{Appendix}.
+The relevant input files can be accessed online \cite{chaube_arfci2cner_2021}.
 The objective function in our single-region model is the overall cost of the transition.
@@
 Miscellaneous assumptions are summarised in Table \ref{misc-assump}.
-In other words, our model minimises the transition cost while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
+In summary, our model minimises the transition cost while meeting the increasing electricity demand and achieving the required emission cuts using a combination of generation and storage technologies.
 
-While Japanese electricity demand is expected to grow in the near future  \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's ageing population.
-However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
-Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes.
-The model captures the initial condition of the post-Fukushima Japanese electricity supply system using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
-Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100.
-We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology.
-Using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}, the daily and seasonal variability of renewables is incorporated.
-The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.
-
-\begin{table}[!ht]
+\begin{table}[H]
+\centering
 	\caption{Electricity demand increase over the simulation time frame.}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
+\centering
 	\caption{Emission constraints.}
@@
 
+While Japanese electricity demand is expected to grow in the near future  \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's ageing population.
+However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors.
+Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes.
+The model captures the initial condition of the post-Fukushima Japanese electricity supply system using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
+Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100.
+We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology.
+Using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}, the daily and seasonal variability of renewables is incorporated.
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.
+
 %scenario description
@@
 
-%misc assumptions
-Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in Tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
-Prices and projections for fossil fuels and nuclear fuel are incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
-Learning curves for costs and life-cycle emissions are compiled from existing data (Table \ref{eco}) based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
-These learning curves are modelled as piecewise linear functions interpolated between the available data points, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}.
-Capacity limits of renewables and \gls{PWS} are based on their land-use requirements.
-The maximum annual capacity growth rates for existing technologies are held constant.
-The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}.
-The reactor size assumed in this study is 1165 MWe, based on Watts-Bar Unit 2 \cite{iaea_pris_nodate-1}.
-Due to a projected increase in the share of renewables, nuclear power plants must be able to load-follow to a certain extent, which is approximated in our model based on French reactors' range of capacity factors.
-The growth rates of all emerging technologies are modelled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
-One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
-We assume that these technologies, some of which are already commercialised or close to commercialisation, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
-Therefore, they could be deployed as rapidly as conventional solar photovoltaic cells.
-
-All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load-following.
-Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
-For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
-Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
-
-\begin{table}[!ht]
+\begin{table}[H]
+\centering
 	\caption{Electricity supply transition scenario definition based on enabled technologies.}
@@
 
+%misc assumptions
+Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in Tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.
+Prices and projections for fossil fuels and nuclear fuel are incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}.
+Learning curves for costs and life-cycle emissions are compiled from existing data (Table \ref{eco}) based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components.
+These learning curves are modelled as piecewise linear functions interpolated between the available data points, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}.
+Capacity limits of renewables and \gls{PWS} are based on their land-use requirements.
+The maximum annual capacity growth rates for existing technologies are held constant.
+The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}.
+The reactor size assumed in this study is 1165 MWe, based on Watts-Bar Unit 2 \cite{iaea_pris_nodate-1}.
+Due to a projected increase in the share of renewables, nuclear power plants must be able to load-follow to a certain extent, which is approximated in our model based on French reactors' range of capacity factors.
+The growth rates of all emerging technologies are modelled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate.
+One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies.
+We assume that these technologies, some of which are already commercialised or close to commercialisation, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain.
+Therefore, they could be deployed as rapidly as conventional solar photovoltaic cells.
+
+All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load-following.
+Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
+For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
+
 \subsection{Sensitivity analysis}
@@
 
-While there is significant uncertainty in the investment cost of nuclear power plants \cite{lovering_historical_2016}, it varies for individual plants and not for the technology as a whole.
-Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions.
-Consequently, we eliminated nuclear power's investment cost as a candidate for sensitivity analysis.
-Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster.
-In order to assess these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose Scenario 5 (Table \ref{scen-table}) as our base scenario for sensitivity analysis.
-Ten model parameters were sampled 30 times from appropriate distributions (Table \ref{sa-vars}).
-The parameter value at the first year of deployment (Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios.
-For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.
-This makes learning-based cost-reductions proportionate across all sensitivity analysis runs.
-These parameters were randomly co-varied in 30 simulations.
-The share of each electricity generation technology (as the ratio of cumulative technology output to the cumulative electricity demand) and output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
-A similar approach was also used to correlate these parameters with the system's transition cost.
-
-\begin{table}[!ht]
+\begin{table}[H]
+\centering
 	\caption{Candidate parameters and their variation in our sensitivity analysis.}
@@
 \end{table}
+
+While there is significant uncertainty in the investment cost of nuclear power plants \cite{lovering_historical_2016}, it varies for individual plants and not for the technology as a whole.
+Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions.
+Consequently, we eliminated nuclear power's investment cost as a candidate for sensitivity analysis.
+Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster.
+In order to assess these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose Scenario 5 (Table \ref{scen-table}) as our base scenario for sensitivity analysis.
+Ten model parameters were sampled 30 times from appropriate distributions (Table \ref{sa-vars}).
+The parameter value at the first year of deployment (Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios.
+For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.
+This makes learning-based cost-reductions proportionate across all sensitivity analysis runs.
+These parameters were randomly co-varied in 30 simulations.
+The share of each electricity generation technology (as the ratio of cumulative technology output to the cumulative electricity demand) and output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix.
+A similar approach was also used to correlate these parameters with the system's transition cost.

### 2021-06-15 publications/2020-03-paper/revisions/review-responses.tex
adds reviwer comments + responses

@@
 this paper. Your suggestions, clarifications, and comments have resulted in 
-changes which certainly improved the paper.
+changes which improved the paper.
 
@@
         %---------------------------------------------------------------------
+
+         \question "The largest contribution to global greenhouse gas (GHG) emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors [2]."
+Since the focus of the paper is on electricity, the share of GHG should be presented separately.
+
+        \begin{solution}
+                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+         \question "Japan has been rapidly deploying renewables and has attempted to transition away from nuclear power since the Fukushima Daiichi accident [3].
+Yet Japan is also considering reinvigorating its nuclear power sector, evidenced by the restart of its nuclear reactors [4]."
+ away from nuclear energy is not true and contradicts itself directly in the following sentence
+
+        \begin{solution}
+                Thank you for these comments.
+For the comment above, the following text has been added to the paper to make the transition between the two statements less jarring.
+However, the narrative was fundamentally true for a while, as indicated by the /slow-restart of nuclear power plants and increasing reliance on coal, as shown by TEPCO(CHECK PUBLISHER NAME)'s Annual Electricity Review.
+
+        \end{solution}
+
+                      %---------------------------------------------------------------------
+
+         \question "lessons learnt from these decarbonisation simulations could inform global energy policy by delineating potential transition pathways, identifying key novel technologies, and their most significant parameters."
+	added value not clearly elaborated in comparison to existing literature        
+        \begin{solution}
+                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+         \question "We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology"
+         Describe in more detail how calculations are made here.
+How do the factors enter the model?
+Statically?
+Separately for the production, use and disposal phases?
+Where does the data come from?
+CO2 only or CO2 equivalents?
+
+        \begin{solution}
+                Thank you for these comments.  For the comment above, the following text has been added to the paper
+        \end{solution}
+
+                    %---------------------------------------------------------------------
+
+         \question "or hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis."
+Does this mean that H2 goes in emission-free? Then this would have to be clearly stated.
+        \begin{solution}
+                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+        \end{solution}
+
+   %---------------------------------------------------------------------
+
+         \question Figure 1-5 starts at 2013, until when is historical data shown and when does simulation start?
+        \begin{solution}
+                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+        \end{solution}
 
@@
 We have simply referenced a source of funding.
-The focus of the paper is on modelling the electricity supply sector using TIMES while reducing carbon emissions.
+The focus of the paper is on modelling the electricity supply sector of a developed nation using TIMES while reducing carbon emissions.
 Cultural impacts are beyond the scope of our paper.
@@
         \end{solution}
+
+                                      %--------------------------------------------------------------------
+
+        \section{Reviewer 3}
+
+         \question Table 1. Please, remove the refrence from the table and include it in the table caption.
+        \begin{solution}
+                Thank you for these comments. We appreciate your detailed review. The requested changes have been made to Table 1, and the caption now reads
+
+        \end{solution}  
+                                      %--------------------------------------------------------------------
+
+         \question Line 14 of page 15, please remove bold text.
+        \begin{solution}
+                Thank you for these comments.
+The requested text has been switched from bold to normal.
+To make similar text congruent with this change, all other transition costs have been changed from bold to normal.
+
+        \end{solution}  
+                                      %--------------------------------------------------------------------
+
 \end{questions}

### 2021-06-16 publications/2020-03-paper/revisions/review-responses.tex
minor changes to reviewer comments

@@
 The final paragraph of the Conclusion section has been revised to indicate the same :
+                 ...as trucks and pipelines on hydrogen and CCS is also worth investigating.
+\textbf{Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.}
 
@@
 While carbon capture technology has been available in some form for a variety of applications since early 2000s, high-efficiency utility-scale carbon capture and sequestration plants have not been developed beyond the pilot stage in any nation, including Japan.
-This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022.
+This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022-23 (see Table A.8).
 We have amended the initial reference to "carbon capture and sequestration" to "utility-scale carbon capture and sequestration" for further clarity.

### 2021-06-16 publications/2020-03-paper/introduction.tex
updates manuscript to latest version

@@
 In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}.
-The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
-Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
+The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
+However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system.
+The emergence of novel technologies like \gls{CCS} and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.
+
+We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies.
+We use Japan as a proxy for a developed nation committed to addressing climate change.
+However, the results have global significance.
+Like many other developed nations, Japan has been rapidly deploying renewables and has attempted to transition away from nuclear power since the Fukushima Daiichi accident \cite{international_energy_agency_latest_2019}.
+Yet Japan is also considering reinvigorating its nuclear power sector, evidenced by the restart of its nuclear reactors \cite{iaea_pris_nodate}.
+Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{meti_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}.
+Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, lessons learnt from these decarbonisation simulations could inform global energy policy by delineating potential transition pathways, identifying key novel technologies, and their most significant parameters.
+
+%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
 However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
-Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
+Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .
 
-Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
+The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans.
+Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
 The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid).

### 2021-06-18 publications/2020-03-paper/revisions/review-responses.tex
edits to comments, track changes

--- 2021-06-15 publications/2020-03-paper/revisions/review-responses.tex
@@
         \begin{solution}
-                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper:
+
+                The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors [2].
+Energy use in buildings in particular generates 17.5\% of all emissions [3].
         \end{solution}
@@
                 Thank you for these comments.
-For the comment above, the following text has been added to the paper to make the transition between the two statements less jarring.
-However, the narrative was fundamentally true for a while, as indicated by the /slow-restart of nuclear power plants and increasing reliance on coal, as shown by TEPCO(CHECK PUBLISHER NAME)'s Annual Electricity Review.
+Our narrative was based on the slow, reluctant restart of nuclear power plants and increasing reliance on coal, as shown by the data from The Federation of Electric Power Companies of Japan's Annual Electricity Review and data from the EDMC.
+However, the jarring transition between the two sentences has been revised as follows:
+
+                Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal [4, 5].
+However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors [6].
 
@@
         \begin{solution}
-                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+                Thank you for these comments. For the comment above, the following text has been added to the paper:
+
+                Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy.
+Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.
         \end{solution}
@@
         \begin{solution}
-                Thank you for these comments.  For the comment above, the following text has been added to the paper
+                Thank you for these comments.
+The values are taken directly from literature, and the sources are cited in Table A.8.
+The incorporation is dynamic and the variation has been mentioned in Table A.8 and in the methodology section, but further changes have been made for clarity (see below).
+The references report one lifecycle emission value which incorporates cradle to grave emissions.
+For further details please refer to individual references.
+The data use CO$_2$ equivalents - the units in Table A.8 have been changed to reflect this, thank you for catching this.
+The following sentences has been added to incorporate this information and further clarify the text:
+
+                We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology.
+The emission coefficient data and their sources are listed in Table A.8.
+The emission coefficients vary dynamically for technologies that have projections available in literature, and are linearly interpolated between available data points until the last available projection, beyond which they are held constant.
+For hydrogen fuel cells and electrolysers, emission coefficients vary in magnitude across different technologies but the learning curves follow similar trajectories due to the similarity of technologies.
+The lifecycle emissions for \gls{PWS} are unknown, hence we have assumed them to be the same as that of \glspl{SOEC} as both are lab-scale technologies with similar deployment time-frames, and \gls{PWS} must have similar or lower life-cycle emissions as \gls{SOEC} to be competitive.
+
         \end{solution}
@@
         \begin{solution}
-                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+                Thank you for these comments.
+Hydrogen technologies are not emission-free as life-cycle emissions from the stack are still incorporated into the model.
+Their respective emission coefficients are detailed in Table A.8, a clearer reference to which has been added in response to your comment:
+
+                For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered (see Table A.8), as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+
         \end{solution}
@@
         \begin{solution}
-                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
+                Thank you for catching this.
+Historical data is shown from 2013-2016, and while this was mentioned briefly in the methodology section when discussing the initial condition, it lacked clarity.
+We have added the following text to the methodology section:
+                \begin{itemize}
+
+                \item The model captures the initial condition of the post-Fukushima Japanese electricity supply system using historical data The Energy Data and Modelling Centre’s data from 2013-2016 [27].
+                \end{itemize}
+
+                And the following text to the results section:
+                \begin{itemize}
+
+                \item Note that the years 2013-2016 represent the initial condition modelled using historical data [27], and the simulation results begin from 2017 onwards.
+
+                \end{itemize}
+
         \end{solution}
@@
 Regarding the parameters that must be considered, we have referenced the Paris Agreements which state the international considerations, and the Japanese Basic Energy Plan and the 3E+S approach, which we have summarised briefly in the introduction chapter.
-Since the focus of our paper is not on energy policy review and analysis, further details of these parameters are left in the references for the sake of brevity.
+Since the focus of our paper is not on energy policy review and analysis, further details of these parameters are provided in the references.
         \end{solution}
@@
                  Thank you for your comment.
-We have conducted a thorough literature review to identify key technologies that could play a significant role in decarbonisation at scale.
+For existing and emerging technologies, we have conducted a thorough literature review to identify key technologies that could play a significant role in decarbonisation at scale.
 Likely changes in key technology parameters such as investment cost, emission coefficient etc.
@@
 Many of these data sources identify median values and ranges of key parameters in the original references.
-Beyond that, it is true that novel technologies may emerge in the future, and they will be incorporated in any future simulations that we conduct.
+Beyond that, it is true that completely novel technologies may emerge in the future, and they will be incorporated in any future simulations that we conduct.
 The final paragraph of the Conclusion section has been revised to indicate the same :
+
+                 ...as trucks and pipelines on hydrogen and CCS is also worth investigating.
+Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.
 
@@
 While carbon capture technology has been available in some form for a variety of applications since early 2000s, high-efficiency utility-scale carbon capture and sequestration plants have not been developed beyond the pilot stage in any nation, including Japan.
-This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022.
-We have amended the initial reference to "carbon capture and sequestration" to "utility-scale carbon capture and sequestration" for further clarity.
+This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022-23 (see Table A.8).
+We have amended the initial reference in the introduction from "carbon capture and sequestration" to "high-efficiency utility-scale carbon capture and sequestration" for further clarity.
 
@@
                  Thank you for your comment.
-One form of environmental impact, namely the direct and lifecycle CO$_2$ emissions, has been incorporated for all methods of electricity generation and storage using TIMES's emission coefficient feature.
-For all energy sources including renewables like wind and solar, the references for lifecycle emissions include the carbon cost of materials, manufacturing, and disposable as and when applicable.
-Since the focus of our paper is on modelling energy systems while focussing on \textbf{carbon emissions}, other forms of environmental impact such as recycling, acidification, human toxicity etc.
+One form of environmental impact, namely the direct and lifecycle CO$_2$ emissions, has been incorporated for all methods of electricity generation and storage using TIMES's emission coefficient feature (please see Table A.8).
+For all energy sources including renewables like wind and solar, the references for lifecycle emissions include the carbon cost of materials, manufacturing, and disposal as and when applicable.
+Since the focus of our paper is on modelling energy systems while focussing on carbon emissions alone, other forms of environmental impact such as recycling, acidification, human toxicity etc.
 are beyond the scope of our paper.
@@
 We have touched upon this issue in our discussion, by identifying a need for improving safety standards within the Japanese regulatory framework, and for the need of engendering public acceptance by creating trust in nuclear power.
+To further emphasise the urgency of using existing options like nuclear power, the following sentence has been added to the discussion section in light of recent developments
+
+                 \begin{itemize}
+                 \item An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain especially considering the more ambitious carbon reduction goals recently announced by <ORGANIZATION NAME> <REFERENCE>.
+                 \end{itemize}
+
                   Since the focus of our paper is not on policy and creating public acceptance, further discussion on this issue is beyond the scope of our paper.
 
-                 The lines 18-19 in page 2 have been revised as follows for further clarity:
+                 The lines 34-36 in the abstract simply indicate the results of our findings, which are talking about future projections, whereas lines 18-19 on page 2 refer to the changes that have occurred in the Japanese electricity supply sector in the recent past.
+While we do not see any direct contradiction, your and Reviewer 1's comments have prompted us to revise the rather abrupt transition in lines 34-36 on page 2 as follows:
+
+                 \begin{itemize}
+
+                  \item  Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal [4, 5].
+However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors [6].
+
+                 \end{itemize}
 
@@
                  Thank you for your comment.
-We have simply referenced the policy as named by the Japanese government.
-We are not responsible for the nomenclature and are unable to modify its name for the sake of precision.
-We have referenced the need for social acceptance in the Discussion section, especially when discussing nuclear power.
+We have simply referenced the policy as it was named by the Japanese government.
+We are not responsible for the nomenclature and are unable to modify its name as we need to be precise in our references.
+We have attemped to address your concerns by discussing the need for social acceptance in the Discussion section, especially in relation to nuclear power.
 
@@
 We have identified research gaps by highlighting the lack of clarity in the transition pathway, the emergence of new technologies, the incorporation of carbon emission coefficients for all technologies, and the use of sensitivity analysis in determining key parameters across our abstract, introduction, and conclusion.
-A separate section has not been added for brevity.
+The research gap you mentioned hhas been further highlighted by an additional sentence in the introduction:
+
+                 Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.
 
@@
                  Thank you for your comment.
-The same table is present in the draft at the end of Section 4.2.
+This table is present in the draft at the end of Section 4.2.
 We have not placed the table at the beginning of the section for the sake of readability, specifically so that the reader may first be introduced to the concept and scope of our sensitivity analysis and the parameters therein, before diving into the detailed ranges of variation.
@@
                  Thank you for your comment.
-We have simply referenced a source of funding.
-The focus of the paper is on modelling the electricity supply sector of a developed nation using TIMES while reducing carbon emissions.
-Cultural impacts are beyond the scope of our paper.
+We have simply referenced a source of funding that happens to be the Japanese Ministry of Education, Culture, Sports, Science and Technology.
+The focus of the paper is on modelling the decarbonisation of the electricity supply sector of a developed nation using TIMES.
+We cannot comment on the aspects of our research in relation to culture, education, or sports, as only the science and technology aspects fall within the scope of our paper.
 
@@
 Investigating impediments to any specific technology and proposing solutions to such impediments is beyond the scope of our paper, which aims to conduct an technologically-impartial analysis into decarbonisation transition scenarios.
+Further, any arguments we make in favour of any technology are informed by the energy analysis we have conducted, and any discussion about reliability theory is beyond the scope of our paper.
 
@@
         \begin{solution}
-                Thank you for these comments. We appreciate your detailed review. The requested changes have been made to Table 1, and the caption now reads
+                Thank you for these comments. We appreciate your detailed review. The requested changes have been made to Table 1, and the caption now reads:
+
+                Electricity demand increase over the simulation time frame. The demand for 2017-2030 is obtained from [5], the rest of the curve is based on estimated population growth trends.
 

### 2021-06-18 publications/2020-03-paper/difftest/intro-changes.tex
edits to comments, track changes

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \mbox{\cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \mbox{\cite{ge_4_2020}}\added{, of which electricity generation comprises (INSERT PERCENTAGE HERE) (INSERT REFERENCE HERE)}. However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system. The emergence of novel technologies like \added{high-efficiency utility-scale } \gls{CCS} \added{(henceforth referred to as \gls{CCS}} and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables\deleted{and has attempted to transition away from nuclear power since the } \added{, and in the wake of the } Fukushima Daiichi accident\deleted{\mbox{\cite{international_energy_agency_latest_2019}}. Yet Japan is also } \added{, it shut down its nuclear reactors and increased its reliance on coal \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}. However, now Japan is } considering reinvigorating its nuclear power sector, evidenced by the restart of its nuclear reactors \mbox{\cite{iaea_pris_nodate}}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \mbox{\cite{meti_basic_2017}} and has shown interest in utilising \gls{CCS} \mbox{\cite{meti_report_2020}}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, \deleted{lessons learnt from these decarbonisation simulations } \added{simulating likely transition pathways for decarbonisation of the Japanese electricity sector } could inform global energy policy\added{. Our simulations provide these insights } by delineating potential transition \deleted{pathways, identifying } \added{scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify } key novel technologies \deleted{, } and their most significant parameters.

%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \mbox{\cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \mbox{\cite{meti_japans_2018}}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \mbox{\cite{meti_annual_2018}}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \mbox{\cite{matsuo_quantitative_2018}}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \mbox{\cite{ashina_roadmap_2012}}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \mbox{\cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}}.

This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using the \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand. Additionally, we assess the significance of key economic parameters of emerging technologies through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2021-06-18 publications/2020-03-paper/revisions/introduction.tex
edits to comments, track changes

@@
 The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
-Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
+Energy use in buildings in particular generates 17.5\% of all emissions \cite{ritchie_emissions_2021}.
+However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system.
+The emergence of novel technologies like high-efficiency utility-scale \gls{CCS} (henceforth referred to as \gls{CCS}) and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.
+
+We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies.
+We use Japan as a proxy for a developed nation committed to addressing climate change.
+However, the results have global significance.
+Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal \cite{international_energy_agency_latest_2019, noauthor_electricity_2019}.
+However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}.
+Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}.
+Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy.
+Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.
+
+%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
 However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.
-Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.
+Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .
 
-Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
+The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans.
+Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{noauthor_basic_2017}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}.
 The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid).
@@
 For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}.
-The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.
+The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
 

### 2021-06-21 publications/2020-03-paper/revisions/review-responses.tex
Adds 'track changes' copy

@@
                  \begin{itemize}
-                 \item An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain especially considering the more ambitious carbon reduction goals recently announced by <ORGANIZATION NAME> <REFERENCE>.
+                 \item An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain especially considering the more ambitious carbon reduction goals recently announced by METI[42, 43].
                  \end{itemize}

### 2021-06-21 publications/2020-03-paper/changes/Appendix-revised.tex
Adds 'track changes' copy

--- 2021-01-15 publications/2020-03-paper/Appendix.tex
@@
 \begin{table}[H]
+\centering
 	\caption{Data for defining the initial condition across all simulations.}
 	\vspace{0.1in}
-	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
+	\begin{tabularx}{0.75\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
 		\hline
@@
 \begin{table}[H]
-	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
+\centering
+	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{carbonbrief_carbon_2018}.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
+	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
 		\hline
@@
 \begin{landscape}
+\centering
 \begin{longtable}{ |*{8}{c|} }
@@
  & \textbf{cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{efficiency} & \textbf{coefficient} & \textbf{available} \\
- & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\
+ & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$\added{-eq} /kWh)  &  \\
 \hline
@@
 \begin{table}[H]
+\centering
 	\caption{Nameplate capacity deployment limits.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
+	\begin{tabularx}{0.7\textwidth}{p{0.35\textwidth} p{0.35\textwidth} }
 		\hline
@@
 \begin{table}[H]
+\centering
 %\begin{minipage}{\textwidth} 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+	\begin{tabularx}{0.8\textwidth}{p{0.35\textwidth} p{0.45\textwidth}}
 		\hline
@@
 \begin{table}[H]
+\centering
 	\caption{Miscellaneous model parameters and assumptions.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
+	\begin{tabularx}{0.5\textwidth}{p{0.3\textwidth} p{0.2\textwidth}}
 		\hline

### 2021-06-21 publications/2020-03-paper/changes/acks.tex
Adds 'track changes' copy

--- 2021-01-19 publications/2020-03-paper/acks.tex
@@
-\section{CRediT Statement}
-
-The authors contributed to this work as described below.
-
-\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.
-
-\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.
-
-\textbf{Akari Minami}: data curation, validation.
-
-\textbf{James Stubbins}: writing - review and editing, supervision.
-
-\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
+%\section{CRediT Statement}
+%
+%The authors contributed to this work as described below.
+%
+%\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.
+%
+%\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.
+%
+%\textbf{Akari Minami}: data curation, validation.
+%
+%\textbf{James Stubbins}: writing - review and editing, supervision. 
+%
+%\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
 

### 2021-06-21 publications/2020-03-paper/changes/conclusion-revised.tex
Adds 'track changes' copy

--- 2020-12-14 publications/2020-03-paper/conclusion.tex
@@
 The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating.
-Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.
+\added{Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.} Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.
 
@@
 %grid resilience - analysis of grid stability of similar mixes at the resolution of minutes. Maybe in TIMES (ugh).
-\section{Declaration of Competing Interest}
-The authors declare no conflict of interest.
+%\section{Declaration of Competing Interest}
+%The authors declare no conflict of interest.

### 2021-06-21 publications/2020-03-paper/changes/introduction-revised.tex
Adds 'track changes' copy

--- 2021-06-18 publications/2020-03-paper/revisions/introduction.tex
@@
 The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}.
-Energy use in buildings in particular generates 17.5\% of all emissions \cite{ritchie_emissions_2021}.
-However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system.
-The emergence of novel technologies like high-efficiency utility-scale \gls{CCS} (henceforth referred to as \gls{CCS}) and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.
+\added{Energy use in buildings in particular generates 17.5\% of all emissions \mbox{
+\cite{ritchie_emissions_2021}}.} However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system.
+The emergence of novel technologies like \added{high-efficiency utility-scale }  \gls{CCS} \added{(henceforth referred to as }\gls{CCS}\added{) }  and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.
 
@@
 However, the results have global significance.
-Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal \cite{international_energy_agency_latest_2019, noauthor_electricity_2019}.
-However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}.
+Like many other developed nations, Japan has been rapidly deploying renewables \deleted{and has attempted to transition away from nuclear power since the }  \added{, and in the wake of the }  Fukushima Daiichi accident \deleted{\mbox{
+\cite{international_energy_agency_latest_2019}}.
+Yet Japan is also considering }  \added{, it shut down its nuclear reactors and increased its reliance on coal \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}.
+However, now Japan is } reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}.
 Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}.
-Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy.
-Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.
-
-%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
+Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies,  \deleted{lessons learnt from these decarbonisation simulations} \added{simulating likely transition pathways for decarbonisation of the Japanese electricity sector} could inform global energy policy \added{.
+Our simulations provide these insights} by delineating potential transition \deleted{pathways, identifying} \added{scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify} key novel technologies  \deleted{,} and their most significant parameters.
+%
+%%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants.
 However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}.

### 2021-06-21 publications/2020-03-paper/changes/litreview-revised.tex
Adds 'track changes' copy

--- 2021-01-19 publications/2020-03-paper/litreview.tex
@@
 Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}.
-Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid ageing, Kuriyama et al.
+Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid population ageing, Kuriyama et al.
 suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}.
@@
 From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}.
-Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}.
+Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}.
 The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}.
@@
 The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050.
-This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
+This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam:_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients.
 Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality.

### 2021-06-21 publications/2020-03-paper/revisions/cover-letter/cover_letter.tex
Adds 'track changes' copy

--- 2021-01-20 publications/2020-03-paper/cover-letter/cover_letter.tex
@@
 
-Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff
-are submitting for exclusive consideration for publication as a research 
-article in Applied Energy.
+Please find enclosed a revised version of our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff
+are submitting for exclusive consideration for publication as a research article in Applied Energy.
 
-Our work uses the TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies.
-This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs.
-We assess emerging technologies’ impact using a rigorous sensitivity analysis.
+Thank you for giving us the opportunity to revise and resubmit our manuscript.
+The comments provided by the reviewers were considered seriously and their feedback has improved the readability and academic rigour of our work.
 
-Our results approach true carbon-neutrality with the incorporation of lifecycle emissions.
-We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen.
-Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy.
-Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.
-
-Our work offers a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers.
-Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.
+We look forward to working with you towards moving towards publication.
 
@@
 \fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
-Eng.\\University of Illinois.\\achaube2@illinois.edu}
+Eng.\\University of Illinois at Urbana-Champaign.\\achaube2@illinois.edu}
 }

### 2021-06-23 publications/2020-03-paper/changes/Appendix-revised.tex
fixes references

@@
 \centering
-	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{carbonbrief_carbon_2018}.}
+	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{noauthor_carbon_2018}.}
 	\vspace{0.1in}
@@
 \endlastfoot
-\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
-\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
-Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+\gls{USC} \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
 Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019,oliveira_environmental_2015} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
-Solar \cite{eia_cost_2020,ipcc_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
  & 615(2050) & & & & & &  \\
 Onshore wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
 LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
- \cite{eia_cost_2020,ipcc_climate_2014} & 1422(2050) &  & &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\
 USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
- \cite{eia_cost_2020,ipcc_climate_2014} & 4091(2050) &  &  &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\

### 2021-06-23 publications/2020-03-paper/revisions/Appendix.tex
adds response to reviewer 2
fixes references

--- 2021-01-15 publications/2020-03-paper/Appendix.tex
@@
 \begin{table}[H]
-	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
+\centering
+	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{noauthor_carbon_2018}.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
+	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
 		\hline
@@
  & \textbf{cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{efficiency} & \textbf{coefficient} & \textbf{available} \\
- & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\
+ & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$-eq/kWh)  &  \\
 \hline
@@
 \endlastfoot
-\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
-\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
-Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
+\gls{USC} \cite{eia_cost_2020, intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
+\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
+Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
 Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019,oliveira_environmental_2015} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
  & 1446 (2025) &  &  &  &  & 87(2050) &  \\
-Solar \cite{eia_cost_2020,ipcc_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
+Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
  & 615(2050) & & & & & &  \\
 Onshore wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
 Offshore wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
 Offshore wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
-\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
+\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
 LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
- \cite{eia_cost_2020,ipcc_climate_2014} & 1422(2050) &  & &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\
 USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
- \cite{eia_cost_2020,ipcc_climate_2014} & 4091(2050) &  &  &  &  &  & \\
+ \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\
 Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\

### 2021-08-02 publications/2020-03-paper/revisions/review-responses.tex
addresses editor's comments

@@
 
-%\journal{Annals of Nuclear Energy}
+%\journal{Applied Energy}
 
@@
 \title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals\\
-\large Response to Review Comments}
+\large Response to Editor and Review Comments}
 \author{Anshuman Chaube, Andrew Chapman, Akari Minami, James Stubbins, Kathryn Huff}
@@
 \section*{Review General Response}
-We would like to thank the reviewers for their detailed assessment of
+We would like to thank the reviewers and editors for their detailed assessment of
 this paper. Your suggestions, clarifications, and comments have resulted in 
 changes which improved the paper.
+This version adds detailed responses to the Editor's comments.
+Changes made are reflected in both the revised copy \texttt{times-paper-revised.pdf} and the ``track-changes" copy \texttt{times-paper-changes.pdf}.
 
 \begin{questions}
+
+        \section*{Editor's Comments}
+
+        %---------------------------------------------------------------------
+
+         \question REVISION FORMAT: Please include both ``TRACK CHANGES" revision (not only marked in coloured highlighting but also with tracked changes to indicate the original and revised versions) as well as a clean version.
+
+        \begin{solution}
+                Thank you for these comments.
+This ``track changes" revision has been provided in \texttt{times-paper-changes.pdf}, in which the changes are highlighted in blue.
+Not only have the changes been highlighted, but the removed text has been denoted with a strikethrough line and the added text is in plain blue.
+This matches the requirement of indicating the changes in the original and revised versions by tracking changes beyond coloured highlighting.
+Please note that we used Latex's track changes feature as Applied Energy does not prescribe the use of any particular word processor or text editor, only that the changes be tracked and highlighted.
+Any other format is not possible as we have used Latex to prepare our paper.
+
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+         \question RELEVANCE: The relevance to energy related issues should be enhanced. Please note Applied Energy is focused on energy related topics with emphasis on application.
+
+        \begin{solution}
+                Thank you for these comments.
+The focus of the paper is entirely on applied energy-related issues, in that we use an energy analysis code to simulate a variety of realistic near- to long-term transition scenarios for a developed nation.
+Our analysis is grounded in the realities of the existing energy landscape and carbon emission goals, and takes into account a wide variety of emerging energy technologies.
+
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+     \question  PROOF READING: Proof reading by a native English speaker should be conducted to improve both language and organization quality.
+
+        \begin{solution}
+                Thank you for these comments.
+Our co-authors Chapman, Stubbins, and Huff are native speakers of English who have proof-read the paper and approved the quality of the language and organisation within the paper.
+
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+ \question ORGANIZATION: In addition to detailed discussions and analyses of the results, the whole paper shall be written as an integrated article with the new results responding to the research questions (objectives).
+Detailed descriptions such as equations, input data/datasets and assumptions, or system components can be briefly discussed in the main text and leave the detailed materials in the APPENDIX.
+
+        \begin{solution}
+                Thank you for these comments.
+Our paper closely follows this structure, with the main results integrated into a cohesive narrative, and with an appendix that has secondary details necessary to fully understand and reproduce our analysis.
+
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+\question  
+ABBREVIATIONS: Please avoid using abbreviations in the TITLE, HIGHLIGHTS, ABSTRACT, and CONCLUSION, if possible.
+
+        \begin{solution}
+                Thank you for these comments.
+We largely avoid acronyms in the sections mentioned.
+A few acronyms related to the energy analysis software used (TIMES) and key transition technologies are mentioned as keywords to attract our target audience and to convey salient features of our methodology and results in a concise way.
+Their use will improve the readability of our paper and its ease of discovery by energy analysis experts reviewing literature similar to our work.
+
+        \end{solution}
+
+    %---------------------------------------------------------------------
+
+   \question  
+REFERENCES AND CITING: Please also avoid "lump sum references", such as XXXXX [1-5], OR 1, 2, 3, 4, 5; all references should be cited with detailed and specific descriptions.
+In the references, all authors (if less than 6 authors) should be included; avoid using "et al.” For more than 6 authors, the first 6 should be listed, followed by "et al."
+        \begin{solution}
+                Thank you for these comments.
+We largely avoid lump sum references, except where multiple references are necessary to obtain a particular simulation parameter, or to demonstrate to the reader that a consensus exists around key simulation parameters or assumptions used.
+The following ``lump sum" references have been split based on your recommendation:
+                \begin{itemize}
+
+\item On page 2, line 11 - references [4,5] have been split into [4] and [5].
+
+\item On page 2, last line - references [7,10,11] have been split into [10,11] and [7].
+
+                \end{itemize}
+
+        \end{solution}
+
+    %------------------------------------
+
+   \question
+
+TITLE: The title normally consists of about 12-15 keywords, which shall not be too general or too narrow.        
+        \begin{solution}
+                Thank you for these comments.
+Our title is 17 keywords, which is in agreement with "about 12-15".
+It includes two that are part of a hyphenated term (mid- and long-term).
+We consider the title adequate and necessary to succinctly convey the objective as well as the novelty of our work.
+
+        \end{solution}
+
+    %------------------------------------
+
+ \question
+
+HIGHLIGHTS: Highlights are mandatory for this journal.
+They consist of a short collection of bullet points that convey the core NEW findings of the article, and should be submitted in a separate editable file in the online submission system.
+Please use 'Highlights' in the file name, and include 3 to 5 bullet points (maximum 85 characters, including spaces, per bullet point).
+
+ \begin{solution}
+                Thank you for these comments. We have submitted highlights in the prescribed format.
+
+        \end{solution}
+
+    %------------------------------------
+
+ \question
+
+ABSTRACT: The abstract should be about 150-250 words, with concise text in a single paragraph.
+Answer the questions: What problem did you study and why is it important?
+What methods did you use?
+What were your main results?
+And what conclusions can you draw from your results?
+Please include in your abstract more specific and quantitative results when it suits broader audiences.
+The abstract stands alone: no references, figures, tables or equations are cited.
+
+ \begin{solution}
+                Thank you for these comments. Our abstract adheres to the format described above and addresses each question mentioned above.
+
+        \end{solution}
+
+    %------------------------------------
+
+ \question
+
+CAPTIONS: Captions for figures and tables should be presented with more specific descriptions rather than general sentences like "Results of the experiments ...", "A studied system ...."
+
+ \begin{solution}
+                Thank you for these comments. Our captions are in accordance with the above guidelines.
+
+        \end{solution}
+
+    %------------------------------------       
+      \question
+
+UNITS: SI units shall be used.
+
+ \begin{solution}
+                Thank you for these comments.
+Our paper largely uses SI units.
+The sole exception to this is the values of life-cycle emissions or emission coefficients, which are in $g-CO_2/kWh$.
+This is in accordance with the conventions used in lifecycle analysis by other authors and organisations (e.g.: the IPCC) in the field, and it is also necessary to avoid long suffixes such as $\times 10^{-3}$ or $\times 10^{-6}$ that are associated with the small emission coefficient values of existing and emerging low-carbon technologies.
+
+        \end{solution}
+
+    %------------------------------------
+
+  \question
+
+DATA: All data shall be carefully presented with consistent accuracy. Uncertainty of input data/assumptions shall be addressed.
+
+ \begin{solution}
+                Thank you for these comments.
+Our paper presents all simulation parameters used in as much detail as possible within the methodology section and the appendix, in addition to providing a link to our simulation input files as a reference.
+Assumptions and uncertainty regarding the input parameters of emerging technologies has been discussed in the methodologies section.
+The references cited for each technology's data provide further details on the calculation and uncertainty of each parameter.
+The overall uncertainty associated with these transitions has been dealt with by simulating multiple transition scenarios with different likely combinations of emerging technologies, and by conducting a sensitivity analysis based on likely ranges of input parameters.
+
+        \end{solution}
+
+    %------------------------------------        
+      \question
+
+CONCLUSION: The paragraph shall be independent from the main text, without citing tables, figures or references. It should be concise, including the most important new findings.
+
+ \begin{solution}
+                Thank you for these comments.
+Our conclusion adheres to these guidelines for the most part, however the first paragraph of conclusions has been modified to remove references to specific figures.
+
+        \end{solution}
+
+    %------------------------------------        
+        \question
+
+ORIGINALITY: The originality of the paper needs to be further clarified. Sufficient results are important to justify the novelty of a high-quality journal paper.
+
+ \begin{solution}
+                Thank you for these comments.
+We have highlighted the novelty of the paper across the abstract, highlights, and the last paragraphs of both the introduction and the literature review by pointing to the wide range of emerging technologies considered, the dynamic incorporation of learning curves for economic parameters and lifecycle emissions, the use of five different transition scenarios, the assessment of their long-term impact on the energy system and emissions, and the use of sensitivity analysis to identify key technologies, parameters, and trade-offs.
+The following sentence has been added to the end of the Literature Review section to further emphasize the novelty of our paper:
+                \begin{itemize}
+
+\item "Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions."
+
+                \end{itemize}
+
+        \end{solution}
+
+    %------------------------------------        
+              \question
+
+LITERATURE REVIEW:  An updated and complete literature review should be conducted to present the state-of-the-art and knowledge gaps in the research, with strong relevance to the topic of the paper.
+ \begin{solution}
+                Thank you for these comments.
+Our literature review follows these guidelines by highlighting the previous research done in this field, the emerging consensus from literature, and how our research builds upon this body of work by extending transition scenario simulation by incorporating dynamic simulation parameters, a wide-variety of emerging technologies, and using sensitivity analysis to derive key insights that are not present in the literature reviewed.
+
+        \end{solution}
+
+    %------------------------------------   
+          \question
+
+APPLIED VALUES: The results should be further elaborated to show how they could be used for real applications. Modeling results should be validated by experiments.
+ \begin{solution}
+                Thank you for these comments.
+Our results are focused on a real energy system and the exploration of realistic transition pathways that reduce carbon emissions using existing or pre-commercialisation stage technology solutions.
+Validation is impossible as the changes to a nation's energy system cannot by simulated by experiments, long-term impacts cannot be re-created within our lifetimes, and emerging technologies cannot be accessed before maturity.
+
+        \end{solution}
+
+    %------------------------------------
+
+       \question
+
+INTERNATIONAL PERSPECTIVE: The paper shall not be discussed from the viewpoint of only one country.
+ \begin{solution}
+                Thank you for these comments.
+Our abstract and introduction highlight that the paper uses Japan as a proxy for any developed nation planning on undertaking a similar decarbonisation-focussed energy transition.
+This requirement was also pointed out by Dr.
+Yan, the editor, before the reviewers were assigned.
+The paper was modified based on his feedback and accepted, before being forwarded to reviewers.
+
+        \end{solution}
+
+    %------------------------------------
+
         \section*{Reviewer 1}

### 2021-08-02 publications/2020-03-paper/changes/conclusion-revised.tex
addresses editor's comments

@@
 We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100.
-Scenario 1 (Figure \ref{scen1}) proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure.
-The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Figure \ref{scen2}), investing heavily in hydrogen (Figs.
-\ref{scen3} and \ref{scen5}), or using a combination of both (Figure \ref{scen4}).
+\deleted{Scenario 1 (Figure \ref{scen1})} \added{Our transition scenarios} prove\deleted{d} that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure.
+\deleted{The remaining scenarios} \added{These results also} demonstrate that emission goals can be met by either investing heavily in nuclear \deleted{(Figure \ref{scen2})}, investing heavily in hydrogen \deleted{(Figs.
+\ref{scen3} and \ref{scen5})}, or using a combination of both \deleted{(Figure \ref{scen4})}.
 Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050.

### 2021-08-02 publications/2020-03-paper/revisions/conclusion.tex
minor changes to reviewer comments
addresses editor's comments

--- 2020-12-14 publications/2020-03-paper/conclusion.tex
@@
 We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100.
-Scenario 1 (Figure \ref{scen1}) proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure.
-The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Figure \ref{scen2}), investing heavily in hydrogen (Figs.
-\ref{scen3} and \ref{scen5}), or using a combination of both (Figure \ref{scen4}).
+Our transition scenarios prove that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure.
+These results also demonstrate that emission goals can be met by either investing heavily in nuclear, investing heavily in hydrogen, or using a combination of both.
 Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050.
@@
 The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating.
+Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.
 Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

### 2021-08-02 publications/2020-03-paper/revisions/cover-letter-2/cover_letter.tex
addresses editor's comments

--- 2021-06-21 publications/2020-03-paper/revisions/cover-letter/cover_letter.tex
@@
 
-Thank you for giving us the opportunity to revise and resubmit our manuscript.
-The comments provided by the reviewers were considered seriously and their feedback has improved the readability and academic rigour of our work.
-
-We look forward to working with you towards moving towards publication.
+Thank you for giving us the opportunity to address editors' comments.
+We are pleased that the reviewers have approved the revision of our manuscript.
+We look forward to working with you on moving towards publication.
 

### 2021-08-02 publications/2020-03-paper/revisions/introduction.tex
addresses editor's comments

@@
 However, the results have global significance.
-Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal \cite{international_energy_agency_latest_2019, noauthor_electricity_2019}.
+Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors \cite{international_energy_agency_latest_2019} and increased its reliance on coal  \cite{noauthor_electricity_2019}.
 However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}.
@@
 For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}.
-The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
+The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis \cite{ashina_roadmap_2012, matsuo_quantitative_2018} as well as hydrogen imports from abroad \cite{noauthor_basic_2017}.
 

### 2021-08-02 publications/2020-03-paper/revisions/litreview.tex
adds response to reviewer 2
addresses editor's comments

--- 2021-01-19 publications/2020-03-paper/litreview.tex
@@
 By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
+Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions.

### 2021-08-02 publications/2020-03-paper/revisions/changes/discussion-revised.tex
reorganises changes dir

--- 2021-01-15 publications/2020-03-paper/discussion.tex
@@
 Deploying nuclear in tandem with hydrogen provides a cost-effective compromise.
-An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain.
+An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain \added{especially considering the more ambitious carbon reduction goals recently announced by METI \mbox{\cite{noauthor_japans_2021,yamaguchi_japan_2021}}} .
 At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a ``bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment.

### 2021-08-02 publications/2020-03-paper/revisions/changes/introduction-revised.tex
reorganises changes dir

--- 2021-06-21 publications/2020-03-paper/changes/introduction-revised.tex
@@
 \cite{international_energy_agency_latest_2019}}.
-Yet Japan is also considering }  \added{, it shut down its nuclear reactors and increased its reliance on coal \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}.
-However, now Japan is } reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}.
+Yet Japan is also considering}  \added{, it shut down its nuclear reactors \mbox{\cite{international_energy_agency_latest_2019}} and increased its reliance on coal \mbox{\cite{noauthor_electricity_2019} }} \deleted{ \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}}.
+\added{However, now Japan is} reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}.
 Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}.
@@
 For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}.
-The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
+The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis \added{\mbox{\cite{ashina_roadmap_2012,matsuo_quantitative_2018}}} as well as hydrogen imports from abroad \added{\mbox{\cite{noauthor_basic_2017}}} \deleted{\mbox{\cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}}}.
 

### 2021-08-02 publications/2020-03-paper/revisions/changes/litreview-revised.tex
reorganises changes dir

--- 2021-06-21 publications/2020-03-paper/changes/litreview-revised.tex
@@
 By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
+\added{Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions.}

### 2021-08-02 publications/2020-03-paper/revisions/changes/methods-revised.tex
reorganises changes dir

--- 2021-06-14 publications/2020-03-paper/revisions/methods.tex
@@
 \subsection{TIMES Model Description}
-\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}.
+\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints
+\cite{loulou_etsap-tiam:_2008} .
 The generation, refinement, supply, storage, and trade of energy commodities are modelled across multiple sectors and multiple regions using a wide variety of in-built commodity and process types.
@@
 \centering
-	\caption{Electricity demand increase over the simulation time frame.}
+	\caption{Electricity demand increase over the simulation time frame. \added{The demand for 2017-2030 is obtained from \mbox{
+\cite{noauthor_electricity_2019}}
+, the rest of the curve is based on estimated population growth trends.} }
 	\vspace{0.1in}
@@
 \hline
-2017-2030 & 1.7 \% \cite{noauthor_electricity_2019} \\
+2017-2030 & 1.7 \% \deleted{\mbox{
+\cite{noauthor_electricity_2019} }
+} \\
 2031-2050 & 1.0 \% \\
@@
 Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes.
-The model captures the initial condition of the post-Fukushima Japanese electricity supply system using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
+The model captures the initial condition of the post-Fukushima Japanese electricity supply system using \added{historical data} The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}.
 Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100.
+Using \gls{TIMES} day-night and seasonal time periods
+\cite{loulou_etsap-tiam:_2008}, the daily and seasonal variability of renewables is incorporated.
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan\mbox{\cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}}.
+
 We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology.
-Using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}, the daily and seasonal variability of renewables is incorporated.
-The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.
+Using day-night and seasonal time periods\cite{loulou_etsap-tiam:_2008}, the daily and seasonal variability of renewables is incorporated.
+The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \mbox{\cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}}.
+\added{The emission coefficient data and their sources are listed in Table \ref{eco}.
+The emission coefficients vary dynamically for technologies that have projections available in literature, and are linearly interpolated between available data points until the last available projection, beyond which they are held constant.
+For hydrogen fuel cells and electrolysers, emission coefficients vary in magnitude across different technologies but the learning curves follow similar trajectories due to the similarity of technologies \mbox{\cite{iea_technology_2015} } \mbox{\cite{pinaud_technical_2013}}.
+The lifecycle emissions for \gls{PWS} are unknown, hence we have assumed them to be the same as that of \glspl{SOEC} as both are lab-scale technologies with similar deployment time-frames, and \gls{PWS} must have similar or lower life-cycle emissions as \gls{SOEC} to be competitive}.
 
@@
 Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}.
-For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
+For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered \added{(see Table \ref{eco})} , as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis.
 Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

### 2021-08-02 publications/2020-03-paper/revisions/changes/results-revised.tex
reorganises changes dir

--- 2021-01-19 publications/2020-03-paper/results.tex
@@
 The transition simulations' results are shown in Figures \ref{scen1}-\ref{scen5}, and summarised in Table \ref{tab:results_summary} (see Table \ref{scen-table} for scenario definitions).
-The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology.
+\added{Note that the years 2013-2016 represent the initial condition modelled using historical data \mbox{
+\cite{the_institute_of_energy_economics_japan_energy_2018}}
+, and the simulation results begin from 2017 onwards.
+} The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology.
 The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user.
@@
 The third plot details the sources of direct and averaged life-cycle emissions from each source.
+
+\begin{table}[H]
+\centering
+	\caption{Summary of decarbonisation simulations' results.}
+	\vspace{0.1in}
+	\begin{tabularx}{0.9\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
+		\hline
+\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
+ & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD) \\
+ &  & \textbf{emission} & \textbf{emission} & \textbf{2050-} &  \\
+ &  & \textbf{goals} & \textbf{goals} & \textbf{2100} &  \\
+\hline
+1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
+2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
+3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
+4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
+5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
+\hline 
+	\end{tabularx}
+\label{tab:results_summary}
+\end{table}
 
@@
 The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%).
-The total cost of this transition is \textbf{3.51 trillion USD}.
+The total cost of this transition is \deleted{\textbf{3.51 trillion USD}}
+ \added{3.51 trillion USD}.
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
@@
 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%).
-The total transition cost of this scenario is the lowest, at \textbf{2.66 trillion USD.}
+The total transition cost of this scenario is the lowest, at \deleted{\textbf{2.66 trillion USD.}} \added{2.66 trillion USD.}
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
@@
 Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness.
-The cost of this transition is \textbf{3.19 trillion USD}.
+The cost of this transition is \deleted{{3.19 trillion USD}} \added{3.19 trillion USD}.
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
@@
 From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3.
-The cost of this transition is \textbf{2.80 trillion USD}.
+The cost of this transition is \deleted{\textbf{2.80 trillion USD}} \added{2.80 trillion USD} .
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
@@
 \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%.
-The cost of this transition is \textbf{3.18 trillion USD}.
+The cost of this transition is \deleted{\textbf{3.18 trillion USD}} \added{3.18 trillion USD}.
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
@@
 \end{figure}
-
-\begin{table}[!ht]
-	\caption{Summary of decarbonisation simulations' results.}
-	\vspace{0.1in}
-	\begin{tabularx}{0.9\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
-		\hline
-\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
- & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD) \\
- &  & \textbf{emission} & \textbf{emission} & \textbf{2050-} &  \\
- &  & \textbf{goals} & \textbf{goals} & \textbf{2100} &  \\
-\hline
-1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
-2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
-3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
-4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
-5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
-\hline 
-	\end{tabularx}
-\label{tab:results_summary}
-\end{table}
 
@@
 
-\begin{figure}[b!] 
+\begin{figure}[H] 
 \centering
